\chapter{Appetizers}

\begin{minipage}{\linewidth}\rtitle{BRIE AND CHERRY PASTRY CUPS} \index{BRIE AND CHERRY PASTRY CUPS}
\step{1 sheet frozen puff pastry	\\ 
\nicefrac{1}{3} to \nicefrac{1}{2} cup red cherry preserves \\ 
2 Tbsp chopped fresh chives	\\ 
\nicefrac{1}{4} cup chopped pecans \\ 
4 oz Brie cheese, cut into $\nicefrac{1}{2} \times \nicefrac{1}{2}$" pcs
}{Heat oven to 375$^\circ$F. Spray 36 miniature muffin cups with cooking spray. Cut pastry into 36 squares. Slightly press each square into muffin cup. Press center with finger. Bake 10 minutes. Press center of each with handle of wooden spoon. Bake 6--8 minutes longer or until golden brown. Immediately press again in center. Fill each with about \nicefrac{1}{2} tsp preserves. Top with cheese piece, pecans and chives. Bake 3--5 minutes or until cheese is melted. Serve warm.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{POTATO SKINS (GF)} \index{POTATO SKINS (GF)} \index{Gluten Free!appetizers}
\step{12 new potatoes	\\
2 Tbsp butter, melted \\
1 tsp Dijon mustard	\\
coarse salt \\
\nicefrac{3}{4} cup cheese, grated	\\
8 slices bacon, cooked crisp and crumbled \\
Garnish:  sour cream, sliced onion greens}
{Cut potatoes crosswise into thirds. Use the 2 ends for potato skins and save the middle slices in water for future use. Preheat oven to 425$^\circ$F. Whisk together butter and mustard. Halve each potato piece and hollow out, leave \nicefrac{1}{4} inch shells. Immediately toss the halves in the mustard mixture. Roast, cut side down, on a lightly oiled baking sheet, until nicely browned, 20--30 minutes. Sprinkle with coarse salt. Turn the potatoes upright and cover with grated cheese. Sprinkle with bacon. At this point, potatoes can be held at room temp for up to 2 hours before serving. Return potatoes to oven and bake until hot, about 5 minutes. Garnish with sour cream and onion greens.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GORGONZOLA AND HAZELNUT STUFFED MUSHROOMS} \index{GORGONZOLA AND HAZELNUT STUFFED MUSHROOMS}
%\step{1 lb fresh whole mushrooms	\\
			%\nicefrac{1}{3} cup gorgonzola cheese, crumbled \\
			%\nicefrac{1}{4} cup fine bread crumbs	\\
			%\nicefrac{1}{4} cup hazelnuts, chopped \\
			%\nicefrac{1}{4} cup red bell pepper, finely chopped	\\
			%4 med green onions, chopped\\
			%\nicefrac{1}{2} tsp salt}
%{Heat oven to 350$^\circ$F. Remove stems from mushroom caps. Reserve caps. Finely chop enough stems to measure \nicefrac{1}{2} cup. Discard remaining stems. Mix chopped mushroom stems and remaining ingredients in small bowl until well blended. Spoon into mushroom caps, mounding slightly. Place in ungreased pan. Bake 15--20 minutes or until thoroughly heated. Serve warm.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GINGER CHICKEN AND BACON BITES (GF)} \index{GINGER CHICKEN AND BACON BITES (GF)} \index{Gluten Free!appetizers}
\step{8 oz can whole water chestnuts	\\
\nicefrac{1}{4} cup orange marmalade \\
2 Tbsp soy sauce	\\
\nicefrac{1}{2} tsp ground ginger \\
\nicefrac{1}{8} tsp garlic powder	\\
12 slices bacon \\
12 oz skinless, boneless chicken breasts}
{Cut chicken into 24 bite size pieces. For marinade, combine orange marmalade, soy sauce, ginger and garlic powder in med mixing bowl. Add chicken pieces, tossing to coat. Cover and chill for 30 minutes, stirring occasionally. Meanwhile, arrange bacon slices on unheated rack of broiler pan. Broil 4--5 inches from heat for 1--2 minutes or until partially cooked but not crisp. Drain off fat. Cool bacon and halve slices crosswise. Cut water chestnuts in half crosswise. Drain chicken pieces, discarding marinade. Wrap a piece of bacon around chicken piece and water chestnut half. Secure with wooden toothpick. Place on unheated rack of broiler pan. Broil 4--5" from heat for 3--5 minutes or until check is tender and no longer pink, turning once. Makes 24.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHRISTMAS TREE APPETIZERS} \index{CHRISTMAS TREE APPETIZERS}
%\step{1 pkg cream cheese, softened	\\
	%\nicefrac{1}{2} cup roasted red bell peppers, chopped 	\\
	%\nicefrac{1}{4} cup ripe olives, chopped 	\\
	%\nicefrac{1}{4} cup fresh basil leaves, chopped	\\
	%\nicefrac{1}{4} cup parmesan cheese, shredded		\\
	%4 spinach flavour flour tortillas (8-10-inch)	\\
	%Ripe olive pieces}
%{Mix all ingredients except tortillas and olive pieces. Divide mixture among tortillas, spreading to edges. Roll up tightly. Press each tortilla roll into triangle shape, using fingers. Wrap in plastic wrap. Refrigerate at least 2 hours but no longer than 24 hours.
%To serve, cut rolls into \nicefrac{1}{2}-inch slices. Place olive piece at bottom of each triangle to look like tree trunk. Secure with toothpick.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEEF AND SPINACH ROLL-UPS} \index{BEEF AND SPINACH ROLL-UPS}
%\step{\nicefrac{1}{4} cup mayonnaise	\\
	%\nicefrac{1}{2} tsp garlic powder \\
	%2 spinach flavoured tortillas	\\
	%1 cup fresh spinach \\
	%\nicefrac{1}{4} lb thinly sliced cooked roast beef	\\
	%\nicefrac{3}{4} cup shredded cheddar cheese \\
	%1 med tomato, chopped}
%{Mix mayonnaise and garlic powder in small bowl. Spread mixture evenly over tortillas. Top tortillas with layers of spinach, beef, cheese and tomato. Roll up tightly. Trim ends from rolls. Cut each roll into 12 slices. Secure with toothpicks. Serve immediately or refrigerate until serving.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MUSHROOM TRIANGLES} \index{MUSHROOM TRIANGLES}
%\step{1 \nicefrac{1}{2} cups sliced fresh mushrooms	\\
%\nicefrac{1}{4} cup chopped onion\\
%1 Tbsp butter	\\
%125 g cream cheese, cut up	\\
%\nicefrac{1}{4} tsp Worcestershire sauce\\
%\nicefrac{1}{4} tsp salt	pepper sprinkle\\
%Garlic powder sprinkle
%}{Saut\'e until onion is soft and clear. Add remaining ingredients. Stir to melt cheese. Spread on buttered, crustless bread. Fold to make triangles. Press edges. Brush with melted butter. Toast triangles at 400$^\circ$F for about 10--15 minutes.}


%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{POACHED SALMON APPETIZER (LC*,GF*)} \index{POACHED SALMON APPETIZER (LC*,GF*)} \index{Gluten Free!appetizers} \index{Low Carb!appetizers}
%\step{
%1 lb salmon fillet\\
%4 cups water	\\
%3 or 4 slices lemon, cut in half\\
%3 or 4 slices onion, cut in half\\
%\nicefrac{1}{4} cup small springs parsley\\
%\nicefrac{1}{2} tsp salt \\
%\nicefrac{1}{4} tsp coarsely ground pepper}
%{In 10 or 12" skillet, heat water, lemon and onion slices, parsley, salt and pepper, to boiling. Boil 3 minutes. Reduce heat to med-low. Add salmon, skin side down. Cover and cook 5--6 minutes or until salmon flakes easily with fork. Remove salmon from liquid in skillet. Cool completely. Cover and refrigerate at least 2 hours but no longer than 24 hours. Discard liquid in skillet.}
%
%\step{Sauce:\\
%2 Tbsp lemon juice	\\
%1 Tbsp honey\\
%1 Tbsp Dijon mustard	\\
%1 Tbsp olive or vegetable oil\\
%\nicefrac{1}{4} cup chopped fresh parsley	\\
%2 Tbsp finely chopped red onion\\
%2 tsp capers	\\
%1 tsp grated lemon peel\\
%\nicefrac{1}{4} tsp salt	\\
%cocktail bread slices or crackers, if desired}
%{In small bowl, mix lemon juice, honey, mustard and oil until well blended. In another small bowl, mix chopped parsley, red onion, capers and lemon peel. To serve, carefully remove skin from salmon. Place salmon on serving plate. Sprinkle with \nicefrac{1}{4} tsp salt. Drizzle honey-mustard sauce over salmon; sprinkle with parsley mixture. Serve with bread slices.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{COCKTAIL MEATBALLS} \index{COCKTAIL MEATBALLS}
\step{1 lbs lean ground beef
\\ 1 egg
\\ 2 Tbsp water
\\ \nicefrac{1}{2} cup bread crumbs
\\ 3 Tbsp minced onion
\\ 1 8-oz can jellied cranberry sauce
\\ \nicefrac{3}{4} cup sweet Thai chili sauce
\\ 1 Tbsp brown sugar
\\ 1 \nicefrac{1}{2} tsp lemon juice}{Preheat oven to 350${}^\circ$F. In large bowl, mix beef, egg, water, bread crumbs and onion. Roll into small meatballs. Bake in oven for 20--25 minutes, turning once. In a slow cooker or large saucepan over low heat, blend cranberry sauce, chili sauce, brown sugar and lemon juice. Add meatballs and simmer for 1 hour before serving.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DEVILS ON HORSEBACK} \index{DEVILS ON HORSEBACK}
\name{The first time I tried these was at the British High Commission in Nairobi.  Daddy and I were part of a 5 voice ensemble that performed a debut work together with a white Kenyan actor and playwright. I don't remember her name but if I remember right the debut work was in celebration of her decades of contributions to the theatre scene in Nairobi. The performance was a farcical look at British history through music and acting. It was all very ``colonial.'' I have a vivid image of the Egyptian ambassador sitting in front of me, sleeping through most of it. The evening must have been a fund-raiser for something medical because our family doctor, Dr. Safwat, was there to give a speech. These traditional British appetizers were served at the reception.} \\
\step{30 pitted prunes \\
10 strips smoked bacon, cut in thirds \\
30 toothpicks}{
Place prune on one end of bacon strip. Roll and secure with toothpick. Place on baking sheet. Bake at 375${}^{\circ}$F until bacon is cooked and crispy, approximately 15--20 min. Flip the appetizers half way through. Serve hot.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BACON WRAPPED SMOKIES} \index{BACON WRAPPED SMOKIES} 
\name{(Kelly Penner)}\\
\step{1 lb bacon, sliced in thirds \\
14 oz pkg beef cocktail weiners \\
\nicefrac{3}{4} cup brown sugar (or more if needed)}{
Sprinkle sugar on bacon strips. Wrap cocktail wiener in strip of bacon. Place wrapped wieners on foil-lined baking sheet. Sprinkle with sugar. Bake at 325${}^{\circ}$F for 25 min. Raise temperature to 350${}^{\circ}$F for last 15 min of baking. }


%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WINGS PARMESAN} \index{WINGS PARMESAN}
%\name{(Company's Coming)} \\
	%\step{\nicefrac{3}{4} cup Grated parmesan cheese	 \\
	 %\nicefrac{1}{4} cup fine dry bread crumbs \\
	 %1 tsp paprika \\	
	 %1 tsp salt \\
	 %\nicefrac{1}{4} tsp pepper	 \\
	 %\nicefrac{1}{4} tsp oregano \\
	 %\nicefrac{1}{4} tsp thyme	 \\
	 %\nicefrac{1}{2} cup melted butter \\
	 %900 g chicken wings}{Mix first 7 ingredients together. Cut off chicken wing tips and discard. Dip wings into melted butter then coat with dry mixture. Arrange on greased, foil lined baking sheet. Bake in 350$^\circ$F oven for 30--45 minutes until tender.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BARBECUE SAUCED WINGS (GF)} \index{BARBECUE SAUCED WINGS (GF)} \index{Gluten Free!appetizers} 
\step{1 kg chicken wings	\\
\nicefrac{1}{4} cup ketchup\\
\nicefrac{1}{4} cup water	\\
\nicefrac{1}{4} cup brown sugar, packed	\\
\nicefrac{1}{4} cup vinegar	\\
2 Tbsp Worcestershire sauce	\\
2 Tbsp cooking oil	\\
1 tsp prepared mustard\\	
1 tsp paprika	\\
1 tsp salt	\\
\nicefrac{1}{4} tsp pepper	\\
1 Tbsp dry onion flakes
}
{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TERIYAKI CHICKEN WINGS (LC*,GF*)} \index{TERIYAKI CHICKEN WINGS (LC*,GF*)} \index{Gluten Free!appetizers}
\step{1.35 kg chicken wings\\
\nicefrac{1}{2} cup soy sauce	\\
\nicefrac{1}{2} cup sake (or apple juice)\\
3 Tbsp sugar	\\
1 garlic clove minced\\
\nicefrac{1}{4} tsp ginger	\\
\nicefrac{1}{2} tsp paprika \\
\nicefrac{1}{2} tsp chili powder}
{Remove chicken wing tips and discard. Arrange in greased pan large enough to hold in single layer. Mix remaining 7 ingredients together. Spoon over chicken. Bake uncovered in 350$^\circ$F oven for 30--45 minutes until tender.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BOURBON CIDER BONELESS WINGS} \index{BOURBON CIDER BONELESS WINGS}
\step{SAUCE: \\
12 oz apple cider or apple juice concentrate, thawed \\
1 cup bourbon \\
\nicefrac{1}{2} cup soy sauce \\
\nicefrac{1}{4} cup apple cider vinegar \\
\nicefrac{1}{4} cup brown sugar \\
5 cloves garlic, grated finely \\
1 Tbsp maple syrup \\
1 tsp salt \\
\nicefrac{1}{4} tsp red pepper flakes \\
\nicefrac{1}{4} tsp cayenne pepper}{Add all ingredients to saucepan and bring to a boil over high heat. Reduce to low and simmer for 35 minutes, until sauce has reduced and chickened. Set aside to cool.}

\step{2 lbs chicken breasts, diced into \nicefrac{1}{2}--1" pieces \\
2 cups buttermilk \\
Salt and pepper \\
1 tsp dried thyme \\
2 cups flour \\
\nicefrac{1}{3} cup panko breadcrumbs \\
\nicefrac{2}{3} Tbsp buttermilk \\
Oil for frying}{Sprinkle diced chicken with salt, pepper and thyme. Cover with buttermilk and stir until chicken is well-coated. Cover and refrigerate for 30 minutes. Heat oil in large pot. Add flour, panko, salt and pepper to a large ziplock bag. Shake to combine. Add in 2--3 Tbsp buttermilk and stir until breading mixture is clumpy. Use slotted spoon to transfer chicken into plastic bag. Seal bag and toss to coat chicken. Add chicken, about 8 pieces at a time, to hot oil and fry 4--5 minutes, flipping halfway through. Cool chicken on wire cooling rack. Toss fried chicken with sauce.  Optional: Place glazed chicken on a parchment paper lined baking sheet and broil 2--3 minutes until extra sticky.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{QUESADILLAS} \index{QUESADILLAS}
	\step
	{125 g cream cheese, softened	 \\
	 \nicefrac{1}{3} cup salsa, medium \\
	 \nicefrac{1}{3} cup chopped green pepper \\	
	 1 large tomato, seeded and diced \\
	 3 green onions, chopped	 \\
	 6 flour tortillas \\
	 114 ml canned chopped green chillies, drained \\
	 375 ml (1 \nicefrac{1}{2} cups) grated Monterey Jack cheese \\
 Guacamole, salsa and sour cream for dipping}{Mash cream cheese and salsa together with fork. Set aside. Toss next 4 ingredients in bowl. Spread \nicefrac{1}{2} of each tortilla with cream cheese mixture to \nicefrac{1}{2} inches from edge. Sprinkle green pepper mixture over cream cheese mixture. Sprinkle each with grated cheese. Fold uncovered half over filling. Press edges lightly with your hand. Arrange on ungreased baking sheet. Bake in 425$^\circ$F oven for 10--15 minutes or toast under broiler. Cut into 4 wedges each. Serve with dipping sauces.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{JAMAICAN ROTI} \index{JAMAICAN ROTI}
\name{(Yvonne Hiebert)} \\
  \step{PASTRY: \\
	 2 cup flour	\\
	 1\nicefrac{1}{2} tsp baking powder	\\
	 1 tsp curry		\\
	 \nicefrac{1}{2} tsp salt	\\
	 \nicefrac{2}{3} cup shortening		\\
	 \nicefrac{1}{4} cup butter	\\
	 \nicefrac{1}{3}--\nicefrac{1}{2} cup water	
	\stepspace  MEAT FILLING: \\
	 1 small onion \\
	 3 green onions \\
	 2 cloves garlic \\
	 2 tsp oil. \\
   1 lb ground beef, browned	 \\
	 pinch cayenne pepper \\
	 1 tsp thyme	 \\
	 \nicefrac{1}{2} tsp salt and pepper \\
	 \nicefrac{2}{3} cup water \\
	 1 cup fresh bread crumbs}{Mix pastry ingredients as for pie dough. Roll out and cut rounds with a cup. Fill with meat filling and fold over. Brush edges with water to help stick together. Press edges together with a fork and pierce top twice. Bake 20 minutes at 375$^\circ$F. For meat filling, saute onions and garlic in toil. Add beef and brown. Add spices and water and bring to boil. Add bread crumbs. Let cool.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MEAT PRIZHKY} \index{MEAT PYROHY} \index{MEAT PRIZHKY}
\name{(Loraine Hiebert)} \\
\step{1 pkg. yeast	
	\\ 1 tsp sugar
	\\ \nicefrac{1}{2} cup water
	\\ 1 cup milk, scalded
	\\ 1 tsp sugar	
	\\ \nicefrac{1}{2} cup warm water
	\\ \nicefrac{1}{3} cup oil	
	\\ 2 eggs, beaten
	\\ 1 TBSP salt	
	\\ 2 \nicefrac{1}{2} cups flour
	\\ 2 \nicefrac{1}{2} cups flour}{
Dissolve yeast and sugar in water. Let stand 10 minutes and add yeast to rest of ingredients, except final flour.
Beat thoroughly and gradually add final 2 \nicefrac{1}{2} cups more of flour. Knead well. Cover. Let stand in warm place to rise until double in bulk. (1 hour or so). Roll out. Place filling on dough. I use cookie cutter to make my pyrohy. Let rise. Bake at 350$^\circ$F for 25 minutes. Makes 4-5 doz. Serve with sour cream.}

\step{FILLING:
	\\ 1 med. onion, chopping fine	
	\\ 4 Tbsp butter
	\\ 1 lb. ground beef or half pork/half beef
	\\ 1 tsp salt 
	\\ pepper	
	\\ 1 Tbsp flour
	\\ \nicefrac{1}{2} cup soup stock of water	
	\\ 1 tsp chopped parsley
	\\ 2 hard cooked eggs, chopped}{
Cook onions in half the butter until tender. Add remaining butter (Mom doesn't) and meat. Brown meat lightly. Season with salt and pepper. Cover and cook over low heat until done. Remove meat. Stir flour into drippings. Add soup stock then cook, stirring until sauce comes to boil. Combine with meat. Cool. Mix in parsley and chopped eggs.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{OLIVE CHEESE BALLS} \index{OLIVE CHEESE BALLS}
\name{(Jeanie Little)} \\
\step
{2 cup sharp cheddar cheese, grated \\
 1 cup flour \\
 \nicefrac{1}{2} cup butter \\
 1--2 tsp chili powder \\
 48 stuffed olives}{Drain and dry olives. Blend cheese with butter. Add dry ingredients. Mix well. Wrap about 1 tsp of this mixture around olive, covering completely. This is the tricky bit and can take a bit of patience! Flatten the dough in the palm of your hand and then wrap it. Bake at 400$^\circ$F for 15 minutes on a cookie sheet.}


%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{JALAPENO BACON DEVILED EGGS (GF)} \index{JALAPENO BACON DEVILED EGGS (GF)} \index{Gluten Free!appetizers}
	%\step
	%{12 large eggs, hard-boiled and peeled\\
	 %paprika\\
	 %1.5 tsp rice vinegar	\\
	 %\nicefrac{3}{4} tsp ground mustard \\
	 %2 jalapenos, seeded and chopped	\\
	 %6 pieces bacon, cooked, crumbled
		%}{}
		
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRAB PURSES} \index{CRAB PURSES}
\name{A little fussy but very elegant looking. Can be steamed up to an hour ahead then resteamed to heat them just before serving.} \\
	\step
	{24 green onion tops, cut into 3-inch julienne pieces	 \\
	 6 oz lump crabmeat	 \\
	 1  4-oz block cream cheese \\	
	 \nicefrac{1}{4} cup minced green onions	 \\
	 2 tsp fresh lemon juice \\
	 \nicefrac{1}{2} tsp hot sauce	 \\
	 \nicefrac{1}{4} tsp salt \\
	 \nicefrac{1}{8} tsp pepper	 \\
	 24 won ton wrappers \\
	 1 egg white, lightly beaten	 \\
	 2 Tbsp soy sauce \\
	 1 Tbsp water	 \\
	 1 Tbsp fresh lemon juice	
		}{
Drop green onion strips in boiling water and cook 10 seconds or until limp. Drain and set aside. Combine crabmeat and next 6 ingredients in a medium bowl and stir well. Working with 1 won ton wrapper at a time, cover remaining wrappers with a damp towel, spoon 2 tsp mixture into center of wrapper. Moisten edges of wrapper with egg white. Gather 4 corners of wrapper and crimp to seal, forming a purse. Tie 1 green onion strip around crimped top of purse (like a child's drawstring purse). Repeat with remaining won tons wrappers. Arrange half of won ton purses in a single layer in a vegetable steamer coated with cooking spray. Steam purses, covered, 8 minutes or until tender. Carefully remove purses from steamer; set aside and keep warm. Repeat with remaining purses. Combine soy sauce, water and 1 Tbsp lemon juice in a small bowl. Stir well. Serve with purses.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRAB SALAD (GF)} \index{CRAB SALAD (GF)} \index{Gluten Free!appetizers}
\name{Ideal as salad or as filling for Pita sandwiches.}\\
\step{8--10 oz. sea legs (fake crab)
\\	\nicefrac{1}{2} cup mayonnaise	
\\	\nicefrac{1}{4} cup sour cream
\\	\nicefrac{1}{4} cup chopped green onion	
\\	\nicefrac{1}{4} cup chopped cucumber or celery
\\	1 hard cooked egg, chopped	
\\	1 Tbsp lemon juice
\\	2 tsp chopped fresh or dried dill weed	
\\	\nicefrac{1}{8} tsp pepper}{Pull sea legs apart into small pieces. Remove seeds from cucumbers. Assemble.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MANGOS WITH SPICY PRAWNS (GF)} \index{MANGOS WITH SPICY PRAWNS (GF)} \index{Gluten Free!appetizers}
\step{3 cups uncooked prawns \\
2 whole mangoes\\
juice of 1 lemon\\
2 Tbsp ketchup	\\
3 cups whipped cream\\
\nicefrac{1}{2} cup chopped apple	\\
1 Tbsp horseradish\\
parsley and lemon for garnish\\
}
{Cut the mangoes into halves and remove stone. Drop prawns into boiling salted water with juice of one lemon and boil for five minutes. Remove the prawns, cool and peel. Mix the prawns with the cocktail sauce (ketchup, whipped cream, apple, and horseradish) and place them in the center of each mango half. Garnish with parsley and lemon wedges. Serves 4.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HERBED BRUSCHETTA} \index{HERBED BRUSCHETTA}
Yield: 32 slices \\
	\step
	{8 fresh ripe plum tomatoes, very finely diced \\
	 2 Tbsp finely minced garlic	\\
	 \nicefrac{1}{2} cup coarsely chopped fresh basil\\
	 Pinch crushed red pepper flakes	\\
	 salt and pepper\\
	 32 \nicefrac{1}{4}-inch thick slices French baguette	\\
	 6 garlic cloves, cut in half
		}{
Combine tomato, minced garlic, basil, parsley, lemon juice, red pepper, salt and pepper. Toss and set aside for at least 3 hours. Just before serving, toast the bread and rub on one side with cut sides of garlic cloves. Place a small bowl in center of serving platter. Fill bowl with tomato mixture and arrange toast around the bowl. }

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SURPRISE SPREAD (LC,GF)} \index{SURPRISE SPREAD (LC,GF)} \index{Gluten Free!appetizers}
	\step
	{8 oz. cream cheese	\\
	 \nicefrac{1}{2} cup sour cream\\
	 \nicefrac{1}{4} cup mayonnaise	\\
	 1 or 2 cans small or broken shrimp\\
	 1 cup seafood cocktail sauce (or \nicefrac{1}{2} cup ketchup \& \nicefrac{1}{2} cup horseradish) \\
	 2 cups shredded mozzarella cheese	\\
	 1 green pepper\\
	 3 green onions	\\
	 1 tomato, diced}{Mix first 3 ingredients. Spread in pizza pan and layer next 6 ingredients in order given. Cover and chill. Serve with crackers.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRAB CHEESE DIP (GF)} \index{CRAB CHEESE DIP (GF)} \index{Gluten Free!appetizers}
	\step
	{\nicefrac{1}{2} cup mayonnaise	\\
	 1 8-oz pkg cream cheese\\
	 2 Tbsp milk	\\
	 4 scallions, sliced\\
	 1 Tbsp lemon juice	\\
	 1 tsp red pepper sauce\\
	 1 tsp Worcestershire sauce	\\
	 \nicefrac{1}{2} tsp garlic salt\\
	 \nicefrac{1}{2} cup grated parmesan cheese	\\
	 1 lb lump crab meat\\
	 \nicefrac{1}{4} cup parsley, chopped\\
		}{
Spray 6 cup shallow baking dish (quiche dish). Combine first 8 ingredients plus \nicefrac{1}{4} cup parmesan cheese. Gently stir in crab meat. Sprinkle remaining \nicefrac{1}{4} cup cheese over top. Bake 30 minutes at 350${}^\circ$F. Sprinkle with parsley. Serve warm with tortilla chips.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED SPINACH DIP} \index{BAKED SPINACH DIP}
\name{(Priscilla Koehler)}\\
\step{8 oz cream cheese, softened
\\ \nicefrac{1}{2} cup mayonnaise
\\ 2 cloves garlic, minced or pressed
\\ \nicefrac{1}{2} cup freshly grated parmigiano reggiano (parmesan cheese)
\\ \nicefrac{1}{2} cup shredded asiago cheese
\\ 1 tsp onion powder
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{4} tsp black pepper
\\ 1 10-oz. pack of chopped frozen spinach (thawed and drained)}{Preheat oven to 350${}^\circ$F. Combine all ingredients, except the spinach, and mix until well blended. Add spinach. Pour mixture into a small casserole dish. Sprinkle some shredded asiago cheese on top. Bake for 30 minutes.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SPINACH DIP IN PUMPERNICKEL BREAD} \index{SPINACH DIP IN PUMPERNICKEL BREAD}
	%\step
	%{1 pkg. frozen chopped spinach (thaw and drain well, wring out moisture)\\
	 %1 pkg. vegetable soup mix\\	
	 %1 onion green, chopped\\
	 %1 cup sour cream	\\
	 %1 cup mayonnaise \\
	 %1 8-oz. can water chestnuts	\\
	 %1 loaf pumpernickel bread \\
	%opt:\\
	%rosemary sprigs\\
	%fresh spinach leaves\\
	%cherry tomatoes
		%}{
%Combine ingredients. Cut and hollow out 3-inch wide rim on top of bread to within \nicefrac{1}{2}-inch of bottom, leave center of loaf intact. Reserve scooped out bread. Spoon spinach dip into hollowed out ring. Tear reserved bread into bite size pieces. Use bread for dipping. Garnish tip:  Make a wreath of rosemary sprigs and fresh spinach leaves around the base of the bread bowl. Add cherry tomatoes to represent berries in the wreath.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CAMEMBERT AND PUMPERNICKEL BREAD} \index{CAMEMBERT AND PUMPERNICKEL BREAD}
I got this idea from Sabine, my German neighbour in Matumbatu Estates \#25. We shared equal passions for cooking and gardening. Sometimes Sabine would give me a jar of her homemade tree tomato jam, which went along perfectly with this dish.
Hollow out a pumpernickel bread (or other round bread). Reserve bread for dipping. Place a round of camembert into the bread round. Place bread round on cookie sheet and heat in oven (350$^\circ$F) until cheese is soft.

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SNOWBALL DIP WITH FRENCH BREAD} \index{SNOWBALL DIP WITH FRENCH BREAD}
\name{(Robert Derosiers	from Southern Health)}\\
\step{2 pkgs cream cheese
\\ 1 cup mayonnaise
\\ \nicefrac{1}{2} cup green onions, chopped
\\ 1 cup old cheddar cheese, grated
\\ \nicefrac{1}{2} cup bacon bits
\\ 1 tsp dill
\\ Garlic salt to taste
\\ 3 generous dashes Worcestershire
\\ 3 dashes of tabasco
\\ 1 heaping tsp Dijon mustard
\\ 2 loaves of French bread (not baguettes)}{Cut top of one loaf of bread and hollow it out.  Use the pieces of bread for dipping. Cut up the other loaf for dipping as well. Combine dip ingredients.  Fill hollowed out loaf. Wrap in foil. Put in oven at 350${}^\circ$F for 45--60 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MEXICAN FIESTA DIP (GF)} \index{MEXICAN FIESTA DIP (GF)} \index{Gluten Free!appetizers} \index{BEAN DIP}
	\step
	{8 oz container sour cream		\\
	 1 envelope taco seasoning mix	\\
	 16 oz can refried beans		\\
	 \nicefrac{1}{2} cup pickled jalapeno peppers, sliced	\\
	 4 oz (1 cup) cheddar cheese, shredded		\\
	 1 \nicefrac{1}{2} cups lettuce, shredded	\\
	 1 large tomato, chopped}
	{Combine sour cream and taco seasoning mix. Spread refried beans onto a 9-inch round serving plate; spoon sour cream mixture evenly over beans. Layer with jalapeno peppers and the next 4 ingredients. Serve with tortilla chips.
}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CILANTRO BLACK BEAN DIP (GF)} \index{CILANTRO BLACK BEAN DIP (GF)} \index{Gluten Free!appetizers}
	\step
	{1 540 mL can of black beans, drained \& rinsed \\
	 \nicefrac{2}{3} cup packed, chopped cilantro (leaves \& stems)	\\
	 3 cloves garlic, crushed		\\
	 2 Tbsp lime juice	\\
	 1 Tbsp tomato paste		\\
	 1 Tbsp olive oil	\\
	 1 tsp sea salt		\\
	 \nicefrac{1}{2} tsp cayenne pepper or chipotle chili powder \\
   \nicefrac{1}{2} tsp ground coriander \\
   \nicefrac{1}{2} tsp cumin \\
   \nicefrac{1}{4} cup water to thin dip as desired}{Blend in food processor or blender.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHILI DIP (GF*)} \index{CHILI DIP (GF*)} \index{Gluten Free!appetizers} 
\name{(Erma Penner)}\\
	\step{250 g cream cheese		\\
	 1 cup sour cream	\\
	 1 28 oz can mild chilli or use homemade chilli	\\
	 1 cup salsa	\\
	 shredded cheddar cheese
		}{Mix cream cheese and sour cream together. Spoon chilli on top of this. Pour salsa on top. Bake at 400$^\circ$F for 20 minutes. Cover with shredded cheese and bake 5 more minutes. Serve hot with taco chips.}
		
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GUACAMOLE (GF)} \index{GUACAMOLE (GF)} \index{Gluten Free!appetizers} 
\step{4 avocados
\\ 1 tomato
\\ \nicefrac{1}{2} onion
\\ 1 jalape\~no
\\ small bunch of cilantro
\\ 1-2 garlic cloves
\\ fresh juice of 1--2 limes
\\ salt to taste}{Mash avocados. Finely chop tomato, onion, and jalape\~no. Add all ingredients.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{VEGETABLE DIP (GF)} \index{VEGETABLE DIP (GF)} \index{Gluten Free!appetizers}
\step{1 cup mayonnaise	\\
\nicefrac{1}{2} cup sour cream \\
1 Tbsp onion	\\
\nicefrac{1}{4} tsp paprika \\
1 Tbsp chives	 \\
\nicefrac{1}{8} tsp curry powder \\
1 tsp garlic salt	\\
\nicefrac{1}{2} tsp Worcestershire sauce}
{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TACO DIP (GF)} \index{TACO DIP (GF)} \index{Gluten Free!appetizers} 
\name{Makes a nice change from salsa with taco chips.}\\
\step{1 cup mayonnaise \\
1 cup sour cream \\
1 pkg. taco spices}{}

\end{minipage}