\chapter{Breads and Muffins}

\begin{minipage}{\linewidth}\rtitle{GF JULES FLOUR} \index{GF JULES FLOUR} \index{Gluten Free!flour}
\step{4 tsp xanthan gum
\\ \nicefrac{1}{2} cup cornstarch
\\ 1 cup tapioca starch
\\ 1 cup potato starch
\\ 1 cup white rice flour
\\ \nicefrac{1}{2} cup cornflour}{}
\end{minipage}

\section{Yeast Breads}

\begin{minipage}{\linewidth}\rtitle{WHITE BREAD} \index{WHITE BREAD}
\textit{(Food that Schmecks)\\
Excellent basic recipe. Can be varied for raisin bread, cheese bread, herb bread, hotdog and hamburger buns (roll \nicefrac{1}{2}" thick).}\\
\step{1 tsp white sugar	
\\ 2 Tbsp yeast
\\ 1 cup lukewarm water
\\ 2 cups lukewarm water	
\\ \nicefrac{1}{2} cup white sugar
\\ 1 heaping tsp salt	
\\ \nicefrac{1}{2} cup melted shortening}{Dissolve sugar and yeast in water. Let stand for 10 minutes. Add remaining water, sugar, salt, and shortening. Beat, then stir in 1 cup at a time, about 9 cups flour. Knead on well floured surface until smooth and elastic. Let rise until double. Punch down. Shape 3 loaves. Let rise. Bake at 400${}^\circ$F for 20 minutes. Remove from pans to cool. Freezes well.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHITE BREAD FOR BREAD MACHINE} \index{WHITE BREAD FOR BREAD MACHINE}
\step{1 cup warm water
\\ 1 pkg yeast
\\ 2 Tbsp white sugar
\\ \nicefrac{1}{4} cup vegetable oil
\\ 3 cup white flour
\\ 2 tsp salt}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROWN BREAD} \index{BROWN BREAD}
\textit{(Lorraine Hiebert)}\\
\step{1 pkg. dry yeast	
\\ 1 cup lukewarm water
	\\ 1 Tbsp sugar	
	\\ 2 cups lukewarm water
	\\ 1 Tbsp salt	
	\\ 3 cups whole wheat flour
	\\ 3 cups flour}{Sprinkle yeast over lukewarm water in which 1 Tbsp sugar has been dissolved. Let stand for 10 minutes. Make sponge by adding 2 cups water, salt and whole wheat flour. Let stand for about \nicefrac{3}{4} hour, then mix in flour and knead until smooth. Cover and let rise until double in bulk. Divide in 2 loaves and let rise again to about double in bulk. Then put in cool oven and turn on heat to 325 or 350$^\circ$F and bake 1 hour.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROWN BREAD FOR BREAD MACHINE} \index{BROWN BREAD FOR BREAD MACHINE}
\step{1 \nicefrac{1}{2} cup water
\\ 1 \nicefrac{3}{4} cup white flour
\\ 1 \nicefrac{1}{2} cup whole wheat flour
\\ \nicefrac{3}{4} cup oats
\\ 2 Tbsp molasses
\\ 2 Tbsp honey
\\ 2 tsp salt
\\ 2 Tbsp butter
\\ 1 \nicefrac{1}{2} pkg yeast}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RYE BREAD} \index{RYE BREAD}
\textit{(Lorraine Hiebert)}\\
\step{\nicefrac{1}{2} cup warm water	
\\ 1 tsp honey
\\ 1 Tbsp yeast
\\ 2 Tbsp honey	
\\ \nicefrac{1}{4} cup oil
\\ 1 Tbsp salt	
\\ 1 Tbsp caraway seeds
\\ 1 \nicefrac{3}{4} cups warm water	
\\ 1 Tbsp lemon juice
\\ 3 cups dark rye flour	
\\ 2 \nicefrac{1}{2} -- 3 \nicefrac{1}{2} cups white flour}{Dissolve honey and yeast in warm water and let stand for 10 minutes. In a large bowl, measure honey, oil, salt, caraway seeds, warm water and lemon juice. Add yeast mixture and mix well. Add rye flour and beat vigorously by hand or at low speed with electric mixer for 2 minutes. Stir in sufficient white flour to make a workable dough. Turn dough out on lightly floured surface. Knead 5 minutes until dough is smooth and elastic. Form dough into a ball and place in greased bowl, turning once. Grease the top. Cover. Let rise in a warm place until doubled in bulk (about 1 hour). Punch dough down; form into two smooth balls. Cover and let rest 20 minutes. Roll each ball to form a long, rounded loaf and place on greased baking sheet, sprinkled with cornmeal. Using a sharp knife, make 3 or 4 shallow diagonal slashes across the top of each loaf. Let rise until almost double in bulk, about \nicefrac{1}{2} hour. Bake in 375${}^\circ$F oven for about 40-50 minutes or until done. Remove from pans and cool on wire rack. Makes two loaves.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MOM'S BUNS} \index{MOM'S BUNS}
\textit{(Lorraine Hiebert)}
\step{6--7 cups water	
\\ 2 Tbsp yeast (add sugar)
	\\ 1 cup lard (little less, maybe)	
	\\ 1 cup oil
	\\ 2 Tbsp salt	
	\\ 13--16 cups flour}{(approx 13 cups flour if using hard flour (found in Canada),	approx 16 cups flour when using soft flour, such as that found in Kenya.) Make sponge first with 3--4 cups of flour, yeast, sugar and water. Beat smooth with electric beater. Add oil and melted lard and salt. Mix with spoon. Then knead in rest of flour.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MOM'S BUNS FOR BREAD MACHINE} \index{MOM'S BUNS FOR BREAD MACHINE}
\step{1 cup warm water	
\\ 1 Tbsp yeast
\\ \nicefrac{1}{2} Tbsp sugar
\\ \nicefrac{3}{4} cup water
	\\ \nicefrac{1}{3} cup lard	
	\\ \nicefrac{1}{3} cup oil
	\\ \nicefrac{3}{4} Tbsp salt	
	\\ 5 cup flour}{}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{YEAST PIZZA CRUST} \index{YEAST PIZZA CRUST}
\step{1 Tbsp yeast 
\\ 1 \nicefrac{1}{3} cups warm water
\\ 4 cups flour
\\ 2 Tbsp olive oil	
\\ 1 tsp salt}{Dissolve yeast in warm water. Add remaining ingredients. Knead for 10 minutes. Roll out immediately into two oiled pizza pans. Bake at 400${}^\circ$F until lightly browned. Crusts are ready for sauce and toppings. With a pre-baked crust the pizza itself should only need at 15-20 minutes of baking.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PIZZA BUNS} \index{PIZZA BUNS}
\textit{(Brenda Koop)}\\
\step{2 \nicefrac{1}{2} cups flour	
\\ \nicefrac{1}{2} tsp salt
\\ 1 pkg yeast	
\\ 1 cup hot water 
\\ 3 Tbsp oil}{Mix all ingredients together and let dough rest on counter for 10-15 minutes. Divide dough in two sections. Roll out into thin rectangle (width of tall plastic cup).  Spread light layer of salsa or pizza sauce. Add pizza toppings (shredded cheese; 120 g salami, chopped; 120 g pepperoni, chopped). Roll up tightly. Cut 1 \nicefrac{1}{2}" pieces. Bake on greased cookie sheet, not touching, for approx 15 minutes. at 350${}^\circ$. Yield: 30 buns.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAGELS} \index{BAGELS}
\step{1 Tbsp yeast	
\\ 1 cup warm water
	\\ 2 Tbsp sugar	
	\\ 2\nicefrac{1}{2} tsp salt
	\\ 2\nicefrac{1}{4} cup flour}{Knead 10 minutes. Let rise 15 minutes. Punch down. Divide dough into 8 parts. Roll each part 6" long, moisten ends and join. Let rise 20 minutes. Heat 2 litres of water to boiling and reduce heat. Simmer bagels 3 or 4 at a time in the water for about 7 minutes, turning once. Drain on towel. Bake on greased cookie sheet at 375$^\circ$F for 30--35 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEIGNETS} \index{BEIGNETS}
\step{1 envelope active dry yeast	
\\ 3 Tbsp warm water
\\ \nicefrac{3}{4} cup milk	
\\ \nicefrac{1}{4} cup sugar
\\ \nicefrac{1}{4} cup shortening	
\\ 1 tsp salt
\\ 1 large egg, lightly beaten	
\\ 3 cups flour
\\ Oil for deep frying	
\\ powdered sugar}{Combine yeast and warm water. Let stand for 5 minutes. Heat milk. Stir in sugar, shortening and salt. Cool to lukewarm. Add milk mixture, egg and 2 cups flour to yeast mixture. Gradually stir in enough remaining flour to make a soft dough.
Turn dough out onto floured surface and knead 8-10 minutes or until dough is smooth and elastic. Let rise for 1 hour or until doubled.
Punch dough down. Roll in 12 x 10 rectangle. Cut into 2" squares. Place on floured surface, cover and let rise 30 minutes or until doubled. Fry beignets in 2-3 inches hot oil. Drain and sprinkle with powdered sugar while hot. Yield:  30.
Note:  dough can be made the night before and refrigerated.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PORZELKY} \index{PORZELKY}
\textit{(Loraine Hiebert)}\\
\step{2 pkg yeast	
\\ 2 cups warm water
\\ 5 tsp sugar
\\ 2 cups flour
\\ 1 \nicefrac{1}{3} cups milk, scalded \& cooled	
\\ 2 tsp salt
\\ 2 tsp baking soda	
\\ 4 eggs
\\ 1 lb raisins	
\\ approx. 4 cups flour (enough to make a stiff dough)}{Let yeast, water, and sugar stand for 15 minutes. Add flour to make sponge. When light, add the remaining ingredients. Let the dough rise until double in bulk. Drop spoonfuls into hot oil. Deep fry. Yield: 7 dozen}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PORZELKY (GF)} \index{PORZELKY (GF)} \index{Gluten Free!porzelky}
\step{2 cups warm milk
\\ 2 Tbsp unsalted butter, softened
\\ 1 tsp sugar
\\ 1 Tbsp rapid rise yeast
\\ 2 large eggs
\\ 1 Tbsp oil
\\ 1 tsp vanilla extract
\\ 2 \nicefrac{1}{4} cups brown rice flour
\\ \nicefrac{3}{4} cup tapioca starch
\\ \nicefrac{1}{2} cup potato starch
\\ \nicefrac{1}{4} cup granulated sugar
\\ 2 Tbsp dry milk powder or almond meal
\\ 2 tsp xanthan gum
\\ \nicefrac{1}{2} tsp salt
\\ 2 cups raisins}{Add the butter to the warm milk. Stir until the butter is melted. Add 1 tsp sugar and the yeast. Stir and let proof for 5 minutes, until it is frothy.
While the yeast is proofing whisk together all the dry ingredients in the bowl of your stand mixer. Add the eggs, oil and vanilla extract to the yeast mixture. With the mixer on low speed, pour in the milk/egg mixture. Mix on medium speed for about 1 minute. Add raisins and stir until evenly distributed.
Place the bowl in a draft-free warm place and let rise until double in size (about 30 min).
Heat oil in thick-bottomed pot. Carefully drop 1--2 Tbsp of dough into the hot oil. Fry until golden brown on each side. Drain on paper towel. Can be rolled in icing sugar.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TWISTERS} \index{TWISTERS}
\textit{(Loraine Hiebert)}\\
\step{8 cups flour	
\\ 4 eggs, beaten
\\ 1 lb shortening or lard	
\\ 2 cups sour cream
\\ 1 tsp salt	
\\ 2 tsp vanilla
\\ 1 tsp sugar	
\\ 2 pkg yeast}{Make crumbs from lard and flour. Measure \nicefrac{1}{2} cup lukewarm water and 1 tsp sugar in bowl. Sprinkle yeast over the top and let stand for 10 minutes. Make a well in the lard and flour mixture and add all the other ingredients. Mix well. Refrigerate for 2 hours. Take about \nicefrac{1}{4} of the dough and roll out on board. Sprinkle liberally with sugar. Coat both sides of dough. Then fold the dough and roll out again. The third time, fold the dough and roll out on a mixture of cinnamon and sugar. Cut into strips about 1" wide and about 3" long. Twist and bake on cookie sheet, 15 minutes. 350-375${}^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ENGLISH MUFFINS} \index{ENGLISH MUFFINS}
\textit{(Sarah Reed)}\\
	\step{\nicefrac{1}{2} cup shortening	
	\\ 2 cups boiling water
	\\ 4 tsp salt	
	\\ 2 Tbsp yeast
	\\ 2 tsp sugar	
	\\ 5 cups flour}{
Mix shortening, salt and sugar in large bowl. Pour boiling water over ingredients and stir until shortening melts. Cool to lukewarm. Sprinkle yeast over this. Stir to dissolve. Let stand until bubbles begin. Add flour and beat.
Roll out on floured board to 3/8" thickness. Cut with round cutter (empty tuna can). Sprinkle cookie sheets with cornmeal. Set muffins on these. Let rise until double in bulk. Set griddle to 350$^\circ$F. Sprinkle with cornmeal. Put muffins rounded side down on griddle. Bake 7 minutes on each side. They will freeze nicely if split with fork before freezing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ENGLISH MUFFIN CHEESE LOAF} \index{ENGLISH MUFFIN CHEESE LOAF}
\textit{This cheese-flavoured bread has a pleasantly coarse texture that makes it perfect for toasting.}\\
\step{1 tsp sugar	
\\ \nicefrac{1}{4} cup lukewarm water
\\ 1 pkg. yeast	
\\ 1 cup milk
\\ 1 tsp salt	
\\ 2 \nicefrac{1}{2} cups flour
\\ 1 tsp dry mustard	 
\\ \nicefrac{1}{4} tsp baking soda
\\ \nicefrac{3}{4} cup grated cheddar cheese	
\\ 2 Tbsp cornmeal}{Dissolve sugar in water. Sprinkle yeast over and let stand for 10 minutes. In saucepan, combine milk and salt. Scald and let cool to lukewarm. Add to dissolved yeast. Add 1 cup flour, mustard, baking soda and cheese. Mix until smooth. Stir in remaining flour. Grease 8 x 4 inch loaf pan; dust with some of the cornmeal. Place dough in pan and sprinkle more cornmeal on top. Cover. Let rise in warm place about 45 minutes or until center of loaf is about 1 \nicefrac{1}{2} inch above edge of pan. Bake in 400${}^\circ$F oven for 25 minutes or until loaf sounds hollow when tapped on bottom. Remove from pan. Let cool.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{sweetdoughlink}{SWEET DOUGH}} \index{SWEET DOUGH}
\textit{Mom got this recipe from George Pongoski and uses it for all her sweet dough recipes.}\\
	\step{4 \nicefrac{3}{4} cups lukewarm water*	
	\\ 1 cup sugar
	\\ 2 Tbsp yeast	
	\\ \nicefrac{1}{2} cup milk powder
	\\ 13-16 cups flour	
	\\ 6 eggs
	\\ 1 cup shortening	
	\\ 1 Tbsp salt}{(Instead of using milk powder, you can do half water, half milk.)\\
Place half of the lukewarm water in a bowl. Add yeast and sugar. Ferment. Place flour, milk powder, soft cell, eggs, shortening and salt in mixing bowl. Add yeast mixture. Mix 1 minute. Add remaining water. Mix 10 minutes.
NB:  approx 13 cups flour if using hard flour (found in Canada). approx 16 cups flour when using soft flour, such as that found in Kenya.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{sweetdoughlink}{SWEET DOUGH FOR BREAD MACHINE}} \index{SWEET DOUGH FOR BREAD MACHINE}
	\step{1 \nicefrac{1}{2} cup warm milk	
	\\ \nicefrac{1}{3} cup sugar
	\\ 2 tsp yeast	
	\\ \nicefrac{1}{6} cup milk powder
	\\ 4 \nicefrac{1}{2} cup flour	
	\\ 2 eggs
	\\ \nicefrac{1}{3} cup shortening	
	\\ 1 tsp salt}{(Instead of using milk powder, you can do half water, half milk.)\\
Place half of the lukewarm water in a bowl. Add yeast and sugar. Ferment. Place flour, milk powder, soft cell, eggs, shortening and salt in mixing bowl. Add yeast mixture. Mix 1 minute. Add remaining water. Mix 10 minutes.
NB:  approx 13 cups flour if using hard flour (found in Canada). approx 16 cups flour when using soft flour, such as that found in Kenya. Enough for 2 pans of cinnamon rolls.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MAPLE BAR DOUGHNUTS} \index{MAPLE BAR DOUGHNUTS}
\step{\nicefrac{1}{3} cup cream	
\\ 1 cup brown sugar
\\ 1 Tbsp butter	vanilla}{Use \hyperlink{sweetdoughlink}{Sweet Dough} recipe. Let rise once. Punch down and cut with doughnut cutter. Let rise. Deep fry. Boil ingredients until spoon coats in layers. Dip maple bars in icing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON ROLLS} \index{LEMON ROLLS}
Use \hyperlink{sweetdoughlink}{Sweet Dough} recipe. Let rise once. Roll out and cut with doughnut cutter. Twist into figure 8. Fill with cooked lemon pie filling. Let rise. Bake.

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CINNAMON ROLLS} \index{CINNAMON ROLLS}
Use \hyperlink{sweetdoughlink}{Sweet Dough} recipe. Let rise. Roll out dough. Spread \nicefrac{1}{4} cup softened butter on dough. Combine \nicefrac{3}{4} cup brown sugar and 1 Tbsp cinnamon. Sprinkle over dough. Sprinkle raisins on dough. Roll like a jelly roll. Slice. Place on prepared pan.\\
To prepare pan: spread 1 cup of unmelted butter on pan. Sprinkle approx 1 cup brown sugar (for 9x13" pan) on bottom of pan. Add \nicefrac{1}{2} cup cream. Stir together to mix.
Place cinnamon rolls closely together on the pan to ensure that the bottom stays soft when baking.

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CINNAMON ROLLS (GF)} \index{CINNAMON ROLLS (GF)} \index{Gluten Free!desserts}
\step{Topping:
\\ 4 Tbsp butter
\\ \nicefrac{1}{2} cup brown sugar
\\ 2 Tbsp corn syrup
\\ 1 tsp vanilla
\\ 2 Tbsp heavy whipping cream
\\ Pinch of salt}{Over low heat, combine butter, sugar and syrup, stirring until sugar dissolves. Add vanilla, whipping cream and salt. Stir. Remove from heat and pour into the bottom of a greased 9x13" pan with high sides.}

\step{Filling:
\\ 2 Tbsp butter, very soft
\\ \nicefrac{1}{2} cup firmly packed brown sugar
\\ 1-2 Tbsp cinnamon
\\ raisins or pecans (opt)}{}

\step{Dough:
\\ 1 \nicefrac{2}{3} cup brown rice flour
\\ \nicefrac{1}{2} cup potato starch
\\ \nicefrac{1}{3} cup + \nicefrac{1}{2} cup tapioca starch
\\ 1 Tbsp xanthan gum
\\ 1 Tbsp rapid rise yeast
\\ 3 Tbsp sugar
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{4} cup instant vanilla pudding mix OR dry milk powder
\\ 1 tsp baking powder
\\ 4 Tbsp margarine or butter
\\ \nicefrac{1}{2} cup water
\\ 1 large egg
\\ \nicefrac{3}{4} cup milk
\\ 1 tsp cider vinegar
\\ 2 Tbsp oil
\\ 1 tsp vanilla}{Mix all dry ingredients until combined. Set aside. Put water and margarine in a glass measuring cup and microwave just until the margarine has melted. Add milk. Stir. Add other wet ingredients and whisk to combine.
With the stand mixer running (use paddle attachment), pour the wet ingredients into the dry ingredients. Allow to mix on med speed for 3 minutes. Take a piece of plastic wrap and lay it out on a slightly damp counter to, so it covers an area bigger than 8x16". Sprinkle 2 Tbsp of sugar on the wrap. Lay ball of dough on top of that. Gently lay another piece of plastic wrap over the dough. Pat the dough into a rectangular shape. Life and reposition the top plastic wrap whenever you need to. Roll the dough out wo approx. 8x16". 
Remove plastic wrap. Spread filling evenly across dough's surface, leaving 1 \nicefrac{1}{2}" along one long end bare. This is where your cinnamon rolls will be sealed.
Starting along the long end, use the bottom sheet of plastic wrap to lift the edge of the dough and roll it up. Using a long piece of dark thread, cut the long log into 8 pieces, about 1 \nicefrac{1}{2}". Place rolls in prepared pan, with cut side up. Push the rolls down to about 1" high.
Allow the rolls to rise in a warm, draft free place for about 30 minutes, or until nearly double in size. Bake at 350${}^\circ$F for 20-25 minutes. Allow to cool for about 5 minutes before inverting on a serving tray.}
\end{minipage}

\section{Quick Breads}
\begin{minipage}{\linewidth}\rtitle{JIFFY CINNAMON ROLLS} \index{JIFFY CINNAMON ROLLS}
Prepare MJ's Tea Biscuit Dough. Turn dough out on lightly floured surface. Knead 8-10 times. Roll into rectangle about \nicefrac{1}{3}" thick and 12" long. Cream butter, brown sugar and cinnamon together well. Drop 1 measuring tsp into each of 12 greased muffin tins. Spread the remaining cinnamon mixture over dough rectangle. Sprinkle raisins over top. Roll up as for jelly roll. Cut into 12 slices. Place cut side down in muffin pan. Bake at 400$^\circ$F for 20-25 minutes.

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROLLKUCHEN} \index{ROLLKUCHEN}
\textit{Always to be eaten with lots of watermelon!!!} \\
	\step{4 tsp baking powder	
	\\ 6 eggs
	\\ 2 cups sour milk	
	\\ 2 tsp salt
	\\ 1 cup butter}{
Mix dry ingredients. Add melted butter to milk. Enough flour to roll out. Knead a little but handle dough as little as possible. Cut into long strip, approx. 5 by 2 inches. Make a slit lengthwise. Fry in hot fat as you would doughnuts.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROLLKUCHEN (GF)} \index{ROLLKUCHEN (GF)} \index{Gluten Free!rollkuchen} 
\textit{(EMC Convention in High Level, AB)}\\
\step{1 cup milk
\\ 1 cup cream
\\ 4 eggs
\\ 2 Tbsp salt
\\ 1 tsp baking powder (heaping)
\\ Celiemix bread mix, enough to make a soft dough}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PASKA} \index{PASKA}
	\step{3 pkgs. yeast	
	\\ 4 cups sugar
	\\ \nicefrac{1}{2} cup lard	
	\\ 16 eggs
	\\ 1 tsp salt	
	\\ \nicefrac{1}{2} cup butter
	\\ juice and rind of 1 lemon	juice 
	\\ rind of 1 orange
	\\ 3 cups scalded milk	
	\\ 8 cups flour}{
Soften yeast in 1 cup warm water and 2 tsp sugar. Beat eggs well. Add sugar gradually and beat until dissolved. Sift flour and salt. Make well in flour, put in scalded milk. Stir and add egg mixture. Beat well. Add softened butter and fruit juices and rind. Now add yeast mixture and knead as you do sweet buns, adding flour as you need it. Let this rise in a warm place. When light, punch and let rise until double in bulk. Grease honey pails and fill \nicefrac{1}{3} with dough. Let rise until light and bake in 325$^\circ$F oven for 1 hour. Yield: 12 paska}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHEESE SPREAD FOR PASKA} \index{CHEESE SPREAD FOR PASKA}
	\step{4 cups cottage cheese	
	\\ yolks of 9 hard-cooked eggs
	\\ 1 cup cream	
	\\ 1 cup butter
	\\ 1 cup sugar	
	\\ 1 tsp grated lemon rind
	\\ 1 Tbsp lemon juice}{Press cheese and egg yolks through a sieve. Bring cream to a boil and then cool. Cream together the butter and sugar and add the other ingredients. Mix thoroughly. This is now ready to use as a spread when serving Paska.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MJ'S TEA BISCUITS} \index{MJ'S TEA BISCUITS}
\textit{(from MJ'S Restaurant, Steinbach's fantastic Mennonite restaurant)} \\
	\step{3 cups flour	
	\\ 4 tsp baking powder
	\\ \nicefrac{1}{2} tsp salt	
  \\ 1 \nicefrac{1}{2} cups cream	
  \\ \nicefrac{1}{4} cup lard
	\\ \nicefrac{1}{4} cup margarine}{Mix dry ingredients. Add remaining ingredients. Knead lightly. Dough should not be sticky. Rest 15 minutes. Roll thin. Then roll as jelly roll and cut. Brush with cream and bake. 350$^\circ$F, 20-30 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FEATHERLIGHT BISCUITS (GF)} \index{FEATHERLIGHT BISCUITS (GF)} \index{Gluten Free!breads} \index{Gluten Free!flours}
\textit{(Jackie Buhler)}\\
\step{Featherlight Flour:
\\ 1 part rice flour
\\ 1 part cornstarch
\\ 1 part tapioca flour
\\ 1 Tbsp potato flour per cup of the other ingredients}{}

\step{1 cup featherlight mix
\\ \nicefrac{1}{2} tsp xanthan gum
\\ 1 \nicefrac{1}{2} tsp baking powder
\\ \nicefrac{1}{2} tsp baking soda
\\ 1 tsp sugar
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{4} cup shortening or butter
\\ \nicefrac{1}{2} cup yoghurt}{Combine dry ingredients. Cut in shortening. Stir in yoghurt. Work gently till it forms a ball.  Pat or lightly roll out to \nicefrac{3}{4}" thickness and cut into biscuits. Bake 10-12 minutes at 450${}^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROWN SUGAR SCONES} \index{BROWN SUGAR SCONES}
\step{3 cups flour	
\\ 2 tsp baking powder
\\ 1 cup golden brown sugar	
\\ 1 cup butter
\\ 1 cup raisins	
\\ 1 cup milk}{Stir flour, baking powder and sugar together. Cut in butter until mixture is like coarse meal. Mix in raisins. Add milk and stir until sticky dough forms. On floured surface, roll dough into a long rectangle about \nicefrac{3}{4}" thick. With sharp knife, but dough into triangles. Place on ungreased cookie sheet and bake at 375${}^\circ$F until golden brown.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BANANA BREAD} \index{BANANA BREAD}
\textit{(Moira Neufeld)}\\
	\step{\nicefrac{1}{2} cup butter	
	\\ 1 cup sugar
	\\ 3 large ripe bananas	
	\\ 1 egg
	\\ 1 cup flour	
	\\ 1 tsp baking soda
	\\ \nicefrac{1}{8} tsp salt	
	\\ \nicefrac{1}{2} cup wheat bran
	\\ \nicefrac{1}{2} cup oat bran
	\\ 1 cup chocolate chips (opt)}{Cream butter and sugar. Add egg. Mash banana and add. Sift in dry ingredients. Makes 1 loaf. 350$^\circ$F for 50--55 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE CHIP BANANA MUFFINS (GF)} \index{CHOCOLATE CHIP BANANA MUFFINS (GF)} \index{Gluten Free!breads}
\step{1 cup sorghum flour
\\ \nicefrac{1}{2} cup oat flour
\\ \nicefrac{1}{4} cup tapioca starch
\\ 1 tsp xanthan gum
\\ \nicefrac{1}{2} cup brown sugar
\\ 2 tsp baking powder
\\ 1 tsp baking soda
\\ \nicefrac{1}{2} tsp salt
\\ 2 large eggs
\\ \nicefrac{1}{3} cup oil
\\ \nicefrac{1}{2} cup yoghurt or sour cream
\\ 1 tsp vanilla
\\ 1 cup ripe bananas, mashed
\\ \nicefrac{3}{4} cup chocolate chips}{Combine the dry ingredients. In another bowl, whisk together the remaining ingredients, except the chocolate chips.  Combine the wet and dry ingredients. Fold in the choc chips. Bake 20-22 minutes at 350${}^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DOUBLE CHOCOLATE SURPRISE MUFFINS} \index{DOUBLE CHOCOLATE SURPRISE MUFFINS}
\step{1 \nicefrac{3}{4} cups flour	
\\ 4 tsp baking powder
\\ \nicefrac{1}{4} cup cocoa	
\\ \nicefrac{1}{2} cup sugar
\\ \nicefrac{1}{2} cup chocolate chips	
\\ 75 g butter
\\ 2 large eggs	
\\ \nicefrac{3}{4} cup milk
\\ \nicefrac{3}{4}-1 cup raspberry jam	
\\ extra chocolate chips}{Sift dry ingredients together. Add sugar and chocolate chips. Melt the butter then add the eggs and milk. Pour liquids into dry ingredients and fold together. Stop as soon as there are no pockets of flour left. Grease muffin pans. Half fill each pan with a Tbsp of the mixture. Using a damp tsp make a small hollow in each muffin and fill it with a tsp of jam. Divide the remaining mixture between the muffins, ensuring that the jam is completely covered. Sprinkle the muffins with extra chocolate chips and bake at 200${}^\circ$C for about 10 minutes.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SPECIAL CARROT BREAD} \index{SPECIAL CARROT BREAD}
\textit{(Brenda Koop)}\\
\step{\nicefrac{1}{2} cup oil	
\\ 1 cup white sugar
\\ 2 eggs, beaten	
\\ \nicefrac{1}{2} cup milk
\\ 1 tsp. Vanilla	
\\ 1 \nicefrac{1}{2} cups flour (\nicefrac{1}{2} whole wheat, \nicefrac{1}{2} white)
\\ 1 tsp baking powder	
\\ 1 tsp baking soda
\\ \nicefrac{1}{4} tsp salt	
\\ 1 tsp cinnamon
\\ \nicefrac{1}{2} cup chopped walnuts	
\\ \nicefrac{1}{2} cup raisins
\\ \nicefrac{1}{2} cup glazed cherries}{Mix sugar and oil. Add beaten eggs. Stir in carrots, milk, and vanilla. Sift flour, baking powder, baking soda, salt, and cinnamon. Add to liquid mixture, stirring just enough to blend. Add walnuts, raisins, and cherries.
Bake at 350 in 2 greased loaf pan (22.2 cm x 11.7 cm x 5.7 cm) for 40 minutes. Toothpick should come out clean. Mix sugar and oil. Add beaten eggs. Stir in carrots, milk, and vanilla. Sift flour, baking powder, baking soda, salt, and cinnamon. Add to liquid mixture, stirring just enough to blend. Add walnuts, raisins, and cherries.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CARROT MUFFINS} \index{CARROT MUFFINS}
\step{1 cup sugar	
\\ \nicefrac{3}{4} cup cooking oil
\\ 1 \nicefrac{1}{2} cups flour	
\\ \nicefrac{1}{2} cup chopped raisins
\\ 1 tsp baking soda	
\\ 1 cup grated carrots
\\ 1 tsp baking powder	
\\ pinch of salt
\\ 1 tsp cinnamon	
\\ 2 eggs, well beaten
\\ 1 tsp vanilla}{Cover \nicefrac{1}{2} cup raisins with hot water, let cool, drain, chop and flour. Grate carrots to make one cup. Mix all ingredients together, adding the eggs last. Bake at 375${}^\circ$F for 15-20 minutes.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUMPKIN BREAD} \index{PUMPKIN BREAD}
\textit{(Janet Felten)}\\
	\step{2 eggs	
	\\ 1 tsp baking soda
	\\ \nicefrac{1}{2} cup canola oil	
	\\ \nicefrac{3}{4} tsp cinnamon
	\\ 3 Tbsp water	
	\\ \nicefrac{1}{4} tsp ginger
	\\ 1 cup pumpkin (15 oz)	
	\\ \nicefrac{1}{2} tsp nutmeg
	\\ 2 cup flour	
	\\ \nicefrac{3}{4} tsp salt
	\\ 1 cup sugar 	
	\\ 2 cup chocolate chips (1 pkg)}{
Spray pan and flour it. Mix wet ingredients in a bowl. Mix dry ingredients in another bowl. Mix together. Add chocolate chips. Pour into pan. 350$^\circ$F for 55--70 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUMPKIN CHOCOLATE CHIP MUFFINS (GF)} \index{PUMPKIN CHOCOLATE CHIP MUFFINS (GF)} \index{Gluten Free!breads}
\step{\nicefrac{2}{3} cup tapioca flour
\\ \nicefrac{1}{3} cup brown rice flour
\\ \nicefrac{1}{3} cup sorghum flour
\\ \nicefrac{1}{3} cup millet or GF oat flour
\\ \nicefrac{1}{2} tsp xanthan gum
\\ \nicefrac{3}{4} cup sugar
\\ 2 tsp cinnamon
\\ \nicefrac{1}{2} tsp ground cloves
\\ \nicefrac{1}{2} tsp ginger
\\ \nicefrac{1}{2} tsp baking soda
\\ 1 tsp baking powder
\\ \nicefrac{1}{4} tsp salt
\\ 2 large eggs
\\ 1 cup plain pumpkin puree
\\ \nicefrac{1}{4} cup oil
\\ \nicefrac{1}{4} cup applesauce or plain yoghurt
\\ \nicefrac{3}{4} cup chocolate chips}{Whisk together all dry ingredients. In another bowl mix together the wet ingredients. Fold wet ingredients into the dry until mixture is thoroughly moistened. Fold in chocolate chips. Bake at 350${}^\circ$F for 20-25 minutes.  Yield 12 large muffins.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUMPKIN CREAM CHEESE MUFFINS} \index{PUMPKIN CREAM CHEESE MUFFINS}
\step{2 cups flour	
\\ \nicefrac{1}{2} cup sugar
\\ \nicefrac{1}{4} tsp ginger	
\\ pinch nutmeg
\\ \nicefrac{1}{4} tsp cinnamon	
\\ \nicefrac{1}{4} tsp cloves
\\ \nicefrac{1}{4} tsp allspice	
\\ 1 Tbsp baking powder
\\ \nicefrac{1}{2} tsp salt	
\\ 2 eggs, slightly beaten
\\ \nicefrac{3}{4} cup cooked or canned pumpkin
\\ \nicefrac{1}{2} cup butter, melted	
\\ \nicefrac{1}{4} cup sour cream
\\ 1 125 gram pkg. cream cheese, cut in cubes}{Mix flour, sugar, spices, baking powder and salt. In a small bowl, mix egg, pumpkin, butter and sour cream. Add to flour mixture and stir just until blended. Fill greased muffin cups \nicefrac{1}{3} full. Place a cream cheese cube in center of each. Add more batter to fill cups \nicefrac{2}{3} full. Bake at 400${}^\circ$F for 15 to 25 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APPLE MUFFINS} \index{APPLE MUFFINS}
\step{1 \nicefrac{3}{4} cups flour	
\\ 1 egg
\\ \nicefrac{3}{4} tsp salt	
\\ 1 cup milk
\\ 4 tsp baking powder	
\\ \nicefrac{1}{3} cup melted shortening
\\ \nicefrac{1}{4} cup sugar	
\\ 1 tsp lemon rind
\\ \nicefrac{1}{4} tsp nutmeg	
\\ \nicefrac{3}{4} cup apples, peeled and chopped.}{350${}^\circ$F for 25 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BRAN MUFFINS} \index{BRAN MUFFINS}
	\step{1 cup flour	
	\\ 1 tsp baking powder
	\\ 1 tsp baking soda	
	\\ \nicefrac{1}{2} tsp salt
	\\ \nicefrac{3}{4} cup raisins	
	\\ 1 cup buttermilk or sour milk
	\\ 1 cup natural bran	
	\\ \nicefrac{1}{3} cup cooking oil
	\\ \nicefrac{1}{4} cup molasses 
	\\ 1 egg
	\\ \nicefrac{1}{4} cup packed brown sugar	
	\\ \nicefrac{1}{2} tsp vanilla}{
Combine flour, baking powder, soda, salt and raisins. Stir together well. Make well in center. In another bowl, combine buttermilk and bran. Let stand 5 minutes. Add remaining ingredients to bran mixture in order given. Beat with spoon until mixed. Pour into well. Stir just to moisten. Batter will be lumpy. Fill greased muffin tins \nicefrac{3}{4} full. Bake at 375$^\circ$F for 20-25 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RAISIN BRAN MUFFINS (GF)} \index{RAISIN BRAN MUFFINS (GF)} \index{Gluten Free!breads}
\step{\nicefrac{1}{2} cup ground flax seed
\\ \nicefrac{1}{2} cup oat bran
\\ 1 cup yoghurt
\\ \nicefrac{1}{3} cup oil
\\ 1 large egg
\\ \nicefrac{2}{3} cup brown sugar
\\ \nicefrac{1}{2} tsp vanilla
\\ \nicefrac{1}{3} cup oat flour
\\ \nicefrac{1}{3} cup brown rice flour
\\ \nicefrac{1}{3} cup tapioca starch
\\ 1 tsp xanthan gum
\\ 1 tsp baking soda
\\ 1 tsp baking powder
\\ \nicefrac{1}{2} tsp cinnamon
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} cup rehydrated raisins}{Mix together the flax seed, oat bran and yoghurt. Let sit for 10 minutes. In a large mixing bowl, combine the flours, xanthan gum, baking soda, baking powder, cinnamon and salt. In a medium bowl beat together the oil, egg, sugar and vanilla.  Add the yoghurt mixture. Stir this into the dry ingredients, just until blended. Fold in the raisins.  Bake 15-20 minutes at 375${}^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON POPPY SEED BREAD} \index{LEMON POPPY SEED BREAD}
\textit{Makes 2 large loaves.}\\
\step{3 cups flour	
\\ 1 egg
\\ 4 egg whites	
\\ 1 \nicefrac{1}{2} cups skim milk
\\ 2 \nicefrac{1}{4} cups sugar	
\\ \nicefrac{1}{2} tsp salt
\\ 1 \nicefrac{1}{2} tsp baking powder	
\\ \nicefrac{1}{2} cup oil
\\ \nicefrac{1}{2} cup applesauce	
\\ 2 Tbsp poppy seeds
\\ 1 tsp vanilla extract	
\\ 4 Tbsp chopped lemon zest
\\ 1 Tbsp fresh lemon juice}{Mix until well blended. Divide dough between two 10x5" pans and bake for 40 minutes at 350. Whisk glaze ingredients together. Spoon mixture over loaves while they are still warm and in the pan. Cool and loosen sides with a knife.}
\step{Glaze:
\\ \nicefrac{1}{3} cup icing sugar	
\\ 2 tsp lemon juice
\\ \nicefrac{1}{2} tsp milk	
\\ 2 tsp chopped lemon zest}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON POPPY SEED MUFFINS (GF)} \index{LEMON POPPY SEED MUFFINS (GF)} \index{Gluten Free!breads}
\step{1 \nicefrac{1}{3} cups all purpose GF flour
\\ 2 Tbsp poppy seed
\\ 1 \nicefrac{1}{2} tsp baking powder
\\ 1 tsp baking soda
\\ \nicefrac{3}{4} tsp xanthan gum
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{2}{3} cup sugar
\\ \nicefrac{1}{2} cup butter, softened
\\ 2 eggs
\\ \nicefrac{2}{3} cup sour cream
\\ 2 Tbsp grated lemon peel
\\ 2 Tbsp fresh lemon juice
\\\\GLAZE:
\\ \nicefrac{1}{2} cup powdered sugar
\\ 1-2 Tbsp fresh lemon juice}{Combine first 6 ingredients. Beat sugar and softened butter until light and fluffy. Add eggs, one at a time, beating 1 minutes after each addition. Beat in sour cream, lemon peel and 2 Tbsp lemon juice until smooth. Gradually beat or stir in dry mixture. Dough will be thick. Makes 12 muffins. Bake 20-24 minutes at 375${}^\circ$F. Cool 5 minutes in pan. Remove from pan to cooling rack. Drizzle glaze over muffins.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CAKE DOUGHNUTS} \index{CAKE DOUGHNUTS}
\step{3 Tbsp melted butter	
\\ 1 cup sugar
	\\ 2 eggs	
	\\ 1 cup milk
	\\ 1 tsp vanilla	
	\\ 4 cups flour
	\\ 4 tsp baking powder	
	\\ \nicefrac{1}{2} tsp salt
	\\ \nicefrac{1}{2} tsp cinnamon	
	\\ \nicefrac{1}{2} tsp nutmeg
	\\ 4-6 inches deep hot fat}{
Combine melted butter, sugar, eggs, milk and vanilla. Mix together. Measure in flour, baking powder, salt, cinnamon and nutmeg. Stir well.
Roll out dough \nicefrac{1}{4}-inch thick on floured surface. Cut out with doughnut cutter. Drop into hot fat a few at a time so as not to crowd. Turn when light brown to cook other side.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CORNBREAD} \index{CORNBREAD}
	\step{1 cup cornmeal	
	\\ 1 cup flour
	\\ 4 tsp baking powder	
	\\ \nicefrac{1}{2} tsp salt
	\\ 2 Tbsp sugar	
	\\ \nicefrac{1}{2} cup dry milk
	\\ 1--2 eggs	
	\\ 1 cup water
	\\ \nicefrac{1}{4} cup oil}{
Mix dry ingredients. Add wet ingredients. Bake 25 minutes in 400$^\circ$F oven.
NOTE: for a crunchy crust, put a bit of oil in a caste iron skillet and heat it in the oven while you're mixing the batter. Then pour the batter in the sizzling oil and bake.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BUTTERMILK CORNBREAD MUFFINS (GF)} \index{BUTTERMILK CORNBREAD MUFFINS (GF)} \index{Gluten Free!breads}
\step{\nicefrac{1}{2} cup butter or margarine
\\ \nicefrac{2}{3} cup sugar (or less)
\\ 2 large eggs
\\ 1 cup buttermilk
\\ \nicefrac{1}{2} tsp baking soda
\\ 1 cup cornmeal
\\ 1 cup GF flour 
\\ \nicefrac{1}{2} tsp xanthan gum
\\ \nicefrac{1}{2} tsp salt}{Melt butter. Stir in sugar. Add eggs and stir to combine. Stir in buttermilk. Add dry ingredients. Bake for 20 minutes at 350${}^\circ$F.  Yield 12.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FRENCH TOAST} \index{FRENCH TOAST}
\step{3 eggs	
\\ 1 tsp sugar
\\ \nicefrac{1}{2} tsp salt	
\\ \nicefrac{3}{4} cup milk
\\ 8-10 slices bread}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{wafflelink}{WAFFLES}} \index{WAFFLES}
\textit{(quick version)}\\
	\step{1 \nicefrac{1}{2} cups flour	
	\\ 2 Tbsp sugar
	\\ 1 Tbsp baking powder	
	\\ \nicefrac{1}{2} tsp salt
	\\ 2 eggs, beaten	
	\\ 1 \nicefrac{1}{2} cups milk
	\\ \nicefrac{1}{4} cup melted butter}{
Put flour, sugar, baking powder and salt into mixing bowl. Stir very well. Make a well in center. Beat eggs well until frothy in separate bowl. Stir in milk and butter. Pour into well. Beat only until smooth. Fill hot waffle iron according to its instructions.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRISPY WAFFLES} \index{CRISPY WAFFLES}
\textit{(Joy of Cooking)}\\
\textit{Although a little more work than the quick version \hyperlink{wafflelink}{waffle} recipe, the resulting texture is more tender, with a crisp exterior. If used with savoury food, omit the sugar.}\\
	\step{1 \nicefrac{3}{4} cups cake flour	
	\\ 2 tsp baking powder
	\\ \nicefrac{1}{2} tsp salt	
	\\ 1 Tbsp sugar
  \\ 3 egg yolks, beaten
  \\ 2-7 Tbsp melted butter
	\\ 1 \nicefrac{1}{2} cups milk
	\\ 3 egg whites, beaten}{
Make a hole in center of dry ingredients. Pour in liquid ingredients and combine with a few swift strokes. Batter should be pebbled, similar to muffin batter. Beat 3 egg whites until stiff but not dry.
Fold whites into batter until they are barely blended. Bake in a waffle iron.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PANCAKES} \index{PANCAKES}
\textit{(Company's Coming)}\\
	\step{1 \nicefrac{1}{2} cups flour	
	\\ 1 Tbsp granulated sugar
	\\ 1 Tbsp baking powder	
	\\ \nicefrac{1}{2} tsp salt
	\\ 1 egg, beaten	
	\\ 2 Tbsp oil
	\\ 1 \nicefrac{1}{2} cups milk}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{crepelink}{CREPES}} \index{CREPES}
\textit{(Company's Coming)}\\
	\step{4 eggs	
	\\ 1 cup milk
	\\ 1 cup water	
	\\ 2 cups flour
	\\ 4 Tbsp cooking oil	
	\\ 1 tsp sugar
	\\ \nicefrac{1}{4} tsp salt}{
Beat eggs in large bowl until frothy. Add rest of ingredients. Beat smooth. Cover and store in refrigerator overnight or at least a few hours. Add milk before cooking if too thick. Pour 2 Tbsp in greased hot crepe pan. Tip pan to swirl batter all over pan bottom. Remove when underside is lightly browned. Stack with waxed paper between each crepe. Secure in plastic bag to store in freezer. Use as needed. Makes 24 crepes.
Chocolate Sauced Crepes: Cut vanilla ice cream about 1x1x4 inches long and lay on edge of unbrowned side of crepe. Roll. Allow 2 crepes per serving. Spoon hot chocolate sauce over top.
Strawberry cream crepes: spread with: 250 g cream cheese, \nicefrac{1}{4} cup sugar and 1 cup sour cream. Roll. Combine slices strawberries and sugar and spoon over crepes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED OATMEAL (GF)} \index{BAKED OATMEAL (GF)}
\textit{(LaDonna Mann)}\\
	\step{\nicefrac{2}{3} cup oil	
	\\ \nicefrac{2}{3} cup brown sugar
	\\ 3 eggs, beaten	
	\\ 3 \nicefrac{2}{3} cup oatmeal
	\\ 3 tsp baking powder	
	\\ \nicefrac{2}{3} tsp salt
	\\ 1 \nicefrac{1}{4} cup milk}{
Mix well and pour into greased pan. Bake at 350$^\circ$F about 30 minutes or until center is set. Serve with warm milk, cinnamon, bananas, etc. This keeps well in the refrigerator.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PANELLE (GF)} \index{PANELLE (GF)}
\step{3 cups water
\\ 2 cups chick pea flour
\\ 1 tsp coarse salt (or kosher salt)
\\ 2 Tbsp olive oil
\\ \nicefrac{1}{4} cup chopped flat leaf parsley}{Line loaf pan with parchment. Whisk together all ingredients until smooth. Cook over moderate heat, constantly stirring, until mixture pulls away from pan (approx. 20-25 min). Transfer the dough to the loaf pan, smoothing the top. Cool uncovered. Then chill at least 3 hours.
Lift chick pea block from the pan. Gently flip over. Discard the parchment and pat dry. Cut into \nicefrac{1}{4}" slices. Heat \nicefrac{1}{3}-\nicefrac{1}{2}" of olive oil in a deep skillet. Fry the slices, turning occasionally, until golden and puffed (3-5 minutes. per batch).  Although it's best served fresh, it can be fried up to 4 hours ahead of time.  Keep uncovered at room temp. Reheat at 350 for 10-15 mins.
Suggested additions:  cheese, rosemary, parsley}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEFSA} \index{LEFSA}
\textit{(Saskatoon Folkfest Norwegian booth)}\\
\step{5 lbs white potatoes
\\ \nicefrac{1}{2} cup melted Crisco 
\\ 3 beaten eggs
\\ 1 tsp salt
\\ 1 tsp bkg powder
\\ 1 \nicefrac{1}{2} cups flour}{Boil and rice the potatoes.  Add Crisco and rice again.  Do NOT add salt. Cool overnight in a glass or metal bowl. Cover with a towel. The following day add remaining ingredients. Knead.  Add up to \nicefrac{1}{2} cup additional flour if the dough is sticky. Make into 4 logs. Each log makes 6--8 lefsa. Keep logs in fridge covered with towel and take out one at a time. Roll and bake in a frying pan, similar to how tortillas are made.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PANNEKUCHEN} \index{PANNEKUCHEN}
\textit{(Kyle Kroening)}\\
	\step{8 eggs	
	\\ 1 \nicefrac{1}{3} cups milk
	\\ 1 \nicefrac{1}{3} cups flour	
	\\ 1 tsp salt
	\\ 6 Tbsp butter}{Combine ingredients except butter. Pour mixture into pan. Dot surface with butter. Bake at 450${}^\circ$F for 15 minutes. Lower temperature to 350${}^\circ$F. Bake for additional 10 minutes. Serve with jam or syrup.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{YORKSHIRE PUDDING} \index{YORKSHIRE PUDDING}
	\step{4 eggs	
	\\ 1\nicefrac{1}{2} cups milk
	\\ 1 \nicefrac{1}{2} cups flour	
	\\ 1 tsp salt}{
Beat eggs. Mix in milk. Beat in flour and salt until bubbly. Pour \nicefrac{1}{4} cup hot droppings from roast into 8 x 8 inch pan. Pour in batter. Bake uncovered in 425$^\circ$F oven until risen and browned, about 30 minutes. Cut into squares to serve.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{POPOVERS} \index{POPOVERS}
\step{}{Make as for Yorkshire pudding, adding 1 Tbsp melted butter to the batter. Pour into well greased muffin tins about \nicefrac{1}{2} full. Place in cold oven. Turn temp to 400${}^\circ$F. Bake for about 40 minutes until puffed and well browned. Makes 12.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HUSH PUPPIES} \index{HUSH PUPPIES}
\textit{(LaDonna Mann)\\
These brought on my labour with Victoria!}\\
	\step{2 cups maize (cornmeal)	
	\\ 1 large onion, chopped fine
	\\ 2 Tbsp flour	
	\\ 1 egg
	\\ 2\nicefrac{1}{2} tsp 
	\\ baking powder	
	\\ 1 tsp salt}
{Mix and add enough milk to make stiff batter. Drop by teaspoonfuls into deep pan with hot fat. Cook until lightly browned. Makes about 24.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DUMPLINGS} \index{DUMPLINGS}
\step{1 cup flour	
\\ 2 tsp baking powder
\\ 1 tsp sugar	
\\ \nicefrac{1}{2} tsp salt
\\ 1 Tbsp butter	
\\ \nicefrac{1}{2} cup milk}{Stir dry ingredients together. Cut in butter until crumbly. Stir in milk to make soft dough. Drop by spoonfuls onto boiling stew. Cover and simmer 15 minutes without lifting lid. Makes 6 dumplings.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FLOUR TORTILLAS} \index{FLOUR TORTILLAS}
\step{2 cups unsifted flour	
\\ 1 tsp salt
\\ \nicefrac{1}{4} cup oil	
\\ \nicefrac{1}{2} cup lukewarm water}{Combine flour, salt, oil, and water. Knead the dough a bit. Divide into 8 or 11 balls. Roll them out (round). Cook them on an ungreased griddle, about 20 seconds per side. They should get little brown flecks in them when cooked. Use for Mexican dishes. OPT: to make tortilla shells for taco salad, take a flour tortilla. Find a metal bowl that's about the size you want your shell to be. Put the tortilla on the outside of the bowl and plunge it into deep, hot oil and hold it there. Don't let the bowl fill with oil. Let it fry until crisp.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CORN TORTILLAS} \index{CORN TORTILLAS}
\step{1 cup sifted flour	
\\ \nicefrac{1}{2} cup cornmeal
\\ \nicefrac{1}{2} tsp salt
\\ 1 small egg	
\\ 1 \nicefrac{1}{2} cup cold water}{Stir flour, cornmeal, and salt together. Add and beat 1 small egg and cold water. Warm a lightly oiled smooth surfaced frying pan. Place 2 Tbsp batter on the pan and spread with the back of a spoon, quickly, to as large a circle as possible, 8" or so. Keep over a low fire, The edges will curl, so you can pick up the edge and peel it off the pan. If it resists peeling, wait a moment, turn down the fire if it's getting too brown. Turn it over, cook about 30 seconds on the second side and set on a rack to cool. Use these for enchiladas or burritos. Deep fry for tostadas or tacos. Makes 12.
OPT: cut into triangles and deep fry for corn chips.}

\end{minipage}