\section{Cakes}

\begin{minipage}{\linewidth}\rtitle{CHOCOLATE CAKE FOR A BLACK FOREST TORTE} \index{CHOCOLATE CAKE FOR A BLACK FOREST TORTE}
\name{(Karen Schwab)}\\
\step{1 \nicefrac{1}{2} cups sugar	
	\\ 2 extra large eggs
	\\ 1 cup oil	
	\\ 1 -- 19 oz. can beets, drained and pur\'eed
	\\ 6 Tbsp cocoa	
	\\ 1 \nicefrac{3}{4} cup unsifted flour
	\\ 1 \nicefrac{1}{2} tsp baking soda	
	\\ \nicefrac{1}{4} tsp salt
	\\ 1 tsp vanilla}{Combine sugar and eggs. Add oil and beets. Mix. Stir in cocoa, flour, baking soda, salt and vanilla. Beat for 2 minutes on medium speed. Either grease and flour 3 round cake pans or line with wax. Bake cake at 350${}^\circ$F.
To assemble for Black Forest Torte:
Spread bottom layer with Black currant jam, place black cherries soaked in kirsch on top of the jam. Add whipped cream. Continue same for second layer. On third layer, spread entire torte with whipped cream. Garnish with kirsch-soaked cherries and shaved chocolate. Each cake layer can also be sprinkled with kirsch before assembling.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GERMAN CHOCOLATE CAKE} \index{GERMAN CHOCOLATE CAKE}
\step{One baked chocolate cake (either $9 \times 13$" or 2 round layers)
\stepspace  FROSTING:
\\ 1 cup evaporated milk
\\ 1 cup brown sugar
\\ 3 egg yolks
\\ \nicefrac{1}{2} cup butter
\\ 1 tsp vanilla extract
\\ 1 cup chopped pecans
\\ 1 \nicefrac{1}{3} cups flaked coconut}{In a large saucepan combine all the ingredients except pecans and coconut. Cook over low heat, stirring constantly until thick. Remove from heat. Stir in nuts and coconut. Let cool to room temp before spreading on cake. Note: The chocolate cake recipe in the GF section works well with this frosting.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE FUDGE CAKE} \index{CHOCOLATE FUDGE CAKE}
\step{\nicefrac{1}{2} cup melted butter	
\\ \nicefrac{1}{2} cup flour
	\\ 1 cup brown sugar	
	\\ 1 tsp vanilla
	\\ 2 Tbsp cocoa	
	\\ 1 egg
	\\ \nicefrac{3}{4} cup walnuts
	\stepspace   ICING:\\
1\nicefrac{1}{2} cups icing sugar \\
	2 Tbsp butter\\
	3 Tbsp cocoa\\
	cream or milk to moisten}{Melt butter, add sugar, egg and vanilla. Beat well, then add dry ingredients. Bake at 350$^\circ$F for 20 to 25 minutes and ice with chocolate butter frosting while cake is still warm.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TRIPLE CHOCOLATE CAKE} \index{TRIPLE CHOCOLATE CAKE}
\step{2 \nicefrac{1}{2} cups cake flour	
	\\ \nicefrac{1}{3} cup unsweetened cocoa
	\\ 1 tsp baking soda	
	\\ \nicefrac{1}{2} tsp salt
	\\ 1 cup butter	
	\\ 2 cups sugar
	\\ 3 eggs	
	\\ 1 tsp vanilla
	\\ 1 \nicefrac{1}{3} cups water
	\stepspace  GLAZE:\\
1 cup sugar	
	\\ \nicefrac{1}{2} cup unsweetened cocoa
	\\ \nicefrac{1}{4} cup heavy cream	
	\\ \nicefrac{1}{4} cup water}{Bake at 350${}^\circ$F in 2 9" pans for 30-35 minutes. When cool, cut each layer horizontally to give 4 layers. Spread each layer with apricot jam (10 oz jar needed) and chocolate butter cream (use Whipped Butter Cream Icing in icing section).\par
	GLAZE:Cook over low heat, stirring until smooth. Bring to boil. Boil for 1 minute. Cool slightly. Pour glaze over cake. Refrigerate. Garnish with whipped cream.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE CAKE WITH SEMI-SWEET CHOCOLATE ICING (GF)} \index{CHOCOLATE CAKE WITH SEMI-SWEET CHOCOLATE ICING (GF)} \index{Gluten Free!cakes}
\step{\nicefrac{1}{2} cup sorghum flour
\\ \nicefrac{1}{2} cup tapioca flour
\\ \nicefrac{1}{2} cup rice flour
\\ 1 cup cocoa powder
\\ 1 \nicefrac{1}{2} tsp xanthan gum
\\ 2 \nicefrac{1}{2} tsps. Baking powder
\\ 1 tsp baking soda
\\ \nicefrac{3}{4} cup butter, room temp
\\ \nicefrac{3}{4} cup dark brown sugar
\\ 1 cup white sugar
\\ 3 eggs
\\ 2 egg yolks
\\ 2 tsp vanilla extract
\\ 1 \nicefrac{1}{2} cups buttermilk or yoghurt
\\ 5 oz chocolate chips
\\ \nicefrac{1}{2} cups sour cream
\\ \nicefrac{1}{2} tsp vanilla extract
\\ 1 Tbsp heavy cream}{Preheat oven to 350${}^\circ$F. Grease a $9 \times 13$" inch pan.
In a medium bowl sift together the flours, cocoa powder, xanthan gum, baking powder and baking soda. In a large mixer bowl cream the butter until light and fluffy. Slowly beat in the brown and white sugars; whip until fluffy. Beat in the eggs and egg yolks one at a time. Add the vanilla. On low speed, alternately combine the buttermilk with the flour mixture. Pour batter into prepared pan. Bake for 30-35 minutes.
To make the icing, melt the chocolate chips in the microwave. Cool until warm. Stir in the sour cream and vanilla. Add the cream. Stir in additional cream for desired consistency.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WACKY CAKE} \index{WACKY CAKE}
	\step{3 cups flour	
	\\ 2 cups sugar
	\\ 1 tsp salt	
	\\ 6 Tbsp cocoa
	\\ 2 tsp soda	
	\\ \nicefrac{1}{2} cup oil + 2 Tbsp
	\\ 2 Tbsp vinegar	
	\\ 2 tsp vanilla
	\\ 2 cups water}
{Bake at 350$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ITALIAN SPONGE CAKE} \index{ITALIAN SPONGE CAKE}
\step{\nicefrac{1}{2} cup + 1 \nicefrac{1}{2} Tbsp sugar \\
4 extra large eggs, room temperature \\
Pinch of salt \\
1 tsp grated lemon zest or vanilla extract, optional \\
1 cup + 1 Tbsp flour, sifted}{Butter and flour an 8" round pan. Beat eggs, sugar, salt and lemon zest until very fluffy and pale yellow, about 15--20 minutes.  To test, let small amount of batter fall into the bowl. If it remains ``sitting'' on top, it's ready. Sift flour on top of egg mixture, a little at a time, and fold in gently with a wooden spoon. Pour batter into prepared pan. Don't smooth the top or bang the pan on the counter. Leave it as is! Bake for 40 minutes or until a toothpick inserted in the center comes out clean. Do not open the oven for the first 30 minutes. Turn off the oven but leave cake inside for 5 to 10 minutes. Keep door slightly open using a wooden spoon. Remove sponge cake from oven. Let cool for 10 more minutes, then loosen around the edges with a knife and flip it onto a wire rack upside down (without the pan) to cool completely. 
Note:  For Chocolate Sponge omit flavouring.  Decrease flour by 2 Tbsp and add 3 Tbsp cocoa.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GENOISE FRENCH SPONGE LAYERS FOR TORTES} \index{GENOISE FRENCH SPONGE LAYERS FOR TORTES}
\name{This is a perfect base for many cake desserts, plain or fancy. Use it and your imagination to make extraordinary sweets.}\\
\step{1 cup sugar	
\\ \nicefrac{1}{4} butter
\\ 6 eggs
\\ 1 cup flour}{Put unbroken eggs in a bowl and cover with hot tap water. Let stand until water is lukewarm. Drain and repeat once again. Don't use boiling water---you are just warming the eggs, not cooking them. Grease two $9$" layer cake pans and line bottoms with waxed paper. Heat oven to 350${}^\circ$F. Warm large mixer bowl with hot tap water. Dry bowl, then break warm eggs into bowl. Add sugar and beat at high speed until mixture stands in peaks, about 20 minutes. Melt butter and cool. to lukewarm. Sprinkle 2 Tbsp flour over egg mixture and fold in gently but quickly with a rubber scraper. Repeat until all flour is added. Sprinkle butter, 1 tsp at a time, over the batter, folding gently but quickly after each addition. Speed is important here. Turn the batter into prepared pans and bake 25 to 30 minutes or until tops spring back when touched in the middle. Cool 10 minutes, then loosen cakes carefully around the sides and turn out on rack to finish cooling. Peel off paper carefully while cake is still warm.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BANANA TORTE} \index{BANANA TORTE}
\step{2 French Sponge layer cakes
\\ \nicefrac{1}{3} cup sugar	
\\ 1 \nicefrac{1}{2} Tbsp cornstarch
\\ pinch salt	
\\ 2 eggs
\\ 1 \nicefrac{1}{2} cups milk	
\\ 2 tsp grated lemon rind
\\ \nicefrac{1}{4} tsp vanilla extract	
\\ 2 \nicefrac{1}{2} med. bananas
\\ 1 Tbsp lemon juice
\stepspace BANANA BUTTER ICING:
\\ 3 cups icing sugar	
\\ \nicefrac{1}{3} cup soft butter
\\ \nicefrac{1}{2} banana, mashed
\\ \nicefrac{1}{2} tsp vanilla
\\ light cream}{Mix sugar, cornstarch and salt in med. saucepan. Add eggs and beat well. Stir in milk. Set over high heat and cook, stirring constantly, until thick and smooth, reducing heat to med. as mixture begins to thicken. turn heat to low and continue stirring 3 minutes. Remove from heat, stir in lemon rind and vanilla. Cover tightly and chill well. Peel and slice bananas and sprinkle the slices with lemon juice. Split each cake layer into 2 thin layers. Put lemon filling and some of the banana slices between the layers, saving a few banana slices for garnish. Ice the whole outside of the cake with Banana Butter Icing and garnish with remaining banana slices or an edible flower.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ORANGE RUM TORTE} \index{ORANGE RUM TORTE}
\step{uncooked batter for French Sponge Layers (see above recipe)
\\ 1 Tbsp grated orange rind	
\\ 6 Tbsp light rum
\\ 2 tsp unflavoured gelatin	
\\ 2 Tbsp cold water
\\ 2 cups whipping cream	
\\ \nicefrac{1}{2} cup icing sugar
\\ \nicefrac{1}{4} cup light rum
\stepspace  ORANGE BUTTER ICING:
\\ 3 cups icing sugar	
\\ 1 cup soft butter
\\ 2 Tbsp grated orange rind	
\\ 2 Tbsp orange juice (approx.)}{Make French Sponge batter, folding in grated orange rind along with the butter. Bake and cool as directed in recipe. Split each layer into 2 thin layers and sprinkle each layer with 1 \nicefrac{1}{2} Tbsp rum. Soak gelatin in cold water 5 minutes, then set dish in simmer water and heat until gelatin is dissolved. Cool slightly. Whip cream and icing sugar in a well chilled bowl until beginning to thicken and continue beating while adding \nicefrac{1}{4} cup rum and gelatin mixture. Beat until stiff. Spread this mixture between the layers. Chill for a few minutes. Spread whole outside of torte with Orange butter icing and garnish top edge with more grated orange rind or orange sections, if desired. Chill.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PERSIAN ORANGE TORTE WITH CREAM CHEESE FROSTING (GF)} \index{PERSIAN ORANGE TORTE WITH CREAM CHEESE FROSTING (GF)} \index{Gluten Free!cakes}
\step{2 large navel oranges
\\ 250 g. slices almonds
\\ 250 g sugar
\\ 1 tsp baking powder
\\ Pinch of salt
\\ 6 large eggs
\stepspace FROSTING:
\\ 180 g cream cheese, divided and softened
\\ 90 g unsalted butter, softened
\\ 90 g icing sugar
\\ 1 tsp lemon juice
\stepspace  GARNISH:
\\ 4 dried orange slices, snap in half
\\ 2 black mission figs, quartered
\\ Handful of cubed quince paste
\\ 2 Tbsp chopped pistachios
\\ 2 Tbsp dried rose petals}{Place oranges in med saucepan.  Cover with water. Bring to boil, then simmer for 2 hours until soft. Cool to room temp. You can do this ahead of time and store the boiled oranges covered with cooking liquid in the fridge. Preheat oven to 375${}^\circ$F. Line a 7" round cake pan with parchment. You can also use an 8" spring form cake pan and wrap the exterior with foil to prevent leakage during baking. Place almond, sugar, baking powder and salt in food processor. Pulse until nuts turn floury. Empty to a large bowl and set aside. Lightly squeeze boiled oranges free of excess water and blend until smooth. Add beaten eggs and almond meal mixture to food processor. Blend until homogenous. Pour batter into cake pan. Set on top of a baking sheet and bake at least an hour, until cake tester comes out with only a few moist crumbs. (recipe notes say it could take up to 105 min).\\
Place 90 g cream cheese and butter in bowl and beat at med speed until smooth. Beat in icing sugar and lemon juice. Add remaining cream cheese and beat until fluffy. Spread a thick layer of cream cheese frosting on top of cake. Smooth to even thickness and make attractive swirls.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WALNUT OR HAZELNUT TORTE} \index{WALNUT OR HAZELNUT TORTE}
\step{3 cups ground walnuts or skinned, toasted hazel nuts, lightly packed (about 350 grams)
\\ 1 \nicefrac{1}{4} cups sugar	
\\ 6 eggs
\\ \nicefrac{1}{4} cup fine dry bread crumbs	
\\ 1 tsp baking powder
\\ 2 tsp grated lemon rind	
\\ pinch salt
\\ 2 tsp unflavoured gelatin	
\\ 2 Tbsp cold water
\\ 2 cups whipping cream	
\\ \nicefrac{1}{2} cup icing sugar
\\ \nicefrac{1}{2} tsp almond extract	
\\ \nicefrac{1}{2} tsp vanilla extract
\\ \nicefrac{1}{3} cup cherry jam	walnut halves}{Grease three 8" cake pans and line bottoms with waxed paper. Separate eggs. Beat egg whites until soft peaks form, then beat in \nicefrac{1}{2} cup of the sugar gradually. Beat until stiff. Beat egg yolks, beating in remaining sugar gradually and continue beating at high speed until thick and light coloured. Stir in the 1 \nicefrac{1}{2} cup nuts, bread crumbs, baking powder, lemon rind, salt and about \nicefrac{1}{4} of the egg white mixture. Fold this mixture gently but quickly back into the remaining egg whites. Turn into pans and bake at 350${}^{\circ}$F about 20 minutes or until tops spring back when lightly touched. Cool slightly in pans, then turn out on racks. Combine gelatin and cold water in a small dish and let stand 5 minutes. Set in a pan of simmering water and heat until gelatin dissolves. Cool slightly. Whip cream and icing sugar until soft peaks form. Beat in almond extract and vanilla and drizzle in the gelatin, beating until stiff. Put about half of the whipped cream into another bowl and fold in \nicefrac{3}{4} cup ground nuts. Spread this mixture between the cake layers. Ice the sides and 1" rim on top with the remaining plain whipped cream. Spread the cherry jam in the centre of the top of the torte and decorate whipped cream border with nut halves. Press remaining \nicefrac{3}{4} cup ground nuts lightly into the cream on the sides of the cake. Chill several hours.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GAZEBO HAZELNUT TORTE} \index{GAZEBO HAZELNUT TORTE}
\step{5 eggs, separate	
\\ \nicefrac{3}{4} cup sugar
\\ \nicefrac{1}{2} cup hazelnuts	
\\ \nicefrac{1}{4} cup butter
\\ \nicefrac{1}{2} cup icing sugar	
\\ 1 sq. unsweetened chocolate, melted
\\ 2 cups icing sugar	
\\ 4 sq. unsweetened chocolate, melted
\\ 1 Tbsp hazelnut chocolate spread}{Grease two 7" layer cake tins and line the bottoms with waxed paper. Beat egg yolks and sugar until thick and creamy. Beat egg whites until they form stiff peaks. Fold the ground hazelnuts and egg whites into egg yolk mixture. divide between the two prepared pans and bake at 350${}^\circ$F for 30 minutes. Leave for 10 minutes before removing to racks to cool. Cream butter and icing sugar. Add 1 sq. of melted chocolate. Spread this over one of the take layers and place the other layer on top. Mix remaining icing sugar, melted chocolate and hazelnut chocolate spread. Add enough water to make it of spreading consistency. Ice top and sides of layered cake. This recipe freezes well when iced. It takes 1 hour at room temperature to defrost.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SACHER TORTE} \index{SACHER TORTE}
\name{(Note:  Ruth Stalder's Swiss cookbook has 8 egg yolks and 10 egg whites)\\
(Company's Coming)}\\
\step{\nicefrac{1}{2} cup butter	
\\ \nicefrac{3}{4} cup sugar
\\ 1 cup semisweet choc chips, melted	
\\ 1 tsp vanilla
\\ 6 egg yolks	
\\ \nicefrac{3}{4} cup flour
\\ 7 egg whites, room temperature
\stepspace TOPPING:
\\ 4 Tbsp apricot jam, sieved	
\\ \nicefrac{1}{2} cup semisweet chocolate chips
\\ 2 Tbsp evaporated milk}{Cream butter and sugar together. Slowly beat in melted chocolate and vanilla. Add egg yolks, one at a time, beating after each addition. Stir in flour. Beat egg whites until stiff. Fold into batter. Spoon into a greased 9" round layer pan. Bake at 350${}^\circ$F for about 35 minutes. Cool 10 minutes. turn cake out on rack. Cool. Place on flat plate, round side up. Glaze with apricot jam and icing. Cake may be sliced into 2 layers. In that case, increase jam to 6 Tbsp and spread between layers, on top layer and sides. Glaze with chocolate. Spread jam over top of cake. Melt chips and milk in saucepan over medium heat. Cool to lukewarm. Spread over top and sides of cake.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SCHMOO TORTE} \index{SCHMOO TORTE}
\name{A scrumptious dessert from the Jewish community of Winnipeg.}\\
\step{CAKE: \\
12 large egg whites, room temperature \\
Pinch of salt \\
1 tsp cream of tartar \\
1 \nicefrac{1}{3} cups white sugar \\
1 tsp vanilla extract \\
1 cup flour \\
1 cup pecan flour, sifted at least twice \\
1 tsp baking powder 
\stepspace FROSTING: \\
2 cups heavy whipping cream, chilled \\
3 Tbsp icing sugar \\
1 tsp vanilla extract
\stepspace CARAMEL SAUCE: \\
\nicefrac{1}{2} cup butter \\
1 \nicefrac{1}{2} cups brown sugar \\
\nicefrac{1}{2} cup whipping cream \\
1 tsp vanilla extract \\
24--36 pecans for garnish}{Whip egg whites, salt and cream of tartar on low speed until stiff peaks form. Turn mixer to medium speed and add vanilla and sugar, adding half the sugar at a time, just until combined. In a separate bowl, sift together pecan flour, flour and baking powder to remove any large pieces of pecans. Fold in the pecan mixture in two or three additions. Scrape batter into an Angel Food Cake pan and bake at 350${}^{\circ}$F for 35--40 minutes or until toothpick inserted in center comes out clean. Cool upside-down until completely cool and slice into three layers with a serrated knife. \par
FROSTING: Whip all three ingredients on high speed until stiff peaks form. \par
CARAMEL SAUCE: Melt butter over medium heat. Add sugar and whipping cream, whisking until smooth and mixture reaches a boil. Boil 2 minutes. Add vanilla and remove from heat. Cool.\par
ASSEMBLY: Place bottom layer on cake plate. Fill hole with whipped cream. Pipe cream around outer edge. Pour \nicefrac{1}{4} cup sauce inside border. Repeat layers. Spread remaining cream over outside of cake. Top with pecans and drizzle caramel sauce over cake. Cake can be stored in fridge up to a few hours before serving.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE ALMOND TORTE (GF)} \index{CHOCOLATE ALMOND TORTE (GF)} \index{Gluten Free!cakes}
\name{(Jackie Buhler)} \\
\step{1 cup whole almonds, toasted 	\\
	2 Tbsp sugar\\
	2 Tbsp vegetable oil\\
	\nicefrac{3}{4} cup butter\\
	\nicefrac{1}{2} cup whipping cream\\	
	4 x 4 oz bittersweet or semisweet chocolate bars, finely chopped\\
	6 large eggs, separated	\\
	\nicefrac{1}{3} cup sugar\\
	1 cup whipping cream	\\
	2 Tbsp sugar\\
	3 Tbsp almond liqueur}{
Butter and flour a 9" springform pan. Line with wax paper, butter paper.
Process \nicefrac{1}{2} cup whole almonds and 2 Tbsp sugar in a food processor until ground. Spoon into a bowl. Set aside.
Process remaining \nicefrac{1}{2} cup whole almonds and oil in a food processor 3 minutes or until a thick paste forms, stopping often to scrape down sides. Bring butter and whipping cream to a boil in a heavy saucepan over med heat. Remove from heat and whisk in chocolate until smooth. Stir in almond mixtures. Cool slightly.
Beat egg whites at high speed until foamy. Add \nicefrac{1}{3} cup sugar, 1 Tbsp at a time, beating until stiff peaks form and sugar dissolves.
Beat egg  yolks until thick and pale. Gradually add chocolate mixture to yolks, beating until blended. Fold in one-third of egg whites. Gradually fold in remaining egg whites. Pour batter into pan.
Bake at 350${}^\circ$F for 35 minutes or until almost set. Cool on wire rack. Run a sharp knife around edges to loosen. Remove sides of pan. Cover and chill up to 3 days. Beat cream at medium speed until foamy. Gradually adding 2 Tbsp sugar, beat until soft peaks form. Stir in liqueur. Serve with torte.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE CHIP DATE CAKE} \index{CHOCOLATE CHIP DATE CAKE}
\name{(Mary Kennedy)} \\
\step{1 cup dates, cut up	
	\\ 1 cup boiling water
	\\ 1 tsp baking soda
	\\ 1 cup shortening	
	\\ 2 cups sifted flour
	\\ 1 cup sugar	
	\\ 2 Tbsp cocoa
	\\ \nicefrac{1}{2} tsp salt	
	\\ 2 eggs
	\\ 1 tsp vanilla	
	\\ 1 cup chocolate chips
	\\ \nicefrac{1}{2} cup chopped walnuts}{Pour boiling water over dates. Let cool. Add soda. Cream shortening. Add sugar., eggs and vanilla. Beat well. Add cooled date mixture, then flour mixture. Fold in chocolate chips and nuts. Bake in 350${}^\circ$F oven for 45 minutes. cool in pan 10--15 minutes then turn out on to a wire rack. Sprinkle with icing sugar or ice with a chocolate icing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RICH ALMOND CAKE} \index{RICH ALMOND CAKE}
\name{Excellent choice from Favourite Teatime Recipes, a book given to me by Maud Kells, WEC missionary from Northern Ireland, working in Mulita, DRC}\\
\step{4 oz butter	
	\\ 5 oz caster sugar
	\\ 3 eggs	
	\\ 3 oz ground almonds
	\\ 1 \nicefrac{1}{2} oz plain flour	
	\\ 2 drops almond essence}{Grease and line a 7" deep cake tin. Set oven to 350$^\circ$F. Soften butter and add sugar gradually, beating well. Add eggs one at a time with one third of the almonds with each. Fold in well sieved flour and essence. Bake 40-45 minutes. When cool, dust with caster sugar.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MAPLE WALNUT CHIFFON CAKE} \index{MAPLE WALNUT CHIFFON CAKE}
\step{1 \nicefrac{2}{3} cups flour	
\\ \nicefrac{1}{2} cup oil
\\ 3 tsp baking powder	
\\ 5 egg yolks
\\ 1 tsp salt	
\\ \nicefrac{3}{4} cup water
\\ 1 cup finely chopped walnuts	
\\ 1 tsp vanilla
\\ \nicefrac{1}{2} tsp cream of tartar	
\\ \nicefrac{1}{4} tsp maple flavouring
\\ 1 cup egg whites	
\\ 1 \nicefrac{1}{2} cups sugar}{Sift dry ingredients into bowl and make a well in center. Add in this order without mixing:  oil, egg yolks, water, vanilla, maple, stir to mix and beat until smooth. Stir in walnuts. Measure into a large bowl 1 cup egg whites, sprinkle with cream of tartar and beat until very stiff. Add batter to egg whites, one quarter at a time, folding in gently. Bake at 350${}^\circ$F for one hour.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{POPPYSEED CAKE} \index{POPPYSEED CAKE}
\name{(Liz from Winnipeg Book Club)}\\
\step{\nicefrac{1}{2} cup poppy seeds
\\ 1 cup buttermilk OR almond milk plus 1 Tbsp lemon juice to equal 1 cup
\\ 1 cup margarine or butter, cut in chunks
\\ 1 \nicefrac{1}{2} cups sugar
\\ 4 eggs
\\ 2 tsp vanilla extract
\\ 2 \nicefrac{1}{2} cups flour
\\ 2 tsp baking powder
\\ 1 tsp baking soda}{Soak poppy seeds in buttermilk for at least \nicefrac{1}{2} hour. Combine margarine, sugar, eggs and vanilla extract for 2 minutes. Add poppy seed/milk mixture. Blend. Add remaining ingredients and beat. Pour batter into sprayed 12 cup fluted tube pan or bundt pan. Bake for 50-60 minutes at 350${}^\circ$F, until cake tests done. Cool for 15 minutes before removing from pan.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MANGO UPSIDE-DOWN CAKE} \index{MANGO UPSIDE-DOWN CAKE}
\step{2 cups mangoes
\\ 2 Tbsp lemon juice
\\ 1 Tbsp butter
\\ \nicefrac{1}{3} cup brown sugar
\\ \nicefrac{1}{4} cup shortening	
\\ \nicefrac{3}{4} cup sugar
\\ 1 egg
\\ 1 \nicefrac{1}{4} cup flour	
\\ 2 tsp baking powder
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{2} cup milk}{Slice mangoes. Pour lemon juice over sliced mangoes and let stand for 15 minutes. Melt butter in an 8" pan and add brown sugar and mangoes. Cream shortening and sugar. Add egg and sift in dry ingredients. Add alternately with milk. Pour over the mangoes. Bake 50--60 minutes at 375${}^\circ$F. When cake is done, turn it upside down and serve while still warm with whipped cream.
OPT: Use fresh pineapple instead of mangoes and add \nicefrac{1}{2} tsp salt.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MOTHER'S LEMON CAKE} \index{MOTHER'S LEMON CAKE} 
\step{1 pkg. yellow cake mix	
\\ 4 eggs
\\ 1 pkg. lemon instant pudding (jelly powder works too)
\\ \nicefrac{3}{4} cup water	
\\ \nicefrac{3}{4} cup oil}{Mix well and bake 45 minutes at 325${}^\circ$F. Prick with fork while hot and ice with 2 cups icing sugar and juice of 3 lemons.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RASPBERRY LEMON CAKE (GF)} \index{RASPBERRY LEMON CAKE (GF)} \index{Gluten Free!cakes}
\name{(Jo Johnson)\\
Jo made this for us when we stayed with them in High Wycombe, England. I soon found out that its popularity was similar carrot cake in Canada. A popular variation was orange rather than lemon. See Persian Orange Torte.}\\
\step{150 ml olive oil
\\ Zest and juice of 1 lemon
\\ \nicefrac{1}{2} cup sugar
\\ 1 \nicefrac{2}{3} cup ground almonds
\\ \nicefrac{1}{2} cup polenta (cornmeal)
\\ \nicefrac{1}{2} tsp baking soda
\\ 1 tsp baking powder
\\ 3 large eggs
\\ 150 g frozen raspberries (do not thaw)}{Beat oil and lemon zest together. Add sugar. In a separate bowl, combine ground almonds, polenta, baking soda and baking powder. Add a spoonful of oil and sugar to mixture. Add 1 egg. Add \nicefrac{1}{3} of almond and polenta mixture. Continue this way until all has been incorporated. Fold in frozen raspberries. Bake in a square cake pan at 350${}^\circ$F for 40 minutes.  Remove cake from oven and pour or brush lemon juice on top. Serve the cake warm.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RASPBERRY LEMON CREAM CAKE} \index{RASPBERRY LEMON CREAM CAKE}
\name{I made this for Priscilla's bridal shower.}\\
\step{SPONGE CAKE: \\
6 eggs \\
1 cup sugar \\
1 Tbsp grated lemon rind \\
1 tsp vanilla \\
1 cup flour \\
\nicefrac{1}{2} tsp baking powder \\
Pinch salt \\
\nicefrac{1}{3} cup melted butter 
\stepspace LEMON CREAM: \\
1 pkg gelatin \\
3 eggs \\
2 egg yolks \\
1 \nicefrac{1}{4} cup granulated sugar \\
1 Tbsp grated lemon rind \\
\nicefrac{2}{3} cups lemon juice \\
1 \nicefrac{1}{3} cup whipping cream \\
2 \nicefrac{1}{3} cups raspberries
\stepspace  TOPPING: \\
\nicefrac{2}{3} cup raspberries \\
1 Tbsp icing sugar}{Line 10" springform pan with parchment paper. Grease sides.
Set eggs in warm water for 5 minutes. Beat eggs until foamy. Gradually beat in sugar until pale yellow, about 10 minutes. Fold in lemon rind and vanilla. Sift together flour, baking powder and salt. Fold one-third into egg mixture.  Repeat twice. Fold in butter. Pour into pan. Bake at 325${}^{\circ}$F for 45--50 minutes. Remove sides of pan and cool.\par
LEMON CREAM: Sprinkle gelatin over 3 Tbsp water. In double boiler, whisk together next 5 ingredients. Cook, stirring frequently, until translucent and thick enough to softly mound on spoon, about 20 minutes. Strain into bowl. Stir in gelatin mixture until melted. Place plastic wrap directly on surface and refrigerate, stirring every 10 minutes, until cool and mixture mounds on spoon, about 1 hour. Beat cream. Fold one-third into lemon mixture. Fold in remaining cream. Fold in 2 \nicefrac{1}{3} cups raspberries.\par
TOPPING: Line bottom and side of same pan with waxed or parchment paper. Cut cake horizontally into thirds. Place top cake layer, cut side up, in pan. Spread with half of lemon cream. Top with middle cake layer, remaining lemon cream and remaining cake layer, cut side down. Refrigerate until set, about 4 hrs. Sprinkle top with icing sugar. Arrange remaining raspberries around top edge.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ORANGE COCONUT CAKE} \index{ORANGE COCONUT CAKE}
\step{2 cups sugar	
\\ 3 eggs
\\ \nicefrac{1}{2} cup butter	
\\ 2 cups flour
\\ 2 tsp baking powder	
\\ 1 orange, pulp \& juice
\\ \nicefrac{1}{2} cup coconut, add milk to make 1 cup}{Cream sugar, butter and eggs. Add dry ingredients alternately with sweet milk and coconut mixture. Add orange and mix well. Bake at 350${}^\circ$F for 35 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ZUCCHINI CAKE} \index{ZUCCHINI CAKE}
\step{\nicefrac{1}{2} cup margarine	
\\ \nicefrac{1}{2} cup oil
\\ 1 \nicefrac{1}{3} cup sugar	
\\ 2 eggs
\\ 1 tsp vanilla	
\\ \nicefrac{1}{2} cup sour milk (add 1 tsp lemon juice)
\\ 2 \nicefrac{1}{2} cup flour	
\\ 4 Tbsp cocoa
\\ \nicefrac{1}{2} tsp baking powder	
\\ 1 tsp soda
\\ \nicefrac{1}{2} tsp cinnamon	
\\ \nicefrac{1}{2} tsp cloves
\\ 2 cups zucchini	
\\ \nicefrac{1}{4} cup chocolate chips}{Cream margarine, oil and sugar. Add eggs, vanilla and sour milk. Mix together all dry ingredients and add to creamed mixture. Beat well. Stir in diced zucchini. Spoon batter into greased and floured 9 x 12 pan. Sprinkle top with chocolate chips. Bake at 325${}^\circ$F for 40-45 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CARROT CINNAMON CAKE} \index{CARROT CINNAMON CAKE}
\step{2 cups flour (whole wheat can be used)	
\\ 1 \nicefrac{1}{2} tsp baking soda
\\ 2 \nicefrac{1}{2} tsp baking powder	
\\ 1 tsp salt
\\ 4 tsp cinnamon	
\\ 1 \nicefrac{1}{3} cups brown sugar
\\ 2 cups carrots, grated	
\\ 4 eggs
\\ \nicefrac{1}{2} tsp vanilla
\\ 1 \nicefrac{1}{2} cups crushed pineapple, drained	
\\ 1 cup vegetable oil
\\ 1 cup nuts	
\\ 1 cup raisins}{Mix all dry ingredients. In a separate bowl, beat eggs well. Add vegetable oil and beat again. Add pineapple, carrots. Add liquid mixture. Mix and add nuts and raisins. Pour in a greased tube pan. Optional: Replace pineapple with additional cup of carrots.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CARROT CAKE AND CREAM CHEESE FROSTING} \index{CARROT CAKE AND CREAM CHEESE FROSTING}
\step{1 \nicefrac{1}{2} cups sugar	
\\ 1 tsp baking soda
\\ 1 cup oil	
\\ 1 tsp vanilla
\\ 3 eggs	
\\ \nicefrac{1}{2} tsp salt
\\ 2 cups flour	
\\ \nicefrac{1}{4} tsp nutmeg
\\ 1 \nicefrac{1}{2} tsp cinnamon	
\\ 3 cups grated carrots
\stepspace FROSTING:
\\ 500 g cream cheese	
\\ 1 Tbsp milk
\\ 1 tsp vanilla	
\\ 2 \nicefrac{1}{2} -- 3 cups icing sugar}{Cream together sugar, oil and eggs for 1 minute. Stir in remaining ingredients except for the carrots and beat for one more minute. Stir in carrots. Bake at 180${}^\circ$C for 35-45 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SOUR CREAM COFFEE CAKE} \index{SOUR CREAM COFFEE CAKE}
\name{(Company's Coming)}\\
\step{\nicefrac{1}{2} cup butter or margarine	
\\ 1 cup sugar
\\ 2 eggs	
\\ 1 tsp baking soda
\\ 1 cup sour cream	
\\ 1 \nicefrac{1}{2} cups flour
\\ 1 \nicefrac{1}{2} tsp baking powder	
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{2} cup packed brown sugar	
\\ 1 tsp cinnamon
\\ \nicefrac{1}{2} cup finely chopped nuts}{Cream butter, sugar and 1 egg together. Beat in second egg. Add soda and sour cream.
Mix flour, baking powder and salt together. Add to batter. Stir to mix. Put one half batter in creased $9\times9$" pan. Mix brown sugar, cinnamon and nuts together. Sprinkle one half over batter. Spoon second half of batter here and there over top. Sprinkle second half of cinnamon mixture over all. Bake in 350${}^\circ$F oven for 45 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRANBERRY COFFEE CAKE} \index{CRANBERRY COFFEE CAKE}
\step{2 cups flour	
\\ \nicefrac{1}{2} cup sugar
\\ 3 tsp baking powder	
\\ \nicefrac{1}{2} tsp salt
\\ 2 eggs	
\\ \nicefrac{1}{4} cup oil
\\ \nicefrac{3}{4} cup milk	
\\ 1 cup cranberries, fresh or frozen
\stepspace  TOPPING:
\\ \nicefrac{1}{3} cup flour	
\\ \nicefrac{1}{3} cup brown sugar
\\ \nicefrac{1}{4} cup butter or margarine	
\\ 1 tsp cinnamon}{Mix flour, sugar, baking powder and salt together in mixing bowl. In another bowl, beat eggs until frothy. Mix in oil and milk. Pour into dry ingredients. Mix together. Fold in cranberries. Scrape into greased 9" tube pan.\par
TOPPING: Mix ingredients. Sprinkle over top of batter. Bake in 350${}^\circ$F oven for 50--60 minutes or until it begins to shrink away from sides of pan. Cool about 30 minutes before removing from pan. Turn right side up.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APPLE COFFEE CAKE} \index{APPLE COFFEE CAKE}
\step{1 \nicefrac{1}{3} cups flour	
\\ \nicefrac{3}{4} cups sugar
\\ 3 tsp baking powder	
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{4} cup butter	
\\ 1 egg, beaten
\\ \nicefrac{3}{4} cup milk	
\\ 1 tsp vanilla
\\ 2 apples, peeled and sliced
\stepspace  TOPPING: 
\\ \nicefrac{1}{3} cup packed brown sugar
\\ \nicefrac{1}{2} tsp cinnamon}{Put flour, sugar, baking powder and salt in large bowl. Cut or rub in butter until crumbly. Make a well in the center. In another bowl beat egg until frothy. Mix in milk and vanilla. Pour into well. Stir just enough to moisten. Pour into greased $8 \times 8$" pan. Push apples well into batter close together. Sprinkle topping over batter. Bake at 350${}^\circ$F for 50--60 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{JELLY ROLL} \index{JELLY ROLL} 
\step{4 eggs, separated (room temp)
\\ 1 cup sugar
\\ 1 cup flour
\\ \nicefrac{1}{4} cup water
\\ 1 tsp vanilla
\\ \nicefrac{1}{4} tsp salt
\\ 2 tsp baking powder
\\ icing sugar}{Beat egg yolks until creamy yellow.  Slowly add sugar. Add vanilla and water. Set aside. Beat egg whites until soft peaks form. Fold egg whites into egg yolks. Sift together flour, baking powder and salt. Fold dry ingredients into eggs, \nicefrac{1}{4} cup at a time.  Line $10 \times 15$" pan with wax paper. Pour batter into pan. Bake at 400${}^{\circ}$F for 12 minutes. Sift icing sugar on damp towel. Turn cake out onto towel. Peel off wax paper. Roll cake tightly from narrow end with towel and cake together.  Cool.  Unroll, fill with favourite filling (e.g. lemon pie filling, chocolate filling, jelly).  Reroll and slice.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SWISS ROLL} \index{SWISS ROLL}
\name{(Christine Stalder, Priscilla's Swiss friend)}\\
\step{Jelly Roll Recipe
\stepspace 	FILLING: 
\\ \nicefrac{1}{4} cup	soft butter 
\\ \nicefrac{2}{3} cup icing sugar
\\ 2 Tbsp coffee liquid (or less)}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SELF-FILLED CUPCAKES} \index{SELF-FILLED CUPCAKES}
\name{(Martha Kroeker)}\\
\step{Chocolate cake mix (or mix a chocolate cake from scratch)
\\ 1 pkg. (8 oz.) cream cheese	
\\ \nicefrac{1}{3} cup sugar
\\ salt	
\\ 1 egg
\\ chocolate chips (16 oz.)}{Combine ingredients for filling. Fill cupcake liners \nicefrac{1}{3} full with cake batter. Place 1 tsp filling on each cupcake. Add batter to cupcake to make it \nicefrac{2}{3} full. Bake.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{EASY SPICE CAKE} \index{EASY SPICE CAKE}
\step{1 cup sugar	
\\ 1 egg
\\ \nicefrac{1}{2} cup margarine	
\\ 1 cup sour milk
\\ 2 cups flour	
\\ a pinch of salt
\\ 1 tsp baking soda	
\\ 1 tsp baking powder
\\ 1 tsp cinnamon	
\\ \nicefrac{1}{2} tsp ground cloves
\\ \nicefrac{1}{2} tsp nutmeg}{Bake at 180${}^\circ$C for 20--25 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHRISTMAS CAKE} \index{CHRISTMAS CAKE}
\name{(Great Aunt Elizabeth Toews)}\\
\step{3 lb. raisins (1350 grams)	
\\ 2 cups flour
\\ 1 \nicefrac{1}{2} l lb. figs (650 grams)	
\\ 1 lb. butter
\\ 1 lb. mixed peel (450 grams)	
\\ 1 lb. brown sugar
\\ 1 lb. glazed cherries (450 g)	
\\ 10 eggs
\\ 1 lb. walnuts}{Soak fruit and nuts overnight in 10 oz brandy. Prepare and mix fruit; cover with about 1 cup flour. Prepare batter. Add fruit. Bake in very slow oven with a pan of water in the oven.}
\end{minipage}

\section{Cheesecakes}

\begin{minipage}{\linewidth}\rtitle{TIRAMISU CHEESECAKE} \index{TIRAMISU CHEESECAKE}
\name{(Yvonne Hiebert)}\\
\step{CRUST:
\\ 1 \nicefrac{3}{4} cups finely crushed chocolate wafers or ginger biscuits
\\ 3 Tbsp butter or margarine, melted
\stepspace FILLING:
\\ 2 tsp instant espresso coffee powder (regular instant coffee can be substituted)
\\ 2 Tbsp brandy or milk	
\\ 3  8 oz pkgs cream cheese
\\ 1 cup sugar	
\\ 1 Tbsp cornstarch
\\ 1 tsp vanilla	
\\ 3 eggs
\\ 1  8 oz carton dairy sour cream	
\\ 1 envelope vanilla sugar
\stepspace TOPPING:
\\ \nicefrac{1}{4} to 2 \nicefrac{1}{2} tsp unsweetened cocoa powder
\\ shaved semisweet chocolate}{CRUST:  combine crushed wafers and melted butter. Press evenly on bottom of 9" spring form pan and part way up the sides. \par
FILLING: Beat cream cheese until smooth. Gradually add sugar, beating on med to high speed until smooth. Beat in cornstarch and vanilla. Add eggs one at a time. Beat. Spread half the mixture in prepared pan. Set aside.
Stir coffee mixture into remaining cheese mixture; carefully spoon and spread over layer in pan. Place pan on a shallow baking pan on the oven rack. Bake in 350 oven for 45-50 minutes or until center appears nearly set when shaken. Remove from oven. Mix vanilla sugar with sour cream and spread over top of HOT cheesecake to within 1 inch of edge.
Remove springform pan from baking pan. Cool on rack for 15 minutes. Use narrow metal spatula to loosen crust from sides of pan. Cool 30 minutes. Remove sides of pan. Cool 1 hour; cover and chill at least 4 hours. \par
TOPPING: To serve, sift cocoa powder and sprinkle shaved chocolate over top.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HOT BUTTERED RUM CHEESECAKE} \index{HOT BUTTERED RUM CHEESECAKE}
\step{1 cup finely crushed shortbread cookies	
\\ 3 Tbsp packed brown sugar
\\ 2 Tbsp butter, melted	
\\ 5 pkgs (8 oz each) cream cheese
\\ 1 \nicefrac{1}{4} cups sugar	
\\ \nicefrac{1}{3} cup whipping cream
\\ 2 Tbsp rum (or 2 tsp rum extract)	
\\ \nicefrac{1}{4} tsp ground cinnamon
\\ \nicefrac{1}{8} tsp ground cloves	
\\ \nicefrac{1}{8} tsp ground nutmeg
\\ 3 eggs
\stepspace SAUCE:
\\ \nicefrac{1}{2} cup backed brown sugar	
\\ \nicefrac{1}{2} cup butter
\\ \nicefrac{2}{3} cup whipping cream	
\\ \nicefrac{1}{4} cup rum (or 2 tsp rum extract + 3 Tbsp water)}{Heat oven to 350${}^\circ$F. Mix crushed cookies, sugar and butter. Press firmly in bottom of ungreased 9" springform pan. Bake 10 minutes. Cool completely. Reduce oven temp to 325${}^\circ$F.
While crust is cooling, beat cream cheese, sugar, \nicefrac{1}{3} cup whipping cream rum, and spices with electric mixer on med speed until smooth (about 1 minute). Beat in eggs on low speed until well blended. Pour into partially baked crust. Smooth top.
Bake 75-85 minutes, or until edge is set and center is still soft. Turn off oven and leave oven door open about 4 inches. Leave cheesecake in oven 30 minutes. Remove from oven and cool in pan on wire rack away from drafts 30 minutes.
Without releasing or removing side of pan, run metal spatula carefully along side of cheesecake to loosen. Refrigerate uncovered about 3 hours or until chilled. Cover and continue refrigerating at least 9 hours but no longer than 48 hours.
Mix all rum sauce ingredients in saucepan. Heat to boiling over medium heat, stirring constantly. Boil 3 to 4 minutes, stirring constantly, until slightly thickened. Serve warm, drizzled over slice of cheesecake.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHITE SILK RASPBERRY TART} \index{WHITE SILK RASPBERRY TART}
\name{An exceptional dessert. Received rave reviews Christmas 2006.}\\
\step{20 cr\`eme-filled chocolate sandwich cookies, crushed (2 cups)
\\ \nicefrac{1}{4} cup butter, melted	
\\ 6 oz white chocolate, chopped
\\ 2 cups whipping cream	
\\ 1 tsp vanilla
\\ 1 pkg cream cheese, softened	
\\ 1 pkg frozen raspberries in syrup, thawed
\\ 2 tsp cornstarch	
\\ 1 cup fresh raspberries}{Heat oven to 375${}^\circ$F. Mix crushed cookies and butter. Press in bottom and 1" up side of ungreased 9 or 10" springform pan. Bake 7-9 minutes or until set. Cool completely. Meanwhile, heat white baking bars and \nicefrac{1}{2} cup whipping cream in saucepan over low heat, stirring frequently until chocolate melts. Stir in vanilla. Cool to room temp, about 15 minutes.
Beat cream cheese with electric mixer until smooth. Add white chocolate mixture. Beat on med speed until creamy. Beat remaining 1 \nicefrac{1}{2} cups whipping cream until stiff peaks form. Fold half of whipped cream in cream cheese mixture until blended. Fold in remaining whipped cream. Spoon into crust. Refrigerate 3--4 hours or until set. Pour package of raspberries into small strainer set over saucepan. Press raspberries through strainer with back of spoon to remove seeds. Stir cornstarch into raspberry puree. Heat to boiling over medium heat. Cool completely, about 20 minutes. Spoon fresh raspberries around edge of dessert. Remove side of pan. Cut tart into wedges. Drizzle raspberry sauce over individual servings.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUMPKIN CHEESECAKE WITH GINGERSNAP CRUST} \index{PUMPKIN CHEESECAKE WITH GINGERSNAP CRUST}
\step{CRUST:  \\
1 \nicefrac{1}{2} cups finely ground gingersnap crumbs \\
\nicefrac{1}{4} cup sugar \\
5 Tbsp unsalted butter, melted
\stepspace FILLING: \\
15 oz pumpkin  \\
1 \nicefrac{1}{3} cups sugar \\
1 tsp cinnamon \\
\nicefrac{1}{2} tsp ginger \\
\nicefrac{1}{4} tsp nutmeg \\
\nicefrac{1}{4} tsp cloves \\
\nicefrac{1}{2} tsp salt \\
1 cup heavy cream \\
3 8 oz packages cream cheese, chunks \\
5 large eggs, room temperature
\stepspace CARAMEL SAUCE: \\
1 cup sugar \\
2 Tbsp corn syrup \\
2 Tbsp water \\
\nicefrac{1}{8} tsp lemon juice \\
\nicefrac{1}{2} cup heavy cream \\
1 Tbsp unsalted butter}{Set oven rack in lower middle position. Wrap a 10" springform pan with foil for hot water bath. Grease pan. Pulse crust ingredients. Press into pan. Bake at 325${}^{\circ}$F for 15 min. Cool. \par
FILLING: Combine pumpkin, sugar, spices, and salt. Bring mixture to a sputter. Reduce heat to medium-low. Cook 5 minutes. Beat mixture 1 minute. Continue beating while adding cold cream. Add cream cheese and beat for 30 seconds. Add eggs and beat 5 seconds. Pour batter over cooled crust. Place cake pan in boiling water bath. Bake until cake is just set, 1 \nicefrac{1}{2} to 1 \nicefrac{3}{4} hours. Remove roasting pan from oven. Run a knife around the edges to loosen the cake. Cool 45 minutes. Remove springform pan from water bath. When barely warm refrigerate until chilled.\par
CARAMEL SAUCE: Combine sugar, syrup, water and lemon juice. Microwave until caramel is just starting to turn pale yellow, approx. 4--8 minutes. Let the caramel sit for 5 minutes. It will turn dark.  If it's not dark enough after 5 minutes, microwave for 30 seconds. Once caramel reaches the right color, immediately stir in hot cream a few tablespoons at a time.  Incorporate butter. Add more cream if mixture is too thick. Drizzle over cheesecake. Top with whipped cream if desired.}

\end{minipage}