\section{Cookies}

\begin{minipage}{\linewidth}\rtitle{TING-A-LINGS} \index{TING-A-LINGS}
\textit{(Loraine Hiebert)}\\
\step{1 cup semi -sweet chocolate chips
\\ 1 cup cornflakes
\\ \nicefrac{1}{2} cup shredded coconut
\\ 1 tsp vanilla
\\ \nicefrac{1}{2} cup peanuts}{Melt chocolate. Remove from heat. Add remaining ingredients. Drop by teaspoonful onto waxed paper. Refrigerate.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHIPITS CRUNCHIES} \index{CHIPITS CRUNCHIES}
\step{1 cup chocolate chips	
\\ 1 cup butterscotch chips
\\ 1 cup broken thin pretzel sticks	
\\ 1 cup chopped nuts}{Melt chocolate and butterscotch chips. Remove from heat and stir in pretzel sticks and nuts. Drop by spoonfuls onto wax paper. Chill until firm. Makes about 2 doz. crunchies. Variation: substitute for pretzels: 1 cup corn flakes; 1 cup rice cereal; or 1 cup chow mein noodles.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DAD'S COOKIES} \index{DAD'S COOKIES}
\step{\nicefrac{1}{2} cup white sugar	
\\ 1 tsp baking powder
\\ \nicefrac{1}{2} cup brown sugar	
\\ \nicefrac{1}{2} tsp salt
\\ 1 egg	
\\ 1 tsp baking soda
\\ 1 cup margarine	
\\ 1 tsp vanilla
\\ 1 \nicefrac{1}{2} cups oatmeal	
\\ 1 cup cornflakes
\\ 1 cup flour}{Cream margarine and sugar. Add egg and beat until creamy. Mix in oatmeal. Add dry ingredients and vanilla. Add cornflakes. Mix well. Roll in balls and press with a fork. Bake at 350${}^\circ$F for 13-15 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAMY SNOWBALLS} \index{CREAMY SNOWBALLS}
\step{4 oz cream cheese	
\\ 2 cups icing sugar
\\ 	2 Tbsp milk	
\\ \nicefrac{2}{3} cup semi sweet chocolate chips
\\ 	\nicefrac{1}{2} tsp vanilla	
\\ 3 cups miniature marshmallows}{Chill \nicefrac{1}{2} hour. Shape into 1 \nicefrac{1}{4}" balls. Roll in coconut.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CARDAMOM DROP COOKIES} \index{CARDAMOM DROP COOKIES}
\step{\nicefrac{1}{2} cup soft butter	
\\ \nicefrac{1}{4} cup soft shortening
	\\ 1 cup brown sugar, packed	
	\\ 2 eggs
	\\ 1 Tbsp milk	
	\\ 2 cups sifted flour
	\\ \nicefrac{1}{2} tsp soda	
	\\ \nicefrac{1}{2} tsp cardamom
	\\ \nicefrac{1}{8} tsp salt	
	\\ 2 cups chopped dates
	\\ \nicefrac{1}{2} cup chopped walnuts}{
Cream butter, shortening, sugar and eggs until light and fluffy. Stir in milk. Sift dry ingredients together into mixture and stir to blend. Stir in dates and walnuts. Bake 12 min until golden brown. Makes 2 dozen.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM COOKIES} \index{CREAM COOKIES}
\step{2\nicefrac{1}{2} cups white sugar	
\\ 2 cups margarine
\\ 6 eggs	
\\ 2 cups cream
\\ 1 tsp soda	
\\ 2 Tbsp vanilla
\\ flour}{Roll out cookies and cut.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SHORTBREAD} \index{SHORTBREAD}
\textit{An excellent recipe that rivals the expensive imported shortbreads}\\
\step{1 cup butter, softened	
\\ 3 Tbsp cornstarch
\\ \nicefrac{1}{4} cup sugar	
\\ 1 \nicefrac{3}{4} cups flour}{Beat butter until fluffy; gradually beat in cornstarch, then sugar. Beat in flour, about \nicefrac{1}{4} cup at a time. (I used an electric beater.) On a floured surface, roll out dough to \nicefrac{1}{4}" thickness. Using floured fluted 2" round cookie cutters, cut our cookies. Place on waxed paper-lined trays: prick each cookie three times with fork. Freeze until firm. (Cookies can be prepared to this point and stored in airtight container in freezer for up to 1 month.) Place frozen rounds on ungreased baking sheet. Bake at 275${}^\circ$F for 40-50 minutes or until firm to the touch. Yield: 2 dozen}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHIPPED SHORTBREAD} \index{WHIPPED SHORTBREAD}
\textit{(Neta Loewen)}\\
\step{1 cup soft margarine	
\\ \nicefrac{1}{4} cup cornstarch
	\\ \nicefrac{1}{2} cup icing sugar	
	\\ 1 \nicefrac{1}{2} cups sifted flour}{
Mix ingredients with mixer until blended. Turn to high speed and beat until it resembles the texture of whipped cream. Drop by spoonfuls on a cookie sheet. Bake at 325$^\circ$F for 20 min.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHRISTMAS BISCOTTI} \index{CHRISTMAS BISCOTTI}
\textit{(Canadian Living)}\\
\step{1 \nicefrac{1}{3} cups flour	
\\ \nicefrac{1}{2} tsp baking soda
\\ \nicefrac{1}{2} tsp aniseed, crushed	
\\ \nicefrac{1}{4} cup each red and green candied cherries, chopped
\\ 2 eggs	
\\ \nicefrac{1}{3} cup granulated sugar
\\ 1 tsp vanilla	
\\\\ TOPPING:
\\ 1 egg white, beaten
\\ 1 tsp sugar}{Stir together flour, baking soda and aniseed. Stir in cherries. In separate bowl, whisk together eggs, sugar and vanilla. Stir into flour mixture to make soft sticky dough. Turn out onto lightly floured surface. Divide in half and place on greased baking sheet. Shape into two 9x3" rectangles. Brush dough with egg white and sprinkle with sugar. Bake in 350${}^\circ$F oven for 15-18 minutes or until light golden on top and golden brown on sides. Let cool on pan on rack for 10 minutes. Transfer to cutting board. With serrated knife, cut diagonally into \nicefrac{1}{2}" thick slices. Stand slices up, about \nicefrac{1}{2} inch apart on baking sheet; bake at 275${}^\circ$F for 35-40 minutes or until golden and completely dry. Makes 2 dozen cookies.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEPPERNUTS} \index{PEPPERNUTS}
\step{3 cups brown sugar	
\\ 1 cup water
	\\ 1 cup syrup
	\\ 1 cup shortening	
	\\ 1 tsp soda
	\\ 4 beaten eggs	
	\\ 1 tsp cinnamon
	\\ 1 tsp cloves	
	\\ 1 tsp aniseed
	\\ enough flour to make a soft dough}{Bring first two ingredients to a boil and cool slightly. Then add remaining ingredients. Roll dough in small strips and cut desired size. Bake in 375$^\circ$F oven until nicely browned.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MENNONITE PEPPERMINT COOKIES} \index{MENNONITE PEPPERMINT COOKIES}
\textit{(Jackie Buhler)}\\
\step{2 cups cream	
\\ 3 Tbsp ammonia
\\ 1 cup butter	
\\ 3 tsp peppermint
\\ 3 cups sugar	
\\ 5 tsp baking powder
\\ 5 eggs	
\\ 8 \nicefrac{1}{2} cups flour
\\ \nicefrac{1}{4} cup boiling water}{Mix sugar \& butter thoroughly. Add cream and well beaten eggs. Next, add peppermint and dissolved ammonia. Work in flour and baking powder. Roll out and cut. Bake at 375${}^\circ$F for 12 minutes. Ice while hot. (These are great with a marshmallow topping too.)}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HAMANTASCHEN} \index{HAMANTASCHEN}
\textit{(Canadian Living)}\\
\step{\nicefrac{2}{3} cup butter, softened	
\\ 1 cup sugar
\\ 3 eggs	
\\ 3 Tbsp liquid honey
\\ 1 tsp vanilla	
\\ 3 cups flour
\\ 1 tsp baking powder}{Mix. Wrap in plastic wrap and refrigerate for at least 2 hours or for up to 3 days.}
\step{FILLING:
\\ 2 cups dried apricots	
\\ 1 cup golden raisins
\\ 1 cup orange juice	
\\ \nicefrac{1}{4} cup water
\\ 2 Tbsp granulated sugar	
\\ 1 tsp grated orange rind
\\ 1 egg, lightly beaten}{Bring apricots, raisins and orange juice to boil. Reduce heat and simmer, stirring occasionally, for 10 minutes. Let cool. In food processor, puree together cooled apricot mixture, water, sugar and orange rind until finely chopped. Divide dough into quarters. On lightly floured surface, roll out each portion to 1/8 inch thickness. Using floured 2 \nicefrac{1}{2} €œ round cookie cutter, cut out shapes. Place heaping teaspoonful filling in center of each. Fold up three sides to make three corners; pinch each corner to seal. Place on greased baking sheets. Brush edges with egg. Bake at 350${}^\circ$F for 15-20 minutes. Makes about 60 cookies.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROGLICHKE} \index{ROGLICHKE}
\textit{(Mrs. Joe Hart, Swan River)}\\
\step{\nicefrac{1}{2} cup warm water 
\\ 1 tsp sugar 
\\ 1 pkg yeast
\\ \nicefrac{3}{4} lb shortening	
\\ 1 cup cake flour
\\ \nicefrac{1}{2} cup sour cream	
\\ pinch of salt
\\ 3 cups flour	
\\ 2 egg yolks
\\ \\ FILLING:
\\ 4 egg whites, stiffly beaten	
\\ 2 cup icing sugar
\\ 2 cup crushed walnuts	
\\ 1 tsp vanilla}{Put warm water into bowl, add sugar, and sprinkle yeast. Let stand for 10 minutes. Mix flour, salt and shortening as for pie crust. Add egg yolks, cream and yeast mixture. Mix into lump. Roll the dough into little balls the size of walnuts. Roll each ball quite thin with a rolling pin. Place a tsp of filling on circle of dough and roll up. Place on cookie sheet in crescent shape and bake at 350${}^\circ$F for about 10-12 minutes or until slightly brown.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SESAME SEED COOKIES} \index{SESAME SEED COOKIES}
\textit{(Melissa Vanderburg)}\\
\step{\nicefrac{3}{4} cup blue band	
\\ \nicefrac{1}{2} cup sugar
	\\ \nicefrac{1}{2} tsp almond essence	
	\\ 1 egg
	\\ 2 cups flour	
	\\ \nicefrac{1}{2} tsp salt
	\\ \nicefrac{1}{3} cup sesame seeds}{
Mix dry ingredients together. Mix wet ingredients. Combine. Form balls and press with fork.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{THE ULTIMATE SUGAR COOKIE} \index{THE ULTIMATE SUGAR COOKIE}
\textit{My 20 year search has ended! This is the cookie recipe I use when I care about the taste.} \\
\step{\nicefrac{1}{2} cup butter	
\\ \nicefrac{1}{2} cup sugar
	\\ \nicefrac{1}{2} cup oil	
	\\ \nicefrac{1}{2} cup icing sugar
	\\ \nicefrac{1}{2} tsp baking soda	
	\\ \nicefrac{1}{2} tsp cream of tartar
	\\ \nicefrac{1}{2} tsp salt	
	\\ 1 egg
	\\ \nicefrac{1}{2} tsp vanilla	
	\\ 2 cups flour}{
Mix with electric beater. Chill 4-24 hours. Shape in \nicefrac{1}{2} to 1-inch balls. Place on ungreased pan. Flatten with glass dipped in coloured sugar. Bake at 375$^\circ$F 8-10 min. Yield: 72 cookies.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROLLED SUGAR COOKIES (GF)} \index{ROLLED SUGAR COOKIES (GF)} \index{Gluten Free!cookies}
\step{1 cup unsalted butter, softened
\\ 1 cup sugar
\\ \nicefrac{1}{2} tsp almond extract
\\ 2 tsp vanilla extract
\\ 1 large egg
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} tsp baking powder
\\ 1 \nicefrac{1}{3} cups white rice flour
\\ \nicefrac{2}{3} cup tapioca starch
\\ \nicefrac{2}{3} cup potato starch
\\ 1 \nicefrac{1}{2} tsp xanthan gum}{Cream butter and sugar. Add extracts and egg. Mix just until blended. In a separate bowl whisk together the dry ingredients. Slowly add the dry ingredients to the butter mixture. Mix just until the dough comes together. Scrape the dough onto a sheet of plastic wrap and wrap tightly before refrigerating for at least 1 hr. This will help your butter to solidify and help your cookies to keep their shape. 
Preheat oven to 350${}^\circ$F and line baking sheets with parchment paper. Working with a quarter of the dough at a time, roll the dough to about \nicefrac{3}{8}" thickness between two sheets of plastic wrap. (it helps to dampen the counter before laying the first sheet of plastic wrap down)  Dust with a small amount of sweet rice flour if necessary. Cut to desired shapes and place on baking sheet, leaving 2" between cookies. Bake 8-12 min. The cookies should just barely be turning grown around the edges and have just a light brown colour on the bottom of the cookie. Allow cookies to cool completely before decorating with icing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DOUBLE CRUNCHERS} \index{DOUBLE CRUNCHERS}
\step{\nicefrac{1}{2} cup shortening
\\ \nicefrac{1}{2} cup granulated sugar
\\ \nicefrac{1}{2} cup brown sugar.
\\ 1 egg	
\\ \nicefrac{1}{2} tsp vanilla
\\ 1 cup flour	
\\ \nicefrac{1}{2} tsp baking soda
\\ \nicefrac{1}{4} tsp salt	
\\ 1 cup corn flakes, crushed
\\ 1 cup rolled oats	
\\ \nicefrac{1}{2} cup coconut
\\ \\ FILLING:
\\ 6-oz pkg semi-sweet chocolate chips
\\ \nicefrac{1}{2} cup icing sugar
\\ 1 Tbsp water
\\ \nicefrac{1}{3} cup of cream cheese}{Combine shortening, sugar, and brown sugar. Blend in egg and vanilla. Add remaining ingredients. Remove \nicefrac{1}{3} of dough; reserve. Shape remaining \nicefrac{2}{3} of dough into balls using level teaspoonfuls. Place on greased cookie sheets. Flatten with bottom of glass dipped in flour. Bake at 350${}^\circ$F for 8-10 minutes. Shape reserved dough into balls, using half teaspoonfuls. Bake on greased cookie sheets at 350${}^\circ$F for 8 minutes. Cool.
For chocolate filling, melt chocolate, icing sugar, and water over hot water. Blend in cream cheese. Beat until smooth. Spread filling over larger cookies and top with small ones.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{OAT CAKES} \index{OAT CAKES}
\textit{(Mrs. Mary Kennedy and Mr. Lou Schroeder, who always insisted he was Scottish)\\
For some inexplicable reason women love these and men don't.}\\
\step{3 cups flour	
\\ 3 cups rolled oats
	\\ 1 cup sugar (or less)	
	\\ 2 tsp salt
	\\ 1 tsp soda	
	\\ 1 \nicefrac{1}{2} cup lard
	\\ \nicefrac{3}{4} cup water}{
Mix first five ingredients. Cut in lard. Mix in water. Wrap in wax paper. Make balls the size of tennis balls. Roll very thin. Cut the rounds into four triangles. Bake in 350$^\circ$F oven for 15 min on an ungreased cookie sheet.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{OATMEAL CHOCOLATE CHIP COOKIES} \index{OATMEAL CHOCOLATE CHIP COOKIES}
\textit{The ones I grew up with.}\\
\step{1 cup shortening	
\\ 1 tsp baking powder
\\ 1 cup brown sugar	
\\ 1 tsp baking soda
\\ 1 cup white sugar	
\\ 1 tsp salt
\\ 2 eggs, beaten	
\\ 3 cups oats
\\ 2 Tbsp water	
\\ 2 cups chocolate chips (or raisins)
\\ 1 tsp vanilla	
\\ 1 \nicefrac{1}{2} cups flour}{Mix. Place teaspoonfuls of dough on greased cookie sheet. Bake at 350${}^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHEWY OATMEAL CHOCOLATE CHIP COOKIES (GF)} \index{CHEWY OATMEAL CHOCOLATE CHIP COOKIES (GF)} \index{Gluten Free!cookies}
\step{1 cup GF oats
\\ 1 cup sorghum flour
\\ \nicefrac{1}{2} cup brown rice flour
\\ \nicefrac{1}{4} cup tapioca starch
\\ 1 tsp xanthan gum
\\ 1 tsp baking soda
\\ \nicefrac{1}{2} tsp cinnamon
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{2}{3} cup oil
\\ 1 cup sugar
\\ \nicefrac{1}{2} cup brown sugar
\\ 1 tsp vanilla
\\ 3 large eggs
\\ 2 cups chocolate chips}{Line the baking pan with parchment paper.
Using a food processor, quickly pulse the oats to form smaller flakes, but not too much. Combine dry ingredients (except the sugars). In a separate bowl, whisk together the oil, sugars, vanilla and eggs. Add the wet ingredients to the dry. Mix until combined. Add the chocolate chips. Dampen your hands with a small amount of water and roll 2 tsps of dough into a smooth ball. Place cookies 3" apart on baking sheet. Bake for 10-12 min at 350${}^\circ$F, decreasing time for a chewier cookie. Allow cookies to cool for a few min before moving them to a wire rack.  If you want a slightly puffy cookie, add an additional \nicefrac{1}{2} cup brown rice flour.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEANUT BUTTER CHOCOLATE COOKIES} \index{PEANUT BUTTER CHOCOLATE COOKIES}
\step{\nicefrac{1}{2} cup butter
\\ 1 tsp vanilla
\\ \nicefrac{1}{2} cup sugar	
\\ 1 \nicefrac{1}{2} cups flour
\\ \nicefrac{1}{2} cup packed brown sugar	
\\ \nicefrac{1}{2} cup cocoa
\\ 1 cup creamy peanut butter	
\\ \nicefrac{3}{4} cup icing sugar
\\ \nicefrac{1}{2} tsp baking soda	
\\ 1 egg, beaten}{Cream butter and sugars. Add egg and vanilla. Mix well. Combine flour, cocoa and baking soda. Add to creamed mixture and mix well. Blend icing sugar with peanut butter. Roll into 24 balls, 1" each. Divide dough into 24 pieces. Flatten each into 3" circle. Place one peanut butter ball on each circle. Bring edges over and cover. Place cookies on ungreased baking sheet, seam down. Flatten each cookie slightly. Bake at 375${}^\circ$F for 7-9 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEANUT BUTTER COOKIES} \index{PEANUT BUTTER COOKIES} 
\step{\nicefrac{1}{2} cup butter	
\\ 1 egg
\\ \nicefrac{1}{3} cup brown sugar	
\\ 1 \nicefrac{1}{2} cups flour
\\ \nicefrac{1}{2} cup white sugar	
\\ \nicefrac{1}{2} tsp soda
\\ \nicefrac{1}{2} cup peanut butter	
\\ 1 tsp vanilla
\\ \nicefrac{1}{2} tsp salt}{Mix in order given. Flatten teaspoonfuls of dough on greased cookie sheets. Bake at 350${}^\circ$F for about 10 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEANUT BUTTER COOKIES (GF)} \index{PEANUT BUTTER COOKIES (GF)} \index{Gluten Free!cookies}
\textit{(Sherry Peters)}\\
\step{1 cup creamy peanut butter
\\ 1 cup brown sugar
\\ 1 egg
\\ 1 tsp baking soda.}{Mix and chill. Roll into 1" balls. Flatten with fork. Place on ungreased cookie sheet and bake 8-10 min at 350${}^\circ$F.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHEWY BROWNIE COOKIE} \index{CHEWY BROWNIE COOKIE}
\step{\nicefrac{2}{3} cup shortening	
\\ 1 \nicefrac{1}{2} cup brown sugar
	\\ 1 Tbsp water	
	\\ 1 tsp vanilla
\\ 2 eggs	
\\ 1 \nicefrac{1}{2} cups flour
	\\ \nicefrac{1}{3} cup unsweetened cocoa	
	\\ \nicefrac{1}{4} tsp soda
	\\ \nicefrac{1}{2} tsp salt	
	\\ 2 cups semi-sweet chips (12 oz)}{Bake at 375$^\circ$F.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HERSHEY'S TOLLHOUSE CHOCOLATE CHIP COOKIES} \index{HERSHEY'S TOLLHOUSE CHOCOLATE CHIP COOKIES}
\step{2 \nicefrac{1}{4} cups flour
\\ 1 tsp baking soda
\\ \nicefrac{1}{2} tsp salt
\\ 1 cup butter
\\ \nicefrac{3}{4} cup brown sugar
\\ \nicefrac{3}{4} cup white sugar
\\ 1 tsp vanilla extract
\\ 2 eggs
\\ 2 cups chocolate chips
\\ 1 cup nuts (opt)}{Preheat oven to 375${}^\circ$F.  Yield 5 doz. Bake on ungreased cookie sheet for 8-10 min.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PINWHEEL COOKIES} \index{PINWHEEL COOKIES}
\step{2 cups brown sugar	
\\ 1 tsp soda
\\ 1 cup shortening	
\\ salt
\\ 2 eggs, beaten	
\\ 4 cups flour
\\ 1 tsp cinnamon}{Mix all ingredients. Roll into 2 rolls and let stand overnight. In the morning roll out. Put on filling and nuts. Roll up like jelly roll and cut. Bake at 350${}^\circ$F for 15 minutes.
Filling: 1 pig dates or raisins, sugar to sweeten. Add a little water and boil until thick.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FIG OR RAISIN COOKIES (GF*)} \index{FIG OR RAISIN COOKIES (GF*)}
\textit{For the GF half recipe option, replace the flour with half a cup of oat flour and GF flour blend. DO not use flour to roll. Roll between saran wrap layers.}\\
\step{2 cups lard	
\\ 2 tsp soda
\\ 2 cups brown sugar	
\\ \nicefrac{1}{2} tsp cloves
\\ 2 cups milk	
\\ \nicefrac{1}{2} tsp star anise
\\ 7 Tbsp syrup (or 3 \nicefrac{1}{2} Tbsp sugar and 1 tsp water)
\\ 1 tsp cinnamon
\\ Enough flour to make soft dough.}{Roll out with round cutter. Place filling on half. Fold over and bake.}
\step{Raisin Filling:
\\ 2 \nicefrac{1}{2} cups raisins	
\\ \nicefrac{1}{2} cup sugar
\\ 2 Tbsp cornstarch	
\\ \nicefrac{3}{4} cup water
\\ 3 Tbsp lemon juice}{Boil ingredients together.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SNICKERDOODLES} \index{SNICKERDOODLES}
\step{1 cup shortening	
\\ 1 \nicefrac{1}{2} cups sugar
	\\ 2 eggs, unbeaten	
	\\ 2 \nicefrac{3}{4} cups flour
	\\ 2 tsp cream of tartar	
	\\ 1 tsp baking soda
	\\ \nicefrac{1}{4} tsp salt}{
Make into small balls and roll in: 2 Tbsp sugar and 1 tsp cinnamon. Bake on greased cookie sheet at 400$^\circ$F for 8-10 min.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GINGER CRINKLES} \index{GINGER CRINKLES}
\step{\nicefrac{2}{3} cup oil	
\\ 2 tsp soda
	\\ 1 cup sugar	
	\\ 1 tsp salt
	\\ \nicefrac{1}{3} cup molasses	
	\\ 1 tsp ginger
	\\ 1 beaten egg	
	\\ \nicefrac{1}{2} tsp cinnamon
	\\ 2 cups flour	
	\\ \nicefrac{1}{2} tsp cloves (or less)}
{Beat together oil and sugar. Add molasses and egg. Beat all well. Add dry ingredients. Form into balls and dip in sugar. Do not flatten. Bake at 400$^\circ$F for 8-10 min. (Watch carefully; they burn easily!)}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GINGERSNAP COOKIES (GF)} \index{GINGERSNAP COOKIES (GF)} \index{Gluten Free!cookies}
\step{1 \nicefrac{1}{2} cups butter
\\ 2 cups white sugar
\\ \nicefrac{1}{2} cup molasses
\\ 2 eggs
\\ \nicefrac{1}{2} cup tapioca flour
\\ 1 cup potato starch
\\ 2 \nicefrac{1}{2} cups rice flour
\\ 1 \nicefrac{3}{4} tsp xanthan gum
\\ 4 tsp baking soda
\\ 2 tsp cinnamon
\\ 1 tsp ginger
\\ 1 tsp cloves}{Cream butter, sugar, molasses and eggs. Combine dry ingredients and stir into butter mixture. Refrigerate for several hours. Preheat oven to 350${}^\circ$F. shape dough into \nicefrac{1}{2}" balls. Roll in sugar. Arrange 3" apart on baking sheet.  Bake 8-10 min.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEBKUCKEN} \index{LEBKUCKEN}
\textit{(Great-Grandma Elsie Fingas)\\
Store these cookies in ice cream pails or tins. They get better and better as the weeks go by!}\\
\step{1 cup sugar
  \\ 1 cup honey
  \\ 4 eggs, beaten.
  \\ \nicefrac{1}{4} lb almonds
	\\ \nicefrac{1}{4} lb peel
  \\ \nicefrac{1}{2} tsp salt
	\\ 2 tsp baking soda
	\\ 2 tsp baking ammonia
	\\ 1 tsp cloves
	\\ 1 Tbsp chicken fat
	\\ flour}{
Melt sugar and honey. Add eggs. Add almonds and peel. Add remaining ingredients. Add flour to stiffen. Work dough well. Chill overnight. Roll and cut. Brush tops with beaten egg. Decorate. Bake at 350$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BIRD'S NESTS} \index{BIRD'S NESTS}
\textit{Forever associated in my mind with grade 7 Home Ec cooking class.}\\
\step{\nicefrac{1}{2} cup butter	
\\ 1 cup flour
\\ \nicefrac{1}{4} cup brown sugar	
\\ \nicefrac{1}{2} tsp baking powder
\\ 1 egg yolk	
\\ 1/8 tsp salt}{Combine. Shape small balls of dough. Dip in 1 beaten egg white and roll in \nicefrac{2}{3} cup finely chopped nuts or corn flakes. Make a depression with finger. Bake for 5 minutes. Make depression in each cookie again and fill with red, tart jam. Return to oven to finish baking.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{JAM JAMS} \index{JAM JAMS}
\step{1 cup butter	
\\ \nicefrac{1}{4} cup brown sugar
\\ 	\nicefrac{1}{4} cup white sugar	
\\ \nicefrac{1}{2} cup corn syrup
\\ 2 eggs	
\\ 1 tsp vanilla
\\ 3 cups flour	
\\ \nicefrac{1}{2} tsp baking powder
\\ \nicefrac{1}{2} tsp salt}{Roll dough to 1/8" thick. Cut 2 \nicefrac{3}{4}" circles. Bake and sandwich after baking with jam.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MACAROON JAM SLICES} \index{MACAROON JAM SLICES}
\textit{(Canadian Living)}\\
\step{1 egg white	
\\ \nicefrac{1}{2} cup icing sugar
\\ 	\nicefrac{1}{2} tsp vanilla	
\\ 1 \nicefrac{3}{4} cups ground almonds
\\ 	\nicefrac{1}{3} cup raspberry jam}{Beat egg white until soft peaks form. Beat in \nicefrac{1}{3} cup of the sugar, 2 Tbsp at a time, until stiff peaks form. Fold in vanilla and all but 2 Tbsp of the almonds. Divide dough in half. Dust work surface with half of the remaining sugar and half of the remaining almonds. Roll one half of the dough into 10" LONG LOG. Repeat with remaining sugar, almonds and dough. With 2 spatulas, place logs, 2 inches apart on greased baking sheets. With fingertip, form groove lengthwise along center of each log to \nicefrac{1}{4} inch of bottom, keeping walls about \nicefrac{1}{4} inch thick to support filling. Bake in 350${}^{\circ}$ oven for 10 minutes. spoon raspberry jam into each groove. Bake for about 12 minutes or until cookie is golden and jam is bubbly. Let cool on pan for 5 minutes. cut diagonally into 1" thick slices. Makes about 18 cookies.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{AMARETTI (GF)} \index{AMARETTI (GF)} \label{Gluten Free!cookies} \label{cookies!Gluten Free}
\textit{Usually bought in decorative tins. Gluten free.}\\
\step{2 egg whites	
\\ 1 cup white sugar
\\ \nicefrac{1}{2} tsp almond extract	
\\ 2 \nicefrac{1}{2} cups ground almonds
\\ 2 Tbsp sugar}{Beat egg whites until soft peaks form. Beat in sugar, 2 Tbsp at a time, until glossy peaks form. Beat in extract. Fold in almonds. Drop a generous Tbsp on parchment lined baking sheet. Sprinkle sugar over cookies. Bake in top and bottom \nicefrac{1}{3} of oven at 300${}^\circ$F, rotating and switching pans half way through the baking time. Bake for about 20 minutes or until firm to touch and golden. Yield: 30 cookies.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE WAFERS} \index{CHOCOLATE WAFERS}
\textit{(Canadian Living)\\
An elegant little hazelnut meringue cookie with chocolate spread over its bottom.}\\
\step{\nicefrac{1}{2} cup blanched almonds	
\\ \nicefrac{1}{2} cup hazelnuts
\\ 1 cup icing sugar	
\\ \nicefrac{1}{4} cup cornstarch
\\ 3 egg whites	
\\ 2 Tbsp butter, melted
\\ 2 Tbsp hazelnut or almond liqueur	
\\ 175 g semisweet chocolate, coarsely chopped}{Spread almonds and hazelnuts on rimmed baking sheet. Bake in 350${}^\circ$F oven for 8-10 minutes or until fragrant and browned. Transfer to tea towel; rub skins off hazelnuts. In food processor, combine almonds, hazelnuts, \nicefrac{1}{3} cup of the sugar and cornstarch. Chop coarsely. Transfer to bowl; set aside. In large bowl, beat egg whites until soft peaks form; beat in remaining sugar, 2 Tbsp at a time, until stiff peaks form. Fold in nut mixture. Fold in butter and liqueur. Drop by tablespoonfuls about 2 in. apart onto parchment paper lined baking sheets. Bake at 325${}^\circ$F for about 18 minutes or until browned and firm around edges but still soft in center. Let cool.
In bowl over saucepan of hot water, melt chocolate; spread about 1 tsp over bottom of each cookie. Using cake decorating comb or fork tines, make wavy lines in chocolate. Let cool until set. Makes about 42 cookies.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ALMOND CRUNCH COOKIES} \index{ALMOND CRUNCH COOKIES}
\textit{(Joe Nelson)}\\
\step{\nicefrac{1}{2} cup butter, softened	
\\ \nicefrac{3}{4} cup sugar
\\ 	1 large egg	
\\ \nicefrac{1}{2} tsp almond extract
\\ 	\nicefrac{1}{4} cup ground almonds	
\\ 1 cup sliced almonds
\\ 	1 cup flour	
\\ \nicefrac{1}{4} cup heavy cream
\\ 	1 cup semisweet choc chips	
\\ 2 tsp light corn syrup}{Blend butter and sugar with electric mixer until mixture forms a grainy paste. Add egg and almond extract. Beat at medium speed until light and fluffy. Add ground almonds and flour. Blend at low speed until combined. Do not over-mix. Form dough into 1 \nicefrac{1}{2}" balls and roll in sliced almonds, coating each ball thoroughly. Place balls on ungreased cookie sheets, 2 inches apart. Bake for 15-18 minutes or until cookies are slightly brown along edges. Immediately transfer cookies to a cool surface covered with waxed paper.
Choc glaze: Scaled cream in a small saucepan, then remove from heat. Stir in choc chips and corn syrup. Cover and let stand for 15 minutes. Using a small wire whisk, gently mix glaze until smooth, being careful not to create bubbles in the chocolate. When cookies are completely cool, drizzle patterns on them or dip half of each cookie in the glaze. Refrigerate until glaze sets.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE ALMOND TASSIES} \index{CHOCOLATE ALMOND TASSIES}
\textit{(Joe Nelson)}\\
\step{Pastry:\\
\\ 2 cups flour	
\\ 6 oz cold cream cheese, cut into chunks
\\ 1 cup butter, cold, cut into chunks}{Place flour in bowl. Cut in cream cheese and butter. Continue to mix until dough can be shaped into a ball. Refrigerate dough for 1 hour. Shape dough into 1" balls. Press each ball into ungreased miniature muffin tins (1 \nicefrac{3}{4}"), covering the bottom and sides of cup with dough. Preheat oven to 350${}^\circ$F.}
\step{Filling:
\\ 2 Tbsp butter	
\\ 2-1 oz sq unsweetened chocolate
\\ 1 \nicefrac{1}{2} cups brown sugar	
\\ 2 tsp vanilla
\\ 2 eggs, beaten	
\\ dash of salt
\\ 1 \nicefrac{1}{2} cups chopped almonds (roasted, then chopped)}{Melt butter and chocolate in heavy saucepan over low heat. Remove from heat. Blend in sugar, vanilla, eggs and salt. Beat until thick. Stir in almonds. Spoon about 1 tsp of filling into each unbaked pastry shell. Bake 20-25 minutes or until lightly browned and filling is set. Cool and store in airtight containers.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ICE BOX COOKIES} \index{ICE BOX COOKIES}
\textit{(Canadian Living)}\\
\step{1 cup butter, softened	
\\ 1 cup sugar
\\ 1 egg	
\\ 2 tsp vanilla
\\ 2 \nicefrac{2}{3} cups flour	
\\ \nicefrac{1}{2} tsp baking powder
\\ \nicefrac{1}{4} tsp salt	
\\ \nicefrac{3}{4} cup chopped candied red or green cherries}{Mix ingredients. Divide dough into thirds. Scrape on third onto large piece of waxed paper. Using paper as guide, roll into 8" long log. Remove paper. Wrap in plastic wrap. Repeat with remaining dough. Refrigerate for at least 3 hours or until firm. Cut into \nicefrac{1}{4} inch thick slices. Place on greased baking sheets. Bake at 375${}^\circ$F for 10-12 minutes. Makes about 84 cookies.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BUCKEYES} \index{BUCKEYES}
\textit{(Melinda Moffit)}\\
\step{\nicefrac{2}{3} cup butter	
\\ 1 \nicefrac{1}{2} cup peanut butter
	\\ 3 cups icing sugar (or less)}{
Melt butter. Combine with peanut butter and icing sugar. Roll in balls size of walnuts. Freeze for easier dipping. Put toothpicks in each ball before freezing for easier dipping.
Melt chocolate. Dip, leaving a small circle on top undipped.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FILBERT FINGERS} \index{FILBERT FINGERS}
\step{1 cup butter	
\\ \nicefrac{3}{4} cup brown sugar
\\ 2 \nicefrac{1}{2} cups flour	
\\ 2 Tbsp milk
\\ 1 cup ground filberts
\\ 	2-1 oz sq semisweet chocolate (or 56 grams)
\\ 	2 Tbsp paraffin wax}
{Form first butter, sugar, flour, and milk into a ball. Knead until soft and pliable. Add filberts. Shape into fingers. Place on ungreased cookie sheet and bake at 375${}^\circ$ for 10 minutes. Melt chocolate and wax. Dip ends of fingers.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE FINGERS} \index{CHOCOLATE FINGERS}
\textit{(Mrs. Barry Thiessen)\\
Definitely a ``must'' at Christmas.}\\
\step{1 \nicefrac{1}{2} cup sugar	
\\ \nicefrac{1}{2} cup milk
\\ \nicefrac{1}{2} cup margarine
\\ \nicefrac{1}{2} tsp vanilla	
\\ pinch salt
\\ 3 cups rolled oats	
\\ 1 \nicefrac{1}{2} cups coconut}{Boil sugar, milk, and margarine until it bubbles. Add vanilla, salt, oats, and coconut. Mix well. Press into 9 x9 pan. Chill for 2 hours. Cut into fingers, 4 rows of 12. Melt 6 oz. chocolate chips with \nicefrac{1}{3} bar of paraffin wax. Dip fingers in and let cool on wax paper.}

\end{minipage}