\section{Icings and Candy}

\begin{minipage}{\linewidth}\rtitle{CHOCOLATE SAUCE} \index{CHOCOLATE SAUCE}
\textit{(LaDonna Mann)}\\
\step{1 cup sugar	
\\ 1 tsp vanilla
	\\ \nicefrac{1}{4} cup butter	
	\\ 3 Tbsp cocoa
	\\ \nicefrac{1}{8} tsp salt	
	\\ \nicefrac{3}{4} cup cream}{
Mix together. Boil until smooth and starts to thicken. Serve warm or cold with ice cream or fruit.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{JACKIE'S AMAZING GLOSSY ICING} \index{JACKIE'S AMAZING GLOSSY ICING}
\textit{(Jackie Buhler)} \\
\step{1 cup sugar	
\\ 6 Tbsp cocoa
\\ 3 Tbsp cornstarch
\\ dash salt
\\ 1 cup boiling water
\\ 3 Tbsp butter
\\ 1 tsp vanilla}{
Add first 4 ingredients to small pot. Add 1 cup boiling water. Cook over medium heat until thick. Remove from heat and remaining ingredients. Pour on cooled cake. Icing will harden in fridge. Is a good coating icing to pour over a softer icing or filling.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BOILED NUT CRUNCH ICING} \index{BOILED NUT CRUNCH ICING}
\step{6 Tbsp butter	
\\ \nicefrac{3}{4} cup packed brown sugar
\\ \nicefrac{1}{2} tsp salt	
\\ \nicefrac{1}{4} cup milk or cream
\\ \nicefrac{1}{2} cup coconut	
\\ \nicefrac{1}{2} cup chopped pecans or walnuts}{Boil butter, brown sugar, salt and milk for 3 minutes, until slightly thickened. Remove from heat, add coconut and chopped nuts. Spread on warm cake. Place under broiler under low heat until mixture bubbles and is golden brown.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE WHIPPED BUTTERCREAM FROSTING} \index{CHOCOLATE WHIPPED BUTTERCREAM FROSTING}
\step{\nicefrac{1}{3} cup cocoa powder
\\ 2 Tbsp cornstarch
\\ \nicefrac{3}{4} cup milk
\\ \nicefrac{3}{4} cup unsalted butter, room temp
\\ 1 cup granulated sugar
\\ 2 tsp vanilla extract
\\ Pinch salt}{In a small saucepan, whisk together the cocoa and cornstarch. Whisk in the milk. Heat the mixture over med heat, whisking constantly, until the mixture becomes thick. Remove from heat, place in a bowl and let cool to room temp. In the bowl of a stand mixer beat the butter, sugar, vanilla and salt until light and fluffy, about 4-5 minutes. Add the cooled chocolate mixture. With the mixer on high speed, beat it until it is light and resembles whipped cream. This should take about 5 minutes.  Frost the cake immediately. If you wait too long before frosting, the air starts to deflate.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHIPPED BUTTER CREAM ICING} \index{WHIPPED BUTTER CREAM ICING}
\textit{(Debbie Snead)}\\
\step{1 \nicefrac{1}{3} cups sugar	
\\ \nicefrac{1}{2} cup flour
\\ \nicefrac{1}{2} tsp salt	
\\ 1 \nicefrac{1}{2} cups milk
\\ \nicefrac{1}{2} tsp flavouring or 2 Tbsp liqueur}{Whisk until smooth. Cook over medium heat until the mixture boils. Boil 1 minute (less at Nairobi altitude). Pour into bowl and chill. Stir occasionally until totally cool. On high speed, beak in 1 cup butter in \nicefrac{1}{4} cup increments until mixture is almost smooth after each addition. Continue beating until very light and fluffy like whipped cream. Add flavouring or liqueur.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BUTTER DECORATING ICING} \index{BUTTER DECORATING ICING}
\step{1 cup butter	
\\ 3 or 4 egg whites
\\ 2 cups icing sugar	flavouring}{Cream butter, add icing sugar. Beat egg whites until stiff. Add icing sugar. Beat well. Add enough icing sugar to make icing very stiff. Will hold shape. Use with decorating tube. NB:  This icing will not harden.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHITE SNOW DRIFT FROSTING} \index{WHITE SNOW DRIFT FROSTING}
\step{\nicefrac{1}{2} cup corn syrup	
\\ 2 egg whites
\\ \nicefrac{1}{2} cup white sugar	
\\ \nicefrac{1}{2} tsp vanilla
\\ 2 Tbsp water}{In saucepan beat corn syrup, white sugar and water just to soft ball stage (syrup forms thin thread). Beat egg whites until they form soft peaks. Gradually add heated syrup, beating continually until mixture stands in stiff peaks. Add vanilla and beat thoroughly.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM CHEESE ICING} \index{CREAM CHEESE ICING}
\step{125 g cream cheese, softened	
\\ 1 Tbsp butter, softened
\\ 1 \nicefrac{1}{2} cups icing sugar	
\\ \nicefrac{1}{2} tsp vanilla flavouring}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FLUFFY MAPLE ICING} \index{FLUFFY MAPLE ICING}
\step{1 \nicefrac{1}{2} cups sugar	
\\ 2 egg whites
\\ \nicefrac{1}{3} cup water	
\\ \nicefrac{1}{2} tsp maple flavouring
\\ \nicefrac{1}{8} tsp salt	
\\ \nicefrac{1}{4} tsp cream of tartar}{Boil the above ingredients together for 3 minutes. Beating constantly, pour syrup in fine stream over 2 unbeaten egg whites to which as been added \nicefrac{1}{4} tsp cream of tartar. Beat 5 minutes or until right consistency to spread. Beat in \nicefrac{1}{2} tsp maple flavouring. This makes a lot of icing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON ICING} \index{LEMON ICING}
\step{\nicefrac{1}{2} cup butter
\\ 2 Tbsp lemon juice
\\ \nicefrac{1}{2} tsp vanilla
\\ 3 cups icing sugar}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ICING FOR COOKIE PAINTING} \index{ICING FOR COOKIE PAINTING}
\step{4 cups icing sugar	
\\ \nicefrac{1}{3} cup water
	\\ food colourings}{
Mix icing sugar and water. Add additional water by Tbsp until you have the right consistency for painting with a paint brush. Add food colourings as desired. I usually mix up deep red, deep green, deep blue and yellow and one container of white. When painting the colours can be lightened by adding white paint. Different shades or colours can be achieved by combining these primary colours.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHITE SAUCE FOR WAFFLES} \index{WHITE SAUCE FOR WAFFLES}
\step{\nicefrac{1}{4} cup waffle batter	
\\ milk
\\ sugar}{Cook until thick. Serve with strawberries or other fresh fruit over waffles.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FRUIT LEATHER} \index{FRUIT LEATHER}
Blend your favourite fruits. Mix with half applesauce or pear puree for the pectin content necessary to keep fruit leather together. Pour THIN layer to dehydrate.

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ALMOND ROCA} \index{ALMOND ROCA}
\textit{(Marcia Dale, Royal Bank, Saskatoon)}\\
\step{1 lb. butter	
\\ \nicefrac{1}{2} cup ground almonds
\\ 2 \nicefrac{1}{4} cup sugar	
\\ 3 bars sweet white chocolate
\\ 1 cup almonds, cut in pieces}{Melt butter, add sugar and cook until caramel colour. Stir constantly. Add almond pieces and pour on buttered cookie sheet. When cool, cover with melted chocolate and sprinkle with ground almonds.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SUGAR PEANUTS} \index{SUGAR PEANUTS}
\step{2 cups sugar	
\\ 1 cup water
\\ 4 cups raw peanuts}{Mix and boil sugar and water. Add peanuts with red skins left on. Boil until the nuts are dry. The sugar forms on the nuts. Turn out onto trays and bake in low oven 15 minutes if they aren't completely dried out.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HONEY CARDAMOM MIXED NUTS} \index{HONEY CARDAMOM MIXED NUTS}
\textit{Packaged in a pretty jar and toped with a bow, they make a great hostess gift.}\\
\step{\nicefrac{1}{4} cup honey	
\\ 2 Tbsp butter, melted
\\ \nicefrac{3}{4} tsp ground cardamom	
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} tsp ground cinnamon	
\\ \nicefrac{1}{4} tsp ground cloves
\\ \nicefrac{1}{4} tsp ground ginger	
\\ 2 containers salted nuts}{Heat oven to 275${}^\circ$F. Spray pan with cooking spray. Mix all ingredients except nuts in large bowl. Add nuts; stir to coat. Spread nuts in pan. Bake 45 minutes, stirring every 15 minutes. Cool in pan, stirring occasionally.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE ORANGE STICKS} \index{CHOCOLATE ORANGE STICKS}
\textit{(Roz Bagwell)}\\
\step{2 large thick-skinned oranges	
\\ 1 cup water
\\ 1 cup caster sugar	
\\ 125 g dark chocolate}{Quarter oranges. Peel away skin, including white pith. Cut skin into strips 1 cm wide. Drop strips into med pan of boiling water, return to boil; drain. Repeat boiling and draining twice more.
Combine water and sugar in med pan. Stir over heat, without boiling, until sugar is dissolved. Add orange strips. Bring to boil. Simmer, uncovered, 7 minutes or until strips become translucent. Stir gently from time to time while simmering.
Using tongs, remove orange strips from pan to wire rack over tray. Allow to dry overnight.
Melt chocolate in small heat proof bowl over simmering water. Dip half of each orange strip into chocolate. Place on tray covered with foil. Stand, uncovered, at room temp until set. Yield:  70. Best made 1 day ahead. Store in refrigerator up to 1 week.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CARAMEL POPCORN} \index{CARAMEL POPCORN}
\textit{(Company's Coming)}\\
\step{Popcorn (pop about 1 cup)	
\\ 1 cup butter or margarine
\\ 2 cups brown sugar, packed	
\\ \nicefrac{1}{2} cup corn syrup
\\ 1 tsp salt	
\\ 1 tsp vanilla
\\ \nicefrac{1}{2} tsp baking soda}{Have popcorn ready in extra large container. Combine butter, brown sugar, syrup and salt in heavy saucepan. Heat and stir over medium heat until boiling. Boil without stirring for 5 minutes.
Stir in vanilla and baking soda. Pour over popcorn. Toss together well until all pieces are coated. Spread on 2 large ungreased shallow pans. Bake in 250 oven for 1 hour, stirring every 15 minutes. Cool thoroughly. Break apart and pack in plastic bags.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PECAN BRITTLE} \index{PECAN BRITTLE}
\step{2 cups sugar
\\ \nicefrac{1}{4} cup soft margarine or butter
\\ 1 cup brown sugar	
\\ \nicefrac{1}{8} tsp baking soda
\\ \nicefrac{1}{2} cup corn syrup	
\\ 2 tsp vanilla
\\ \nicefrac{1}{2} cup water	
\\ 2 cups pecans, coarsely chopped
\\ \nicefrac{1}{8} tsp salt}{Boil sugars, syrup, water and salt to 300${}^\circ$F (brittle in cold water), stirring only until sugar is dissolved. Add butter, soda, vanilla, stirring until mixed. Add nuts and pour at once into greased cookie sheets. Smooth out. Mark into squares. When cool, break where marked.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEANUT BRITTLE} \index{PEANUT BRITTLE}
\step{2 cups peanuts
\\ 2 cups sugar
\\ \nicefrac{1}{4} tsp salt	
\\ \nicefrac{1}{4} tsp soda
\\ 1 tsp vanilla}{Heat sugar gradually in a frying pan, stir constantly with the bowl of the spoon until a golden syrup is formed. Remove from heat and stir in quickly the salt, soda and vanilla. Pour syrup over a layer of peanuts in a greased pan.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{NUTS AND BOLTS} \index{NUTS AND BOLTS}
\step{\nicefrac{1}{4} cup butter 
\\ 1 Tbsp Worcestershire sauce
\\ \nicefrac{1}{2} tsp paprika
\\ \nicefrac{1}{4} tsp garlic salt
\\ \nicefrac{1}{2} tsp onion salt
\\ \nicefrac{1}{2} tsp celery salt
\\ 2 cups thin pretzel sticks	
\\ 1 cup triangles
\\ 1 \nicefrac{1}{2} cups peanuts	
\\ 2 cups Cheerios
\\ 1 cup Shoureddies}{Melt butter and mix Worcestershire sauce, paprika, garlic salt, onion salt, celery salt. Mix. Bake one hour at 250. Stir every 15 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TOFFEE} \index{TOFFEE}
\step{\nicefrac{3}{4} cup cream	
\\ 2 Tbsp butter
\\ \nicefrac{3}{4} cup syrup	
\\ 1 tsp vanilla
\\ 1 cup sugar}{Combine cream, syrup and sugar in a saucepan. Bring mixture to a boil and then lower to a medium heat. Cook for a few minutes longer and reduce to a low heat. Cook until a hard ball stage. Remove from heat, then add butter and flavouring. Stir well and pour into a buttered 8-inch square pan. Let cool and break into pieces.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HEATH TOFFEE BAR} \index{HEATH TOFFEE BAR}
\step{1 cup toasted blanched slivered almonds
\\ 1 cup butter
\\ 1 cup sugar
\\ \nicefrac{1}{3} cup chocolate chips}{Chop almonds and spread half a cup in the bottom of a butter 7x11" pan. Combine butter and sugar in heavy pan and cook, stirring constantly, until it boil. Boil to hard crack stage, 300${}^\circ$F. Pour carefully over almonds. Let stand about 10 minutes until top is set. Sprinkle chocolate chips over the top. Smooth with spatula when melted. Sprinkle remaining almonds over the top. Let stand until cold. Break into squares.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE TRUFFLES} \index{CHOCOLATE TRUFFLES}
\textit{(Kathy Schmidt)}\\
\step{12 oz dark chocolate (5 Bourneville bars)	
\\ 500 ml heavy whipping cream
	\\ 3 Tbsp butter (NO margarine)	
	\\ \nicefrac{1}{4} to \nicefrac{1}{2} cup rum or 1-2 Tbsp extract}{Bring whipping cream to a boil in heavy pan. Stir and watch closely as it boils over easily. Add chocolate broken up in pieces. Stir until chocolate is melted. Continue stirring and allow to come to a gentle boil for 3 minutes. Add butter and rum. Remove from heat and let stand uncovered overnight. Do not put in refrigerator. In morning, cover and let stand for 24 hours. Afterwards, refrigerate. Can be used for making truffles, chocolate butter cream for filling, fruit dip or cake covering. To make truffles: Powder hands with cocoa powder or powdered sugar. Roll balls in cocoa powder, icing sugar or ground nuts. Put in refrigerator to harden. Then re-roll in cocoa powder, icing sugar or ground nuts.}	
\end{minipage}