\chapter{Main Meals}

\section{Beef}

\begin{minipage}{\linewidth}\rtitle{SWISS "STINK" STEAK} \index{SWISS "STINK" STEAK}
\name{(Moira Neufeld)}\\
\step{steak (round or chuck), cut into 2--3" pieces \\
onions, slices\\
carrots, chopped\\
parsnips, chopped\\
celery and leaves, chopped\\
1 can tomato soup	\\
2 Tbsp Worcestershire sauce\\
1 Tbsp brown sugar	\\
\nicefrac{2}{3} tsp dry mustard\\
1 clove garlic	\\
oregano\\
1 bay leaf\\
Salt and pepper \\
strong cheddar, grated}{Brown steak well in oil in heavy skillet. Salt and pepper while browning. Place in baking dish and cover with onions, carrots, parsnips, and celery. Mix remaining ingredients except cheese and add to vegetables and steak. Cover with tin foil. Bake in 400$^\circ$F oven for 2--3 hours. Optional: last 5 minutes, remove cover and sprinkle with grated strong cheddar.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROUND STEAK SAUERBRATEN} \index{ROUND STEAK SAUERBRATEN}
\step{1\nicefrac{1}{2} lb. round steak	\\
1 envelope brown gravy mix (or 2 	bouillon cubes and 2 Tbsp cornstarch) \\
1 Tbsp minced onion	\\
1 Tbsp brown sugar\\
2 Tbsp wine sugar	\\
1 tsp Worcestershire sauce\\
\nicefrac{1}{4} tsp ginger	\\
1 bay leaf
}{Cut meat in 1" squares. Brown in 1 Tbsp shortening. Remove from skillet. Add gravy mix and 2 cups water. Bring to boil. Stir in next six ingredients plus \nicefrac{1}{2} tsp salt and pepper. Add meat. Turn into casserole. Cover. Bake 350$^\circ$F for 1\nicefrac{1}{2} hours. Serve on hot buttered noodles.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HUNGARIAN GOULASH} \index{HUNGARIAN GOULASH}
\step{3 lbs chuck steak
\\ 2 Tbsp butter
\\ 1 \nicefrac{1}{2} litres water or stock
\\ 1 large onion, chopped
\\ 1 bay leaf
\\ 1 tsp salt
\\ Dash of cayenne pepper
\\ 6 med potatoes
\\ 1 tsp paprika
\\ 3 Tbsp flour
\\ 3 Tbsp butter}{Cut meat in cubes, brown quickly in butter, then add the onion and brown slightly. Add stock or water, bay leaf, cayenne, paprika and salt. Simmer 2 \nicefrac{1}{2} hours. Add potatoes and cook about \nicefrac{1}{2} hour, reducing liquid to approx. 3 cups. Thicken with butter and flour.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEEF STROGANOFF} \index{BEEF STROGANOFF}
\step{2 lbs beef chuck roast
\\ \nicefrac{1}{2} tsp salt
\\ 1 tsp prepared mustard
\\ \nicefrac{1}{2} tsp black pepper
\\ 4 oz butter
\\ 4 green onions, white parts only (sliced)
\\ 4 Tbsp flour
\\ 1 10.5 oz can condensed beef broth
\\ 1 cup sliced mushrooms
\\ \nicefrac{1}{3} cup sour cream
\\ \nicefrac{1}{3} cup white wine}{Remove any fat and gristle from the roast and cut into strips \nicefrac{1}{2}" long. Season with \nicefrac{1}{2} tsp salt and \nicefrac{1}{2} tsp pepper. In a large skillet, over med heat, melt butter and brown beef strips quickly. Push beef off to one side. Add onions and mushrooms and cook slowly for 3-5 minutes, then push to the side with the beef strips. Stir flour into the juice. Pour in beef broth and bring to a boil, stirring constantly. Lower the heat and stir in mustard. Cover and simmer for 1 hour or until meat is tender. Five minutes before serving, stir in the sour cream and white wine. Heat briefly then salt and pepper to taste.  Serve over noodles or rice.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEEF BOURGUIGNON} \index{BEEF BOURGUIGNON}
\name{(Company's Coming)}\\
\step{
	2 lbs boneless lean beef	\\
	2 Tbsp butter\\
	2 Tbsp cooking oil	\\
	225 grams small fresh mushrooms\\
	\nicefrac{1}{4} cup flour	\\
	\nicefrac{1}{2} tsp salt\\
	\nicefrac{1}{2} tsp pepper\\	
	2 cups Burgundy (or alcohol free red wine)\\
	1 clove garlic, minced	\\
	1 bay leaf\\
	1 Tbsp ketchup	\\
	1 tsp parsley flakes\\
	\nicefrac{1}{2} tsp thyme	\\
	3 beef bouillon cubes\\
	1 cup boiling water	\\
	398 ml canned small onions, drained}{
Cut beef into 1 inch cubes. Brown in butter and cooking oil. Transfer to large saucepan when browned. Saut\'e mushrooms for 3-4 minutes. Add to meat in saucepan. Put flour, salt and pepper into frying pan. Add enough butter to moisten flour if needed. Stir in burgundy, garlic, bay leaf, ketchup, parsley and thyme until it boils and thickens. Dissolve beef cubes in boiling water. Add to wine mixture. Stir. Pour over meat. Cover. Simmer for 1 hour. Add onions. Simmer, covered for about 30 minutes more until tender. Discard bay leaf.
Note: 1 \nicefrac{1}{2} cups cooked whole pearl onions or cut up onions, cooked may be substituted for canned onions.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MARINATED ROAST BEEF} \index{MARINATED ROAST BEEF}
\name{(Ruth Stalder)}\\
\step{dry mustard	\\
soy sauce \\
	lots of garlic	\\
	herbes de province \\
	red wine
}{Marinate beef for 2 days. Cook in an open roaster for 45 minutes. Baste frequently with the marinade sauce.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{UMAMI ROAST BEEF} \index{UMAMI ROAST BEEF}
\name{Great pressure cooker recipe}\\
\step{1--3 lb roast
\\ 1 Tbsp olive oil
\\ 2 small onions, sliced
\\ 4 cloves of garlic
\\ 8 white mushrooms
\\ 2 Tbsp of wine or balsamic vinegar
\\ 1 cup chicken stock
\\ 1 Tbsp soy sauce
\\ 1 Tbsp fish sauce
\\ pinch of rosemary
\\ pinch of thyme
\\ 2 bay leaves
\\ 2 carrots, chopped
\\ 2--4 potatoes, quartered
\\ 1.5 Tbsp cornstarch
\\ 2 Tbsp water}{Heat pressure cooker on high with Saut\'e button. Pat roast dry, season generously with salt and pepper, and brown roast for 10 minutes on each side. Remove roast. Add oil and saut\'e onions. Add garlic. Add mushrooms. Add wine or balsamic vinegar to deglaze. Add chicken stock, soy sauce, fish sauce, rosemary, thyme, and bay leaves. Place roast back into pot, close lid, and pressure cook on high pressure for 45 minutes. Turn off heat and let it naturally release for 25 minutes. Remove roast and cover with aluminum foil. Add vegetables to pot and cook at high pressure for 4 minutes. Release pressure. Adjust seasonings and mix cornstarch with water and mix with sauce to make a gravy.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HOMESTYLE STEW} \index{HOMESTYLE STEW}
\name{(Company's Coming)}\\
\step{
	1 kg stew meat, cut up	\\
	3 Tbsp cooking oil\\
	4 cups water	\\
	2 med onions, cut up\\
	1 Tbsp Worcestershire sauce	\\
	\nicefrac{1}{2} cup ketchup\\
	1 tsp salt	\\
	1 tsp basil\\
	2 cups sliced carrots	\\
	3 cups potatoes, cup up\\
	1 cup frozen peas}{
Brown meat in cooking oil. Add remaining ingredients, except vegetables. Cover and simmer about 1 \nicefrac{1}{2} hours. Add vegetables. Boil until tender. If desired, gravy may be thickened. Mix 1 Tbsp flour with 2 Tbsp water for each cup of juice.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WIENER SCHNITZEL} \index{WIENER SCHNITZEL}
\name{(Company's Coming)}\\
\step{
	1 \nicefrac{1}{2} lbs veal cutlets\\
	\nicefrac{1}{4} cup flour	\\
	1 tsp salt\\
	\nicefrac{1}{4} tsp pepper	\\
	2 eggs\\
	1 Tbsp water	\\
	1 cup fine dry bread crumbs\\
	2 Tbsp margarine	\\
	2 Tbsp cooking oil}{
Place cutlets between sheets of waxed paper. Pound thin. Repeat. Mix flour with salt and pepper. Beat eggs with water to make a wash. Dip cutlets into flour mixture, then into egg wash, then into crumb mixture to coat well. These may be chilled at this point until ready to cook. Heat margarine and cooking oil in frying pan. Cook cutlets browning on both sides turning with puncturing. Add more margarine and cooking oil if needed. Serves 4.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEEF PARMIGIANA} \index{BEEF PARMIGIANA}
\name{(Company's Coming)}\\
\step{
	1 \nicefrac{1}{2} lbs thinly cut round steak\\
	\nicefrac{1}{3} cup fine dry bread crumbs	\\
	\nicefrac{1}{3} cup grated parmesan cheese\\
	1 egg, fork beaten	\\
	\nicefrac{1}{3} cup cooking oil\\
	1 cup chopped onion	\\
	156 ml tomato paste\\
	2 cups water\\	
	1 tsp salt\\
	\nicefrac{1}{4} tsp pepper	\\
	\nicefrac{1}{2} tsp oregano\\
	1 tsp sugar	\\
	225 g mozzarella cheese slices}{
Cut steak into serving size pieces. Place each piece between waxed paper and pound with meat mallet to \nicefrac{1}{4} in. thickness. Combine crumbs and cheese. Dip meat into egg then into crumb mixture. Fry in cooking oil to brown both sides. Transfer to greased $9\times13$" baking pan. Saut\'e onion in pan until soft. Add more oil if necessary. Add tomato paste, water, salt, pepper, oregano and sugar. Stir. Pour over meat. Layer cheese over top. Cover. Bake in 350$^\circ$F oven until tender, about 1 \nicefrac{1}{4} to 1 \nicefrac{1}{2} hours. Serves 4.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HAMBURGERS} \index{HAMBURGERS}
\step{1 lb ground beef (reg ground beef is just fine)
\\ 2 cloves garlic
\\ 1 tsp black pepper
\\ 1 \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} tsp basil
\\ 2 Tbsp olive oil}{Combine all ingredients.  Shape mixture into 4 patties. Grill on BBQ set at high heat for a few minutes on each side.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEEF TACO CASSEROLE} \index{BEEF TACO CASSEROLE}
\name{(Merle Fingas)\\
Loren's favourite childhood casserole.}\\
\step{1 lb. ground beef	
	\\ 2 tsp chilli powder
	\\ 1 med. onion, chopped	
	\\ \nicefrac{1}{2} tsp garlic salt
	\\ 1 can kidney beans	
	\\ 1 cup tortilla chips (broken)
	\\ 1 can tomato sauce	
	\\ 1 cup shredded cheddar cheese
		}{Cook hamburger and onion. Add beans, tomato sauce, chilli powder and garlic salt. Heat to boiling. Pour half meat mixture into casserole. Pat in tortillas, then rest of meat. Cover. Bake 25--30 minutes at 350$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SIMPLE BEEF PATTY CASSEROLE} \index{SIMPLE BEEF PATTY CASSEROLE}
\step{2 lbs ground beef	\\
	1 cup dry bread crumbs\\
	1 cup water	\\
	2 tsp salt\\
	\nicefrac{1}{2} tsp pepper	\\
	2 Tbsp onion flakes\\
	6 Tbsp flour	\\
	4--6 Tbsp butter\\
	1 tsp salt	\\
	4 cups milk\\
	1 cup water}{Mix first 6 ingredients and form into patties. Brown on both sides. Remove and put in casserole dish. Make sauce with remaining ingredients and meat drippings. Pour gravy over patties. Cover and bake for 1 hour at 350$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SEVEN LAYER CASSEROLE} \index{SEVEN LAYER CASSEROLE}
\step{
	\nicefrac{1}{2}" layer of potatoes, thinly sliced \\
onions, thinly sliced \\
4-5 carrots, thinly sliced \\
\nicefrac{1}{4} cup rice \\
1 cup of peas with liquid \\
1 lb. hamburger\\
1 398 mL can tomato sauce \\
\nicefrac{1}{2} cup water \\
Salt and pepper}
{Layer potatoes, onions, carrots in 9" greased casserole dish. Sprinkle rice over vegetables. Add peas, hamburger, salt and pepper. Combined tomato sauce and water. Pour over casserole. Season and bake, covered in oven for 1 hour. Uncover and bake 1 more hour.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{STUFFED PEPPERS} \index{STUFFED PEPPERS}
\name{(Loraine Hiebert)}\\
\step{\nicefrac{1}{2} lb. hamburger	\\
2 Tbsp raw rice\\
	onion as desired\\	
	salt\\
	2 green peppers \\
	tomato juice or tomato sauce
}
{Cook rice. Brown onions. Add to hamburger. Add salt. Fill 4 halves of peppers. Place in casserole and cover with tomato juice or tomato sauce. Bake at 350$^\circ$F about 1 \nicefrac{1}{2} hours.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SWEDISH MEATBALLS} \index{SWEDISH MEATBALLS}
\step{	\nicefrac{3}{4} lb. lean ground beef	\\
\nicefrac{1}{2} lb. ground veal\\
\nicefrac{3}{4} lb. ground pork	\\
1 \nicefrac{1}{2} cups soft bread crumbs\\
1 cup light cream	\\
\nicefrac{1}{2} cup chopped onion\\
3 Tbsp butter	\\
1 egg\\
\nicefrac{1}{4} cup parsley	\\
1 \nicefrac{1}{4} tsp salt\\
dash pepper	\\
dash ground nutmeg\\
dash ground ginger\\	
\\GRAVY:\\
Drippings\\
2 Tbsp butter\\
2 Tbsp flour\\
1 beef bouillon cube \\
1 \nicefrac{1}{4} cup boiling water \\
\nicefrac{1}{4} instant coffee powder}{Grind meats together twice. Soak bread in cream about 5 minutes. Cook onion in 1 Tbsp of butter until tender. Mix meat, crumb mixture, onion, egg, parsley and seasonings. Beat 5 minutes at medium speed with electric mixer. Chill. Shape into 1 \nicefrac{1}{2} inch balls; brown in remaining butter. Remove from skillet. Make gravy. Add meat. Cover. Cook 30 minutes, basting occasionally with gravy.\\
GRAVY: In skillet, melt butter with drippings. Stir in flour. Dissolve bouillon cube in boiling water. Add to flour mixture along with coffee powder. Cook, stirring constantly, until gravy is thickened and bubbly.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SLOPPY JOES} \index{SLOPPY JOES}
\step{1 kilo ground beef\\
	2 med onions, chopped	\\
	10 oz tinned tomato soup\\
	2 soup cans water	\\
	1 Tbsp sugar\\
	3 Tbsp flour	\\
	1 tsp salt\\
	\nicefrac{1}{2} tsp black pepper}{Brown beef. Add remaining ingredients. Simmer and serve over hot rolls.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROAST MEAT LOAF} \index{ROAST MEAT LOAF}
\step{2 lbs lean ground beef	\\
\nicefrac{1}{2} cup onion, chopped\\
1 large egg	\\
\nicefrac{1}{2} cup oats\\
\nicefrac{1}{2} cup milk	\\
1 \nicefrac{1}{2} tsp salt\\
\nicefrac{1}{2} tsp savoury or thyme	\\
\nicefrac{1}{4} tsp pepper\\
1 Tbsp parsley, snipped\\
\nicefrac{1}{2} cup ketchup or chili sauce\\
	2 Tbsp brown sugar}{Combine all ingredients except the ketchup and brown sugar and put into loaf pan. Combine ketchup and brown sugar and pour over meatloaf. Bake at 350$^\circ$F for 1 \nicefrac{1}{4} hours. Let stand for 10 minutes before slicing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SICILIAN MEAT ROLL} \index{SICILIAN MEAT ROLL}
	\step{2 beaten eggs	\\
	\nicefrac{1}{2} cup tomato juice\\
	\nicefrac{3}{4} cup bread crumbs (soft)	\\
	2 Tbsp parsley\\
	\nicefrac{1}{2} tsp oregano	\\
	\nicefrac{1}{4} tsp each salt and pepper\\
	\nicefrac{1}{2} tsp garlic	\\
	2 lb. ground beef\\
	thinly sliced ham	\\
	mozzarella cheese}{Mix all ingredients except cheese and ham. Pat meat to an 8 x 10" rectangle on waxed paper. Arrange ham and cheese on meat. Roll meat, using paper to lift. Seal edges and end. Place seam side down. Bake at 350$^\circ$F for 1 \nicefrac{1}{4} hours.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CABBAGE ROLLS (HOLUBSCHI)} \index{CABBAGE ROLLS (HOLUBSCHI)}
\step{1 large head cabbage
\\ 1 \nicefrac{1}{2} lbs hamburger
\\ 1 cup cooked rice
\\ 1 med onion, chopped and Saut\'ed
\\ Salt and pepper to taste
\\ 1 large tin tomato sauce}{Place cabbage in boiling water and peel off leaves as they become tender.  Set aside.  Combine onions, meat, rice and seasoning. Blend well. Place a spoonful of meat on a cabbage leaf. Roll up and secure. Place in greased casserole. Repeat until all the meat mixture has been used.  Pour tomato sauce over all. Bake in 350${}^\circ$F oven for 2 hours or until the cabbage is very tender.}


\end{minipage}

\section{Pork}

\begin{minipage}{\linewidth}\rtitle{GRILLED RIBS} \index{GRILLED RIBS}
\name{Bake these ribs ahead of time and leave to marinate overnight.}\\
\step{4 lbs pork spareribs
\\ 1 cup brown sugar
\\ \nicefrac{1}{4} cup ketchup
\\ \nicefrac{1}{4} cup soy sauce
\\ \nicefrac{1}{4} cup Worcestershire sauce
\\ \nicefrac{1}{4} cup rum
\\ \nicefrac{1}{2} cup chili sauce
\\ 2 cloves garlic, crushed
\\ 1 tsp dry mustard
\\ Dash ground black pepper}{Preheat oven to 350${}^\circ$F. Cut spareribs into serving size portions. Wrap in double thickness of foil and bake for 1 \nicefrac{1}{2} hours. Unwrap and drain drippings. Place ribs in a large roasting pan. In a bowl, mix together remaining ingredients. Coat ribs with sauce and marinate at room temp for 1 hour or refrigerate overnight. Preheat grill for med heat. Brush grill grate with oil. Place ribs on grill and cook for 30 minutes, basting with marinade.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PORK TENDERLOIN WITH MUSHROOMS AND OLIVES} \index{PORK TENDERLOIN WITH MUSHROOMS AND OLIVES}
\step{1 lb or more pork tenderloin \\
Seasoned flour\\
2 Tbsp butter\\
onion, sliced\\
\nicefrac{1}{2} cup dry white wine \\
\nicefrac{1}{2} lb mushrooms, sliced\\
\nicefrac{1}{8} tsp fresh rosemary \\
6 green olives, stuffed with almonds and sliced\\
2 Tbsp lemon juice \\
2 Tbsp parsley, garnish}{Cut pork tenderloin into 1" crosswise slices and pound. Roll in seasoned flour. Saut\'e pork and onions in butter until golden. Bring wine just to the boiling point, pour over the meat, and add mushrooms and rosemary. Simmer until done, about 45 minutes. Add olives and lemon juice. Garnish with chopped parsley.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{OVEN BAKED PORK CHOPS WITH POTATOES} \index{OVEN BAKED PORK CHOPS WITH POTATOES}
\step{4 pork chops\\
1.6 lbs baby potatoes\\
1 Tbsp olive oil\\
Salt and pepper
\\\\RUB:\\
1 tsp Worcestershire sauce\\
2 Tbsp ketchup\\
1 Tbsp soy sauce\\
2 Tbsp brown sugar\\
1 Tbsp olive oil\\
1 clove garlic, minced\\
2 tsp apple cider vinegar\\
}{
Preheat oven to 430${}^{\circ}$F. Toss potatoes in oil, sprinkle with salt and pepper and scatter on baking tray. Place in oven for 15 minutes.  Meanwhile, mix Rub ingredients together and slather pork on both sides with the rub, reserving some rub for basting. Take tray out of oven. Toss potatoes then push them to the edge. Place pork on tray. Bake for 15 minutes. Remove tray from oven. Flip pork, spoon over reserved rub and grill 7--10 minutes until well caramelized. Remove from oven. Use brush to get juices of tray and dab it onto the pork. Pop back under broiler for a couple of minutes to finish off.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PORK TENDERLOIN DIABLO} \index{PORK TENDERLOIN DIABLO} 
\step{1 lb whole pork tenderloin \\
2 tsp oil \\
\nicefrac{1}{2} cup chicken broth \\
2 Tbsp heavy cream \\
1 Tbsp extra-hot prepared horseradish \\
1 Tbsp Dijon mustard \\
\nicefrac{1}{4} tsp cayenne pepper \\
1 Tbsp cold butter \\
1 tsp chopped fresh chives}{
Preheat oven to 375${}^{\circ}$F. Season pork with salt and pepper. Heat oil in skillet. Cook pork until browned on one side, about 3--4 minutes. Flip pork and place skilled in oven. Cook until pork is browned and still slightly pink in the center, about 20--25 minutes. Transfer pork to a plate. Remove excess oil from skillet and place over med-high heat. Pour in chicken broth and bring to a boil, scraping any browned bits off the bottom of the pan. Whisk in cream, horseradish, mustard and cayenne pepper. Cook until mixture is reduced to a chick sauce, 3--4 minutes. Remove from heat and whisk in cold butter. Stir in chives. Slice pork into \nicefrac{1}{2} inch slices and serve topped with sauce.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PORK SCHNITZEL WITH DILL SAUCE} \index{PORK SCHNITZEL WITH DILL SAUCE} 
\name{(Company's Coming)}\\
\step{6 boneless pork loin cutlets\\
	1 egg	\\
	2 Tbsp milk\\
	\nicefrac{1}{2} cup fine dry bread crumbs	\\
	1 tsp salt\\
	\nicefrac{1}{4} tsp pepper\\	
	1 tsp paprika\\
	\nicefrac{1}{4} cup margarine\\
	\\DILL SAUCE:\\
2 Tbsp flour\\
2 Tbsp butter\\
\nicefrac{1}{2} tsp dill weed	\\
2 chicken bouillon cubes\\
1 \nicefrac{1}{2} cups boiling water	\\
1 cup sour cream}{
If not already tenderized, place meat between sheets of waxed paper and pound to a \nicefrac{1}{4} in thickness. Snip edges to prevent curling. Fork beat egg and milk. Mix crumbs and spices. Dip meat into egg mixture then into crumbs. Fry, browning both sides until no pink remains. Spoon Dill Sauce over top or serve on the side.\\
DILL SAUCE: Add flour, butter and dill weed to frying pan in which meat was cooked. Mix together. Dissolve bouillon cubes in water. Add and stir until sauce boils and thickens. Add sour cream. Stir and heat through.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PORK AND PINEAPPLE KEBABS WITH PEANUT SAUCE} \index{PORK AND PINEAPPLE KEBABS WITH PEANUT SAUCE}
\step{1 Tbsp thinly sliced green onions	\\
	2 Tbsp peanut butter\\
	2 Tbsp lemon juice	\\
	1 Tbsp soy sauce\\
	1 Tbsp water	\\
	\nicefrac{1}{4} tsp hot sauce\\
	\nicefrac{3}{4} tsp curry powder\\	
	\nicefrac{1}{2} lb lean pork loin, cubed\\
	\nicefrac{1}{2} cup fresh or canned pineapple chunks	\\
	1 small red bell pepper, cut into 1" pieces}{
Combine first 6 ingredients. Reserve \nicefrac{1}{4} cup peanut butter mixture. Cover and Chill. Add curry powder and pork to remaining mixture in bowl. Cover and marinate 1--8 hours. Let reserved \nicefrac{1}{4} cup peanut butter mixture stand at room temp for 30 minutes. Thread pork, pineapple and bell pepper alternately onto skewers. Grill 4 minutes on each side or until done. Serve with reserved sauce and rice.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROAST PORK WITH APPLE AND RAISIN SAUCE} \index{ROAST PORK WITH APPLE AND RAISIN SAUCE}
\step{3 lb. pork loin roast	\\
little melted shortening or oil\\
seasoning	\\
1 \nicefrac{1}{4} cups cider\\
1 lb. small onions or shallots\\
\\SAUCE:\\
1 lb. cooking apples	\\
1 Tbsp sugar\\
\nicefrac{1}{3} cup seedless raisins	\\
juice of \nicefrac{1}{2} lemon\\
\nicefrac{1}{2} tsp ground ginger}{
Score the fat and brush with shortening or oil and sprinkle very lightly with salt. Stand on wire rack in the roasting pan and pour the cider into the pan. Roast at 325$^\circ$F for 3 hours. Boil the onions for 25 minutes in well salted pure water, drain, and add to meat pan 30 minutes before end of cooking time. Peel, core and slice the apples and simmer with the other ingredients needed for the sauce. Serve the roast with onions and sauce, together with a green vegetable and boiled potatoes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROAST PORK WITH FIGS} \index{ROAST PORK WITH FIGS}
\name{(Yvonne Hiebert)}\\
\step{ROAST:
\\ 1 Tbsp hot red pepper flakes
\\ 1 Tbsp salt
\\ 1 Tbsp minced garlic
\\ 4 bay leaves, crumbled
\\ \nicefrac{1}{3} cup olive oil
\\ 3 lb boneless loin of pork, rolled and tied for roasting
\\ \nicefrac{1}{2} cup butter
\\ 1 cup dry white wine}{In a small bowl combine the seasonings and olive oil. Place the meat, fat side up, in a roasting pan and rub the marinade over it. Cut the butter into pats and lay along the top of the roast. Pour the wine into the pan. Roast at 350${}^\circ$F for 1 \nicefrac{1}{2} hours or until juices run golden clear and the internal temp is 170. Spoon wine and meat juices over the roast every 15 minutes. Add more wine to the pan if needed.}

\step{SAUCE AND GARNISH:
\\ 3 oranges
\\ 16 moist dried figs
\\ 2 Tbsp brandy
\\ 1 Tbsp honey
\\ \nicefrac{1}{2} cup orange juice
\\ Salt and pepper to taste}{Peel and slice 2 oranges. Blend figs, orange slices, brandy and honey until fairly smooth. Set aside.
Simmer 8 figs in orange juice for 10 minutes and set aside. \\
10 minutes before the roast is done, remove it from the oven. Arrange the whole figs along the top and pour the orange juice over the meat. Return the meat to the oven for 10 minutes. Place roast on serving platter and keep warm. Pour the pan juices into a small saucepan, scraping the pan to include all the flavorful brown bits, and add the pureed orange and fig mixture. Bring to a boil and simmer for 5 minutes. Add more white wine if needed. Strain the sauce carefully and add salt and pepper to taste. Slice the last orange into half round slices to garnish the roast on its platter.  Pass the sauce separately.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MAPLE-GLAZED PORK ROAST} \index{MAPLE-GLAZED PORK ROAST}
%\step{1 lb. boneless lean pork shoulder butt, trimmed\\
	%1 Tbsp dark rum or orange juice\\
	%2 cloves garlic, sliced thin	\\
	%1 \nicefrac{1}{2} Tbsp maple syrup\\
	%2 tsp lime juice	\\
	%\nicefrac{1}{8} tsp cayenne pepper}{
%Insert garlic slices in gashes in the roast, then rub lime juice into the pork. Combine the rum, maple syrup and cayenne pepper. Add the pork, turning to coat well. Cover and refrigerate at least 8 hours. Turn the pork occasionally in the marinade. Preheat oven to 425$^\circ$F. Placed pork on a rack in a shallow roasting pan. Roast uncovered, brushing often with the marinade, for 20 minutes. Lower the heat to 350$^\circ$F and roast another 20 minutes, brushing often with the remaining marinade. Let the roast stand for 10 minutes at room temperature before slicing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SPARE RIBS} \index{SPARE RIBS}
\name{(Loraine Hiebert)}\\
\step{2 lb. spare ribs\\	
	\nicefrac{1}{2} cup brown sugar\\
	\nicefrac{1}{4} cup vinegar	\\
	2 Tbsp cornstarch\\
	\nicefrac{3}{4} cup ketchup	\\
	1 cup water\\
	1 Tbsp chilli sauce	\\
	3 Tbsp Worcestershire sauce\\
	2 Tbsp soya sauce	\\
	2 Tbsp HP sauce	\\
	1 tsp dry mustard	\\
	1 medium onion}{
Put ribs, salt, pepper and chopped onion in oven at 350${}^\circ$F. Baked until tender and browned. Drain. Add remaining ingredients. Return to oven for one and a half hours.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BBQ (PULLED) PORK} \index{BBQ (PULLED) PORK}
%\step{1 40 oz can beef broth\\
	%3 lbs pork roast (can use a cheap cut)\\
	%1 18 oz bottle BBQ sauce}{
%Pour broth into slow cooker. Add pork. Cook on high for 4 hours or until meat shreds easily. Remove meat and pull apart with 2 forks. At first it will be difficult but keep at it. It gets easier. Preheat oven to 350$^\circ$F. Transfer meat to a Dutch oven. Stir in the BBQ Sauce. Bake 30 minutes. DON'T BE TEMPTED TO SKIP THE OVEN STEP.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SLOW COOKER TEXAS PULLED PORK} \index{SLOW COOKER TEXAS PULLED PORK} 
\step{1 tsp oil \\
4 lb pork shoulder roast \\
1 cup BBQ sauce \\
\nicefrac{1}{2} cup apple cider vinegar \\
\nicefrac{1}{2} cup chicken broth \\
\nicefrac{1}{4} cup light brown sugar \\
1 Tbsp prepared yellow mustard \\
1 Tbsp Worcestershire sauce \\
1 Tbsp chili powder \\
1 extra large onion, chopped \\
2 cloves garlic, crushed \\
1 \nicefrac{1}{2} tsp dried thyme}{Pour vegetable oil into slow cooker. Place pork roast in slow cooker. Combine remaining ingredients and pour over meat. Cover and cook on high until roast shreds easily with a fork, 5--6 hours. Remove meat from slow cooker and shred meat using two forks. Return shredded pork to slow cooker and stir meat into the juices. Serve on toasted hamburger buns with creamy coleslaw.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FRUITED PORK} \index{FRUITED PORK}
\step{1 kg lean pork, cubed	\\
	1 Tbsp Worcestershire sauce\\
	\nicefrac{1}{4} cup flour	\\
	3 Tbsp brown sugar\\
	3 Tbsp oil	\\
	1 tsp salt\\
	1 cup orange juice	\\
	\nicefrac{1}{4} tsp pepper\\
	2 Tbsp lemon juice	\\
	1 Tbsp cornstarch\\
	\nicefrac{1}{4} cup water	\\
	\nicefrac{1}{3} cup raisins\\
	284 ml canned orange sections, drained}{
Coat meat with flour. Heat cooking oil in frying pan. Brown meal on all sides. Transfer to 2 qt casserole. Discard fat in frying pan. Pour orange and lemon juice into pan. Add Worcestershire sauce, sugar, salt and pepper. Stir cornstarch into water. Pour into juice and bring to a boil. Pour over meat. Add raisins \& orange sections. Stir lightly. Cover. Bake at 350$^\circ$F for 1 \nicefrac{1}{2}--2 hours until cooked through and very tender. Serves 6.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CASSEROLE OF PORK AND RED CABBAGE} \index{CASSEROLE OF PORK AND RED CABBAGE}
\step{\nicefrac{3}{4} lb. boneless lean pork butt cut into 1 inch cubes \\
	1 small red cabbage, cored and coarsely shredded (about 2 \nicefrac{1}{2} cups)\\
	2 Tbsp flour	\\
	3 Tbsp red wine vinegar\\
	1 med. size yellow onion, sliced thin	\\
	\nicefrac{1}{2} cup chicken broth\\
	1 med-size carrot, sliced	\\
	2 bay leaves\\
	3 cloves garlic, minced	\\
	\nicefrac{1}{2} tsp allspice\\
	1 large apple, peeled, quartered, sliced thin	\\
	\nicefrac{1}{4} tsp dried sage, crumbled}{
Coat the pork cubes with flour, shaking off any excess. Brown the pork in Dutch oven. Transfer to a bowl and set aside. Preheat the oven to 350$^\circ$F. Add the onion, carrot, and garlic to the Dutch oven and cook, uncovered, over moderate heat until soft, about 5 minutes. Add the apple and cabbage, cover and cook 15 minutes longer or just until the cabbage is wilted. Stir in the remaining ingredients and the reserved pork. Cover and bake for 1 hour. Remove bay leaves.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WURST BUBBAT} \index{WURST BUBBAT}
\name{(Mennonite Treasury)}\\
\step{1 pkg. yeast	\\
3 cups milk\\
\nicefrac{1}{2} cup butter\\	
5 cups flour\\
2 cups raisins\\	
1 \nicefrac{1}{2} tsp salt\\
1 ring of farmer sausage}{Mix as for buns. Line bottom of deep pan with sausage or other meat. Cover with batter. Place more sausage on top of batter. Let rise in warm place for 1 hour. Bake for 1 hour in 375$^\circ$F oven.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HAM STEAKS CANADIENNE} \index{HAM STEAKS CANADIENNE}
\step{2 \nicefrac{1}{2} inch ham steaks	\\
2 tsp dry mustard\\
	12 whole cloves	\\
	3 Tbsp vinegar\\
	\nicefrac{3}{4} cup brown sugar	\\
	\nicefrac{1}{2} cup apple juice\\
	2 Tbsp flour	\\
	3 cored peeled apples\\
	Tart red jelly}{
Press cloves into fat side of each steak and snip fat between cloves. Mix dry ingredients; blend in vinegar and apple juice. Cut 6 apple rings \nicefrac{1}{4}" thick to garnish top, slice remaining apples thinly. Place one steak in greased baking dish, cover with sliced apples and pour \nicefrac{1}{4} cup apple juice mixture over them. Place second steak over apples and garnish top with apple rings. Cover and bake 30 minutes at 325$^\circ$F. Remove cover and pour remaining apple juice mixture over steaks. Continue baking, uncovered about 30 minutes, basting occasionally. Place a tsp of red jelly in center of each apple ring before serving. Serves 6}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TOURTIERE} \index{TOURTIERE}
\step{1 lb ground pork	\\
	\nicefrac{1}{2} tsp allspice\\
	2 lbs ground beef \\	
	pinch of cloves\\
	1 med onion, finely chopped	\\
	2 tsp salt\\
	\nicefrac{1}{2} tsp pepper	\\
	\nicefrac{1}{2} tsp garlic powder\\
	1 \nicefrac{1}{2} cup water\\
	2 med potatoes, cooked and mashed \\
	pastry for two 9" covered pies}{Bring first 8 ingredients to a boil. Simmer 20 minutes. Add potatoes. Cool the mixture. Line two 9" pie pans with pastry. Spoon meat into pie crust. Cover with top crust and bake 1 hour at 375$^\circ$F. Makes 2 pies.}
\end{minipage}

\section{Chicken}

\begin{minipage}{\linewidth}\rtitle{CHICKEN POTPIE} \index{CHICKEN POTPIE}
\name{(Melinda Moffitt)}\\
\step{\nicefrac{1}{4} cup margarine	\\
	\nicefrac{1}{2} tsp salt\\
	3 \nicefrac{1}{2} cups chopped chicken	\\
	4 med cooked potatoes, cubed\\
	2 \nicefrac{3}{4} cup chicken broth	\\
	\nicefrac{1}{3} cup flour\\
	\nicefrac{1}{4} tsp pepper	\\
	3 hard boiled eggs, chopped\\
	3 cooked carrots, sliced\\
	\\TOPPING: \\
  1 cup flour	\\
	1 tsp salt\\
	\nicefrac{1}{2} cup melted margarine	\\
	\nicefrac{1}{2} tsp pepper\\
	2 tsp baking powder	\\
	1 cup milk}{
Melt margarine in a heavy saucepan over low heat; add flour, stirring until smooth. Cook 1 minutes, stirring constantly. Gradually add chicken broth. Cook over medium heat. Stir until thickened. Stir in salt, pepper, chicken, potatoes, carrots and eggs. Spoon into lightly greased $9 \times 13$" pan. Do not increase the amount of topping. It will soak up the gravy and result in a dry potpie.\\
TOPPING: Mix dry ingredients with milk and margarine. Pour over chicken mixture. Bake at 425${}^\circ$F until brown (about 35--40 minutes).}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN MEAT PIE} \index{CHICKEN MEAT PIE}
\name{(Heather Wiebe)}\\
\step{2 cups diced peeled potatoes \\
1 \nicefrac{3}{4} cups sliced carrots \\
1 cup butter, cubed \\
\nicefrac{2}{3} cup chopped onion \\
1 cup flour \\
 1 \nicefrac{3}{4} tsp salt \\
1 tsp dried thyme \\
\nicefrac{3}{4} tsp pepper \\
3 cups chicken broth \\
1 \nicefrac{1}{2} cups whole milk \\
4 cups cubed cooked chicken \\
1 cup frozen peas \\
1 cup frozen corn \\
Pastry for two covered pies}{
Preheat oven to 425${}^{\circ}$F. Boil potatoes and carrots until crisp-tender. Drain. In large skillet, heat butter. Add onion. Cook until tender. Stir in flour and seasonings. Gradually stir in broth and milk. Bring to a boil. Cook until thickened. Stir in remaining ingredients. Remove from heat. Line two 9" pie plates with pastry. Add chicken mixture to pie pies. Cover with pastry. Trim, seal and flute edges. Cut slits in top for steam to escape. Bake 35--40 minutes. or until crust is lightly brown. Let stand 15 minutes before cutting.  Freezer option:  Cover and freeze unbaked pies. Remove from freezer 30 minutes before baking.  Do not thaw. Bake 30 minutes at 425${}^{\circ}$F. Bake another 70--80 minutes longer at 350${}^{\circ}$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{EASY GARLIC CHICKEN} \index{EASY GARLIC CHICKEN}
\name{(Erma Penner)}\\
\step{4 chicken breasts \\
2 garlic cloves, minced \\
\nicefrac{1}{4} cup brown sugar \\
1 Tbsp oilive oil}{
Preheat oven to 500${}^{\circ}$F. Line casserole dish with foil and grease lightly. In small saut\'e pan, saut\'e garlic with oil till tender. Remove from heat and stir in brown sugar. Place chicken in dish and cover with the garlic and brown sugar mixture. Add salt and pepper to taste. Bake uncovered for 30 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{COCONUT CHICKEN} \index{COCONUT CHICKEN}
\step{1 can coconut milk
\\ 4 chicken breasts, cut in 1-2" cubes.
\\ 3 cloves garlic, minced
\\ \nicefrac{1}{2} onion grated or chopped fine
\\ \nicefrac{1}{2} tsp dried ground chili pepper
\\ 3 Tbsp peanut butter
\\ 1 tsp sugar
\\ 1 Tbsp soy sauce
\\ 2 tsp curry powder
\\ 1 chicken bouillon cube}{Simmer chicken in coconut milk for 30 minutes. Add remaining ingredients and continue to simmer for another 15 minutes. Serve with rice.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BRAISED BALSAMIC CHICKEN} \index{BRAISED BALSAMIC CHICKEN}
\name{I like to make this dish in summer and replace the dried herbs with fresh herbs from my garden.}\\
\step{6 skinless, boneless chicken breast halves
\\ Black pepper to taste
\\ 1 tsp garlic salt
\\ 2 Tbsp olive oil
\\ 1 onion, thinly sliced
\\ \nicefrac{1}{2} cup balsamic vinegar
\\ 1 14.5-oz can diced tomatoes (or fresh tomatoes)
\\ 1 tsp dried basil
\\ 1 tsp dried oregano
\\ 1 tsp dried rosemary
\\ \nicefrac{1}{2} tsp dried thyme}{Season chicken breasts with pepper and garlic salt. Heat olive oil in a med skillet. Brown the onion and seasoned chicken breasts. Pour tomatoes and vinegar over the chicken. Season with herbs. Simmer about 15 minutes. or until the chicken is no longer pink and the juices run clear.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ZESTY SEARED CHICKEN} \index{ZESTY SEARED CHICKEN}
\step{\nicefrac{1}{4} cup firmly packed brown sugar	\\
	2 garlic cloves, minced\\
	1 \nicefrac{1}{2} tsp ground cumin	\\
	1 \nicefrac{1}{2} tsp ground coriander\\
	\nicefrac{1}{2} tsp salt	\\
	\nicefrac{1}{2} tsp pepper\\
	\nicefrac{1}{4} tsp dried crushed red pepper	\\
	1 tsp grated fresh ginger\\
	\nicefrac{1}{4} cup lemon juice	\\
	\nicefrac{1}{4} cup soy sauce\\
	4 skinned and boned chicken breast halves\\
	2 Tbsp vegetable oil	\\
	hot cooked couscous}{Combine first 10 ingredients in shallow dish or large zip lock bag. Add chicken and chill 30 minutes, turning chicken occasionally. Remove chicken from marinade. Discard marinade. Cook chicken in hot oil in large skillet over high heat for 4 minutes. Reduce heat to med-low. Turn and cook 10 minutes or until done. Serve with hot cooked couscous.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SWEET-AND-SOUR APRICOT CHICKEN} \index{SWEET-AND-SOUR APRICOT CHICKEN}
\step{2 Tbsp lemon juice	\\
	\nicefrac{3}{4} cup orange juice\\
	2 tsp olive oil	\\
	1 tsp brown sugar\\
	2 cloves garlic, minced	\\
	1 Tbsp cider vinegar\\
	1 chicken cut into serving pieces	\\
	2 tsp minced fresh ginger\\
	\nicefrac{1}{4} tsp black pepper	\\
	1 tsp Dijon or spicy brown mustard\\
	8 med. size dried apricots}{Preheat oven to 425$^\circ$F. In a small bowl, combine lemon juice, oil and half the garlic. Rub the chicken with the mixture and sprinkle with pepper. Arrange the chicken in a single layer on a greased rack in a shallow roasting pan. Place in the oven and roast, uncovered for 30 minutes. Meanwhile, in small saucepan, simmer the apricots in orange juice, uncovered for 10 minutes or until apricots are tender. Stir in sugar, vinegar, ginger, mustard and remaining garlic. Simmer 2 minutes longer. Whirl the mixture in a blender for 15 sec. Coat one side of the chicken with the glaze and roast for 10 more minutes. Turn and coat the other side and roast 10 minutes longer or until the chick if fork-tender. Raise the oven temperature to broil.
Transfer the chicken to the broiler and broil about 5 inches from the heat for 1 to 2 minutes or until tipped with brown. Arrange on a heated platter and serve with a green vegetable.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN WITH DUMPLINGS} \index{CHICKEN WITH DUMPLINGS}
\name{(Loraine Hiebert)}\\
\step{3 \nicefrac{1}{2} lb. stewing chicken, cut up	\\
	3 cups boiling water\\
	2 tsp salt	\\
	1 cup sliced celery\\
	1 cup sliced carrots	\\
	3 onion slices\\
	\nicefrac{1}{8} tsp pepper	\\
	\nicefrac{1}{4} cup sifted, all purpose flour\\
	1 cup cold water\\
	\\DUMPLINGS:\\
\nicefrac{3}{4} cup sifted flour	\\
	1 tsp salt\\
	2 tsp baking powder	\\
	\nicefrac{1}{2} cup cornmeal\\
	\nicefrac{1}{2} cup milk	\\
	1 egg}{Rinse chicken. Pat dry. Place in large cooking utensil. Add boiling water and salt. Bring to boil. Reduce heat to simmer. For 2 hours. Add vegetables and pepper. Cook 30 minutes longer. Remove chicken and add flour and water to chicken broth. Stir constantly until thickened. Return chicken pieces to kettle.\\
	DUMPLINGS: Add beaten egg and milk to sifted dry ingredients. Moisten spoon in hot liquid and drop batter from Tbsp onto hot chicken base. Cover. Cook 20 minutes. Serves 6.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN CREPES} \index{CHICKEN CREPES}
\step{3 Tbsp butter	\\
	\nicefrac{1}{2} tsp salt\\
	3 Tbsp flour	\\
	1 \nicefrac{1}{4} cups milk\\
	2 Tbsp butter	\\
	1 cup diced cooked chicken\\
	2 Tbsp chopped onion	\\
	2 Tbsp chopped pimento (opt)\\
	salt and pepper	\\
	2--3 cups sliced mushrooms\\
	\nicefrac{1}{2} cup mayonnaise	\\
	\nicefrac{1}{4} cup whipping cream, whipped\\
	sauce	grated parmesan cheese}{Melt butter in saucepan. Add flour and salt and stir until blended. Gradually stir in milk. Cook over medium heat, stirring constantly, until thickened. Remove from heat. Set aside. Saut\'e onion and mushrooms in butter until onion is tender. Add chicken and pimento and Saut\'e 1 minute longer. Add \nicefrac{1}{2} cup white sauce and stir until just blended. Remove from heat and add salt and pepper to taste. Refrigerate until ready to use. Combine remaining sauce with mayonnaise. Mix well. Fold in cream.\\
CREPES: I use \hyperlink{crepelink}{Company's Coming recipe}. Make them about 4". Place 1 Tbsp filling on each and roll. Arrange crepes in buttered $9 \times 13$" baking dish. Cover with foil and bake at 350$^\circ$F for 20--25 minutes until heated through. Spoon topping over crepes and sprinkle with parmesan cheese. Broil 4--6" from heat until nicely browned (watch carefully).}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN ENCHILADAS} \index{CHICKEN ENCHILADAS}
\step{
2 lbs chicken breast \\
1 can condensed cream of chicken soup \\
1 \nicefrac{1}{4} cups sour cream \\
\nicefrac{1}{4} twp chili powder \\
1 Tbsp butter \\
1 small onion, chopped \\
4 oz can chopped green chilies, drained \\
1 pkg mild taco seasoning \\
1 bunch green onions, chopped \& divided \\
1 cup water \\
1 tsp lime juice  \\
\nicefrac{1}{2} tsp onion powder \\
\nicefrac{1}{2} tsp garlic powder \\
8 10" flour tortillas \\
3 cups cheese, shredded \& divided \\
1 \nicefrac{1}{4} cups enchilada sauce \\
6 oz can sliced black olives\\
\\ENCHILADAS SAUCE: \\
\nicefrac{1}{4} cup vegetable oil \\
2 Tbsp flour \\
\nicefrac{1}{4} cup chili powder \\
8 oz can tomato sauce \\
1 \nicefrac{1}{2} cups water \\
\nicefrac{1}{4} tsp ground cumin \\
\nicefrac{1}{4} tsp garlic powder \\
\nicefrac{1}{4} tsp onion salt \\
Salt to taste}{
Simmer chicken until no longer pink. Shred chicken. Set aside. Combine chicken soup, sour cream and chili powder in saucepan. Simmer over low heat. Turn of heat and cover to keep warm. Heat butter in skillet. Saut\'e onion until translucent. Add chicken, green chilies, taco seasoning, half of green onions and water. Simmer for 10 minutes. Stir in lime juice, onion and garlic powder. Simmer an additional 10 minutes. Stir 1 cup soup mixture into skilled with chicken mixture. Spread remaining soup mixture on bottom of a $9 \times 13$" baking dish. Fill each tortillas with chicken mixture. Sprinkle cheddar cheese over chicken filling before loosely rolling tortilla. Reserve half of cheese for topping. Place seam side down in prepared pan. Pour enchilada sauce evenly over enchiladas. Cover with remaining cheddar cheese. Sprinkle reserved green onions and sliced olives on top of cheese. Bake in 350${}^{\circ}$F oven until filling is heated through and cheese is melted and bubbling, about 25 minutes.\\
ENCHILADAS SAUCE: Heat oil in skillet over high heat. Stir in flour and chili powder. Reduce heat to med and cook until lightly browned, stirring constantly to prevent flour from burning. Gradually stir in remaining ingredients. Cook approximately 10 minutes or until slightly thickened.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN ALMONDZINI} \index{CHICKEN ALMONDZINI}
\step{\nicefrac{3}{4} cup mayonnaise	\\
	6 oz. spaghetti, cooked\\
	\nicefrac{1}{3} cup flour	\\
	2 cups cooked chicken, cubed\\
	\nicefrac{1}{4} cup minced onion	\\
	1 cup cooked broccoli, chopped\\
	1 tsp garlic salt	\\
	4 oz. canned, sliced mushrooms\\
	3 cups milk	\\
	2 Tbsp chopped pimento\\
	1 cup shredded Swiss cheese	slivered or sliced almonds}{
In med. saucepan combine mayonnaise, flour, onion and garlic salt. Gradually add milk; cook over low heat, stirring constantly until thickened. Add cheese and stir until melted. In large bowl combine spaghetti, chicken,, mushrooms, broccoli, pimento and cheese sauce. Toss and put in $12 \times 7$" baking dish. Top with almonds. Bake at 350$^\circ$F for 30--40 minutes until heated. Serve with parmesan cheese. Serves 5 or 6.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN BROCOLI} \index{CHICKEN BROCOLI}
\step{3 lb. frying chicken, cooked	\\
	1 10-oz. can mushroom soup\\
	broccoli	\\
	1 10-oz. can cream of chicken soup\\
	1 can of fresh mushrooms	\\
	\nicefrac{1}{2} tsp salt\\
	dash of pepper\\	
	1 \nicefrac{1}{2} cup cooked rice\\
	\nicefrac{1}{4} tsp paprika	\\
	1 small onion, shredded\\
	\nicefrac{3}{4} cup shredded cheddar cheese	\\
	sliced almonds for garnish}{Bone chicken and cut into bite size pieces. Combine soups, salt and pepper, rice and paprika. Set aside. In a greased $9 \times 13$" casserole, arrange chicken and mushrooms on bottom. Cover with broccoli pieces. Top with soup mixture. Sprinkle with cheese and almonds. Bake 20--25 minutes at 375$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MOIRA'S CHICKEN} \index{MOIRA'S CHICKEN}
\name{(Moira Neufeld)}\\
\step{2 \nicefrac{1}{2} to 3 lb. chicken, cut up	\\
	\nicefrac{1}{3} cup flour\\
	\nicefrac{1}{2} tsp paprika\\	
	1 tsp salt\\
	\nicefrac{1}{8} tsp pepper\\
	3 Tbsp cooking oil	\\
	1 clove garlic, crushed\\
	2 green peppers, cut in thin strips	\\
	1 cup orange juice\\
	1 cup water	\\
	\nicefrac{2}{3} tsp crushed chilli pepper\\
	\nicefrac{2}{3} cup seedless raisins}{Dry chicken pieces well with paper towel. Combine flour, paprika, salt, and pepper. Roll chicken pieces in flour mixture to coat all sides. Save any leftover flour. Heat oil in large heavy skillet. Add chicken pieces and brown well on all sides. Push chicken to one side of skillet or remove to another pan. Add garlic and green peppers to drippings. Cook gently, stirring, 5 minutes. Sprinkle in leftover flour and stir to blend. Stir in orange juice and water gradually. Bring to a boil, stirring constantly. Sprinkle in chilli peppers and raisins. Cover pan and simmer until chicken is tender, 30--40 minutes, turning chicken pieces occasionally. You may find that you have to add more liquid.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SWISS CHICKEN CUTLETS} \index{SWISS CHICKEN CUTLETS}
\step{2 thin slices Swiss cheese	\\
	4 chicken cutlets\\
	2 Tbsp flour	\\
	\nicefrac{1}{2} tsp pepper\\
	1 Tbsp butter	\\
	\nicefrac{1}{2} cup chicken broth\\
	\nicefrac{1}{4} cup white wine or chicken broth	\\
	\nicefrac{1}{4} tsp dried oregano\\
	chopped fresh parsley and fresh oregano sprigs for garnish}{
Cut each cheese slice in half. Place 1 half on top of each cutlet. Starting with a short end, tightly roll up cutlets, jelly roll style. Tie securely with string. On waxed paper, combine flour and pepper. Mix well. Coat cutlets. In a large skillet, melt butter. Add cutlets. Cook, turning frequently, until golden, about 3 minutes. Add broth, wine and dried oregano to skillet. Increase heat. Bring to a boil. Reduce heat to medium low. Simmer until chicken is cooked through and sauce is slightly thickened, about 10--12 minutes. Place on a service plate. Remove string. Garnish.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN IN GRAVY} \index{CHICKEN IN GRAVY}
\step{\nicefrac{1}{3} cup flour
\\ 1 tsp salt
\\ \nicefrac{1}{4} tsp pepper
\\ 1 tsp paprika
\\ 3 lbs chicken cut up, or chicken parts
\\ 4 Tbsp butter or margarine
\\ \\ GRAVY:
\\ 5 tbsp flour
\\ 1--4 Tbsp butter or margarine
\\ 4 cup water
\\ 1 tsp salt
\\ \nicefrac{1}{4} tsp pepper
}{Put flour and spices in bag. Shake to mix. Put damp chicken pieces in bag. Shake to coat. Brown chicken in butter. Transfer to casserole or small roaster. Pour gravy over chicken. Cover. Bake at 350${}^\circ$F for 1 hour.\\
GRAVY: Melt butter in pan used to fry chicken. Add flour. Add water and stir until boiling. It should be fairly thin. It will thicken in roaster.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN KIEV} \index{CHICKEN KIEV}
\name{(Company's Coming)}\\
\step{4 large boneless chicken breasts, halved, skin removed \\
	\nicefrac{1}{2} cup butter	\\
	2 Tbsp chopped parsley\\
	1 Tbsp chopped chives	\\
	2 eggs, beaten\\
	2 Tbsp milk	\\
	1 cup fine dry bread crumbs}{
Pound meat with mallet to \nicefrac{1}{8} in thickness. Cover with waxed paper before pounding. Mix butter, parsley and chives. Chill. Shape into 8 balls. Keep chilled. Beat eggs and milk together. Lay butter ball on meat. Fold meat over butter, pressing butter to fit, tucking in ends to cover well. Secure with wooden picks. Dip into egg then crumbs. Deep fry in hot fat for about 15--20 minutes until golden. Remove picks to serve. Serves 8.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN FLORENTINE SANDWICH} \index{CHICKEN FLORENTINE SANDWICH}
%\name{(Company's Coming)}\\
%\step{6 small chicken breasts, halved, skin removed, boned \\
	%\nicefrac{1}{2} cup grated parmesan cheese\\
	%300 g spinach, cooked and drained\\	
	%1 egg\\
	%1 tsp flour	\\
	%\nicefrac{3}{4} tsp salt\\
	%\nicefrac{1}{4} tsp pepper\\	
	%\nicefrac{1}{4} tsp nutmeg\\
	%6 cooked ham, thin slices\\
	%1 egg	\\
	%2 Tbsp water\\
	%1 cup fine dry bread crumbs	\nicefrac{1}{3} cup}
%{Pound chicken flat with meat mallet. Lay all 12 pieces on counter. Sprinkle cheese on 6 pieces. Combine spinach, first egg, flour, salt, pepper and nutmeg in blender. Puree. Put spoonful on each of the 6 pieces over cheese. Cut ham to fit and place over spinach mixture. Lay remaining 6 chicken pieces over all. Pinch edges together. Beat second egg and water with fork to make egg wash. Dip chicken sandwiches into egg wash then coat with crumbs. Arrange in well greased baking pan large enough to hold in single layer. Drizzle with melted butter. Bake in 400$^\circ$F oven for about 30--40 minutes until browned and cooked. Turn at half time for more even browning. Serves 6.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN BREASTS DIANE} \index{CHICKEN BREASTS DIANE}
\step{4 large boneless chicken breast halves or 8 small halves \\
	\nicefrac{1}{2} tsp salt	\\
	\nicefrac{1}{4} tsp black pepper\\
	2 Tbsp olive oil	\\
	2 Tbsp butter\\
	3 Tbsp chopped chives	\\
	juice of \nicefrac{1}{2} lemon\\
	2 Tbsp brandy, (opt)\\	
	3 Tbsp chopped parsley\\	
	2 tsp Dijon style mustard	\\
	\nicefrac{1}{4} cup chicken broth}{Place chicken breast halves between sheets of waxed paper or plastic wrap. Pound slightly with mallet. Sprinkle with salt and pepper. Heat 1 Tbsp each of oil and butter in skillet. Cook chicken over high heat for 4 minutes on each side. Do not cook longer or they will be overcooked and dry. Transfer to warm serving platter. Add chives, lemon juice and brandy. parsley and mustard to pan. Cook 15 sec, whisking constantly. Whisk in broth. Stir until sauce is smooth. Whisk in remaining butter and oil. Pour sauce over chicken. Serve immediately.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PINEAPPLE AND CHICKEN WESTERN STYLE} \index{PINEAPPLE AND CHICKEN WESTERN STYLE}
\step{4 chicken breasts	\\
	\nicefrac{3}{4} cup uncooked long grain rice\\
	1 cup diced celery	\\
	one 10 oz. can pineapple tidbits`\\
	1 Tbsp soya sauce	\\
	1 \nicefrac{1}{2} cups chicken stock\\
	2 tsp salt	\\
	\nicefrac{1}{4} tsp poultry seasoning}{Brown chicken breasts. In casserole combine rice, pineapple juice, salt, seasoning, soya sauce and chicken stock. Place browned meat on top of casserole. Bake 350$^\circ$F for 1 \nicefrac{1}{2} hours. Uncover last 15 minutes of baking. Add pineapple and celery.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BBQ CHICKEN} \index{BBQ CHICKEN}
\name{(Steinbach Bible College)}\\
\step{\nicefrac{1}{8} cup vinegar	\\
	\nicefrac{1}{2} cup water\\
	\nicefrac{1}{2} cup brown sugar	\\
	\nicefrac{1}{4} cup chopped onion\\
	\nicefrac{1}{2} cup chopped celery	\\
	\nicefrac{1}{2} tsp mustard\\
	\nicefrac{1}{2} tsp salt	\\
	\nicefrac{1}{2} tsp pepper\\
	\nicefrac{1}{2} tsp chilli powder	\\
	\nicefrac{1}{4} cup soya sauce\\
	\nicefrac{1}{2} cup ketchup	\\
	12 pieces chicken}{Fry onions and celery a bit. Mix all ingredients. Pour over chicken and bake.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN FINGERS} \index{CHICKEN FINGERS}
	\step{4 chicken breasts, halved. Cut each half into 3 finger length pieces. \\
	 \nicefrac{1}{2} cup butter, melted	 \\
	 \nicefrac{3}{4} cup dry fine bread crumbs. \\
	 \nicefrac{1}{4} cup grated parmesan cheese	 \\
	 \nicefrac{3}{4} tsp salt \\
	 \nicefrac{1}{4} tsp basil	 \\
	 \nicefrac{1}{4} tsp thyme}{Combine bread crumbs, herbs and cheese. Dip each chicken finger in butter then coat with crumbs. Place on greased, foil lined baking sheet. Bake for 25--30 minutes at 400$^\circ$F. Turn at half time.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{POULET DE NORMANDIE} \index{POULET DE NORMANDIE}
\step{1 pkg seasoned bread stuffing	
\\ 	\nicefrac{1}{4} cup margarine or butter
\\ 1 cup water
\\ 2 \nicefrac{1}{2} cups cooked, diced chicken	
\\ \nicefrac{1}{2} cup chopped celery
\\ \nicefrac{1}{2} cup diced onion	
\\ \nicefrac{1}{2} cup mayonnaise
\\ \nicefrac{1}{4} cup chives or green onions	
\\ \nicefrac{3}{4} Tbsp salt
\\ 2 beaten eggs	
\\ 1 \nicefrac{1}{2} cups milk
\\ 1 can condensed cream of mushroom soup}
{Mix bread stuffing, butter, or water lightly. Put one half in $12 \times 8$" buttered dish. Mix chicken, celery, onion, mayonnaise, chives, and salt. Put on top of bread mixture. Then put rest of bread mixture over the meat. Combine eggs and milk and pour over the chicken and stuffing. Cover and refrigerate overnight. Take out 1 hour before baking. Top with mushroom soup. Bake uncovered 40 minutes at 325$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TURKEY DRESSING} \index{TURKEY DRESSING} \index{Gluten Free!dressing}
\name{(Loraine Hiebert)\\
I have successfully made this GF.  Increase the quantities by 5 to serve 20 people.}\\
\step{4 cups bread crumbs
\\ 1 tsp salt
\\ 4 Tbsp butter
\\ 2 Tbsp parsley
\\ 1 onion, finely chopped
\\ 1 \nicefrac{1}{2} tsp poultry seasoning
\\ \nicefrac{1}{4} tsp pepper
\\ Turkey neck and giblets or chicken carcass}{Melt butter.  Add all ingredients except the Turkey neck and giblets. Combine thoroughly. Place in greased slow cooker.  Place Turkey neck and giblets or chicken carcass on top of the dressing.  Cook in slow cooker for 1 hour on high heat. Reduce to low heat and cook another 4 hours.}

\step{POULTRY SEASONING: 
\\ 1 cup dried parsley
\\ \nicefrac{1}{2} cup rubbed sage
\\ \nicefrac{1}{4} cup dried rosemary
\\ \nicefrac{1}{4} cup dried marjoram
\\ 1 Tbsp salt
\\ 1 Tbsp black pepper
\\ 1 tsp onion powder
\\ \nicefrac{1}{2} tsp ground sage}{Makes 2 cups.}


\end{minipage}


\section{Fish}

\begin{minipage}{\linewidth}\rtitle{FRIED FISH THE IRISH WAY} \index{FRIED FISH THE IRISH WAY}
\name{(Loraine Hiebert)}\\
\step{4 Tbsp flour
\\ \nicefrac{1}{2} tsp baking powder
\\ Salt \& pepper
\\ \nicefrac{1}{4} cup cold water
\\ 4 small filets
\\ Hot oil for frying}{Mix the flour, baking powder and seasonings with the cold water until you have the consistency of thick cream.  Dip the filets in the mixture then drop them one at a time into the pan of smoking hot oil. The batter will puff up and become very crisp while the fish remains moist and succulent inside.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SESAME SOLE} \index{SESAME SOLE}
\step{\nicefrac{1}{4} cup buttermilk	\\
	\nicefrac{1}{2} tsp dried tarragon, crumbled\\
	4 sole or other white fish fillets	\\
	2 Tbsp flour\\
	2 tsp Dijon or spice brown mustard	\\
	3 \nicefrac{1}{2} Tbsp sesame seeds\\
	2 tsp tomato paste	\\
	4 tsp oil\\
	lemon slides, optional}{
Pour buttermilk in a shallow dish and dip sole fillets in it, coating well all over. Lay fillets on a platter. Combine mustard, tomato paste and tarragon and spread on both sides of fillets.
Combine flour and sesame seeds in a pie pan and press fillets into mixture to coat all over. Place fillets on a rack and refrigerate, uncovered for 30 minutes to make coating stick.
In heavy skillet, heat oil over mod high heat. Add sole and cook until golden, about 1 \nicefrac{1}{2} minutes on each side. If the sesame seeds brown too quickly, lower the heat. Serve with lemon slices.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED FISH} \index{BAKED FISH}
\step{1 \nicefrac{1}{2} lbs fish fillets, cut in serving pieces. \\
	\nicefrac{1}{4} tsp salt	\\
	dash of pepper\\
	1 Tbsp lemon juice\\
	2 tsp dry mustard.}
{Place fish fillets in shallow, greased baking dish. Sprinkle with salt, pepper, and lemon juice. Add 2 tsp dry mustard. Pour over fish. Sprinkle with \nicefrac{1}{3} cup buttered bread crumbs and 1 Tbsp minced parsley. Bake 35 minutes at 350$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROILED SALMON PATTIES} \index{BROILED SALMON PATTIES}
\step{2 eggs, beaten	\\
	1 tsp salt\\
	\nicefrac{1}{8} tsp pepper	\\
	1 tsp Worcestershire sauce\\
	1 Tbsp lemon juice	\\
	\nicefrac{1}{2} cup cracker or dry bread crumbs\\
	1 \nicefrac{1}{2} cups flaked salmon, fresh or canned}{
Beat eggs, add seasonings, crumbs and lemon juice. Mix well. Add salmon. Form into 5 or 6 flat patties. Place on cold broiler rack. Brush with melted fat or wrap with bacon strips. Broil approx. 7 minutes on each side.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROLLED FISH FILLETS} \index{ROLLED FISH FILLETS}
\step{454 g sole fillets (or other)	\\
	113 g broken shrimp, drained\\
	2 Tbsp grated carrot	\\
	2 Tbsp chopped green onion\\
	sprinkle salt	\\
	sprinkle pepper\\
	2 Tbsp butter, melted	\\
	grated cheddar cheese for garnish\\
	\\LEMON SAUCE:\\
2 Tbsp butter	\\
	2 Tbsp flour\\
	\nicefrac{1}{2} tsp salt	\\
	sprinkle white pepper\\
	\nicefrac{1}{8} tsp onion powder	\\
	1 cup milk\\
	2 Tbsp lemon juice	\\
	2 Tbsp butter (opt)\\
	1 egg (opt)}{
Lay fillets on working surface. Mash shrimp lightly. Divide and spread among fillets. Sprinkle with carrot, onion, salt and pepper. Roll. Place seam side down in greased baking pan. Gently brush with melted butter. Bake uncovered in 425$^\circ$F oven for about 15--20 minutes until fish flakes easily. Transfer to warmed platter. Spoon lemon sauce over top.\\
LEMON SAUCE: Make as for white sauce. Put sauce into blender. Add second amount of butter and egg. Blend until smooth. Return to saucepan. Heat and whisk until it starts to boil.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{STUFFED FISH FILLETS WITH NUTMEG SAUCE} \index{STUFFED FISH FILLETS WITH NUTMEG SAUCE}
\step{2 Tbsp margarine	\\
	4 small flounder, sole or other white fish fillets\\
	1 green onion, chopped	\\
	4 tsp flour\\
	\nicefrac{1}{2} cup cooked brown rice	\\
	\nicefrac{3}{4} cup chicken broth\\
	1 tsp grated lemon rind\\	
	\nicefrac{1}{8} tsp pepper\\
	1 tsp lemon juice\\	
	\nicefrac{1}{4} cup dry white wine or chicken broth\\
	\nicefrac{1}{2} tsp ground nutmeg	\\
	1 Tbsp minced parsley\\
	\nicefrac{1}{8} tsp salt	\\
	lemon wedges}{
Preheat oven to 350$^\circ$F. In heavy skillet, melt half the margarine over mod heat. Add green onion and carrot and cook until just tender. Stir in rice and half of lemon rind, lemon juice, nutmeg and pepper. Add salt. Sprinkle fillets with remaining \nicefrac{1}{8} tsp pepper. Place \nicefrac{1}{4} of rice mixture on half of each fillet and gently pack to compress, leaving about a \nicefrac{1}{4} inch margin on 3 edges. Fold the other half of fillet over filling and carefully pink two ends together with a toothpick. Bake fish in a lightly greased pan for 25 to 30 minutes. Meanwhile, prepare the sauce. Melt the remaining margarine in a small heavy saucepan. Blend in flour and cook 3 to 5 minutes. Add chicken broth and remaining lemon rind, lemon juice and nutmeg and pepper. Cook until thickened and smooth. Stir in wine and parsley. Transfer fish to a warm platter and garnish with lemon wedges.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FILLET OF FISH WITH CASHEWNUTS} \index{FILLET OF FISH WITH CASHEWNUTS}
\step{1 whole fish (1 \nicefrac{1}{2} kg)	\\
	\nicefrac{3}{4} cup crushed cashew nuts\\
	egg yolk	\\
	butter or oil for basting\\
	juice of 1 lemon	\\
	1 Tbsp melted butter\\
	1 Tbsp sherry	\\
	2 Tbsp butter for frying}{
Season the fish with salt and pepper. Grill, basting well with lemon juice, butter or oil. Mix crushed nuts with egg yolk and melted butter to form a paste. Fry the paste in butter until golden brown. Deglaze the pan with sherry to loosen the nuts. Spread the nuts over the fish and serve very hot with wedges of lemon and sprigs of fresh parsley. Serves 3--4.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SALMON WITH GARLIC LEMON BUTTER SAUCE} \index{SALMON WITH GARLIC LEMON BUTTER SAUCE}
\step{
4 salmon fillets, about 1" thick \\
2 tsp olive oil \\
2 garlic cloves, minced \\
\nicefrac{1}{4} cup chicken broth \\
2 Tbsp lemon juice \\
3 Tbsp + 1 tsp unsalted butter, diced into pieces \\
\nicefrac{1}{2} tsp honey \\
2 Tbsp minced fresh parsley}{
In small saucepan melt 1 tsp butter over medium heat. Add garlic and saut\'e. Pour in chicken broth and lemon juice. Let sauce simmer until it has reduced by half. Stir in butter and honey and whisk until combined. Set sauce aside. Dry salmon fillets with paper towel. Season both sides with salt and pepper. Heat olive oil in heavy skillet over medium-high heat. Once oil is shimmering add salmon and cook 4 minutes on first side until golden brown. Flip and cook until salmon has cooked through, about 2--3 minutes longer. Plate salmon and drizzle each serving generously with butter sauce. Sprinkle with parsley and garnish with lemon slices.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED SALMON AND LEEKS} \index{BAKED SALMON AND LEEKS}
\step{1 whole salmon fillet, about 1 \nicefrac{1}{2} pounds
	\\ 2 medium leeks, chopped	
	\\ 1 Tbsp olive oil
	\\ 1 Tbsp butter	
	\\ Salt \& pepper
	\\ 1 lemon, zested \& juiced	
	\\ 1 Tablespoon soy sauce
	\\ 1 Tablespoon olive oil	
	\\ 1 clove garlic	
		}{
Saut\'e leeks in butter and oil until very soft, about 20 minutes. Season with salt. Let cool to lukewarm. Cut a slit on the side of the fillet. Place salmon on a baking sheet with parchment paper. Preheat oven to 350$^\circ$F. Combine remaining ingredients and spoon over fillet. Spread leek mixture inside fish. Spoon remaining marinade over salmon. Bake 15--18 minutes.}
\end{minipage}

\input{Pasta.tex}

\chapter{Vegetables}

\begin{minipage}{\linewidth}\rtitle{VEGETARIAN CASSEROLE} \index{VEGETARIAN CASSEROLE}
\step{thinly sliced cauliflower	\\
	thinly sliced onion \\
	sliced mushrooms	\\
	light sprinkle of salt, pepper, basil and oregano\\
	sliced cheddar cheese (not processed)	\\
	sliced tomatoes\\
	sliced zucchini	\\
	light sprinkle of salt, pepper, basil and oregano\\
	sliced apple (peeled and cored)	whole pecans\\
	sliced mozzarella}{In a large square casserole, place the ingredients in even layers. Set oven at 300$^\circ$F and bake until the cheese is melted and inside is hot. Approximately 1 \nicefrac{1}{2} hours. If cheese begins to brown too much cover with aluminum foil. If casserole is to be cut into portions, let stand at room temperature 15--20 minutes before cutting.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SWEET POTATO CASSEROLE} \index{SWEET POTATO CASSEROLE}
\step{3 cups mashed sweet potatoes
\\ 1 \nicefrac{1}{2} cup sugar
\\ 3 eggs
\\ \nicefrac{3}{4} cup milk
\\ 5 Tbsp melted butter
\\ 1 \nicefrac{1}{2} tsp vanilla
\\\\TOPPING:
\\ 1 cup brown sugar
\\ \nicefrac{1}{3} cup flour
\\ \nicefrac{1}{4} cup melted butter
\\ \nicefrac{1}{2} cup chopped pecans}{Mix thoroughly and put in greased casserole. Spread topping over potato mixture and bake at 350${}^\circ$F for 30 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HERB-ROASTED POTATOES} \index{HERB-ROASTED POTATOES}
\step{Russet new potatoes (about 2 lbs), quartered or left whole \\
	2 Tbsp  olive oil	\\
	2 cloves garlic, peeled \& whole\\
	1 tsp salt and pepper	\\
	2 cups minced mixed fresh herbs (such as parsley, basil, sage, chives, oregano, mint)}{
Combine potatoes, oil, garlic and \nicefrac{1}{2} cup herbs in shallow baking dish. Place in oven and roast at 350$^\circ$F until golden brown, stirring, occasionally, 45 minutes to 1 hour. 
Remove from oven and toss with remaining herbs. Taste and season with salt and pepper. Serve warm.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HASHBROWN CASSEROLE} \index{HASHBROWN CASSEROLE}
\step{1 kg bag frozen hashbrowns	
	\\ 2 tin cream of chicken or mushroom soup
	\\ \nicefrac{1}{2} cup melted margarine	
	\\ \nicefrac{1}{2} cup sour cream
	\\ 2 cup shredded cheddar cheese	
	\\ salt and pepper}{Mix all together and put in greased casserole dish, uncovered. Bake 45 minutes at 375$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GARLIC AND BASIL MASHED POTATOES} \index{GARLIC AND BASIL MASHED POTATOES}
\step{10 cloves garlic, unpeeled	\\
	3 Tbsp olive oil\\
	9 med potatoes	\\
	1 8 ounce carton sour cream\\
	\nicefrac{1}{4} cup grated parmesan 	\\
	\nicefrac{1}{4} tsp salt\\
	about \nicefrac{1}{4} cup milk	\\
	\nicefrac{1}{4} cup packed fresh basil leaves, snipped\\
	2 Tbsp grated parmesan cheese	}{Place garlic in ramekin. Drizzle oil over garlic. Bake at 350$^\circ$F for 20 minutes or until garlic is very soft. Cool. Peel garlic, discarding skins and reserving oil.
Boil potatoes. Drain. Beat potatoes on low speed. Add all ingredients except milk and basil. Gradually beat in enough milk to make fluffy. Fold in basil. Spoon into greased 2 quart casserole. Cover and chill up to 24 hours.
Bake, covered, at 325$^\circ$F for 45 minutes. Stir sprinkle with 3 Tbsp parmesan cheese. Bake 30--45 minutes more or until heated through.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SLOW COOKER MASHED POTATOES} \index{SLOW COOKER MASHED POTATOES}
\step{5 lbs red potatoes, cut into chunks \\
1 Tbsp minced garlic \\
3 cubes chicken bouillon \\
8 oz sour cream \\
8 oz cream cheese \\
\nicefrac{1}{2} cup butter \\
Salt and pepper to taste}{Cook potatoes, garlic and bouillon in salted water until potatoes are tender but firm, about 15 minutes. Drain, reserving water. Mash potatoes with sour cream and cream cheese, adding reserved water as needed to attain desired consistency. Transfer potatoes to a slow cooker. Cover and cook on low for 2--3 hours. Just before serving stir in butter and season with salt and pepper.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FONDANT POTATOES} \index{FONDANT POTATOES}
\name{(Josh Hagen)}\\
\step{3 large russet potatoes \\
2 Tbsp oil \\
3 Tbsp butter \\
4 sprigs thyme \\
\nicefrac{1}{2} cup chicken broth \\
Salt and pepper}{
Preheat oven to 425${}^{\circ}$F. Cut off ends of russet potatoes. Stand potatoes on end and peel potatoes from top to bottom with a sharp knife to make each potato into a uniform cylinder. Cut each cylinder in half crosswise to make 6 potato cylinders about 2 inches long. Place potatoes in a bowl of cold water for about 5 minutes to remove starch from outside. Pat dry with paper towels.  Heat oil in cast iron skillet over high heat. Place potatoes on end in hot oil. Lower heat to medium-high and fry until well browned, 5--6 minutes. Season with salt and pepper. Flip potatoes onto the opposite end. As they cook use paper towel to blot out oil from skillet. Add butter and thyme springs to skillet. Using tongs, pick up thyme spring and paint butter over top of potatoes. Cook until butter foams and foam turns from white to a pale tan color. Season with more salt and pepper. Pour chicken stock into skillet. Transfer skillet to preheated oven and cook until potatoes are tender and creamy inside, about 30 minutes. If potatoes aren't tender, add \nicefrac{1}{4} cup more stock and let cook an additional 10 minutes. Place potatoes on a serving platter and spoon thyme scented butter over potatoes. Let cool 5 minutes before serving.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{POTATO PANCAKES} \index{POTATO PANCAKES}
\step{2 \nicefrac{1}{2} cups grated raw potato	\\
	\nicefrac{3}{4} tsp salt\\
	1 egg	\\
	2 Tbsp chopped onion\\
	\nicefrac{1}{4} cup flour	\\
	\nicefrac{1}{4} cup lard}{Combine egg, onion, flour and salt. Drain grated potatoes and add to first mixture. Melt lard in skillet. Add spoonfuls of potato mixture. Spread lightly and fry until underside is crisp and brown. Turn and brown other side. Serve hot.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ARBY'S COPYCAT CURLY FRIES BATTER} \index{ARBY'S COPYCAT CURLY FRIES BATTER}
\step{\nicefrac{1}{2} cup all-purpose flour
\\ 2 tsp paprika 
\\ 1 tsp seasoned salt 
\\ \nicefrac{1}{2} tsp cayenne 
\\ Kosher salt and freshly ground black pepper
\\ 1 cup of water}{Marinate for 30 minutes before deep frying.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED BEANS} \index{BAKED BEANS}
\name{(Loraine Hiebert)}\\
\step{4 cups beans	\\
	1 tsp soda\\
	1 tsp mustard	\\
	1 can tomato soup\\ 
	1 cup water\\
	\nicefrac{1}{4} lb. butter\\	
	2 tsp molasses}{Soak beans overnight. In morning boil until skins break when you blow on them. Put into bean pot with butter, molasses, mustard, salt and pepper. Bake 3 to 4 hours at 300$^\circ$F. Add 1 cup hot water before putting crock in oven. Boil tomato soup and water together for 5 minutes. When beans are done, add tomato mixture.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SPICY BAKED BEETS} \index{SPICY BAKED BEETS}
\step{5 med. beets	\\
	1 small onion\\
	1 small potato	\\
	2 Tbsp vegetable oil\\
	2 Tbsp white vinegar	\\
	2 Tbsp brown sugar\\
	1 Tbsp water	\\
	\nicefrac{1}{2} tsp salt\\
	\nicefrac{1}{4} tsp freshly ground black pepper\\
	\nicefrac{1}{4} tsp celery seed\\
	\nicefrac{1}{4} tsp ground cloves}{
Peel beets and shred coarsely. You should have about 3 cups. Place in a greased 1 quart casserole. Peel and grate onion and potato and stir into beets. In a cup or small bowl, stir together oil, vinegar, sugar, water, salt, pepper, celery seed and cloves. Stir into vegetable mixture, cover tightly and bake in a 350$^\circ$F oven for 30 minutes. Stir once or twice.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GREEN BEAN CASSEROLE} \index{GREEN BEAN CASSEROLE}
\step{1 lb fresh green beans, halved \\
3 Tbsp butter \\
\nicefrac{1}{2} onion, finely chopped \\
1--2 cloves garlic, minced \\
2 cups fresh mushrooms, thinly sliced \\
3 Tbsp flour \\
1 \nicefrac{1}{2} cups chicken stock \\
Salt and pepper \\
\nicefrac{1}{2} cup heavy cream, half and half or evaporated milk \\
6 oz can French-fried onion rings}{
Boil green beans in salted water or 5 minutes to blanch. Drain and rinse immediately with cold water. Set aside.  Saut\'e onion until translucent, 3 or minutes. Stir in garlic and mushrooms and cook 2--3 minutes more. Sprinkle flour over the mixture and stir in well. Cook a couple more minutes, then whisk in chicken stock. Stir until thickened and bubbly. Stir in green beans and season. Summer another 1--2 minutes. Remove from heat and stir in cream. Adjust seasoning to taste. Put vegetables in an oven proof casserole dish. Top evenly with the fried onion rings. Bake at 350${}^{\circ}$F until bubbling and slightly brown on top, about 10--15 minutes. Serve immediately.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HONEY GARLIC BUTTER ROASTED CARROTS} \index{HONEY GARLIC BUTTER ROASTED CARROTS}
\step{
2 lbs carrots \\
\nicefrac{1}{3} cup butter \\
3 Tbsp honey \\
4 garlic cloves, minced \\
\nicefrac{1}{4} -- \nicefrac{1}{2} tsp salt \\
Black pepper \\
2 Tbsp fresh chopped parsley}{
Preheat oven to 425${}^{\circ}$F. Lightly grease a large baking sheet. Set aside. Trim ends of carrots and cut into thirds. Melt butter in skillet. Pour in honey and cook until better is completely melted. Add garlic and cook 30 seconds. Add carrots and allow sauce to thicken for a further minute, while tossing carrots. Season with salt and pepper. Transfer carrots to baking sheet in a single layer. Toss to evenly coat. Roast 20 minutes then broil for an additional 2--3 minutes to char the edges. Garnish with parsley.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ZUCCHINI PATTIES} \index{ZUCCHINI PATTIES}
\step{2 cups grated zucchini \\
2 eggs, beaten \\
\nicefrac{1}{4}  cup chopped onion \\
\nicefrac{1}{2} cup flour \\
\nicefrac{1}{2} cup parmesan cheese \\
\nicefrac{1}{2} cup shredded mozzarella \\
Salt to taste \\
2 Tbsp vegetable oil}{Combine all ingredients except oil.  Heat oil in skillet over med-high heat. Drop mixture by heaping tablespoonfuls and cook for a few minutes on each side until golden.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROASTED VEGETABLES} \index{ROASTED VEGETABLES}
\step{1 small butternut squash, cubed
\\ 2 red bell peppers, seeded and diced
\\ 1 sweet potato, peeled and cubed
\\ 3 Yukon Gold potatoes, cubed
\\ 1 red onion, quartered
\\ 1 Tbsp chopped fresh thyme
\\ 2 Tbsp chopped fresh rosemary
\\ \nicefrac{1}{4} cup olive oil
\\ 2 Tbsp balsamic vinegar
\\ Salt and pepper}{Mix together herbs, oil, vinegar, salt and pepper.  Add vegetables. Toss until they are coated. Spread evenly on a large roasting pan. Roast 35--40 minutes at 475${}^\circ$F, stirring every 10 minutes. Vegetables should be cooked through and browned.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROASTED BRUSSELS SPROUTS} \index{ROASTED BRUSSELS SPROUTS}
\step{1 \nicefrac{1}{2} lbs brussels sprouts, ends trimmed
\\ 2 Tbsp olive oil
\\ 1 tsp salt
\\ \nicefrac{1}{2} tsp ground black pepper}{Preheat oven to 400${}^\circ$F. Place Brussels sprouts, olive oil, salt and pepper in a large ziplock bag.  Seal tightly and shake to coat. Pour onto a baking sheet and roast 30--45 minutes, shaking the pan every 5--7 minutes for even browning. Reduce heat when necessary to prevent burning. Brussels sprouts should be dark brown, almost black, when done. Serve immediately.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MAPLE-ROASTED BRUSSELS SPROUTS WITH HAZELNUTS} \index{MAPLE-ROASTED BRUSSELS SPROUTS WITH HAZELNUTS}
\step{\nicefrac{1}{2} cup hazelnuts (toasted with skins rubbed off)\\
	6 cups Brussels sprouts (trimmed and halved)\\
	1 small red onion, cut into \nicefrac{1}{2}" wedges	\\
	2 Tbsp olive oil	\\
	\nicefrac{1}{2} tsp salt\\
	\nicefrac{1}{4} tsp pepper\\	
	\nicefrac{1}{4} cup maple syrup\\
	2 tsp cider vinegar}{Coarsely chop nuts. Toss together with sprouts, onion, oil, salt and pepper. Roast in pan at 425$^\circ$F, stirring occasionally, until tender and edges are browned (30 minutes) Add nuts, syrup and vinegar. Roast another 5 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{EGGPLANT PARMIGIANA} \index{EGGPLANT PARMIGIANA}
\step{1 large eggplant\\
	salt and pepper\\
	fine, dry breadcrumbs\\
	egg\\
	oil\\
	2 onions\\
	2 green peppers\\
	1 \nicefrac{1}{2} cups tomato puree or thinned tomato paste\\
	1 tsp mixed oregano\\
	1 tsp basil \\
	1 tsp thyme\\
	8 oz grated cheese}{Slice eggplant, salt, and pepper. Dip into breadcrumbs, then egg, then crumbs again. Fry until tender in oil. Put in baking dish. Chop onions and green peppers and Saut\'e. Add to eggplants. Puree tomato puree with spices and pour over eggplant. Sprinkle with cheese and bake 20--30 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APRICOT-GLAZED CARROTS} \index{APRICOT-GLAZED CARROTS}
\step{2 lbs carrots, sliced	\\
	1 \nicefrac{1}{4} tsp salt\\
	3 Tbsp butter	\\
	\nicefrac{1}{3} cup apricot preserves\\
	\nicefrac{1}{4} tsp ground nutmeg	\\
	1 tsp grated orange rind\\
	2 Tbsp fresh orange juice	\\
	garnish of fresh parsley}{
Cook carrots and 1 tsp salt in boiling water until tender. Drain. Melt butter in saucepan. Stir in apricot preserves until blended. Stir in remaining ingredients. Add carrot and toss to coat.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GARLIC FRIED GREENS} \index{GARLIC FRIED GREENS}
\step{\nicefrac{1}{2} cup golden raisins	\\
	2 Tbsp sherry\\
	1 tsp olive oil\\	
	10 garlic cloves, slivered\\
	3 lbs tender young greens (such as arugula, spinach, young turnip tops, etc)\\
	Freshly ground pepper	\\
	\nicefrac{1}{4} cup toasted pine nuts or slivered almonds}{
Heat raisins in sherry and plump for 30 minutes.
In large skillet, heat oil over med heat. Add garlic and Saut\'e for 1 minutes. Turn heat to med high. Add greens and cover. Cook 30--40 seconds. Remove lid, toss greens with a fork, replace lid and cook for 1 minutes, tossing several times. Some greens may take longer to cook. Pour raisins and sherry over greens. Season generously with pepper. Add pine nuts and toss. Serve immediately.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SCHMOOR KOHL} \index{SCHMOOR KOHL}
\step{12 cups chopped white cabbage	\\
2 cups chopped dried apples\\
15 prunes\\
\nicefrac{3}{4} cups water	\\
\nicefrac{1}{3} cup cooking oil\\
2 \nicefrac{1}{2} tsp salt	\\
\nicefrac{1}{3} cup white sugar}{Cook uncovered in a heavy saucepan for several minutes. Cover and simmer 1 \nicefrac{1}{2} to 2 hours. If the fruit is very sour, add more sugar to taste.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CABBAGE BRAISED WITH CARROTS AND ONIONS} \index{CABBAGE BRAISED WITH CARROTS AND ONIONS}
\step{\nicefrac{1}{2} cabbage	\\
	3 carrots\\
	2 onions	\\
	\nicefrac{1}{4} cup butter\\
	\nicefrac{1}{2} cup parsley	\\
	1 tsp salt\\
	\nicefrac{1}{4} tsp pepper\\	
	1 cup water}{Chop or shred cabbage coarsely. Shoured carrots coarsely and chop onions. In large skillet, melt butter. Add onions and cook over medium heat until soft, about 3 minutes. Then add cabbage, carrots and finely chopped parsley and mix until well coated with butter. Stir in salt, pepper and water. Cover, bring to a boil, reduce heat to low and cook for 10--15 minutes or until vegetables are tender-crisp and still quite bright in colour.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ONIONS IN RAISIN SAUCE} \index{ONIONS IN RAISIN SAUCE}
%\step{1 \nicefrac{1}{2} tsp oil\\	
	%\nicefrac{3}{4} lb. small white onions, peeled\\
	%2 cloves garlic, minced	\\
	%\nicefrac{1}{3} cup dry white wine\\
	%1 cup beef broth	\\
	%2 Tbsp tomato paste\\
	%2 Tbsp raisins	\\
	%\nicefrac{1}{2} tsp grated orange rind\\
	%\nicefrac{1}{4} tsp dried basil \\
	%\nicefrac{1}{4} tsp dried thyme	\\
	%\nicefrac{1}{8} tsp black pepper}{
%Heat oil. Add onion and cook, uncovered, stirring frequently, until they are golden. About 7 minutes. Add garlic, wine, broth, tomato paste, raisins, orange rind, and spices. Simmer. Cook, uncovered for 20 minutes. Raise heat to high and cook, stirring, until sauce is thick. About 3 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MENNONITE CHICKEN STUFFING (BUBBAT)} \index{MENNONITE CHICKEN STUFFING (BUBBAT)}
 \name{(Loraine Hiebert)}\\
\step{1 cup flour	\\
	1 \nicefrac{1}{2} tsp baking powder\\
	\nicefrac{1}{2} tsp salt	\\
	2 Tbsp shortening melted\\
	1 egg (beaten)	\\
	\nicefrac{1}{3} cup milk\\
	1 cup raisins	\\
	2 Tbsp sugar if desired}{
Mix dry ingredients. Add egg, shortening and milk. Mix well, add raisins. Bake 350${}^\circ$F for 20 minutes or use as a filling in chicken.}

\end{minipage}

\chapter{Brunch}

\begin{minipage}{\linewidth}\rtitle{CHEESY AMISH BREAKFAST CASSEROLE} \index{CHEESY AMISH BREAKFAST CASSEROLE}
\step{1 lb bacon, diced \\
1 onion, chopped \\
4 cups frozen shredded hash brown potatoes, thawed \\
9 eggs, lightly beaten \\
2 cups shredded cheddar cheese \\
1 \nicefrac{1}{2} cups cottage cheese \\
1 \nicefrac{1}{4} cups shredded Swiss cheese
}{Saut\'e bacon and onion until bacon is browned. Drain. Transfer to a large bowl. Stir in remaining ingredients. Pour mixture into greased $9 \times 13$" baking dish. Bake at 350${}^{\circ}$F until eggs are set and cheese is melted, about 45--50 minutes. Let stand 10 minutes before cutting and serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BRUNCH ENCHILADAS} \index{BRUNCH ENCHILADAS}
\step{2 cups cubed ham \\
\nicefrac{1}{2} cup chopped green onion \\
\nicefrac{1}{2} cup chopped green or red pepper (opt) \\
10 8" soft tortillas \\
2 cups shredded cheese \\
2 cups half \& half cream \\
6 eggs, lightly beaten \\
\nicefrac{1}{2} tsp salt
}{Place ham, onion and pepper on a tortilla.  Top with 2 tsp cheese.  Roll up and place seam down on greased $9 \times 13$" pan. Mix eggs, cream and salt and pour over tortillas.  Cover with foil and refrigerate 8 hours (or overnight).  Bake covered at 350${}^{\circ}$F for 25 minutes. Sprinkle remaining cheese and Bake 10 minutes longer with the cover. Let sit 10 minutes before serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED OMELETTE} \index{BAKED OMELETTE}
\name{Warning:  prepare the night before. Make 24 hours before.}\\
\step{3 cups bread cubes \\
3 cups ham cubes\\
3 cups shredded cheese\\
1 Tbsp flour\\
1 tsp dry mustard\\
3 cups milk\\
2 Tbsp melted butter\\
6 eggs}{Combine bread cubes, ham, and cheese. Place in $9 \times 13$" pan. Mix flour and mustard and spread over crumbs. Mix milk, butter, and eggs and pour over pan. Bake at 350${}^{\circ}$F for 1 hour.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SPINACH AND CHEESE CREPES} \index{SPINACH AND CHEESE CREPES}
%\step{2 eggs	\\
	%1 \nicefrac{1}{4} cups milk\\
	%1 cup flour\\
	%2 Tbsp oil	\\
	%\nicefrac{1}{2} tsp salt\\
	%spinach\\
	%3 Tbsp butter	\\
	%3 Tbsp flour\\
	%\nicefrac{1}{2} tsp salt	\\
	%1 tsp nutmeg\\
	%1 \nicefrac{1}{2} cups milk\\	
	%1 \nicefrac{1}{2} cups grated cheese\\
	%paprika or parmesan cheese}{
%Beat eggs until frothy. Add milk, flour, oil, and salt. Chill before using. Make 12 crepes. Cook and drain spinach. Melt the butter, add flour, salt and nutmeg. Add \nicefrac{1}{2} cup of milk at a time, boiling and stirring between additions and after the last boil, add cheese. Mix one third of the cheese sauce with the spinach, spread spinach mixture over the crepe and roll it up. Place the filled crepe in a well-oiled oven dish, then pour the remaining sauce over the crepes and sprinkle with paprika. Bake at 200$^\circ$C until bubbly.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{QUICHE LORRAINE} \index{QUICHE LORRAINE}
\step{1 9" unbaked pie shell
\\ \nicefrac{1}{4} lb bacon
\\ \nicefrac{1}{2} cup diced swiss cheese
\\ 2 cups milk or cream
\\ 3 eggs
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{8} tsp white pepper
\\ Fresh grating of nutmeg
\\ 1 tsp chopped chives}{Fry bacon. Don't allow it to become crisp. Break up the bacon and sprinkle in the bottom of the pie shell. Put the diced cheese and chopped chives in the pie shell.  Scald the milk or cream. Remove from heat. Whisk in 3 eggs and the seasonings. Pour the custard mixture into the pie shell.  Bake at 350${}^\circ$F for 35--40 minutes. or until the top is golden and the custard has set.  Allow quiche to rest 5 minutes before serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FRITATTA} \index{FRITATTA}
\name{(Jackie Buhler)}\\
\step{2 tsp oil	\\
	1 chopped onion\\
	10 oz chopped spinach 	\\
	6 oz grated cheddar cheese\\
	\nicefrac{1}{3} cup cottage or feta cheese	\\
	3--4 eggs\\
	\nicefrac{1}{4} tsp cayenne pepper	\\
	salt\\
	\nicefrac{1}{8} tsp nutmeg}{
Preheat oven to 375. Grease 9" pie plate. Cook onion in oil 5 minutes. Add spinach and stir until cooked and water evaporates. Sprinkle cheeses into pie plate. Top with spinach mixture. Beat remaining ingredients and pour over spinach and cheese. Bake 30--40 minutes until set. Let stand 5 minutes before cutting. Variation:  spinach can be omitted and meat or cooked vegetables added.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FRENCH TOAST} \index{FRENCH TOAST}
\step{3 eggs	
\\ 1 tsp sugar
\\ \nicefrac{1}{2} tsp salt	
\\ \nicefrac{3}{4} cup milk
\\ 8--10 slices bread}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{wafflelink}{WAFFLES}} \index{WAFFLES}
\name{(quick version)}\\
	\step{1 \nicefrac{1}{2} cups flour	
	\\ 2 Tbsp sugar
	\\ 1 Tbsp baking powder	
	\\ \nicefrac{1}{2} tsp salt
	\\ 2 eggs, beaten	
	\\ 1 \nicefrac{1}{2} cups milk
	\\ \nicefrac{1}{4} cup melted butter}{
Put flour, sugar, baking powder and salt into mixing bowl. Stir very well. Make a well in center. Beat eggs well until frothy in separate bowl. Stir in milk and butter. Pour into well. Beat only until smooth. Fill hot waffle iron according to its instructions.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRISPY WAFFLES} \index{CRISPY WAFFLES}
\name{(Joy of Cooking)}\\
\name{Although a little more work than the quick version \hyperlink{wafflelink}{waffle} recipe, the resulting texture is more tender, with a crisp exterior. If used with savoury food, omit the sugar.}\\
	\step{1 \nicefrac{3}{4} cups cake flour	
	\\ 2 tsp baking powder
	\\ \nicefrac{1}{2} tsp salt	
	\\ 1 Tbsp sugar
  \\ 3 egg yolks, beaten
  \\ 2--7 Tbsp melted butter
	\\ 1 \nicefrac{1}{2} cups milk
	\\ 3 egg whites, beaten}{
Make a hole in center of dry ingredients. Pour in liquid ingredients and combine with a few swift strokes. Batter should be pebbled, similar to muffin batter. Beat 3 egg whites until stiff but not dry.
Fold whites into batter until they are barely blended. Bake in a waffle iron.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHITE SAUCE FOR WAFFLES} \index{WHITE SAUCE FOR WAFFLES}
\step{\nicefrac{1}{4} cup waffle batter	
\\ milk
\\ sugar}{Cook until thick. Serve with strawberries or other fresh fruit over waffles.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PANCAKES} \index{PANCAKES}
\name{(Company's Coming)}\\
	\step{1 \nicefrac{1}{2} cups flour	
	\\ 1 Tbsp granulated sugar
	\\ 1 Tbsp baking powder	
	\\ \nicefrac{1}{2} tsp salt
	\\ 1 egg, beaten	
	\\ 2 Tbsp oil
	\\ 1 \nicefrac{1}{2} cups milk}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{crepelink}{CREPES}} \index{CREPES}
\name{(Company's Coming)}\\
	\step{4 eggs	
	\\ 1 cup milk
	\\ 1 cup water	
	\\ 2 cups flour
	\\ 4 Tbsp cooking oil	
	\\ 1 tsp sugar
	\\ \nicefrac{1}{4} tsp salt}{
Beat eggs in large bowl until frothy. Add rest of ingredients. Beat smooth. Cover and store in refrigerator overnight or at least a few hours. Add milk before cooking if too thick. Pour 2 Tbsp in greased hot crepe pan. Tip pan to swirl batter all over pan bottom. Remove when underside is lightly browned. Stack with waxed paper between each crepe. Secure in plastic bag to store in freezer. Use as needed. Makes 24 crepes.
Chocolate Sauced Crepes: Cut vanilla ice cream about 1x1x4 inches long and lay on edge of unbrowned side of crepe. Roll. Allow 2 crepes per serving. Spoon hot chocolate sauce over top.
Strawberry cream crepes: spread with 250 g cream cheese, \nicefrac{1}{4} cup sugar and 1 cup sour cream. Roll. Combine slices strawberries and sugar and spoon over crepes.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PANNEKUCHEN} \index{PANNEKUCHEN}
\name{(Kyle Kroening)}\\
	\step{8 eggs	
	\\ 1 \nicefrac{1}{3} cups milk
	\\ 1 \nicefrac{1}{3} cups flour	
	\\ 1 tsp salt
	\\ 6 Tbsp butter}{Combine ingredients except butter. Pour mixture into pan. Dot surface with butter. Bake at 450${}^\circ$F for 15 minutes. Lower temperature to 350${}^\circ$F. Bake for additional 10 minutes. Serve with jam or syrup.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED OATMEAL (GF*)} \index{BAKED OATMEAL (GF*)}
\name{(LaDonna Mann)}\\
	\step{\nicefrac{2}{3} cup oil	
	\\ \nicefrac{2}{3} cup brown sugar
	\\ 3 eggs, beaten	
	\\ 3 \nicefrac{2}{3} cup oatmeal
	\\ 3 tsp baking powder	
	\\ \nicefrac{2}{3} tsp salt
	\\ 1 \nicefrac{1}{4} cup milk}{
Mix well and pour into greased pan. Bake at 350$^\circ$F about 30 minutes or until center is set. Serve with warm milk, cinnamon, bananas, etc. This keeps well in the refrigerator.}

\end{minipage}