\chapter{Marinades, Dry Rubs, and Sauces}

\begin{minipage}{\linewidth}\rtitle{SANTA MARIA TRI TIP DRY RUB} \index{SANTA MARIA TRI TIP DRY RUB}
\step{1 tri tip roast	
	\\ 1 Tbsp kosher salt
	\\ 1 Tbsp ground black pepper	
	\\ 1 Tbsp garlic powder
	\\ 1 Tbsp onion powder	
	\\ \nicefrac{1}{2} tsp cayenne
	\\ 1 Tbsp dried oregano	
	\\ 1 tsp dry rosemary
	\\ \nicefrac{1}{2} tsp dry sage	
		}{Mix dry rub and apply to meat. Let sit for 1 hour. Sear roast 3-4 min per side. Cover grill and cook until tri tip reaches 130$^\circ$F (20-40 min). Remove from grill and let it rest in foil for 10 min.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{STEAK MARINADE FOR GRILLING} \index{STEAK MARINADE FOR GRILLING}
\step{\nicefrac{1}{3} cup soy
\\ \nicefrac{1}{2} cup olive oil
\\ \nicefrac{1}{3} cup lemon juice
\\ \nicefrac{1}{4} cup Worcestershire 
\\ 1 \nicefrac{1}{2} Tbsp garlic powder
\\ 3 Tbsp dried basil
\\ 1 \nicefrac{1}{2} Tbsp parsley, dried
\\ 1 tsp white pepper}{Blend on high for 30 second. Marinate steak up to 8 hrs.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHICKEN MARINADE FOR GRILLING} \index{CHICKEN MARINADE FOR GRILLING}
\step{\nicefrac{3}{4} cup oil
\\ \nicefrac{1}{3} cup soy
\\ \nicefrac{1}{4} cup Worcestershire
\\ \nicefrac{1}{4} cup red wine vinegar
\\ 2\nicefrac{1}{2} Tbsp lemon juice
\\ 1 Tbsp dry mustard
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} Tbsp pepper
\\ \nicefrac{3}{4} tsp parlsey}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TERIYAKI MARINADE} \index{TERIYAKI MARINADE}
\step{\nicefrac{1}{2} cup oil	
	\\ 1 cup soy sauce
	\\ 3 Tbsp brown sugar	
	\\ 3 mashed cloves garlic
	\\ 1 Tbsp grated gingerroot	
	\\ 2 Tbsp sherry	
	\\ \nicefrac{1}{2} cup peanut butter (opt)
		}{Marinate meat 4-12 hours.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BBQ SAUCE} \index{BBQ SAUCE}
\step{\nicefrac{1}{4} cup onion, chopped\\
1 Tbsp drippings\\
\nicefrac{1}{2} cup water	\\
1 cup chilli sauce\\
2 Tbsp vinegar	\\
\nicefrac{1}{2} tsp salt\\
1 Tbsp Worcestershire sauce	\\
\nicefrac{1}{4} tsp paprika\\
\nicefrac{1}{4} cup lemon juice\\	
\nicefrac{1}{4} tsp pepper\\
2 Tbsp brown sugar\\	
1 tsp mustard or curry}{Saute onion in drippings. Add remaining ingredients and simmer for 20 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PREPARED MUSTARD} \index{PREPARED MUSTARD}
\step{2 Tbsp dry mustard \\
2 Tbsp flour\\
2 Tbsp sugar	\\
\nicefrac{1}{2} cup vinegar\\
\nicefrac{1}{2} cup water	\\
1 tsp salt\\
\nicefrac{1}{2} to 1 tsp turmeric}{Combine all ingredients in top of double boiler. Blend until smooth. Cook over boiling water until thickened.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HOLLANDAISE SAUCE} \index{HOLLANDAISE SAUCE}
\step{4 egg yolks
\\ 1 Tbsp lemon juice
\\ \nicefrac{1}{2} cup unsalted butter, melted
\\ Pinch cayenne
\\ Pinch salt}{Vigorously whisk the egg yolks and lemon juice together in a stainless steel or glass bowl until the mixture is thickened and doubled in volume. Put mixture in a double boiler over barely simmering water. Continue to whisk rapidly. Be careful not to let the eggs get too hot or they will scramble. Slowly drizzle in the melted butter and continue to whisk until the sauce is thickened and doubled in volume. Remove from heat, whisk in cayenne and salt. Cover and place in a warm spot until ready to use.
Note:  If the sauce separates, add 1 Tbsp ice water and whisk until smooth.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{AIOLI} \index{AIOLI}
\textit{(Loraine Hiebert)}\\
\step{\nicefrac{1}{2} cloves garlic, chopped
\\ 2 egg yolks, room temp
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{4} tsp prepared mustard
\\ 1 \nicefrac{1}{4} cups olive oil
\\ 2 Tbsp white wine vinegar
\\ 1 red bell pepper roasted, peeled and seeded}{In blender whirl together garlic, yolks, salt and mustard. While blender is running gradually add oil. When all the oil is incorporated, add vinegar, then red pepper. Blend till smooth. Good with grilled seafood.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TARTAR SAUCE} \index{TARTAR SAUCE}
\step{1 cup mayonnaise	\\
1 tsp French mustard\\
1 Tbsp finely chopped parsley	\\
1 tsp minced shallots\\
1 finely chopped egg	\\
1 Tbsp chopped capers\\
1 Tbsp chopped sweet pickle	season to taste}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TRADITIONAL COCKTAIL SAUCE} \index{TRADITIONAL COCKTAIL SAUCE}
\step{1 cup chili sauce or ketchup	\\
1 Tbsp instant minced onions\\
1 Tbsp horseradish\\	
1 Tbsp lemon juice\\
1 tsp Worcestershire sauce}
{Chill for several hours to allow flavours to blend.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TACO SEASONING MIX} \index{TACO SEASONING MIX}
\step{\nicefrac{1}{2} cup onion flakes	\\
3 Tbsp ground cumin\\
\nicefrac{1}{2} tsp chilli powder\\	
\nicefrac{1}{2} tsp cayenne pepper\\
\nicefrac{1}{2} tsp garlic flakes}{Place in jar. Cover tightly and shake well. Allow 2 o 3 Tbsp mix and \nicefrac{1}{2} cup water for each pound of meat or beans. Store in cool, dark dry place for up to 2 months. Makes about \nicefrac{3}{4} cup.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GARAM MASALA} \index{GARAM MASALA}
\step{1 Tbsp cumin, ground 
\\ 1 \nicefrac{1}{2} tsp coriander, ground 
\\ 1 \nicefrac{1}{2} tsp cardamom, ground 
\\ 1 \nicefrac{1}{2} tsp pepper, ground 
\\ 1 tsp cinnamon, ground 
\\ \nicefrac{1}{2} tsp cloves, ground 
\\ \nicefrac{1}{2} tsp nutmeg, ground }{Optionally toast before storing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUMPKIN SPICE} \index{PUMPKIN SPICE}
\textit{Makes 1 tsp}\\
\step{\nicefrac{1}{2} tsp cinnamon
\\ \nicefrac{1}{4} tsp ginger, ground
\\ \nicefrac{1}{8} tsp allspice
\\ \nicefrac{1}{8} tsp nutmeg, ground}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ARBY'S COPYCAT CURLY FRIES BATTER} \index{ARBY'S COPYCAT CURLY FRIES BATTER}
\textit{\nicefrac{1}{2} cup all-purpose flour
\\ 2 tsps paprika 
\\ 1 tsp seasoned salt 
\\ \nicefrac{1}{2} tsp cayenne 
\\ Kosher salt and freshly ground black pepper
\\ 1 cup of water}{Marinate for 30 minutes before deep frying.}

\end{minipage}