\section{Other Desserts}

\begin{minipage}{\linewidth}\rtitle{CHOCOLATE LAVA CAKE (LC,GF)} \index{Gluten Free!cakes} \index{CHOCOLATE LAVA CAKE (LC,GF)} \index{Low Carb!cake}
\step{5 Tbsp salted butter
				\\	1 cup chocolate chips
				\\ 2 Tbsp almond flour	
				\\ 1 Tbsp (heaping) cocoa powder
				\\	\nicefrac{1}{8} tsp sea salt	
				\\ 2 large eggs
				\\	2 large egg yolks	
				\\ 3 Tbsp sugar
				\\ \nicefrac{1}{4} tsp vanilla extract}{
Melt butter and chocolate chips in a double boiler. Combine almond flour, cocoa powder, and salt in a small mixing bowl. In a large mixing bowl whisk eggs, sugar, and vanilla. Fold in chocolate. Sift in dry ingredients. Butter four 4-oz ramekins and fill with chocolate mixture. Refrigerate for 30 minutes. Place ramekins in hot water bath and bake at 425$^\circ$F for 15-18 minutes. Let cool for 10 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BAKED FUDGE DESSERT} \index{BAKED FUDGE DESSERT}
\textit{(Verna (Reimer) Reitmeier)}\\
\step{1 cup flour	
\\ 2 Tbsp baking powder
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} cup sugar	
\\ 3 Tbsp cocoa
\\ \nicefrac{1}{2} cup milk	
\\ 1 Tbsp vanilla
\\ 2 Tbsp melted shortening
\\ 4 Tbsp cocoa	
\\ \nicefrac{1}{2} cup brown sugar
\\ 1 \nicefrac{3}{4} cup hot water}{Sift flour, baking powder, and salt into a casserole or baking dish. STir in sugar and cocoa. Make a well in the center and add milk, vanilla, and shortening. Stir lightly and rapidly. Mix cocoa, brown sugar and hot water and mix well. Pour over uncooked batter. Bake at 350${}^\circ$F until done. Serve it hot with shipped cream or vanilla ice cream.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DIRT CAKE} \index{DIRT CAKE}
\step{454 g cream-filled chocolate cookies	
  \\ \nicefrac{1}{4} cup (50 ml) butter or hard margarine, softened
	\\ 250 g cream cheese, softened	
	\\ 1 cup icing sugar
	\\ 1 tsp vanilla flavouring	
	\\ 4 Instant chocolate puddings, 4 servings per box
	\\ 5 cups milk 	
	\\ 1 L frozen whipped topping, thawed (4 \nicefrac{1}{3} cups)
	\\ 15 gummy worms}{Crush cookies until they become fine crumbs. Set aside. Put butter, cream cheese, icing sugar and vanilla in bowl. Beat at low speed to mix, then on med speed until smooth. Add chocolate pudding powders and milk to the bowl. Beat on low speed to combine. Fold the whipped topping into the pudding mixture. Assemble in ungreased pan or flower pot in layers as follows: \\
	1st layer	\nicefrac{1}{3} cookie crumbs \\
	2nd layer	\nicefrac{1}{2} pudding mixture \\
	3rd layer	\nicefrac{1}{3} cookie crumbs \\
	4th layer	\nicefrac{1}{2} pudding mixture \\
	5th layer	\nicefrac{1}{3} cookie crumbs. \\
Tuck the ends of the gummy worms in the cookie dirt. Store in refrigerator. Chill at least 3 hours.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DELICIOUS BREAD PUDDING (GF*)} \index{DELICIOUS BREAD PUDDING (GF*)}
\textit{This recipe works well with GF bread.}\\
\step{4 cups milk
\\ 2 cups dry bread cubes, packed
\\ \nicefrac{1}{2} cup sugar	
\\ 3 eggs, beaten
\\ 4 Tbsp melted margarine	
\\ \nicefrac{1}{2} tsp salt
\\ 1 tsp vanilla	
\\ \nicefrac{1}{2} cup raisins
\\ \nicefrac{1}{4} tsp nutmeg	
\\ \nicefrac{1}{4} tsp cinnamon}{Heat milk. Add bread. Cool. Combine remaining ingredients with milk mixture. Pour into a buttered baking dish. Place dish in a pan of hot water. Bake at 350${}^\circ$F for 1 hour or until knife inserted comes out clean. Serve warm or chilled.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RICE PUDDING} \index{RICE PUDDING}
\step{2 \nicefrac{1}{2} cup cooked rice	
\\ 1 can evaporated milk
	\\ \nicefrac{2}{3} cup brown sugar	
	\\ 3 Tbsp butter
	\\ 2 tsp vanilla	
	\\ 1 tsp nutmeg
	\\ 3 eggs, beaten	
	\\ \nicefrac{1}{2} cup raisins}{
Bake at 325$^\circ$F until a knife inserted comes out clean.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROWN SUGAR PUDDING FOR TWO} \index{BROWN SUGAR PUDDING FOR TWO}
\textit{(Debbie Heaslip)}\\
\step{2 Tbsp brown sugar	
\\ \nicefrac{1}{4} cup milk
\\ \nicefrac{1}{2} cup flour	
\\ \nicefrac{1}{2} tsp cream of tartar
\\ \nicefrac{1}{4} tsp baking soda
\\ \nicefrac{1}{2} cup brown sugar	
\\ \nicefrac{1}{4} tsp salt
\\ 1 \nicefrac{1}{2} tsp butter	
\\ \nicefrac{1}{2} tsp vanilla
\\ 1 cup boiling water}{Mix brown sugar, milk, flour, cream of tartar, and baking soda. Put in pan and pour the remaining brown sugar, salt, butter, vanilla, and boiling water over it. Bake in oven until flour mixture has risen to the top and it passes the toothpick test for doneness.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{INSTANT PUDDING MIX} \index{INSTANT PUDDING MIX}
\step{\nicefrac{2}{3} cup cornstarch
\\ 1 cup sugar
\\ \nicefrac{1}{2} tsp salt
\\ 4 cups milk powder}{Vanilla Pudding: 1 cup mix, 2 cups water mixed with one egg. Serves 4.
Chocolate pudding: add to Vanilla pudding \nicefrac{1}{3} cup cocoa and \nicefrac{1}{4} cup sugar}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HONEY TAPIOCA CREAM} \index{HONEY TAPIOCA CREAM}
\step{2 Tbsp tapioca	
\\ 1 egg
\\ \nicefrac{1}{4} cup honey	
\\ \nicefrac{1}{4} tsp salt
\\ 2 cups milk	
\\ \nicefrac{1}{2} tsp vanilla}{Beat egg in a saucepan, just enough to blend yolk and white. Add tapioca, honey, salt and milk. Cook over moderate heat until pudding comes to boiling point (stir constantly). Turn of heat and let stand 15 minutes. Stir in vanilla. Serves 4.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APPLE-OATMEAL DESSERT (GF*)} \index{APPLE-OATMEAL DESSERT (GF*)}
\textit{The GF option can use 1 Tbsp cornstarch instead of 1 Tbsp flour. Replace \nicefrac{3}{4} cup flour with \nicefrac{3}{4} cup oat flour.}\\
\step{3 cups apples	
\\ 1 Tbsp flour
	\\ \nicefrac{1}{4} cup sugar	
	\\ 1 tsp cinnamon
\\ \nicefrac{3}{4} cup oatmeal	
\\ \nicefrac{1}{4} tsp soda
	\\ \nicefrac{3}{4} cup flour	
	\\ \nicefrac{1}{4} tsp baking powder
	\\ \nicefrac{3}{4} cup brown sugar	
	\\ \nicefrac{1}{2} cup margarine}
{Combine sugar, flour and cinnamon and sprinkle over apples. Cover with remaining ingredients. Bake at 400$^\circ$F until brown in a 9 by 9-inch pan.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BRANDIED PEACHES} \index{BRANDIED PEACHES}
\textit{(Company's Coming)} \\
\step{2 398 ml cans peaches with juice
\\ \nicefrac{2}{3} cup brown sugar	
\\ 2 Tbsp butter
\\ \nicefrac{1}{4} tsp cinnamon	
\\ 1 tsp lemon juice
\\ 1 tsp brandy flavouring or \nicefrac{1}{4} cup brandy	
\\ \nicefrac{1}{4} tsp almond flavouring
\\ vanilla ice cream}{Cut up peaches into slices and put into saucepan along with juice. Add remaining ingredients, except ice cream. Heat over med heat until boiling. Simmer 5 minutes. Keep hot until ready to serve or make ahead and heat when needed. Put scoops of ice cream into dishes. Ladle brandied peaches over top.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PAVLOVA} \index{PAVLOVA}
\textit{Allow enough time for this dessert to be refrigerated a minimum of 4 hours before serving. It can be made the day before. Refrigeration gives time for the meringue to form the characteristic marshmallow texture of a pavlova.}\\
\step{4 egg whites, room temp	
\\ 1 cup sugar
\\ 	1 tsp cornstarch	
\\ 1 tsp vinegar
\\ 1 tsp vanilla
\\ GLAZE:  
\\ \nicefrac{1}{4} cup sugar
\\ \nicefrac{1}{4} cup water
\\ 1 \nicefrac{1}{2} tsp cornstarch. }{Beat egg whites until soft peaks form. Add sugar and cornstarch gradually, beating until stiff. (You can't overbeat!) Beat in vinegar and vanilla. When rubbing between fingers, there should be no grainy feel to the whites. Outline a foil-lined cookie sheet in a 9 inch circle. Spread meringue in circle. Bake in 250$^\circ$F oven for about 50-60 minutes. Turn off heat. Keep oven closed and allow meringue to stand in oven for a minimum of 1 hour. Cool before removing foil.
 Cover with whipped cream. Place a decorative layer of sliced fresh fruit on top of the whipped cream. A traditional pavlova is done with kiwi but strawberries, peaches and mangoes are all good options. Glaze the fruit by bringing glaze ingredients to a boil, cooling, and painting fruit to seal and shine.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BOCCONNE DOLCE} \index{BOCCONNE DOLCE}
\textit{(Company's Coming)}\\
\step{Meringue:
\\ 6 egg whites, room temperature	
\\ \nicefrac{1}{2} tsp cream of tartar
\\ 1 \nicefrac{1}{2} cups granulated sugar}{Beat egg whites and cream of tartar until soft peaks form. Beat in sugar gradually, beating until stiff and glossy. Line 3 round 8" pans with foil or outline 3 circles, 8" on foil-lined cookie sheets. Very lightly grease the foil. Divide and spread the meringue evenly among the pans. Bake in 250${}^\circ$F oven for about 45 minutes until dry and crispy firm. Cool on racks. Peel off foil.}

\step{Filling:
\\ 1 cup semisweet chocolate chips	
\\ 3 Tbsp water}{In heavy saucepan, melt chips with water over low heat. Spread over 2 meringue shells.
Whip cream, sugar and vanilla until stiff. Spread over all 3 meringue layers. Place 1 layer with chocolate on serving plate. Spoon \nicefrac{1}{2} strawberries over top. Place second layer with chocolate over first on plate. Spoon second \nicefrac{1}{2} strawberries over top. Add third layer. Garnish with whole berries. Chill 4 to 5 hours before serving. Serves 8.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DACQUOISE} \index{DACQUOISE}
\textit{(Company's Coming)}\\
\step{Meringue:
\\ 6 egg whites, room temp	
\\ \nicefrac{1}{4} tsp cream of tartar
\\ \nicefrac{3}{4} cup sugar	
\\ \nicefrac{3}{4} cup ground almonds
\\ \nicefrac{1}{4} cup cocoa	
\\ 1 Tbsp cornstarch}{Beat egg whites and cream of tartar until soft peaks form. Add sugar, 1 Tbsp at a time, beating until very stiff. Stir nuts, cocoa and cornstarch together. Fold into beaten whites. Spread on very lightly greased foil-lined cookie sheets in 2 circles, 9" in diameter. Bake at 250${}^\circ$F for about 50 minutes until dry and fairly firm. Allow to cool before removing foil.}

\step{Creamed Filling:
\\ 6 egg yolks	
\\ \nicefrac{3}{4} cup sugar
\\ 1 cup butter softened	
\\ 1 Tbsp instant coffee granules, crushed
\\ 1 cup whipping cream	
\\ 1 Tbsp sugar
\\ \nicefrac{1}{2} tsp vanilla}{Beat egg yolks until thick and light. Beat in sugar until fluffy. Add butter \nicefrac{1}{4} at a time, beating well. Beat in instant coffee. Beat well. Spread \nicefrac{2}{3} over 1 meringue layer. Cover with second layer. Spread or pipe remaining butter mixture on outside 2 inches.}

\step{3 cups whipping cream	
\\ 5 Tbsp sugar
\\ 2 tsp vanilla	
\\ 3 cups fresh strawberries, sliced}{Whip cream, sugar and vanilla until stiff. Fill center of top meringue and frost sides. Serve within 2 or 3 hours of assembling. Serves 12.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DEEP FRIED ICE CREAM} \index{DEEP FRIED ICE CREAM}
\textit{(Company's Coming)}\\
\step{500 ml ice cream, in scoops	
	\\ 1 cup Graham cracker crumbs
	\\ sprinkle of sugar and cinnamon
	\\ 2 eggs, beaten}{
Scoop ice cream into 4 balls. Put into freezer. Remove and roll in crumbs. Return to freezer. When very firm, dip into beaten eggs and roll in crumbs again. Freeze again. To serve, deep fry 2 balls at a time in hot fat for about 10-12 seconds. Use slotted spoon for easy handling. Serve with or without chocolate sauce.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM PUFFS} \index{CREAM PUFFS}
\step{\nicefrac{3}{4} cup flour	
\\ 5 eggs
	\\ 100 g butter	
	\\ 1 tsp salt
	\\ 2 tsp sugar	
	\\ 1 cup boiling water}{
Combine water, butter and salt. Stir to melt butter. Bring to a boil. Add flour all at once. Stir vigorously until it forms a ball and pulls away from sides of pan. Remove from heat. Add eggs, one at a time, beating thoroughly after each is added. Drop by spoonfuls onto greased baking sheet, leaving room for expansion. Bake at 425$^\circ$F for 30 minutes. They should look dry with no beads of moisture showing. Leave in oven (switched off) with door open for 5 minutes before removing to rack to cool. When cool, cut top almost off, fill with flavoured and sweetened whipped cream. Makes 12 large puffs.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM PUFFS (GF)} \index{CREAM PUFFS (GF)} \index{Gluten Free!desserts}
\step{1 cup water
\\ 4 Tbsp white rice flour
\\ 4 oz. butter
\\ 4 eggs
\\ salt}{Boil water. Add flour. Stir till mixture forms a ball.  Cool. Add eggs one at a time, beating well after each addition. Bake 15 minutes at 450${}^\circ$F. Reduce heat to 350${}^\circ$F. Bake another 10 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM PUFF DESSERT} \index{CREAM PUFF DESSERT}
\textit{(Pat Reimer)\\
This recipe is much less temperamental than the cream puffs recipe.}\\
\step{1 cup water	
\\ \nicefrac{1}{2} cup butter
\\ 1 cup flour	
\\ 5 eggs
\\ 250 g cream cheese, softened	
\\ 1 large tub cool whip
\\ 1 large pkg vanilla instant pudding}{Bring water and butter to a boil. Remove from heat. Add flour. Add eggs one at a time. Spread on large greased cookie sheet. Bake at 425${}^\circ$F for 15-20 minutes. Press down lightly and cool. Make pudding. Blend in cream cheese. Spread on crust. Top with cool whip. Drizzle with chocolate sauce and refrigerate.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CR\`EME BRULEE} \index{CR\`EME BRULEE}
\textit{(Company's Coming)}\\
\step{4 egg yolks	
\\ 4 Tbsp brown sugar
	\\ 1 tsp vanilla	
	\\ 2 cups whipping cream, heat to scald
	\\ 3 Tbsp brown sugar}{
Beat egg yolks, brown sugar and vanilla. Add hot cream slowly to egg mixture, stirring continually. Return to saucepan. Cook and stir to thicken. Pour into 4 custard cups. Place cups in larger container with hot water halfway up sides. Bake at 325$^\circ$F for about 40 minutes. A knife inserted halfway between edge and center should come out clean. Cool. Chill in refrigerator several hours or overnight.
About 2 or 3 hours before serving, sprinkle 1 Tbsp remaining brown sugar over top of each custard. Broil with tops at least 3 inches from heat for about 2 minutes to melt sugar. Watch carefully as it scorches easily. Cool for 15 minutes. Refrigerate. Should be served very cold.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CR\`EME CARAMEL} \index{CR\`EME CARAMEL}
\textit{(Company's Coming)}\\
\step{1 cup sugar	
\\ \nicefrac{1}{2} cup water}{Heat first amount of sugar in heavy pan over med heat. Stir as sugar melts until completely melted and a rich caramel colour. If too light, it has no flavour, if too dark it will be bitter. Add water carefully. It will sputter. Stir until blended well. It will thicken as it blends. Pour into bottom of 6 custard cups or casserole. Tilt cups to distribute sugar over bottom and part way up sides to coat well.}

\step{Custard:
\\ 	3 eggs	
\\ 2 cups milk
\\ \nicefrac{1}{4} cup sugar	
\\ \nicefrac{1}{4} tsp salt
\\ 1 tsp vanilla}{Beat eggs lightly. Add milk, sugar, salt and vanilla. Beat together slightly. Pour into custard cups. Set cups in pan with \nicefrac{1}{2} inch hot water in it. Bake at 325${}^\circ$F for about 35 minutes or until a knife inserted near outside edge comes out clean. Allow to cool \nicefrac{1}{4} hour at room temp. Chill for at least 3 hours. To unmould, run knife around edge. Dip bottom in hot water for a few moments. Place small plate over top and invert together. Remove cup.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MANGO UPSIDE-DOWN CAKE} \index{MANGO UPSIDE-DOWN CAKE}
\step{2 cups mangoes
\\ 2 Tbsp lemon juice
\\ 1 Tbsp butter
\\ \nicefrac{1}{3} cup brown sugar
\\ \nicefrac{1}{4} cup shortening	
\\ \nicefrac{3}{4} cup sugar
\\ 1 egg
\\ 1 \nicefrac{1}{4} cup flour	
\\ 2 tsp baking powder
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{2} cup milk}{Slice mangoes. Pour lemon juice over sliced mangoes and let stand for 15 minutes. Melt butter in an 8" pan and add brown sugar and mangoes. Cream shortening and sugar. Add egg and sift in dry ingredients. Add alternately with milk. Pour over the mangoes. Bake 50--60 minutes at 375${}^\circ$F. When cake is done, turn it upside down and serve while still warm with whipped cream.
OPT: Use fresh pineapple instead of mangoes and add \nicefrac{1}{2} tsp salt.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{EASY ORANGE-CRANBERRY TRIFLE} \index{EASY ORANGE-CRANBERRY TRIFLE}
\step{1 pkg (4 serving size) vanilla pudding mix (not instant)*
\\ 2 cups milk	
\\ 1 cup whipping cream
\\ 1 Tbsp icing sugar	
\\ 1 pound cake
\\ \nicefrac{1}{4} cup liqueur or orange juice	
\\ \nicefrac{3}{4} cup frozen cranberry-orange sauce (thawed)
\\ 1 cup fresh raspberries	
\\ 1 can mandarin orange segments, drained
\\ Additional fresh raspberries, if desired
\\*2 cups pudding made ahead and cooled can be substituted for the pudding mix and milk}{Mix pudding mix and milk in 2 quart saucepan.
Mix pudding mix and milk. Heat to boiling, stirring constantly. Refrigerate 2 hours or until completely cooled. Beat whipping cream until soft peaks form. Add icing sugar. Beat until stiff peaks form. Fold \nicefrac{1}{2} cup of whipped cream into pudding. Cut pound cake into \nicefrac{1}{2}" slices. Cut is slice crosswise in half. Arrange about \nicefrac{1}{3} of cake pieces in bottom of bowl. Sprinkle with 2 Tbsp liqueur. Spread about \nicefrac{1}{3} of cranberry-orange sauce over cake pieces. Top with half each of raspberries and orange segments. Spoon 1 cup of pudding mixture over fruit. Repeat layers. Top with remaining whipped cream. Refrigerate 1 hour before serving. Garnish with additional raspberries.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TROPICAL SYLLABUB} \index{TROPICAL SYLLABUB}
\textit{Vary the basic syllabub recipe by adding mangoes, strawberries, bananas or passion fruit}\\
\step{1 \nicefrac{1}{2} cups sugar	
\\ rind and juice of 3 lemons
\\ 1 cup sweet sherry or white wine	
\\ \nicefrac{1}{4} cup brandy
\\ 3 cups double cream}{Mix together sugar, lemon juice, lemon rind, sherry and brandy in a small saucepan. Warm slightly to dissolve the sugar and blend the flavours. Remove from heat and allow to cool. Whip the cream and fold wine into the mixture. Fold together both mixtures. If desired serve in tall glasses. Vary by folding in 1 cup of mashed strawberries to which \nicefrac{1}{4} cup sugar has been added, or 3 mashed apple mangos or the fruit from 8 passion fruits or 3 mashed bananas. Chill before serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RASPBERRY PARFAIT} \index{RASPBERRY PARFAIT}
\step{3 cups frozen raspberries, thawed	
\\ \nicefrac{3}{4} cup sugar
\\ \nicefrac{1}{2} cup water	
\\ 1 cup Beaujolais or other dry red wine
\\ \nicefrac{1}{4} cup whipping cream	
\\ 2 Tbsp lemon juice}{Combine raspberries and water in container. Process  until smooth. Pour mixture through a wire mesh strainer, pressing raspberries with back of spoon. Discard pulp. Return mixture to blender, add sugar and remaining ingredients. Process 1 minutes. Freeze until almost firm in 9" sq pan. Break mixture in chunks and place in large mixing bowl. Beat at low speed until smooth. Return to pan and freeze until firm. Yield: 3 cups}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LA RUSTIQUE DESSERT} \index{LA RUSTIQUE DESSERT}
\textit{(from Sabine's friend, owner of La Rustique in Nairobi)}\\
\step{3 leaves gelatine (1 Tbsp or less)	
\\ 2 \nicefrac{1}{2} cups cream
\\ 220 g sugar (or less)	
\\ 1 \nicefrac{2}{3} cup yoghurt
\\ 40 ml amaretto}{Soak gelatine in cold water or melt it in microwave. If  you soak it, you have to warm mixture of cream/yoghurt and sugar to dissolve gelatine. If you melt gelatine, mix cream, yoghurt mixture in spoon by spoon. Chill and serve with fruit compote (such as rhubarb compote)}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DANISH SOUFFLE} \index{DANISH SOUFFLE}
\step{4 egg yolks	
\\ \nicefrac{1}{2} cup sugar
\\ \nicefrac{1}{4} cup dark rum (or use water with 1 \nicefrac{1}{2} tsp rum flavouring)
\\ 7g unflavoured gelatin powder	
\\ \nicefrac{1}{4} cup water
\\ 4 egg whites	
\\ \nicefrac{1}{2} cup sugar
\\ 1 cup whipping cream
\\ whipped cream, chocolate curls, cherries for garnish}{Beat egg yolks, fir amount of sugar and rum until light coloured and thickened. Sprinkle gelatin over water. Let stand 5 minutes then heat to dissolve. Add egg yolk mixture. Stir and heat just until it begins to boil. Remove from heat. Cool. Beat egg whites until soft peaks form. Gradually beat in second amount of sugar until stiff. With same beaters, beat cream until stiff. Fold egg whites into egg yolk mixture. Fold in cream. Turn into glass bowl or souffl\'e dish with collar. Garnish with additional whipped cream, chocolate curls and cherries.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHITE SILK RASPBERRY TART} \index{WHITE SILK RASPBERRY TART}
\textit{An exceptional dessert. Received rave reviews Chouristmas 2006.}\\
\step{20 cr\`eme-filled chocolate sandwich cookies, crushed (2 cups)
\\ \nicefrac{1}{4} cup butter, melted	
\\ 1 pkg white chocolate, chopped
\\ 2 cups whipping cream	
\\ 1 tsp vanilla
\\ 1 pkg cream cheese, softened	
\\ 1 pkg frozen raspberries in syrup, thawed
\\ 2 tsp cornstarch	
\\ 1 cup fresh raspberries}{Heat oven to 375${}^\circ$F. Mix crushed cookies and butter. Press in bottom and 1" up side of ungreased 9 or 10" springform pan. Bake 7-9 minutes or until set. Cool completely. Meanwhile, heat white baking bars and \nicefrac{1}{2} cup whipping cream in saucepan over low heat, stirring frequently until chocolate melts. Stir in vanilla. Cool to room temp, about 15 minutes.
Beat cream cheese with electric mixer until smooth. Add white chocolate mixture. Beat on med speed until creamy. Beat remaining 1 \nicefrac{1}{2} cups whipping cream until stiff peaks form. Fold half of whipped cream in cream cheese mixture until blended. Fold in remaining whipped cream. Spoon into crust. Refrigerate 3-4 hours or until set. Pour package of raspberries into small strainer set over saucepan. Press raspberries through strainer with back of spoon to remove seeds. Stir cornstarch into raspberry puree. Heat to boiling over medium heat. Cool completely, about 20 minutes. Spoon fresh raspberries around edge of dessert. Remove side of pan. Cut tart into wedges. Drizzle raspberry sauce over individual servings.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PERSIAN ORANGE TORTE WITH CREAM CHEESE FROSTING (GF)} \index{PERSIAN ORANGE TORTE WITH CREAM CHEESE FROSTING (GF)} \index{Gluten Free!cakes}
\step{2 large navel oranges
\\ 250 g. slices almonds
\\ 250 g sugar
\\ 1 tsp baking powder
\\ Pinch of salt
\\ 6 large eggs}{Place oranges in med saucepan.  Cover with water. Bring to boil, then simmer for 2 hours until soft. Cool to room temp. You can do this ahead of time and store the boiled oranges covered with cooking liquid in the fridge. Preheat oven to 375${}^\circ$F. Line a 7" round cake pan with parchment. You can also use an 8" spring form cake pan and wrap the exterior with foil to prevent leakage during baking. Place almond, sugar, baking powder and salt in food processor. Pulse until nuts turn floury. Empty to a large bowl and set aside. Lightly squeeze boiled oranges free of excess water and blend until smooth. Add beaten eggs and almond meal mixture to food processor. Blend until homogenous. Pour batter into cake pan. Set on top of a baking sheet and bake at least an hour, until cake tester comes out with only a few moist crumbs. (recipe notes say it could take up to 105 min).}

\step{Frosting:
\\ 180 g cream cheese, divided and softened
\\ 90 g unsalted butter, softened
\\ 90 g icing sugar
\\ 1 tsp lemon juice}{Place 90 g cream cheese and butter in bowl and beat at med speed until smooth. Beat in icing sugar and lemon juice. Add remaining cream cheese and beat until fluffy.
Spread a thick layer of cream cheese frosting on top of cake. Smooth to even thickness and make attractive swirls.}

\step{Garnish:
\\ 4 dried orange slices, snap in half
\\ 2 black mission figs, quartered
\\ Handful of cubed quince paste
\\ 2 Tbsp chopped pistachios
\\ 2 Tbsp dried rose petals}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON SHAUM TORTE} \index{LEMON SHAUM TORTE}
\step{6 egg whites
\\ 1 tsp vanilla extract
\\ \nicefrac{1}{8} tsp cream of tartar
\\ 2 cups sugar, divided
\\ 9 egg yolks
\\ \nicefrac{1}{2} cup lemon juice
\\ 1 Tbsp grated lemon peel
\\ 4 cups heavy whipping cream
\\ \nicefrac{2}{3} cup icing sugar
\\ Ground cinnamon}{Place egg whites in a large bowl and let stand at room temperature for 30 minutes. Add vanilla and cream of tartar. Beat on med speed until soft peaks form. Gradually beat in 1 cup sugar, 2 Tbsp at a time, on high speed until stiff glossy peaks form and sugar is dissolved. Spread meringue on the bottom and up the sides of a greased 13x9" baking dish. Bake at 275 for 1 hour. Turn oven off and let stand in oven for 1 hour. do not open door during this time.  Remove from oven. Cool on wire rack.
In a large saucepan, combine the egg yolks, lemon juice, lemon peel and remaining sugar. Cook and stir over med heat until mixture is thickened and coats the back of a spoon. Cool.
In a chilled bowl, beat cream until it begins to thicken. Add icing sugar. Beat until stiff peaks form. Spread half over meringue. Cover with lemon mixture. Top with remaining whipped crea. Sprinkle with cinnamon. Refrigerate. Yield: 12-15 servings.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SCANDINAVIAN COFFEE CAKE} \index{SCANDINAVIAN COFFEE CAKE}
\step{1 cup poppy seeds	
\\ \nicefrac{1}{2} cup milk
\\ 1 cup brown sugar
\\ 4 Tbsp butter
\\ 4 egg yolks
\\ \nicefrac{2}{3} cup almond paste OR 1 cup ground almonds
\\ 3 Tbsp citron (opt)	
\\ 2 tsp lemon juice or 1 tsp vanilla
\\ 2 well-beaten eggs	  
\\ \nicefrac{3}{4} cup lukewarm water
\\ 1 pkg. dry yeast
\\ 4 cups sifted flour	
\\ 1 tsp salt
\\ 2 Tbsp sugar	
\\ \nicefrac{1}{2} cup butter
\\ 1 \nicefrac{1}{2} tsp powdered cardamom
\\ 1 \nicefrac{1}{2} cups butter
\\ 1 egg yolk
\\ 1-2 Tbsp water or milk}{For the filling, put poppy seeds and milk in double boiler and bring to a boil. Remove from heat and add brown sugar and butter. Put over boiling water again and add egg yolks. Heat until mixture thickens, stirring constantly. When cooled add almonds, citron, and lemon juice/vanilla. For the pastry, combine eggs and lukewarm water. Add yeast and let ingredients rest refrigerated for 15 minutes. Meanwhile, blend flour, salt, sugar, butter, and cardamom with a pastry blender. In a large mixing bowl, make a ring of the blended flour. Pour the chilled yeast mixture into the center and work it gradually into the dry ingredients. Knead until smooth, about 2 minutes. Form the dough into a ball and rest it, covered, about 20 minutes in the refrigerator. Roll out the dough lightly into an oblong about ?????? thick. Beat butter until creamy. Spread butter on dough, folding and rolling 4 times. Cover and chill at least 2 hours. Roll again on slightly floured surface to thickness of ?????? thick. Cut off any folded edges that may keep dough from expanding. To shape, roll it first into an oblong, about 29??? x 11???. Spread poppy seed filling over dough. Roll, starting with long edge. Bring two ends of roll together to form a ring. Use a little water to glue. Place ring on greased baking sheet. With floured scissors held perpendicular to the roll, cut bias gashes about 1-2??? apart into upper outer edges of ring, to within one inch of inner circle. Turn each partially cut slice flat onto the tin. Wash top with egg yolk and 1-2 Tbsp water or milk. Be careful not to get the wash on the cut portions. Cover with cloth and let rise about 25 minutes until double in bulk. Bake at 400${}^\circ$F for 25 minutes. Makes two 9??? rings.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SCANDINAVIAN COFFEE RING} \index{SCANDINAVIAN COFFEE RING}
\step{2 eggs
\\ 34 cup warm water
\\ 1 pkg active dry yeast
\\ 4 cups flour
\\ 1 tsp salt
\\ 2 Tbsp sugar
\\ \nicefrac{1}{2} cup butter
\\ 1 \nicefrac{1}{2} tsp cardamom}{Beat well 2 eggs. Add warm water. Dissolve yeast in this mixture. Let it rest refrigerated for 15 minutes. Meanwhile, blend the remaining ingredients with a pastry blender or cut in by hand as for pastry. In a large mixing bowl, make a ring of the blended flour. Pour the chilled yeast mixture into the center and work it gradually into the dry ingredients. Knead until smooth, about 2 minutes. Form the dough into a ball and rest it, covered, about 20 minutes, in the refrigerator. Roll out the dough into an oblong about \nicefrac{3}{8}" THICK.
Beat until creamy:  1\nicefrac{1}{3}-1\nicefrac{1}{2} cups butter (not margarine)
Spread the dough with \nicefrac{1}{4} of the butter.  Fold the pastry in half. Turn it one quarter turn on the counter. Roll into an oblong once more. Spread with \nicefrac{1}{4} of the butter.  Fold. Repeat previous steps until butter is used up.  Chill dough for at least 2 hours. Then roll an oblong 29 x 11" on a slightly floured surface to the thickness of \nicefrac{3}{8}".  Cut off any folded edges that might keep the dough from expanding. Fill it with the filling below.  Roll up the pastry, starting with the long edge.  Bring the two ends together to form a ring. Use a little water for glue. Please the ring on a greased baking sheet. With floured scissors held perpendicular to the roll, cut gashes about 1-2"' apart into the upper OUTER edges of the ring, to within one inch of the inner circles.  As you cut, turn each partially cut slice flat onto the tin.  Brush the top with 1 egg yolk diluted with 1-2 Tbsp milk or water, being care not to cover the cut portions.
Cover the ring with a cloth and let rise about 25 minutes or until double in bulk.
Preheat oven to 400${}^\circ$F. Bake for 25 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{Filling I: Poppy Seed Filling}
\textit{(for 1 9" ring)}\\
\step{\nicefrac{1}{2} cup poppy seeds
\\ \nicefrac{1}{4} cup milk
\\ \nicefrac{1}{3} cup brown sugar
\\ 2 Tbsp butter
\\ 2 egg yolks
\\ \nicefrac{1}{3} cup almond paste or \nicefrac{1}{2} cup ground almonds
\\ 1 tsp vanilla}{Crush or grind the poppy seeds in a mortar. Combine with the milk in a double boiler. Bring to a boil. Remove pan from heat and add the sugar and butter. Return the pan over the boiling water and add the egg yolks. Heat until the mixture thickens, stirring constantly. When it has cooled slightly, add the ground almonds and vanilla. Cool before using in the coffee cake.}

\rtitle{Filling II: Apple Coffee Cake Filling}
\textit{(for 2 9" rings)}\\
\step{2\nicefrac{1}{2} cups pared and chopped apples
\\ 1 cup brown sugar
\\ \nicefrac{1}{3} cup butter
\\ 1 cup raisins
\\ \nicefrac{1}{2} tsp cinnamon
\\ \nicefrac{1}{2} tsp salt}{Combine and boil for 4 minutes. Cool slightly and spread over dough.}

\rtitle{Filling III: Edelweiss Cream}
\step{\nicefrac{1}{2} cup icing sugar
\\ \nicefrac{1}{4}-\nicefrac{1}{2} cup butter
\\ \nicefrac{1}{2} tsp vanilla or 1 tsp grated lemon rind
\\ \nicefrac{1}{2} cup ground blanched almonds
\\ 1 egg}{Cream the sugar and butter.  Stir in the remaining ingredients.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHERRY CHA-CHA} \index{CHERRY CHA-CHA}
\textit{(Loraine Hiebert)\\
Mom's old standby when I was growing up}\\
\step{1 prepared graham wafer crust.
\\ \nicefrac{1}{2} pint whipping cream	
\\ 1 \nicefrac{1}{2} cup miniature marshmallows
\\ 2 Tbsp icing sugar	
\\ 1 tsp vanilla
\\ \nicefrac{1}{2} tin of pie filling cherries.}{Mix whipped cream, marshmallows, icing sugar, and vanilla and pour into crust. Top with cherries. Chill and serve.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GRASSHOPPER DESSERT} \index{GRASSHOPPER DESSERT}
\step{1 \nicefrac{1}{2} cups chocolate cookie crumbs	
\\ \nicefrac{1}{4} cup sugar
\\ 6 Tbsp butter, melted	
\\ 2 pkg cream cheese, cubed and softened
\\ \nicefrac{1}{3} cup green cr\`eme de menthe liqueur*	
\\ \nicefrac{1}{4} cup white cream de cacao liqueur*
\\ 14 oz marshmallow cr\`eme	
\\ 1 \nicefrac{1}{2} cups whipping cream
\\ *\nicefrac{2}{3} cup cr\`eme de menthe syrup can be substituted for the two liqueurs.}{Line $13 \times 9$" pan with foil so edges of foil extend over sides of pan. Spray with cooking spray. Mix cookie crumbs, sugar and butter in pan. Press evenly in bottom of pan. Beat cream cheese and liqueurs until smooth. Add marshmallow cr\`eme. Beat until smooth. Refrigerate about 45 minutes or until mixture mounds when dropped from a spoon. Beat whipping cream until stiff peaks form. Fold whipped cream into marshmallow mixture until blended. Pour over crust. Freeze about 4 hours or until firm. Remove dessert from pan, using foil to lift. Let stand at room temp 10 minutes before cutting.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MARSHMALLOW DELIGHTS} \index{MARSHMALLOW DELIGHTS}
\step{3-56 g Mackintosh toffee bars, broken up
\\ \nicefrac{2}{3} cup sweetened condensed milk
\\ \nicefrac{1}{4} cup hard margarine
\\ 30 large marshmallow
\\ 4 cups rice krispies}{Heat toffee, milk and margarine in a small heavy saucepan on medium heat, stirring till toffee is melted and mixture is smooth. Remove from heat. Dip marshmallow in toffee mixture till coated, using a fork. If mixture becomes too thick for dipping, reheat till desired consistency. Roll coated marshmallow in cereal in med bowl till coated. Place on waxed paper-lined baking sheet. Let stand until set. Freeze in airtight container.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CAKE DOUGHNUTS} \index{CAKE DOUGHNUTS}
\step{3 Tbsp melted butter	
\\ 1 cup sugar
	\\ 2 eggs	
	\\ 1 cup milk
	\\ 1 tsp vanilla	
	\\ 4 cups flour
	\\ 4 tsp baking powder	
	\\ \nicefrac{1}{2} tsp salt
	\\ \nicefrac{1}{2} tsp cinnamon	
	\\ \nicefrac{1}{2} tsp nutmeg
	\\ 4-6 inches deep hot fat}{
Combine melted butter, sugar, eggs, milk and vanilla. Mix together. Measure in flour, baking powder, salt, cinnamon and nutmeg. Stir well.
Roll out dough \nicefrac{1}{4}-inch thick on floured surface. Cut out with doughnut cutter. Drop into hot fat a few at a time so as not to crowd. Turn when light brown to cook other side.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MAPLE BAR DOUGHNUTS} \index{MAPLE BAR DOUGHNUTS}
\step{\nicefrac{1}{3} cup cream	
\\ 1 cup brown sugar
\\ 1 Tbsp butter	vanilla}{Use \hyperlink{sweetdoughlink}{Sweet Dough} recipe. Let rise once. Punch down and cut with doughnut cutter. Let rise. Deep fry. Boil ingredients until spoon coats in layers. Dip maple bars in icing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MANGO SORBET} \index{MANGO SORBET}
\step{4 mangoes	
\\ 3 Tb lemon juice
	\\ 1 cup water	 
	\\ \nicefrac{3}{4} cup sugar}{
Blend mangoes. Boil water and sugar until sugar is dissolved.  Combine everything. Chill.  Pour into ice cream maker.}
\end{minipage}