\section{Pasta, Rice, and Cereals}

\begin{minipage}{\linewidth}\rtitle{SPAGHETTI AND MEATBALLS} \index{SPAGHETTI AND MEATBALLS}
\textit{(Loraine Hiebert)} \\
\step{2 eggs	\\
	1 cup dry bread crumbs\\
	\nicefrac{1}{2} cup onion, finely chopped\\
	2 tsp salt\\
	\nicefrac{1}{2} tsp pepper\\	
	1 \nicefrac{1}{2} lbs beef mince \\
	\nicefrac{1}{2} lb pork mince}{Mix and shape into meatballs. Fry until browned. Put into casserole. Pour following sauce over meatballs and bake for 1--2 hours.}

Sauce:\\
\step{2 tsp cornstarch \\
	\nicefrac{1}{2} cup water \\
	1 cup ketchup	\\
	1 cup brown sugar\\
	1 cup tomato sauce	\\
	\nicefrac{1}{2} cup water\\
	2 tsp Worcestershire sauce	\\
	2 tsp HP sauce\\
	2 tsp chilli powder	\\
	1 clove garlic}{Mix cornstarch and water. Add remaining ingredients.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PASTA WITH SPINACH SAUCE} \index{PASTA WITH SPINACH SAUCE}
\step{8 oz. spaghetti or linguine	\\
	1 Tbsp olive oil\\
	1 small yellow onion, chopped fine	\\
	2 cloves garlic, minced\\
	1 lb. fresh spinach, trimmed and chopped	\\
	\nicefrac{1}{2} cup milk\\
	\nicefrac{1}{2} cup chicken broth	\\
	\nicefrac{1}{4} cup grated Parmesan cheese\\
	\nicefrac{1}{4} tsp pepper}{Cook spaghetti. While cooking, heat olive oil over moderate heat for 1 minute. Add onion and garlic and cook until onion is soft. Add spinach, milk, chicken broth, cheese and pepper. Bring mixture to a boil. Reduce heat and simmer, uncovered for 3 minutes. Pour sauce in blender and swirl until mixture is pureed. Pour the sauce back into the saucepan and reheat over moderate heat until mixture starts to simmer. Drain spaghetti and return to kettle. Add spinach mixture and toss well with two forks to mix.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SPAGHETTI WITH NO-COOK TOMATO SAUCE} \index{SPAGHETTI WITH NO-COOK TOMATO SAUCE}
\textit{Make in the summer with fresh herbs and tomatoes from the garden}\\
\step{350 g spaghetti	\\
	salt\\
	500 g cherry tomatoes	\\
	fresh basil\\
	\nicefrac{1}{4} tsp sugar	\\
	2 garlic cloves, pressed\\
	4 Tbsp olive oil	\\
	freshly ground pepper}{Cook the spaghetti until al dente. Drain. Finely chop the tomatoes and add them to a large bowl with remaining ingredients. Toss in cooked pasta and season with salt and pepper. Serve immediately.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TOMATO MACARONI BAKE} \index{TOMATO MACARONI BAKE}
\step{\nicefrac{1}{4} cup chopped onion	\\
	2 Tbsp butter\\
	1 can tomato soup\\	
	\nicefrac{1}{2} cup water\\
	1 cup grated cheese	\\
	2 cups cooked macaroni\\
	2 Tbsp buttered bread crumbs}{Brown onion in butter. Stir in soup, water and \nicefrac{3}{4} cup cheese. Heat until cheese melts. Mix in macaroni. Pour into greased casserole. Sprinkle remaining \nicefrac{1}{4} cup cheese and bread crumbs on top. Bake at 350$^\circ$F for 30 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MY FAVOURITE CARBONARA} \index{MY FAVOURITE CARBONARA}
\step{\nicefrac{1}{4} lb pancetta, diced	\\
	\nicefrac{3}{4} cup coarsely chopped onion\\
	1 cup dry white wine	\\
	1 lb linguine, cooked\\
	1 egg, lightly beaten	\\
	1 cup finely grated parmesan\\
	\nicefrac{1}{2} cup finely chopped parsley\\	
	salt and pepper to taste}{Cook pancetta slowly until it begins to crisp. Drain off fat. Add onion, increase heat to med and cook until onion is translucent. Quickly pour hot bacon-wine mixture over pasta. Add egg and toss to combine. Add \nicefrac{3}{4} cup of Parmesan and toss. Season with salt and pepper. To serve, divide pasta among 4 heated plates. Sprinkle with remaining cheese and garnish with parsley.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PASTA CARBONARA} \index{PASTA CARBONARA}
\step{450 g fettuccine	\\
	250 g bacon, diced\\
	1 Tbsp garlic	\\
	\nicefrac{3}{4} cup onion, finely diced\\
	1 \nicefrac{1}{4} cups whipping cream	\\
	\nicefrac{1}{4} cup parmesan grated cheese\\
	\nicefrac{1}{4} cup parsley, chopped}{
Cook fettuccine. Fry bacon for 1 minutes. Add onion and garlic. Saut\'e for 8 to 10 minutes. Add cream and cheese. Simmer for 2 minutes or until cream thickens. In large bowl, toss pasta with sauce. Top with chopped parsley. For a twist on this recipe, saut/'e a chopped tomato with onion and garlic. Add fresh, peeled shrimp when cream is added.}
 
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FUSILLI WITH PARSLEY-MUSHROOM SAUCE} \index{FUSILLI WITH PARSLEY-MUSHROOM SAUCE}
\step{\nicefrac{1}{2} cup plain yoghurt	\\
	1 Tbsp olive oil\\
	\nicefrac{1}{4} cup grated parmesan cheese	\\
	6 oz. mushrooms, sliced thin\\
	\nicefrac{1}{4} cup minced parsley	\\
	1 med. size yellow onion, chopped\\
	2 Tbsp sour cream	\\
	2 cloves garlic, minced\\
	\nicefrac{1}{8} tsp pepper	\\
	\nicefrac{1}{4} cup dry white wine\\
	8 oz. fusilli, rotelle or spaghetti}{Combine yoghurt, cheese, parsley, sour cream and pepper. Cover and refrigerate.
Cook fusilli according the directions. Heat olive oil. Add mushrooms, onion and garlic and cook, stirring occasionally, for 5 to 7 minutes. Add wine to mushroom mixture and cook for 1 to 2 minutes or until most of liquid is absorbed. Add yoghurt-cheese mixture and heat through. Do not boil! Drain fusilli and return to kettle. Add mushroom mixture and toss well.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MACARONI AND CHEESE} \index{MACARONI AND CHEESE}
\textit{(Loraine Hiebert)}\\
\step{2 Tbsp butter	\\
	2 \nicefrac{1}{2} cups milk\\
	2 Tbsp flour	\\
	1 \nicefrac{1}{2} cup grated cheese\\
	\nicefrac{1}{2} tsp salt	\\
	\nicefrac{1}{2} cup buttered bread crumbs\\
	\nicefrac{1}{2} tsp pepper	\\
	2 cups macaroni, cooked\\
	\nicefrac{1}{4} tsp paprika}{
Melt butter, blend in flour and seasonings, add milk and cook, stirring constantly until thickened. Add 1 cup cheese, stir until cheese melts. Combine cooked macaroni and sauce in casserole. Top with remaining cheese and crumbs. Bake uncovered at 375$^\circ$F for 25 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MANICOTTI} \index{MANICOTTI}
\step{1 lb lean ground beef	\\
	\nicefrac{1}{4} cup onion, chopped\\
	3 slices bread, torn up small	\\
	1 \nicefrac{1}{2} cups mozzarella cheese, shredded\\
	1 egg	\\
	\nicefrac{1}{2} cup milk\\
	1 tsp salt	\\
	\nicefrac{1}{4} tsp pepper}{Fill uncooked shells with meat. Place in ungreased baking dish. Pour cooked sauce over shells. Bake until shells are tender. Sprinkle with \nicefrac{1}{3} cup parmesan cheese. Cool 5-10 minutes before serving.
}
Sauce:\\
\step{
	4 oz mushroom stems and pieces, undrained	\\
	15 oz tomato sauce\\
	12 oz tomato paste	\\
	\nicefrac{1}{4} cup onion, chopped\\
	1 clove garlic	\\
	4 cups water\\
	\nicefrac{1}{2} tsp sugar	\\
	\nicefrac{1}{2} tsp salt\\
	\nicefrac{1}{8} tsp pepper\\	
	1 Tbsp parsley\\
	1 Tbsp Italian seasoning}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SAUSAGE PASTA} \index{SAUSAGE PASTA}
\textit{(Jeanie Little)}\\
\step{Smoked sausage (1 lb.) or a package of those precooked sausages, sliced thin
	\\ 1 pkg. (16 oz) rotini pasta	
	\\ 1 onion, sliced
	\\ 3 cloves garlic, minced	
	\\ 1 green pepper, in half slices
	\\ olives, sliced 	
	\\ 2 Tbsp olive oil
	\\ 1 can (28 oz) crushed tomatoes	
	\\ 1 cup chicken broth
	\\ 3 heaping tsp Italian seasoning		
	\\ \nicefrac{1}{4} tsp salt
	\\ Parmesan cheese to shake on top or grated cheese}{
Cook pasta. Meanwhile, in a large skillet, Saut\'e the sausage in the oil until lightly browned. (drain off some of the fat/oil, leave a bit). Add the onion, garlic and green pepper and Saut\'e a bit. Stir in the tomatoes, broth, Italian seasoning and salt. Bring to a boil over medium heat; cook and stir for 4-5 min until heated through. Drain pasta; toss with sausage mixture. Serve with Parmesan or grated cheese.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HOME-MADE NOODLES} \index{HOME-MADE NOODLES}
\step{1 egg	
	\\ garlic powder, if desired
	\\ 1 tsp oil	
	\\ \nicefrac{1}{2} tsp salt
	\\ 2 Tbsp milk	
	\\ 1 cup flour}{
Stir and knead until you have a stiff, non-sticky dough. It should form a ball and come clean from your hands. Cover dough and let rest if desired, then roll out on cornstarch, until very thin. Dry 15--30 min. For noodles, stop the drying before it becomes brittle. Roll it up loosely like a scroll. Then cut strips at an angle, very narrow: \nicefrac{1}{8}-\nicefrac{1}{4}". They will absorb water and become wider when they cook. Cut lasagne about the size of your baking dish, or in 1\nicefrac{1}{2}" strips.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LASAGNA} \index{LASAGNA}
\textit{(Erma Penner)\\
Erma brought this lasagna to a Life Group gathering. Everyone of the women there said they were going to replace their current lasagna recipe with this one. I changed mine and haven't been tempted by any other lasagna recipes thus far.}\\
\step{2 Tbsp olive oil
\\ 1 med onion, chopped
\\ 1 clove garlic, minced
\\ 1 lb hamburger
\\ Sliced mushrooms (opt)
\\ 7 \nicefrac{1}{2} oz can tomato sauce
\\ 5 \nicefrac{1}{2} oz can tomato paste
\\ 1 tsp salt
\\ 1 tsp oregano
\\ 1 cup water
\\ 1 egg
\\ 2 cups creamed cottage cheese
\\ \nicefrac{1}{3} cup parmesan cheese
\\ 1 lb mozzarella cheese, sliced thick
\\ Oven ready lasagna noodles}{Saut\'e onions and garlic in oil. Add hamburger and brown. Add mushrooms and fry a little longer. Add tomato sauce and paste, salt, oregano and water. Simmer for 15 min. Mix egg, cottage cheese and parmesan cheese. Put enough meat sauce in a 9x13" pan to cover the bottom. Cover with a layer of noodles. Pour half of the meat sauce on top. Spread cottage cheese mixture over meat sauce. Add another layer of noodles.  Add the rest of the meat sauce. Place mozzarella slices on top. Cover tightly with greased foil. Bake at 350${}^\circ$F for 45-55 min. Uncover for the last 10 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LASAGNA} \index{LASAGNA}
\textit{(Joelle Van Otterloo)\\
I (Katrina) frequently make this low carb by replacing the noodles with zuchini strips, salted, and drained}\\
\step{1 lb ground beef	
	\\ \nicefrac{3}{4} lb pork sausage
	\\ 24 oz tomato sauce	
	\\ 12 oz tomato paste
	\\ 2 garlic cloves	
	\\ 2 tsp sugar
	\\ 1 tsp Italian seasonings	
	\\ 1 tsp salt
	\\ \nicefrac{1}{2} tsp pepper	
	\\ 3 eggs
	\\ 3 Tbsp minced fresh parsley 	
	\\ 3 cups cottage cheese
	\\ 8 oz ricotta cheese 	
	\\ \nicefrac{1}{2} cup grated parmesan
	\\ 9 lasagna noodles	
	\\ 6 slices provolone
	\\ 3 cups shredded mozzarella}{Cook beef and pork over medium heat. Drain. Add tomato sauce, paste, garlic, sugar, seasoning, salt and pepper. Bring to boil. Reduce heat, simmer uncovered for 1 hour. In a separate bowl, combine eggs and parsley. Add cottage cheese, ricotta, and parmesan. Spread 1 cup of meat in 13 $\times$ 9" pan. Layer with 3 noodles, provolone, 2 cups of cheese mix, and 1 cup of mozzarella, 3 noodles, 2 cups of meat sauce, remaining cottage cheese mix, 1 cup mozzarella. Top with remaining noodles, meat sauce, and mozzarella. Cover. Bake at 375$^\circ$F for 50 min. Uncover. Bake at 20 minute. Let stand 15 min before cutting.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{EVERYDAY RED WINE RISOTTO} \index{EVERYDAY RED WINE RISOTTO}
\step{1 tsp olive oil	\\
	1 cup finely minced onion\\
	2 Tbsp finely minced garlic\\	
	3 fresh rosemary sprigs\\
	1 bay leaf	\\
	4 cups beef broth, additional as needed\\
	2 cups Arborio rice	\\
	2 cups dry red wine\\
	1 cup freshly grated parmesan	\\
	salt and pepper\\
	\nicefrac{1}{2} cup chopped parsley}{
In large Dutch oven over med heat, combine oil, onion, garlic, rosemary, and bay leaf. Turn heat to low, cover and simmer until onion is soft and trans, about 15  minutes. Do not brown.
In med saucepan, heat beef broth.
Uncover onion and increase heat to med. Add rice and stir to coat. Saut\'e, stirring with a wooden spoon, for 2-3 minutes, or until rice begins to turn golden.
Stir in 1 cup of red wine; continue to stir until wine is absorbed. Add the remaining wine and stir until absorbed.
Stir in broth, 1 cup at a time, until absorbed. Rice should be creamy but still a little crunchy. Add additional broth \nicefrac{1}{4} cup at a time, to reach desired consistency.
Remove bay leaf and rosemary. Stir in cheese and parsley. Season with salt and pepper.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HERBED LENTILS \& RICE} \index{HERBED LENTILS \& RICE}
\textit{(Moira Neufeld)}\\
\step{5 \nicefrac{1}{3} cups chicken broth
\\ 1 \nicefrac{1}{2} cups green lentils
\\ 1 cup brown basmati rice
\\ 2 med onions, diced
\\ 6-8 mushrooms, sliced
\\ \nicefrac{1}{2} cup cooking sherry
\\ 1 tsp basil
\\ \nicefrac{1}{2} tsp oregano
\\ \nicefrac{1}{2} tsp thyme
\\ \nicefrac{1}{4} tsp garlic powder
\\ \nicefrac{1}{4} tsp pepper
\\ 200 g Swiss cheese, grated
\\ Swiss cheese slices, enough to cover top of casserole}{Combine all ingredients except the cheese slices in order given.  Pour mixture into an ungreased 9x13" pan. With a slotted egg lifter, submerge the grated cheese so it won't stick to the tinfoil cover. Cover tightly with foil. Bake at 350${}^\circ$F for 1 hr 20 min. Uncover and top with cheese slices. Bake 2-3 minutes more, uncovered, to melt cheese.\\
Note:  If, after baking, you think the casserole is a bit dry, boil 1 cup chicken broth. Pour it slowly over casserole and down the edges.  The moisture will be absorbed.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APPLE AND HAZELNUT WILD RICE} \index{APPLE AND HAZELNUT WILD RICE}
\textit{(Can also be served as a cold side dish)}\\
\step{1 cup wild rice, rinsed and drained	\\
	\nicefrac{1}{4} cup coarsely chopped hazelnuts\\
	1 tsp canola oil	\\
	2 scallions, finely sliced\\
	1 rib celery, finely sliced	\\
	\nicefrac{1}{2} med green pepper, seeded and diced\\
	\nicefrac{1}{2} cup coarsely chopped mushrooms	\\
	1 apple, cored and diced\\
	\nicefrac{1}{4} cup finely minced sage\\	
	2 Tbsp chopped fresh thyme\\
	Salt and pepper	\\
	\nicefrac{1}{2} cup chicken broth}{Preheat oven to 325. Cook wild rice in 3 cups water. Bring to a boil. Reduce heat and simmer for 40 minutes or until rice is tender but has not burst. Toast hazelnuts in oven for about 8 minutes, until lightly golden.
Heat oil in large pan. Add scallion, celery, green pepper, mushrooms, apple, sage, thyme and salt and pepper. Saut\'e for 6-8 minutes. Add cooked wild rice and chicken broth and heat through until chicken broth is absorbed. Remove from heat and garnish with chopped hazelnuts.}
\end{minipage}
