\section{Pies and Pastries}

\begin{minipage}{\linewidth}\rtitle{PUMPKIN PIE} \index{PUMPKIN PIE}
\step{\nicefrac{1}{8} tsp salt	
  \\ \nicefrac{2}{3} cup sugar
	\\ 1 tsp cinnamon	
	\\ \nicefrac{1}{4} tsp nutmeg
	\\ \nicefrac{1}{2} tsp ginger	
	\\ 3 eggs slightly beaten
	\\ 1 \nicefrac{2}{3} cup milk	
	\\ 1 \nicefrac{1}{2} cups mashed pumpkin}{Bake at 450$^\circ$F for first 10 min; 325$^\circ$F for 35 minutes more. Makes 1 large pie.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PECAN PIE} \index{PECAN PIE}
\step{1 \nicefrac{3}{4} cup brown sugar
\\ \nicefrac{1}{4} cup corn syrup
\\ \nicefrac{1}{4} cup butter
\\ 1 Tbsp cold water
\\ 2 tsp cornstarch
\\ 3 eggs
\\ \nicefrac{1}{4} tsp salt
\\ 1 tsp vanilla
\\ 1 cup chopped pecans
\\ 1 9" unbaked pie shell.}{Combine sugar, syrup, and butter.  Bring to a full boil. Combine water and cornstarch and add to pot. Boil until thickened. Remove from heat and set aside.  Beat eggs until just frothy.  Add eggs and remaining ingredients to the syrup mixture. Pour into unbaked pie shell.  Bake at 350${}^\circ$F for 45-50 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RUM PECAN PUMPKIN PIE} \index{RUM PECAN PUMPKIN PIE}
\step{1 unbaked 9" pie shell	
\\ \nicefrac{1}{2} cup pecan halves
\\ 1 \nicefrac{1}{2} cups cooked pumpkin (if using home-cooked, add 1 Tbsp cornstarch)
\\ \nicefrac{2}{3} cup firmly packed brown sugar
\\ 1 \nicefrac{1}{4} tsp cinnamon	
\\ \nicefrac{1}{2} tsp ginger
\\ pinch nutmeg	
\\ \nicefrac{1}{4} tsp salt
\\ 1 cup milk	
\\ \nicefrac{1}{4} cup dark rum
\\ 3 eggs, lightly beaten}{Prepare 9" pie shell. Sprinkle shell with pecan halves. Mix pumpkin and sugar until sugar dissolves. Add remaining ingredients, stirring well to blend. Pour filling into pie shell. Bake in a preheated 450${}^\circ$F oven for 10 minutes. reduce heat to 350${}^\circ$F and bake 35 to 45 minutes longer, until inserted knife comes out clean. Serve warm or at room temperature. Garnish with whipped cream or ice cream.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE CREAM PIE} \index{CHOCOLATE CREAM PIE}
\step{2 sq. chocolate or 3 Tbsp cocoa	
\\ 3 Tbsp cornstarch or 4 Tbsp flour
\\ 2 cups milk	
\\ 2 eggs, separated
\\ 1 cup sugar	
\\ 1 tsp vanilla
\\ 1 Tbsp butter	
\\ \nicefrac{1}{4} tsp salt}{Melt chocolate in dbl. boiler. Add 1 \nicefrac{1}{2} cups milk and bring to boiling point. combine sugar, salt and cornstarch. Add remaining milk to make a smooth paste. Add paste to milk and cook until thickened. Add egg yolks. Pour small amount of hot mixture over egg yolks before adding them to milk. Cook 2 minutes. Remove from heat, add butter and vanilla. Cool and pour into pie shell. Cover with meringue or whipped cream.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MUD PIE} \index{MUD PIE}
\textit{(Company's Coming)}\\
\step{Crust:
\\ \nicefrac{1}{2} cup butter	
\\ 2 cups chocolate wafer crumbs
\\ Filling: 
\\ 1 L coffee ice cream, softened
\\\\ Topping:
\\ \nicefrac{1}{3} cup cocoa	
\\ 3 Tbsp butter
\\ \nicefrac{2}{3} cup sugar	
\\ \nicefrac{1}{3} cup heavy cream or evaporated milk
\\ 1 tsp vanilla
\\\\ Final Garnish:
\\ 1 cup whipping cream	
\\ 1 Tbsp sugar
\\ \nicefrac{1}{2} tsp vanilla
\\ 1-2 semisweet chocolate squares}{Crust: Melt butter. Stir in crumbs. Press in bottom and sides of 9" pie plate. Bake at 350${}^\circ$F for 10 minutes. Cool. \\Filling: spoon ice cream into shell. Freeze until firm. \\Topping: Put all 5 ingredients into saucepan. Heat and stir over medium heat until boiling. Remove from heat. Cool for about 10 minutes then smooth over ice cream filling. Return to freezer. To serve, whip cream, sugar and vanilla until stiff. Spread over top. Garnish with shaved chocolate and sliced almonds. Serve with hot chocolate sauce.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE CHIP PIE} \index{CHOCOLATE CHIP PIE}
\textit{(Brackenhurst Conference Center)}\\
\step{4 eggs	
\\ 1 cup brown sugar
\\ 1 cup flour	
\\ 2 cups butter, melted and cooled
\\ 1 cup white sugar	
\\ 2 cups chocolate chips
\\ 2 cups chopped cashews	
\\ two 9" unbaked pie shells}{Beat eggs until foamy. Add flour and sugar. Blend in butter. Stir in chocolate chips and nuts. Pour into pie shells. Bake at 325${}^\circ$F for 1 hour.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BANANA CREAM PIE} \index{BANANA CREAM PIE}
\step{9 inches pie shells, baked 
\\ 2 cups whole milk 	
\\ \nicefrac{3}{4} cup white sugar 
\\ \nicefrac{1}{3} cup all-purpose flour 	
\\ \nicefrac{1}{4} tsp salt 
\\ 3 egg yolks, slightly beaten 	
\\ 2 Tbsp butter 
\\ 1 tsp vanilla 	
\\ 4 bananas}{Have baked 9-inch pie shell ready.  In a large saucepan, scald the milk.  In another saucepan, combine the sugar, flour and salt; gradually stir in the scalded milk.  Over medium heat, stirring constantly, cook until thickened.  Cover and, stirring occasionally, cook for two minutes longer.  In a small bowl, have the 3 egg yolks, slightly beaten, ready; stir a small amount of the hot mixture into beaten yolks; when thoroughly combined, stir yolks into hot mixture.  Cook for one minute longer, stirring constantly.  Remove from heat and blend in the butter and vanilla.  Let sit until lukewarm.  When ready to pour, slice bananas and scatter in pie shell; pour warm mixture over bananas.  If desired, make a meringue (you'll have 3 leftover egg whites) to top the pie, or just let the pie cool until serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON MERINGUE PIE} \index{LEMON MERINGUE PIE}
\step{1 \nicefrac{1}{2} cups boiling water	
\\ 1 cup white sugar
\\ \nicefrac{1}{2} tsp salt	
\\ 6 Tbsp cornstarch
\\ 3 egg yolks	
\\ 5 Tbsp lemon juice
\\ 1 tsp lemon rind	
\\ 1 Tbsp butter}{Mix together \nicefrac{1}{2} cup sugar with cornstarch and salt in double boiler. Slowly add boiling water. Cook until thick and clear. Add yolks beaten with \nicefrac{1}{2} cup sugar and cook 5 minutes. longer. Remove from heat. Stir in lemon juice and rind. Cool and pour into pie shell.}
\step{Meringue:
\\ 3 egg whites	
\\ 3 Tbsp sugar
\\ \nicefrac{1}{4} tsp cream of tartar	
\\ 3 tsp cold water
\\ pinch of salt}{Beat egg whites with cold water and salt until foamy. Add cream of tartar and beat until stiff. Gradually beat in sugar and continue to beat until glossy peaks are formed. Pile lightly on filling. Bake in slow oven until nicely browned.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON CHIFFON PIE} \index{LEMON CHIFFON PIE}
\step{One 7g unflavoured gelatine	
\\ \nicefrac{1}{4} cup lemon juice
\\ 1 cup water	
\\ \nicefrac{2}{3} cup sugar
\\ 1 grated rind of lemon
\\ 2 egg whites}{Sprinkle gelatin over juice. Let stand 1 minute. Heat until gelatin dissolves. Combine water, sugar, and lemon rind and bring to a boil. Stir in gelatin. Chill until it bounds with spoon. Beat 2 egg whites until stiff. Fold into mixture. Pile into graham cracker crust. Top with whipped cream}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEACH PIE} \index{PEACH PIE}
\textit{(Chuck McCullough)}\\
\step{Pastry for 2 crust pie
	\\ \nicefrac{3}{4} cup sugar	
	\\ \nicefrac{1}{4} cup cornstarch
	\\ Pinch salt	
	\\ 3 lb peaches (about 7 cups)
	\\ 1 Tbsp fresh lemon juice	
	\\ 1 Tbsp butter, cut into pieces
	\\ 2 Tbsp milk/sugar mixture}{Prepare pastry dough, chill. Preheat oven to 425$^\circ$F. In large bowl, combine sugar, cornstarch, and salt. Add peaches and lemon juice; gently toss to combine. Press pastry dough into 9-inch pie plate. Trim edge, leaving 1-inch overhang. Reserve trimmings for decorating the pie. Spoon peach filling into crust. Dot with butter. Roll remaining disk of dough into 12-inch round. Cut a \nicefrac{3}{4} inch circle out of the center and 1-inch slits to allow steam to escape during baking. Center dough over filling. Fold overhang under and crimp the edge. Use dough cuttings to decorate as desired. Brush the top with a combination of milk and sugar for a crispy finish to dough. Place pie on foil-lined cookie sheet to catch any overflow during baking. Gently place foil or aluminum pie circle around the edges to prevent burning. Bake 20 minutes. Bake at 375$^\circ$F until filling bubbles in the center (45-60 min). Remove edge protection for the last few minutes to brown edges. Cool for an hour before serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APPLE PIE} \index{APPLE PIE}
\step{Enough pastry for a 9" double crust pie \\
5-6 cups pared, cored and thinly sliced apples \\
\nicefrac{1}{2} cup white or brown sugar \\
\nicefrac{1}{8} tsp salt \\
1-\nicefrac{1}{2} Tbsp cornstarch\\
\nicefrac{1}{4} tsp cinnamon\\
\nicefrac{1}{8} tsp nutmeg}{Combine dry ingredients and sift over the apples.  Increase sugar to \nicefrac{2}{3} cup if the apples are very tart. Use larger amount of cornstarch if the apples are extremely juicy.  Stir apples until well-coated. Place in the pie shell. Dot with 1 \nicefrac{1}{2} Tbsp butter. Cover with pie crust and pinch shut. Cut slits in top for steam to escape.  Brush top of crust with milk.
Preheat oven to 450${}^\circ$F. Bake pie for 10 minutes at this temp then reduce heat to 350${}^\circ$F. Bake another 35-45 minutes or until golden brown. 
If apples are bland, add 1 Tbsp lemon juice and \nicefrac{1}{2} tsp grated lemon rind.  If the apples are very dry, add 2 Tbsp water or cream.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{STRAWBERRY PIE} \index{STRAWBERRY PIE}
\textit{(Dorine Milner)}\\
\step{Crust:
\\ 1 cup flour
\\ 2 Tbsp icing sugar
\\ \nicefrac{1}{2} cup butter
\\\\ Filling:
\\ one 4 oz. pkg. cream cheese	
\\ \nicefrac{1}{2} cup icing sugar
\\ 	\nicefrac{1}{2} tsp vanilla	
\\ 1 cup whipping cream}{Mix crust ingredients until crumbly. Press into a pie plate. Prick with fork. Bake at 400$^\circ$F for 8-10 minutes. Cool. For filling, beat cheese, vanilla and sugar. Whip cream and add. Put fresh strawberries on top. Heat glaze and pour over top. You can add some water to spread better.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{STRAWBERRY RHUBARB PIE FILLING} \index{STRAWBERRY RHUBARB PIE FILLING}
\step{3 \nicefrac{1}{2} cups rhubard, trimmed, \nicefrac{1}{2}-inch-thick slices (1 \nicefrac{1}{2} pounds untrimmed)
\\ 1 16-oz container strawberries, hulled, halved (about 3 \nicefrac{1}{2} cups)
\\ \nicefrac{1}{2} cup (packed) golden brown sugar
\\ \nicefrac{1}{2} cup sugar	
\\ \nicefrac{1}{4} cup cornstarch
\\ 1 tsp ground cinnamon	
\\ \nicefrac{1}{4} tsp salt}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RHUBARB PIE} \index{RHUBARB PIE}
\step{4 cup unpeeled, diced young rhubarb stalks
\\ \nicefrac{1}{4} cup tapioca or cornstarch
\\ 1 \nicefrac{1}{4} -- 2 cup sugar
\\ 1 Tbsp butter
\\ Pastry for a 9" double crust pie.}{Bake in 450 F oven for 10 minutes. Reduce heat to 350 F and bake 35-40 minutes or until golden brown.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRUMBLE PIE TOPPING} \index{CRUMBLE PIE TOPPING}
\step{\nicefrac{3}{4} cup all-purpose flour
\\ \nicefrac{1}{2} cup packed brown sugar
\\ \nicefrac{1}{2} cup oats
\\ \nicefrac{1}{2} cup cold butter, cubed}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GRAHAM CRACKER CRUST} \index{GRAHAM CRACKER CRUST}
\step{\nicefrac{1}{3} cup butter	
\\ 1 \nicefrac{1}{4} cup graham cracker crumbs
\\ \nicefrac{1}{4} cup sugar}{Melt butter. Mix in crumbs and sugar. Press in pan and bake at 350$^\circ$F for 10 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LORAINE'S FLAKY PIE CRUST} \index{LORAINE'S FLAKY PIE CRUST}
\textit{(Loraine Hiebert)\\
Mom's stepmother owned a caf\'e and expected Mom to work there for no pay during her 3 years of Bible school.  Mom worked in the caf\'e every day except Sunday, often until well after midnight.  Mom didn't regard those years in the caf\'e with much fondness but she did learn how to make exceptional pies as a result. Although this is her "foolproof" pie crust recipe, her light touch with the pastry is a little harder to replicate.  The pastry is moister than most.  Don't be tempted to add extra flour. Whatever you do, DON'T ROLL THE PASTRY MORE THAN NECESSARY.}\\
\step{4 cups flour
\\ 2 cups lard 
\\ 1 cup cold water}{Cut lard into flour. Add water. Don't over-mix or the pastry will become leathery.  Makes 2 covered pies.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PIE PASTRY (GF)} \index{PIE PASTRY (GF)} \index{Gluten Free!pastry}
\textit{(Jackie Buhler)}\\
\step{\nicefrac{1}{2} cup tapioca flour
\\ \nicefrac{1}{2} cup corn starch
\\ \nicefrac{1}{4} cup potato starch
\\ 1 cup rice flour
\\ 1 tsp xanthan gum
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} cup butter or margarine
\\ \nicefrac{1}{2} cup shortening or lard
\\ 1 egg
\\ 1 Tbsp vinegar
\\ 4 Tbsp ice water}{Mix all ingredients up to and including shortening till crumbly.  Beat remaining ingredients together. Stir into pastry and mix well. Divide into 3-4 ball.  Chill for at least 1 hour. Moisten the counter. Cover with plastic wrap. Lightly dust with sweet rice flour. Roll dough with another piece of plastic wrap laid over the dough.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUFF PASTRY} \index{PUFF PASTRY}
\step{4 cups flour	
\\ 1 cup sour cream
\\ 1 lb. firm butter}{
Sift flour into bowl. Cut butter into bowl. Blend with flour and add sour cream. Stir with fork until just blended. Chill for 2 hours.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BUTTER TARTS} \index{BUTTER TARTS}
\step{1 egg, beaten	
\\ \nicefrac{1}{2} cup brown sugar
	\\ 3 Tbsp butter	
	\\ \nicefrac{1}{4} cup corn syrup
	\\ 1 \nicefrac{1}{2} tsp vinegar	
	\\ \nicefrac{1}{4} tsp vanilla
	\\ \nicefrac{1}{8} tsp salt	
	\\ \nicefrac{1}{3} cup raisins}{
Pour filling into tart shells. Bake at 375$^\circ$F for 12-15 minutes. Yield: for 12 tarts.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RUM AND CURRANT FLAN} \index{RUM AND CURRANT FLAN}
\textit{(Favourite Teatime Recipes)}\\
\step{8-9 oz shortcrust pastry
\\ 2 oz butter	
\\ 4 oz currants
\\ 4 oz Demerara sugar	
\\ 1 tsp vanilla
\\ 3 tsp rum	
\\ 1 small beaten egg}{Roll out pastry and line pie plate or flan dish. Melt butter in a pan. Add sugar and currants and stir. Remove from heat. Add vanilla and rum. Add enough beaten egg to give mixture a soft consistency. Pour into pastry shell and bake 20-25 minutes  until risen and pastry is golden brown. Allow to cool and cover with a very thin layer of white glace icing OR roll out left-over pastry into strips and make a lattice pattern on top of flan before baking.}

\end{minipage}