\chapter{Pioneer Woman}

\begin{minipage}{\linewidth}\rtitle{MOZZARELLA} \index{MOZZARELLA}
	\step{\nicefrac{1}{2} tsp calcium chloride
	\\ 2 Tbsp distilled water
	\\ \nicefrac{1}{2} tablet Rennet Tablet
	\\ \nicefrac{1}{4} cup distilled water
	\\ 1 gallon whole milk
	\\ 2 tsp citric acid
	\\ \nicefrac{1}{2} tsp flaked salt}{Dissolve Calcium Chlroide in 2 Tbsp distilled water. Dissolve Rennet Tablet in \nicefrac{1}{4} cup distilled water. Place milk in stock pot on stove over medium heat. Heat slowly. Sprinkle in citric acid and dissolved calcium chloride with you gently stir. Heat until milk reaches 88${}^\circ$F. Curd should be forming. Stir in dissolved rennet. Heat slowly to 105${}^\circ$F. Remove from heat and let sit covered for 20 minutes. Curd and whey should be fully separated. Transfer curd to microwave safe dish. Press curds together with spoon to squeeze out as much whey as possible. Microwave on high for one minute. Press curds to remove whey. Repeat for 20-30 seconds as necessary until cheese begins to mass together and becomes sticky. Add salt a little at a time and knead the cheese until it becomes smooth and shiny. Microwave on high for one more minute. Drain. Knead. When cheese stretches like taffy, pull and stretch until it is completely cooled.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{fetalink}{FETA}} \index{FETA}
\step{3 gallons milk
\\ \nicefrac{1}{4} tsp Mesophilic culture
\\ \nicefrac{1}{4} tsp lipase powder
\\ 1 tsp single-strength liquid rennet dissolved in \nicefrac{1}{2} cup of distilled water
\\ kosher salt (no substitute)
\\\\ BRINE:
\\ \nicefrac{1}{2} cup kosher salt (no substitute)
\\ 1 gallon distilled water}{Sterilize all equipment with boiling water, including cheesecloth. Bring milk to 86-88$^\circ$F. Add mesophilic culture and lipase powder. Stir well with an up and down motion. Cover pot and let rest for one hour. Try to maintain the temperature. Add dissolved rennet and stir vigorously for 15-20 seconds. Cover pot and let it stand undisturbed for 30-40 minutes or until the curd 'breaks' cleanly. Cut a \nicefrac{1}{2}-inch grid pattern into the curd. Hold the knife at a 45"' angle and retrace the cuts you've already made, to break curd into roughly \nicefrac{1}{2}-inch pieces. Let the curd rest undisturbed for 10 minutes. After 10 minutes, stir gently. Keep the curd at 86-88$^\circ$F for 45 minutes, stirring occasionally. Put curds into cheesecloth and hang to drain for 3-4 hours. Flip cheese and rehang. Drain for 24 hours. Cut it into blocks the size of a deck of cards. Generously sprinkle all of the surfaces of the cut cheese with kosher salt, place in sterilized container with a lid.
Let the cheese rest at room temperature for 2 to 3 days.
Let the brine come to room temperature before pouring it over the cheese after the 2-3 days. Put the lid in place tightly on the container and store the cheese in the refrigerator. Let the cheese age at least two weeks before eating. It is good for up to a year refrigerated in the brine solution.
}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FETA 2} \index{FETA 2}
	\step{2 Gallons of Whole Milk
\\ \nicefrac{1}{4} tsp MM 100
\\ \nicefrac{1}{4} tsp lipase powder
\\ 1 tsp liquid rennet
\\ \nicefrac{1}{4} cup distilled water
\\ Kosher salt}{Make the brine: \nicefrac{1}{2} cup kosher salt per \nicefrac{1}{2} gallon of water (boiled and cooled to room temperature). Dissolve rennet in distilled water. Warm milk to 88${}^\circ$F (86${}^\circ$F for goat milk). Remove from heat. Add culture and lipase. Stir well and let ripen, covered, for 1 hour. Add rennet and stir briskly for 15 seconds. Cover and let set 30 to 40 minutes, or until you see a clean break. Cut \nicefrac{1}{2}-inch checkerboard pattern. Hold the knife at a 45${}^\circ$ angle and retrace your cuts. Let the curds rest 5 minutes (10 minutes). Stir curd gently and cut any pieces you missed. Hold milk at 88${}^\circ$F (86${}^\circ$F) for 45 minutes; keeping the pot covered will maintain the temperature. If the temperature falls, place the pot in a sink of 86-degree water to raise the temperature. Stir occasionally. Remove curd into cheesecloth and hang to drain for 3-4 hours. Flip it and continue draining for 24 hours. Cut it into usable, 2-inch cubes. Sprinkle all sides of the curds with kosher salt and place them in a sterilized, sealable container. Cover and let sit at room temperature for 2 to 3 days to harden up the blocks. The blocks will continue to release whey during this time. Transfer the blocks to a large sterilized glass container, such as a glass pickle jar, and add the brine. Age the cheese in brine for 1 to 4 weeks before use.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HALLOUMI} \index{HALLOUMI}
\step{1 gallon of milk
\\ \nicefrac{1}{4} tsp MA4002
\\ 3/8 tsp Calcium Chloride
\\ \nicefrac{1}{4} tsp Single Strength Liquid Rennet
\\ \nicefrac{1}{4} cup distilled water
\\ \nicefrac{1}{2} oz Salt
\\ \nicefrac{1}{8} tsp Citric Acid
\\ 1 pint of milk}{Dissolve rennet in a \nicefrac{1}{4} cup of distilled water. Heat milk to 86-88${}^\circ$F. Add culture. Add lipase and/or calcium chloride. Stir briefly to incorporate well into milk. Add rennet. Wait 30-40 minutes for milk to separate. You should notice it at 15-20 minutes. Cut curd with a knife to see if it splits naturally. If it's ready, cut curd vertically into 0.75--1.5 inch squares. Rest for 3-5 minutes. Cut horizontally with spoon. Stir gently, increasing heat to 100-106${}^\circ$F for 20-30 minutes. Keep temperature steady for 20-30 minutes with intermittent stirring every 3-5 minutes. Allow curds to settle for 5 minutes. Remove curds from whey. Heat whey to 185-195${}^\circ$F (do not let it boil). Put curds into form and presss with 1-2 pound weight. Turn at 15-20 minute intervals. When whey reaches 150${}^\circ$F, add citric acid for ricotta. At 165-170${}^\circ$F, add 1 tsp of salt and a pint of milk. As whey reaches 185-195${}^\circ$F, stop stirring and allow ricotta to rise to the top for about 10 minutes. Skim off curds. Drain. Heat whey to 190-195${}^\circ$F. Lower halloumi into whey and heat for 30-40 minutes. When it floats, it is ready. Drain and cool. As it cools, you can flatten and sprinkle it with salt.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{\hypertarget{paneerlink}{PANEER}} \index{PANEER}
\step{1 gallon whole milk
	\\ 3 Tbsp lemon juice}{Bring milk to boil. As soon as it's just about to boil, add lemon juice and reduce heat. Collect curds in a cheese cloth, trying not to break them up. Rinse curds to remove lemon flavour. Hang to let whey drain out for about 1 hour. Put cheese in cloth on a plate with a weight on it for about 2 hours. Refrigerate. Cut into shape. Store in freezer.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BILTONG} \index{BILTONG}
\textit{(A South African jerky that we grew to love while in Kenya)}\\
\step{900 g beef (rump, topside or silverside)
\\ 1\nicefrac{1}{2} tsp whole coriander seeds
\\ 1\nicefrac{1}{2} tsp whole cumin seeds
\\ \nicefrac{1}{2} tsp Chilli powder/flakes
\\ 300 mL Cider Vinegar
\\ 3 Tbsp coarse salt
\\ 1 tsp black peppercorns
\\ 1 tsp oregano}{Slice beef into steaks under an inch thick and trim fat. Rub salt into each side of steaks and drain on a wire rack. Leave for approx. 1\nicefrac{1}{2} hours. Toast coriander and cuminutes. Grind all spices into a powder. Scrape steaks with a knife to remove salt. Pour cider vinegar into a flat container. Place each piece of beef in the vinegar bath for 2--4 minutes. If the beef is not fully covered then turn it over half way through. Cover steaks with seasoning. Leave to marinate for 5-6 hours.
Dehydrate at 65 degrees for approx. 12 hours. Check after 7-8 hours and adjust the remaining time accordingly.}

\begin{minipage}{\linewidth}\rtitle{PICKLED BEETS} \index{PICKLED BEETS} \index{pickles}
Cook small beets or cook and slice larger beets into a 2 quart sealer. Cover with 1 cup vinegar, \nicefrac{3}{4} cup sugar, 1 cup water and seal.

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BREAD AND BUTTER PICKLES} \index{BREAD AND BUTTER PICKLES} \index{pickles}
\step{30 medium sized cucumbers	
	\\ 5 cups sugar
	\\ 8 large white onions	
	\\ 2 Tbsp mustard seed
	\\ 2 sweet peppers	
	\\ 1 tsp turmeric
	\\ \nicefrac{1}{2} cup salt	
	\\ \nicefrac{1}{2} tsp cloves
	\\ 5 cups vinegar
		}{
Wash cucumbers and slice as thin as possible. Chop onions and peppers. Combine with cucumbers and salt and let stand for 3 hours. Drain. Combine vinegar, sugar and spices in large kettle. Bring to a boil. Add drained cucumbers. Heat thoroughly but do not boil. Pack hot in hot jars and seal.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCHO PICKLES}  \index{CHOCHO PICKLES} \index{pickles}
\textit{(Jungle Camp Cookbook)} \\
\step{6-8 cups raw chayotes
	\\ 1 medium onion
	\\ 2 Tbsp coarse salt
	\\ 1 \nicefrac{1}{4} cup mild vinegar	
	\\ 1 \nicefrac{1}{4} cup sugar
	\\ \nicefrac{1}{4} tsp \& \nicefrac{1}{8} tsp turmeric	
	\\ \nicefrac{3}{4} tsp prepared mustard or 1 \nicefrac{1}{2} tsp mustard seed
	\\ \nicefrac{1}{8} tsp ground cloves}{
Slice chayotes and onions. Sprinkle salt over the vegetables and mix well. Let stand for 2 hours. In large saucepan bring remaining ingredients to a boil. When syrup is boiling, add the vegetables gradually with very little stirring. Return to boiling point and cook for 1 minutes. Put into sterilized jars.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DILL PICKLES}  \index{DILL PICKLES} \index{pickles}
\textit{(Loraine Hiebert)}\\
\step{24 3-4" cucumbers
\\ dill
\\ \nicefrac{1}{2} red pepper
\\ 2 cloves garlic
\\\\BRINE:
\\ 1 cup vinegar
\\ 2 cups water
\\ \nicefrac{1}{4} cup pickling salt
\\ 1 Tbsp sugar}{Wash and cut off the flower end of cukes. Cover with ice water and let stand for 2 hours to make the cukes firm. To each jar add dill, red pepper, and garlic. Bring brine to a boil. Pack whole or sliced cukes into jars. Fill the jars with the hot brine. Seal. Makes 2 quarts of pickles.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SALSA}  \index{SALSA}
\step{1 red onion, chopped
\\ 1 white onion, chopped
\\ 1 yellow onion, chopped
\\ 6 pounds fresh tomatoes, peeled and chopped
\\ 2 banana peppers, chopped*
\\ 3 green bell peppers, chopped*
\\ 3 6-oz cans tomato paste
\\ \nicefrac{1}{2} cup white vinegar
\\ 5-6 cloves garlic, minced
\\ 2 Tbsp fresh cilantro
\\ 1 \nicefrac{1}{2} Tbsp salt
\\ 1 tsp cayenne pepper
\\ 2 tsp ground cumin
\\ 2 tsp New Mexico green chili
\\ 3 Tbsp lime juice}{Combine all ingredients.  Allow the ingredients to drain in a Colander for at least 1 hour.  Boil until you have the right consistency.  This could be anywhere between \nicefrac{1}{2} hour and 3 hours.  Pour into hot sterilized jars and seal.
*The total amount of peppers should be around 2 \nicefrac{1}{2} cups.}
\end{minipage}

\end{minipage}