\section{Salads}

\begin{minipage}{\linewidth}\rtitle{GERMAN HOT POTATO SALAD}  \index{GERMAN HOT POTATO SALAD}
\textit{(Elke Muller, Nebobongo Dr's wife)} \\
\step{1 \nicefrac{1}{2} lb potatoes, sliced
	\\ 6 strips bacon, chopped
	\\ 1 med onion, chopped
	\\ \nicefrac{1}{3} cup vinegar	
	\\ \nicefrac{1}{2} cup water
	\\ \nicefrac{1}{2} cup chopped parsley	
	\\ 2 tsp flour
	\\ 3 tsp sugar	
	\\ 1 \nicefrac{1}{2} tsp salt
	\\ \nicefrac{1}{4} tsp pepper}{Boil potatoes. Cook bacon. Cook onions in some of the bacon grease. Add remaining ingredients. Cook slightly until thick. Add potatoes and blend well. Serve warm.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RED SKINNED POTATO SALAD}  \index{RED SKINNED POTATO SALAD}
\step{2 lbs new red potatoes
\\ 6 eggs
\\ 1 lb bacon
\\ 1 onion, finely chopped
\\ 1 stalk celery, finely chopped
\\ 2 cups mayonnaise
\\ Salt and pepper to taste}{Boil potatoes until tender but still firm, about 15 minutes. Drain and refrigerate to cool. Boil eggs. Peel and chop. Cook bacon in skillet until evenly brown. Drain, crumble and set aside. Chop the cooled potatoes, leaving skin on. Combine all ingredients. Chill for an hour before serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{POTATO SALMON SALAD} \index{POTATO SALMON SALAD}
\step{8 small red potatoes, quartered	\\
\nicefrac{1}{2} tsp salt\\
\nicefrac{1}{2} tsp pepper\\	
1 \nicefrac{1}{2} lbs salmon fillet\\
1 cup \nicefrac{1}{2}" thick onion slices	\\
1 cup julienne cut red bell pepper\\
\nicefrac{1}{4} cup chopped fresh cilantro	\\
2 tsp minced seeded jalapeno pepper\\
\nicefrac{1}{4} cup white wine vinegar	\\
\nicefrac{1}{2} tsp grated lime rind\\
2 Tbsp fresh lime juice	\\
1 tsp dried oregano\\
\nicefrac{1}{2} tsp pepper	\\
4 cups mixed salad greens
}{Boil potatoes until tender. Drain.
Sprinkle salt and pepper over salmon fillet. Cook fillet in skillet over med high heat for 5 minutes. Turn fillet. Add onion and cook 5 more minutes. Remove fillet from skillet. Cook onion an additional 3 minutes or until golden. Remove onion from skillet. Add potatoes to skillet. Saut\'e over high heat 3 minutes  or until browned. Remove from heat.
Flake salmon into bite-size pieces. Combine salmon, onion, potatoes, bell pepper, cilantro and jalapeno pepper in a bowl. Combine vinegar, lime rind, lime juice oregano and pepper in small bowl. Drizzle vinegar mixture over salmon mixture. Toss gently to coat. Serve on a bed of mixed greens.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TACO SALAD} \index{TACO SALAD}
\textit{(Brenda Koop)} \\
\step{\nicefrac{1}{2} large bottle French dressing	
	\\ \nicefrac{1}{2} large bottle thousand island dressing
	\\ 1 envelope taco seasoning	
	\\ 1 lb. ground beef, browned with onions
	\\ 1 tin kidney beans	
	\\ shredded cheddar cheese
	\\ 2 tomatoes	
	\\ lettuce (less than a head.)
\\ Tortilla chips}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BOILED COLESLAW} \index{BOILED COLESLAW}
\textit{(Shirley Lysack)} \\
\step{1 fair sized head of cabbage	
	\\ \nicefrac{1}{4} green pepper (opt)
	\\ \nicefrac{3}{4} chopped onion	
	\\ 2 carrots, shredded
	\\\\Dressing:
	\\1 cup vinegar	
	\\ 1 cup sugar
	\\ 2 tsp salt	
	\\ \nicefrac{3}{4} cup salad oil
	\\ 1 clove garlic.}{Boil dressing ingredients. Pour dressing over vegetables and mix well. Should marinate for a while before serving. Celery seeds give a nice change, also. This recipe will keep for a month in the fridge.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CUCUMBER SALAD} \index{CUCUMBER SALAD}
\textit{(Grandma Fingas)}\\
\step{8 large cucumbers, sliced	\\
1 cup sliced onion\\
1 cup diced celery	\\
1 green pepper, diced\\
1 red pepper, diced	\\
1 \nicefrac{1}{2} Tbsp pickling salt\\
\\Dressing:\\
2 cups sugar\\
1 cup vinegar\\
1 tsp celery seed	\\
1 tsp mustard seed}{Mix all together and let stand \nicefrac{1}{2} hour. In meantime, mix together:
Stir until sugar is dissolved and pour over drained cucumber mixture. Put into large jars and refrigerate. It is ready to use anytime. Keeps up to thouree months in fridge.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEAN SALAD} \index{BEAN SALAD}
\step{1 tin cut green beans, 14 oz.	
	\\ 1 14 oz. tin but wax beans
	\\ 1 14 oz. tin red kidney beans	
	\\ 1 14 oz. tin lima beans
	\\ 1 cup celery	
	\\ \nicefrac{1}{2} cup onion rings or chunks
	\\ \nicefrac{1}{4} cup green pepper
	\\\\ Dressing:\\
	\nicefrac{1}{4} cup white vinegar	
\\ 1 tsp sugar
\\ 	1 tsp dry mustard	
\\ \nicefrac{1}{2} tsp basil
\\ \nicefrac{1}{2} cup salad oil	
\\ 1 tsp thyme
\\ \nicefrac{1}{4} tsp pepper	
\\ \nicefrac{1}{2} tsp salt
\\ garlic}{Pour dressing over vegetables. Seal in a container and let stand for one day in refrigerator before serving. Turn upside down occasionally to make sure bean mix is well marinated.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{QUINOA SALAD WITH BLACK BEANS} \index{QUINOA SALAD WITH BLACK BEANS}
\textit{(Laura Jackson)} \\
\step{1 cup dry quinoa, rinsed	
	\\ 1 Tbsp olive oil or coconut oil
	\\ 1 \nicefrac{3}{4} cup water	
	\\ 1 can black beans, drained and rinsed
	\\ 1 avocado, chopped into chunks	
	\\ handful cherry tomatoes, quartered 
	\\ \nicefrac{1}{4} red onion, diced	
	\\ 1 small clove garlic, minced
	\\ 1 red bell pepper, chopped
	\\ handful cilantro, diced
	\\ 1 limes, juiced	
	\\ \nicefrac{1}{2} tsp  cumin
	\\ \nicefrac{1}{2} Tbsp olive oil 	
	\\ salt, to taste}{
Warm the olive/coconut oil in a medium saucepan over medium heat. Once it's hot add the rinsed quinoa and toast for about 2-3 minutes until it starts smelling nutty. Add water, stir once, cover, and simmer with a lid on for 20 minutes.  Combine the lime juice, oil, cumin, and salt. When the quinoa has finished cooking, remove it from heat and fluff with a fork. Add black beans and toss to warm them through. Let the quinoa cool for about five minutes and then add all the remaining ingredients, including the dressing, and mix.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{NICOISE SALAD} \index{NICOISE SALAD}
\step{1 head lettuce, torn	
\\ 1 Romaine Lettuce, torn
\\ 	2-184 gram cans tuna	
\\ 1 red onion, thinly sliced
\\ 	\nicefrac{1}{2} cup black olives, sliced	
\\ 1 cup celery, sliced thinly
\\ 	4 med cooked potatoes, sliced
	\\ 398 ml julienne green beans, drained
	\\ \nicefrac{1}{2} oil	
	\\ 3 Tbsp red wine vinegar
	\\ \nicefrac{1}{4} cup chopped parsley	
	\\ 1 Tbsp lemon juice
	\\ \nicefrac{1}{2} tsp salt	
	\\ \nicefrac{1}{4} tsp pepper
	\\ 1-2 cloves garlic	
	\\ 2 tomatoes, cut in wedges
	\\ 3 hard boiled eggs, quartered
}{Line large platter or salad bowl with lettuce.
Layer tuna, onion, olives, celery, potatoes and beans over top.
Mix oil, vinegar, parsley, lemon juice, salt, pepper and garlic together. Drizzle over salad. Arrange tomato and egg wedges over or around salad.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WALDORF SALAD} \index{WALDORF SALAD}
\textit{(Louise Anderson)}\\
\step{4 cups red apples with skin, sliced	
\\ \nicefrac{1}{2} cup thinly sliced celery
\\ \nicefrac{1}{2} cup raisins	walnuts, chopped
\\ approx \nicefrac{1}{2} cup mayonnaise}{}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FRESH SPINACH AND CHEESE SALAD} \index{FRESH SPINACH AND CHEESE SALAD}
\step{500 g fresh spinach	
\\ 200 g sliced mushrooms
\\ 200 g cheddar cheese	
\\ 1 red onion, sliced
\\ \nicefrac{2}{3} cup olive oil	
\\ \nicefrac{1}{3} cup red wine vinegar
\\ oregano to taste	
\\ salt and ground black pepper}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BRIE AND APPLE SALAD} \index{BRIE AND APPLE SALAD}
\step{1 red apple (not Delicious) with peel, thinly sliced \\
4 oz Brie cheese, thinly sliced \\
4 cups mixed salad greens \\
\\Mustard Dressing: \\
\nicefrac{1}{4} cup whipping cream\\
1 Tbsp lemon juice\\
1 Tbsp grainy mustard\\	
1 Tbsp maple syrup \\
\nicefrac{1}{4} tsp salt}{Arrange salad greens on 4 individual salad plates. Top with apple and cheese. Drizzle dressing over salad.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MULTI-LAYERED SALAD} \index{MULTI-LAYERED SALAD}
\textit{Layered salads with a mayonnaise-based dressing can be refrigerated up to 8 hours. Multi-layered salad should be refrigerated 24 hours.}\\
\step{1 med head lettuce with some spinach or romaine mixed in \\
	1 cup sliced celery	\\
	6 hard boiled eggs, chopped\\
	10 oz frozen peas, thawed	\\
	8 green onions, sliced\\
	170 ml tin water chestnuts, sliced thin	\\
	8 bacon slices, cooked and crumbled\\
	1 cup mayonnaise	\\
	1 cup sour cream\\
	2 Tbsp sugar\\
	1 cup cheddar cheese, grated	\\
	4 bacon slices, cooked and crumbled}{Cut or break lettuce into small pieces. Layer in bottom of 9 x 13" pan or glass bowl. Scatter each layer in order given. Mix mayonnaise, sour cream and sugar. Spread over  top, being careful to seal right to edge of pan. Scatter grated cheese and bacon over top. Store in refrigerator for at least 24 hours before serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MIXED GREEN SALAD} \index{MIXED GREEN SALAD}
\step{6 cups mixed salad greens \\
	\nicefrac{3}{4} cup thinly sliced red onion\\
	\nicefrac{1}{2} cup toasted macadamia nuts\\
	sliced kiwi\\
\\ Dressing: \\
3 Tbsp sesame oil	\\
2 Tbsp red wine vinegar\\
1 Tbsp Dijon mustard	\\
1 Tbsp peanut butter\\
\nicefrac{1}{4} tsp dried thyme	\\
1 garlic clove, minced\\
\nicefrac{1}{4} tsp salt}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RUBY CHARD AND RASPBERRY SALAD} \index{RUBY CHARD AND RASPBERRY SALAD}
\step{6 cups cut or torn ruby chard
\\ 1 cup fresh raspberries
\\ \nicefrac{1}{3} cup thinly sliced red onion
\\ \nicefrac{1}{3} cup coarsely crumbled goat cheese
\\ \nicefrac{1}{3} cup pine nuts, toasted}{}

\step{RASPBERRY VINAIGRETTE:
\\ \nicefrac{1}{4} cup fresh raspberries
\\ 3 Tbsp peanut or cooking oil
\\ 1 Tbsp liquid honey
\\ 1 Tbsp raspberry vinegar
\\ \nicefrac{1}{4} tsp finely grated orange zest
\\ \nicefrac{1}{8} tsp salt
\\ \nicefrac{1}{8} tsp coarsely ground pepper}{Process vinaigrette ingredients in blender until smooth.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRANBERRY AND PEAR SALAD} \index{CRANBERRY AND PEAR SALAD}
\textit{(Yvonne Hiebert)}\\
\step{1 Tbsp olive oil
\\ \nicefrac{1}{4} tsp cumin
\\ \nicefrac{1}{4} tsp cinnamon
\\ \nicefrac{1}{4} tsp chili powder
\\ \nicefrac{1}{8} tsp cayenne
\\ 1 cup walnuts or pecans}{Combine oil and spices in small bowl.  Add nuts and stir until they are well coated. Toast in oven.}

\step{VINAIGRETTE:
\\ 3 Tbsp balsamic vinegar
\\ 1 Tbsp Dijon mustard
\\ 1 Tbsp packed brown sugar
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{4} cup olive oil}{}

\step{SALAD:
\\ 8 cups salad greens
\\ 2 large pears
\\ \nicefrac{1}{2} cup cranberries
\\ 1 cup nuts}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEAR SALAD WITH APPLE AND SNOW PEAS} \index{PEAR SALAD WITH APPLE AND SNOW PEAS}
\step{2 cups fresh snow peas	\\
2 ripe pears, peeled\\
1 \nicefrac{1}{2} tsp fresh lemon juice	\\
1 red delicious apple, peeled\\
2 cups fresh spinach leaves	\\
2 Tbsp balsamic vinegar\\
1 tsp Dijon mustard	\\
1 clove garlic\\
\nicefrac{1}{2} tsp pepper	\\
2 Tbsp olive oil\\
1-2 green onions, thinly sliced	\\
1 Tbsp chopped fresh basil\\
3 Tbsp chopped pecans, toasted}{
Cook snow peas in boiling water to cover 1 minutes. Drain. Plunge into ice water to stop cooking process. Cut lengthwise into \nicefrac{1}{4}" strips. Cut pears into \nicefrac{1}{4}" strips. Toss with lemon juice. Cut apple and spinach into thin strips.
Whisk together vinegar and next 3 ingredients. Gradually add oil, whisking until mixture is well blended. Stir in green onions and basil. Chill 15 minutes. Combine vegetable strips and pear strips. Drizzle with dressing, tossing to coat. Sprinkle with pecans.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GREENS WITH ROASTED BACON-WRAPPED PEARS} \index{GREENS WITH ROASTED BACON-WRAPPED PEARS}
\step{12 ready to serve bacon slices	\\
3 large pears, peeled and quartered\\
6 cups mixed salad greens	\\
\nicefrac{2}{3} cup pecans, toasted\\
\nicefrac{2}{3} cup shaved parmesan cheese\\	
Apple-Ginger vinaigrette}{Wrap one slice of bacon around each pear quarter and secure with a wooden pick. Place pear quarters on a wire rack on a cookie sheet. Bake at 350${}^\circ$F for 10 minutes. Arrange salad greens on 4 serving plates and sprinkle evenly with pecans and parmesan cheese. Place 3 pear quarters on each salad and serve with Apple-ginger Vinaigrette.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HABA\~NERO BLACK BEAN MANGO SALAD} \index{HABA\~NERO BLACK BEAN MANGO SALAD}
\textit{(Loraine Hiebert)}\\
\\ \step{1 540 ml can black beans, rinsed and drained
\\ 1 can corn
\\ \nicefrac{1}{2} yellow pepper, diced
\\ 3 green onions, chopped
\\ 1 mango, diced
\\ \nicefrac{1}{4} cup chopped coriander
\\ \nicefrac{1}{2} cup Haba\~{n}ero BBQ sauce
\\ 1 lime, juice of}{Combine all ingredients and serve on lettuce.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MANGO CHICKEN SALAD} \index{MANGO CHICKEN SALAD}
\step{4 chicken breast halves	\\
1 cup chicken broth\\
\nicefrac{1}{2} cup golden raisins\\	
1 mango, peeled and cubed\\
2 cups seedless green grapes\\	
\nicefrac{3}{4} cup mayonnaise\\
\nicefrac{1}{4} cup mango chutney\\	
2 Tbsp sour cream\\
2 \nicefrac{1}{2} tsp curry powder\\	
\nicefrac{1}{4} cup minced Italian parsley\\
1 cup coarsely chopped fresh pineapple}{Preheat oven to 350. Arrange chicken breasts in baking pan and cover with broth. Bake 25-30 minutes or  until chicken is tender and juices run clear with it is pierced with a knife. Set chicken aside to cool.
In large bowl, shred chicken into bite size pieces. Add raisins, mango and grapes.
Whisk mayonnaise, chutney, sour cream, curry powder and parsley together. Combine with chicken and chill for at least 3 hours. Just before serving stir in pineapple. Serve on a bed of mixed greens.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RICE SALAD} \index{RICE SALAD}
\textit{(Janie Ziprick)}\\
\step{2 cups cooked minute rice	\\
3 Tbsp vinegar\\
1 cup chopped celery\\	
\nicefrac{1}{2} tsp sugar\\
\nicefrac{1}{4} cup chopped onion\\	
\nicefrac{1}{2} tsp accent\\
1 cup drained shrimp	\\
2 Tbsp curry powder\\
green pepper, chopped\\	
\nicefrac{1}{2} tsp celery salt\\
\nicefrac{1}{2} cup salad oil	\\
2 Tbsp soya sauce \\
\nicefrac{1}{2} tsp salt}{Combine and chill.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SEVEN-UP SALAD} \index{SEVEN-UP SALAD}
\textit{(Alberta Knott)}\\
\step{1 lemon or lime jelly powder \\
1 cup hot water\\
1 cup 7Up	\\
1 cup crushed pineapple, drained\\
\nicefrac{1}{2} cup miniature marshmallows	\\
1 banana, cubed}
{Dissolve jelly powder in hot water. Add 7 Up. When it starts to set, add pineapple, marshmallows and banana. Let set then cover with sauce.}
SAUCE:\\
\step{\nicefrac{1}{2} cup pineapple juice	\\
\nicefrac{1}{4} cup sugar\\
1 Tbsp flour	\\
1 Tbsp butter\\
1 egg, slightly beaten}
{Cook sauce. Let cool and add \nicefrac{1}{2} cup whipped cream and spread on jellied salad. Sprinkle with yellow powdered cheese.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PINEAPPLE AND CHEESE SALAD} \index{PINEAPPLE AND CHEESE SALAD}
\textit{(Dorine Milner)}\\
\step{1 can crushed pineapple\\
\nicefrac{2}{3} cup sugar \\
1 3-ox pkg lemon Jello\\
1 cup whipping cream\\
1 cup milk\\
shredded cheddar cheese}{Heat pineapple and sugar. Add and dissolve Jell-O. Cool, then whip and add whipping cream. Fold milk and shredded cheddar cheese. Allow to set in fridge.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMONY APPLE SALAD} \index{LEMONY APPLE SALAD}
\step{\nicefrac{1}{4} cup mayonnaise\\
2 Tbsp lemon juice\\
2 Tbsp honey	\\
\nicefrac{1}{2} tsp grated lemon rind\\
\nicefrac{1}{4} tsp salt	\\
2 red delicious apples, cored and chopped\\
1 Granny Smith apple, cored and chopped\\
\nicefrac{1}{4} cup diced celery\\	
\nicefrac{1}{4} cup raisins\\
cubed cheddar cheese	\\
Garnish:  \nicefrac{1}{4} cup chopped pecans, toasted}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRANBERRY SALAD} \index{CRANBERRY SALAD}
\textit{(Auntie Marie Neufeld)}\\
\step{1 lb. cranberries	\\
1 small orange\\
1 cup sugar	\\
2 pkgs. cherry Jell-O\\
2 cups boiling water	\\
1 tall tin crushed pineapple \\
OR 2 cups diced apples}{In food chopper, grind up cranberries and orange. Add sugar. Dissolve Jell-O in hot water and let stand 1 hour. Combine both mixtures and add pineapple. Let stand in refrigerator.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{12 HOUR SALAD} \index{12 HOUR SALAD}
\step{3 eggs, beaten \\
2 cups pineapple tidbits\\
5 Tbsp lemon juice	\\
4 cups miniature marshmallow\\
5 Tbsp white sugar	\\
1 cup whipping cream\\
2 Tbsp butter	\\
1 large tin fruit cocktail}{Put eggs in double boiler. Add sugar and lemon juice. Heat, beating constantly until thick and smooth. Remove from heat. Add butter and marshmallows and stir while hot. Cool in fridge. When cold (\nicefrac{1}{2}--1 hour) fold in cream and cocktail. Salad should be made 12 hours in advance and stored in fridge. Salad may be unmoulded.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROCCOLI SALAD} \index{BROCCOLI SALAD}
\step{1 head broccoli\\
1 cup raisins (opt)\\
1 cup sunflower seeds	\\
1 cup diced red onion \\
7--9 strips bacon, cooked and crumbled\\
\\Dressing:\\
1 cup mayonnaise\\
3-4 Tbsp sugar \\
1 Tbsp vinegar}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TOSSED CRAB SALAD} \index{TOSSED CRAB SALAD}
\step{2 cups lettuce, cut bite size	\\
1 cup diced cucumber\\
\nicefrac{1}{2} cup diced celery	\\
2 green onions, sliced\\
1 pkg. crab (454 grams)\\
\\Dressing:\\
\nicefrac{1}{2} cup salad dressing\\	
1 Tbsp ketchup\\
1 tsp Worcestershire sauce	\\
1 tsp lemon juice\\
\nicefrac{1}{2} tsp salt	\\
\nicefrac{1}{4} tsp pepper}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CABBAGE AND NOODLE SALAD} \index{CABBAGE AND NOODLE SALAD}
\step{\nicefrac{1}{2} head cabbage, finely cut \\
2 green onions, chopped\\
\nicefrac{1}{2} green pepper, chopped (opt)\\	
\nicefrac{1}{2} cup slivered almonds\\
2 Tbsp sesame seeds	\\
2 Tbsp sunflower seeds\\
1 pkg. ichiban chicken noodles, uncooked and separated \\
12 oz. bean sprouts	mushrooms (opt)\\
\\ Dressing: \\
\nicefrac{1}{2} cup salad oil\\
1 Tbsp sugar\\
3 Tbsp vinegar\\	
\nicefrac{1}{2} tsp pepper\\
2--4 Tbsp soy sauce\\
seasonings from noodle pkg.}{Toss together cabbage, green onions and green pepper and set aside. Toast the almonds, sesame seeds and sunflower seeds on a cookie sheet in oven until golden brown. Add to vegetables along with the noodles and mix well. Mix together dressing ingredients, pour over salad and toss.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ROMAINE MANDARIN SALAD} \index{ROMAINE MANDARIN SALAD}
\step{1 head romaine lettuce	\\
3 green onions, chopped\\
1 cup chopped celery	\\
1 can mandarin oranges, drained (reserve liquid)\\
\nicefrac{1}{2} cup sliced almonds\\
\\Dressing:\\
\nicefrac{1}{3} cup salad oil\\
\nicefrac{1}{4} cup vinegar\\
\nicefrac{1}{4} cup sugar	\\
2 Tbsp liquid drained from oranges\\
1 tsp salt	\\
\nicefrac{1}{2} tsp pepper}{Toss salad with dressing. Garnish with orange segments and almonds.
*To add flavour, almonds may be cooked with 2--4 Tbsp sugar in small saucepan over low heat. Cook, stirring constantly, until sugar is melted and almonds are coated.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CONFETTI SALAD} \index{CONFETTI SALAD}
\step{3 cups cantaloupe cubes\\
3 cups watermelon cubes\\
2 cups honeydew cubes	\\
1 cup halved strawberries\\
Leaf lettuce}{Combine fruits and place on lettuce leaves. Spoon a little of the poppy seed dressing over each plate of salad. Serve immediately.}

\rtitle{POPPI SEED DRESSING}
\step{1 cup salad oil	\\
\nicefrac{1}{3} cup orange juice\\
\nicefrac{1}{4} cup liquid honey	\\
1 tsp salt\\
\nicefrac{1}{2} tsp dry mustard	\\
\nicefrac{1}{2} tsp paprika\\
1 Tbsp poppy seeds}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{KALE SALAD} \index{KALE SALAD}
\textit{(Delgado family, friends of Katrina)}\\
\step{bunch of kale
\\ olive oil
\\ lemon juice
\\ salt \& pepper
\\ parmesan
\\ toasted pine nuts}{Wash and drain kale. Shoured into bitesize pieces. Drizzle with olive oil and massage (this makes the leaves more tender) until silky. Drizzle with lemon juice. Salt and pepper to taste. Add parmesan cheese and toasted pine nuts.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SPINACH BACON SALAD} \index{SPINACH BACON SALAD}
\step{6 oz spinach	
	\\ \nicefrac{1}{2} cup shaved parmesan
	\\ 3 hard-boiled eggs, coarsely chopped	
	\\ 6 bacon slices, crumbled
	\\ Mushourooms, sliced	
	\\ onion greens, chopped
	\\\\Dressing:
  \\ \nicefrac{1}{2} cup spinach	
	\\ 1 \nicefrac{1}{2} tsp dried parsley
	\\ 2 bacon slices, crumbled	
	\\ 1 Tbsp Dijon mustard
	\\ \nicefrac{1}{3} cup yogurt	
	\\ 1 garlic clove
	\\ \nicefrac{1}{4} cup oil	
	\\ \nicefrac{1}{4} tsp pepper
	\\ 2 Tbsp white wine vinegar	
	\\ 2 tsp sugar}{}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APPLEBEE'S GRILLED SHRIMP 'N' SPINACH SALAD} \index{APPLEBEE'S GRILLED SHRIMP 'N' SPINACH SALAD}
\step{BACON VINAIGRETTE:
\\ \nicefrac{1}{2} cup light olive oil
\\ \nicefrac{1}{4} cup finely minced cooked bacon (3-4 slices)
\\ \nicefrac{1}{4} cup red wine vinegar
\\ \nicefrac{1}{2} tsp cornstarch
\\ 1 \nicefrac{1}{2} tsp Grey Poupon Dijon mustard
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{4} tsp black pepper
\\ \nicefrac{1}{4} tsp hickory flavoured liquid smoke}{Combine bacon with \nicefrac{1}{4} cup of oil in small saucepan. Place pan over med heat. Simmer for 1 minutes. remove from heat and let it cool 3-4 minutes. Dissolve cornstarch in vinegar and whisk mixture into the oil and bacon, along with the sugar, mustard, salt, pepper and liquid smoke. Drizzle the remaining \nicefrac{1}{4} cup oil into the saucepan while whisking. Stir into the vinegar mixture. Cover and chill.}

\step{SHRIMP SEASONING:
\\ 1 tsp black pepper
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} tsp garlic powder
\\ \nicefrac{1}{4} tsp onion powder
\\ \nicefrac{1}{4} tsp paprika
\\ \nicefrac{1}{4} tsp ground sage
\\ \nicefrac{1}{4} tsp granulated sugar}{Combine ingredients in bowl.}

\step{SALAD:
\\ 20-24 med shrimp, peeled and deveined
\\ 2 Tbsp butter, melted
\\ \nicefrac{1}{4} cup sliced almonds
\\ 16 cups fresh spinach
\\ \nicefrac{1}{2} cup diced tomato
\\ \nicefrac{1}{2} cup sliced red onion
\\ \nicefrac{1}{4} cup sliced roasted red bell pepper}{Roast bell pepper in oven at 425${}^\circ$F until skin blisters. Use ice water bath to remove the skin. Preheat BBQ grill to high. Pierce 6 shrimp on each skewer. Brush with melted butter and sprinkle a little of the seasoning blend on both sides. Grill skewered shrimp for a couple minutes on each side.
Toast the sliced almonds in a med pan over med heat until golden brown.
Build each salad separately, by tossing 4 cups spinach with \nicefrac{1}{4} of the salad ingredients and 2 Tbsp vinaigrette. Arrange the tossed salad on a serving plate, remove grilled shrimp from skewers and place on top.}

	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CAESAR SALAD DRESSING} \index{CAESAR SALAD DRESSING}
\textit{(Loraine Hiebert)} \\
\step{\nicefrac{1}{2} cup olive oil	
	\\ \nicefrac{3}{4} tsp salt
	\\ \nicefrac{1}{4} tsp pepper	
	\\ \nicefrac{1}{4} tsp dry mustard
	\\ 1 \nicefrac{1}{2} tsp Worcestershire	
	\\ 1 egg
	\\ 2 Tbsp grated parmesan cheese	
	\\ 2 Tbsp lemon juice
	\\ garlic to taste}{}
		
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CILANTRO TACO DRESSING} \index{CILANTRO TACO DRESSING}
\step{1 cup loosely packed cilantro	
	\\ \nicefrac{1}{2} cup yogurt
	\\ 2 cloves of garlic	
	\\ 1 lime
	\\ \nicefrac{1}{4} cup olive oil	
	\\ 2 Tbsp apple cider vinegar
	\\ salt}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ITALIAN DRESSING} \index{ITALIAN DRESSING}
\textit{Great for marinating vegetables as well as for greens}\\
\step{1 cup salad oil	\\
\nicefrac{1}{4} cup lemon juice\\
\nicefrac{1}{4} cup vinegar	\\
2 tsp sugar\\
1 tsp salt	\\
\nicefrac{1}{2} tsp dry mustard\\
\nicefrac{1}{2} tsp onion salt	\\
\nicefrac{1}{2} tsp paprika\\
\nicefrac{1}{2} tsp oregano	\\
\nicefrac{1}{2} garlic salt or 1 clove crushed\\
\nicefrac{1}{8} tsp thyme\\
}{Measure all ingredients into jar. Cover. Shake well. Chill two hours before using.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BALSAMIC VINAIGRETTE} \index{BALSAMIC VINAIGRETTE}
\step{\nicefrac{1}{4} cup balsamic vinegar
\\ 2 tsp brown sugar (opt)
\\ 1 Tbsp garlic, minced
\\ \nicefrac{1}{2} tsp salt
\\ \nicefrac{1}{2} tsp pepper
\\ \nicefrac{3}{4} cup oil}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{APPLE-GINGER VINAIGRETTE} \index{APPLE-GINGER VINAIGRETTE}
\step{\nicefrac{1}{2} cup apple jelly, melted	
\\ \nicefrac{1}{3} cup cider vinegar
\\ 1 Tbsp Dijon mustard	
\\ 2 Tbsp light brown sugar
\\ 3 Tbsp chopped fresh chives	
\\ 2 tsp grated fresh ginger
\\ \nicefrac{1}{4} tsp salt	
\\ 1 cup vegetable oil}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{THOUSAND ISLAND DRESSING} \index{THOUSAND ISLAND DRESSING}
\step{\nicefrac{1}{2} cup salad oil	
\\	\nicefrac{1}{2} cup evaporated milk
\\	\nicefrac{1}{4} cup vinegar	
\\	\nicefrac{1}{4} cup ketchup
\\	\nicefrac{1}{2} tsp salt	
\\	1 tsp Worcestershire sauce
\\	\nicefrac{1}{4} tsp paprika
\\	2 Tbsp minced onion	
\\	2 Tbsp minced sweet pepper
\\	2 minced cloves garlic	
\\	2 chopped, hard-cooked eggs}{Blend oil, milk, vinegar, ketchup, salt, worcestershire sauce, and paprika. Add remaining ingredients and chill.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RANCH STYLE DRESSING} \index{RANCH STYLE DRESSING}
\step{1 cup yoghurt	
\\	1 cup mayonnaise
\\	1 tsp minced parsley	
\\	\nicefrac{1}{2} tsp onion salt
\\	1 tsp garlic salt	minced chives}{Combine and store in fridge.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SNAPPY FRENCH DRESSING} \index{SNAPPY FRENCH DRESSING}
\step{1 cup salad oil	
\\	1 tsp salt
\\	\nicefrac{2}{3} cup ketchup	
\\	1 tsp dry mustard
\\	\nicefrac{1}{2} tsp cider vinegar	
\\	1 tsp paprika
\\	\nicefrac{1}{2} tsp sugar	
\\	\nicefrac{1}{4} tsp garlic powder
\\	\nicefrac{1}{2} small onion	dash pepper
\\	1 Tbsp lemon juice}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HARE KRISHNA SALAD DRESSING} \index{HARE KRISHNA SALAD DRESSING}
\textit{(Fiore Carpino)} \\
\step{1-\nicefrac{1}{2} cups almonds	
\\ 1-\nicefrac{1}{2} cups nutritional yeast
\\ 2 cups water	
\\ 1-\nicefrac{1}{2} cups sunflower oil
\\ \nicefrac{1}{2} cup Bragg's amino acids (or soy sauce)
\\ 1 tsp hing/asafetida}{}

\end{minipage}