\section{Sandwiches}
\begin{minipage}{\linewidth}\rtitle{ZIPPY TUNA SPREAD} \index{ZIPPY TUNA SPREAD}
\step{184 g canned tuna, drained	\\
\nicefrac{1}{4} cup mayonnaise\\
2 tsp prepared horseradish	\\
1 tsp lemon juice\\
\nicefrac{1}{2} tsp salt	\\
1/8 tsp pepper}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{EGG SALAD SPREAD} \index{EGG SALAD SPREAD}
\step{6 hard boiled eggs, chopped	\\
1 cup diced cucumber, peeled and seeded\\
1 cup diced celery	\\
3 Tbsp chopped green onion\\
2 Tbsp chopped pimiento	\\
1 tsp salt\\
\nicefrac{1}{2} cup mayonnaise}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CORNED BEEF SPREAD} \index{CORNED BEEF SPREAD}
\step{340 g canned corned beef, mashed	\\
2 hard-boiled eggs, chopped\\
\nicefrac{1}{2} cup mayonnaise	\\
2 tsp onion flakes\\
2 tsp water	\\
1 tsp Worcestershire sauce}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CUCUMBER SANDWICHES} \index{CUCUMBER SANDWICHES}
\step{200 grams cream cheese
\\ \nicefrac{1}{4} cup fresh mint, whirled in food processor
\\ Chives, minced}{Mix these ingredients. Spread on soft bread. Top with slices of cucumber.  These can be open-faced or not.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MUSHROOM TRIANGLES} \index{MUSHROOM TRIANGLES}
\step{1 \nicefrac{1}{2} cups sliced fresh mushrooms	\\
\nicefrac{1}{4} cup chopped onion\\
1 Tbsp butter	\\
125 g cream cheese, cut up	\\
\nicefrac{1}{4} tsp Worcestershire sauce\\
\nicefrac{1}{4} tsp salt	pepper sprinkle\\
Garlic powder sprinkle
}{Saut\'e until onion is soft and clear. Add remaining ingredients. Stir to melt cheese. Spread on buttered, crustless bread. Fold to make triangles. Press edges. Brush with melted butter. Toast triangles at 400$^\circ$F for about 10-15 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CURRIED CHICKEN SANDWICH FILLING} \index{CURRIED CHICKEN SANDWICH FILLING}
\step{2 cups cubed, cooked chicken
\\ 1 unpeeled red apple, chopped
\\ \nicefrac{3}{4} cup dried cranberries
\\ \nicefrac{1}{2} cup thinly sliced celery
\\ \nicefrac{1}{4} cup chopped pecans
\\ 2 Tbsp thinly sliced green onions
\\ \nicefrac{3}{4} cup mayonnaise
\\ 3 tsp lime juice
\\ \nicefrac{1}{2} tsp curry powder}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{REUBEN SANDWICH} \index{REUBEN SANDWICH}
\step{2 rye bread slices	\\
2-4 thick slices, corned beef\\
2 Tbsp sauerkraut, drained	\\
1 mozzarella cheese slice}{Layer ingredients on bread. Cover with second slice of bread. Butter outside of bread and grill.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MONTE CRISTO} \index{MONTE CRISTO}
\step{3 slices white bread, buttered	\\
2 mozzarella cheese slices\\
1 cooked ham slice	\\
1 slice turkey or chicken\\
1 egg, lightly beaten	\\
2 Tbsp water}{Layer first bread slice with slice of cheese and ham. Top with bread slice. Put turkey and remaining cheese on top. Cover with Bread slice. Mix egg with water. Dip sandwich into egg  mixture. Grill in well greased frying pan, browning both sides. Cut diagonally into 4. Makes 1 large serving.}

\end{minipage}