\section{Soups and Chilis}

\begin{minipage}{\linewidth}\rtitle{MUSHROOM SOUP SUBSTITUTE} \index{MUSHROOM SOUP SUBSTITUTE}
For cream sauces, fry onions in oil. Add 1 can evaporated milk, and 2 Tbsp flour mixed with a bit of water. Add spices (paprika, celery salt, salt, pepper, parsley) and let it cook until thick. If you need more or it's too thick, add regular milk.

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CORN CHOWDER} \index{CORN CHOWDER}
\textit{(Loraine Hiebert)}\\
\step{\nicefrac{1}{2} cup margarine	
\\\nicefrac{1}{2}--\nicefrac{3}{4} cup flour
\\6 strips bacon
\\\nicefrac{1}{2} onion
\\2 potatoes	
\\1 can cream corn
\\1 liter milk	
\\celery salt
\\pepper}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TUNA CHEESE CHOWDER} \index{TUNA CHEESE CHOWDER}
\textit{(Andy Nix)}\\
\step{4 Tbsp butter	
\\ \nicefrac{1}{4} cup chopped celery
	\\ 1 cup chopped onion	
	\\ 1 cup diced potatoes
	\\ 1 \nicefrac{1}{4} tsp salt	
	\\ \nicefrac{1}{4} tsp pepper
	\\ \nicefrac{1}{2} tsp thyme	
	\\ \nicefrac{1}{4} tsp dill weed
	\\ 2 Tbsp flour	
	\\ 1 8-oz. can stewed tomatoes
	\\ 3 cups milk	
	\\ 1 can tuna, drained
	\\ 2 Tbsp parsley	
	\\ 1 cup grated cheddar cheese}{Melt butter in large sauce pan. cook celery, onions and potatoes in butter over heat. Stir until vegetables are tender (15-20 minutes). Stir in seasonings and flour. Slowly add milk and tomatoes, stirring constantly. Add tuna. Makes 5-6 1 cup servings.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MUSHROOM, LEEK AND SEAFOOD CHOWDER} \index{MUSHROOM, LEEK AND SEAFOOD CHOWDER}
\step{2 slices bacon, chopped	
\\ 3 cups sliced fresh mushrooms
\\3 leeks, thinly sliced, white only	
\\2 cloves garlic, minced
\\3 med potatoes, chopped	
\\2 14 \nicefrac{1}{2} oz cans chicken broth
\\8 oz fresh or frozen peeled shrimp
\\8 oz fresh or frozen bay scallops	
\\1 large carrot, shredded	
\\3 Tbsp margarine, melted
\\3 Tbsp flour	
\\2 cups light cream}{Cook bacon in Dutch oven until browned. Remove with slotted spoon, reserving drippings. Add mushrooms, leeks and garlic. Cook until vegetables are tender. Carefully add potatoes, broth and \nicefrac{1}{4} tsp pepper. Bring to boil. Reduce heat and simmer, covered, 15 minutes or until potatoes are tender. Add shredded carrot to vegetable mixture. Bring to boil. Stir together melted margarine and flour. Add flour mixture and cream to pot. Cook and stir over med heat until bubbly. Add shrimp, scallops and bacon. Cook and stir 2-3 minutes more or until shrimp are pink and scallops are opaque. If desired, garnish with lemon slices and/or thyme.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROCCOLI CHEESE SOUP (GF*)} \index{BROCCOLI CHEESE SOUP (GF*)} \index{Gluten Free!soups}
\step{\nicefrac{1}{4} cup chopped onion	\\
1 Tbsp butter or margarine\\
2 \nicefrac{1}{2} cups milk	\\
1 Tbsp chicken bouillon powder\\
284 grams frozen broccoli, chopped\\
\nicefrac{1}{2} tsp salt	\\
\nicefrac{1}{8} tsp pepper\\
1 cup grated medium cheddar cheese \\
}{Put onion and butter in saucepan. Saut\'e until clear and soft. Add next 5 ingredients. Bring to boil. Cover and simmer until vegetables are cooked. Cool and bit then chop to desired coarseness in batches in blender. Return to saucepan. Add cheese. Stir to melt. Garnish with a piece of broccoli.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HAMBURGER SOUP (GF*)} \index{HAMBURGER SOUP (GF*)} \index{Gluten Free!soups}
\step{1 lb. hamburger. \\
2 quarts water	\\
\nicefrac{1}{2} cup diced onion\\
1 cup diced potatoes	\\
1 cup diced carrots\\
1 cup diced cabbage	\\
\nicefrac{1}{4}--\nicefrac{1}{2} cup rice or macaroni\\
2 \nicefrac{1}{2} cups tomatoes \\
salt \\
pepper \\
bay leaf \\
parsley \\}{Brown meat. Add remaining ingredients.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GENERAL CREAM SOUP} \index{GENERAL CREAM SOUP}
\textit{A wide variety of cream soups can be made, based on the vegetable or meat flavour that you wish. In fact, almost any vegetable can be made into a cream soup.} \\
\step{\nicefrac{1}{3}  cup onion, chopped	\\
garlic (opt) \\
mushrooms (opt) \\
\nicefrac{1}{4} cup butter \\
\nicefrac{1}{4} cup flour	\\
2 cup water \\
2 bouillon cubes \\
3 cups milk \\
vegetables and/or cooked meat \\
salt and pepper \\
basil, curry, paprika, dill, parsley, etc. (opt) \\
cheese, grated}{saut\'e onions (garlic and mushrooms) in butter. Add flour. Add water and bouillon cubes. Whisk until smooth. Add milk. Add cooked or tinned vegetables and/or cooked meats. Simmer approximately 10 minutes until soup has thickened. Season with salt and pepper. Add other seasonings. Add cheese at the end of the cooking time.}
	
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM OF MUSHROOM} \index{CREAM OF MUSHROOM}
\step{\nicefrac{1}{4} cup butter	\\
\nicefrac{1}{2} cup chopped onion \\
1 lb. fresh mushrooms, sliced or chopped \\
\nicefrac{1}{4} cup flour	\\
\nicefrac{1}{4} tsp pepper\\
\nicefrac{1}{2} tsp salt	\\
1 clove garlic\\
1 cup beef stock\\	
1 cup chicken stock\\
1 cup milk\\
1 cup light or heavy cream\\
4 tsp white wine (opt)\\
}{saut\'e butter and mushrooms in butter until onion is soft and clear. Add flour, salt, pepper, and garlic. Stir in beef and chicken stock and milk until it boils and thickens. Stir in cream and wine.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM OF SPINACH SOUP} \index{CREAM OF SPINACH SOUP}
\step{\nicefrac{1}{4} cup butter	\\
2 cups chopped onion\\
6 Tbsp flour	\\
1 tsp salt\\
\nicefrac{1}{4} tsp pepper\\	
6 cups chicken stock\\
300 gram frozen chopped spinach, squeezed dry\\
OR 6 cups spinach, chopped \& firmly packed\\
1 cup light cream}{Saut\'e onion in butter until clear and soft. Mix in flour, salt and pepper. Stir in stock. Thicken. Add spinach. Simmer 5 minutes. to cook. Stir in cream. Heat without boiling and serve.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM OF CELERY SOUP} \index{CREAM OF CELERY SOUP}
\step{2 cups milk	\\
1 \nicefrac{1}{2} cups finely diced celery\\
\nicefrac{1}{4} cup chopped onion\\
2 Tbsp butter\\
3 Tbsp flour\\
1 tsp salt\\
\nicefrac{1}{4} tsp pepper\\
3 cups milk}{Bring milk, celery, onion, and butter to a boil and simmer until vegetables are tender. Stir in flour, salt, pepper, and milk until it boils and thickens.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM OF ASPARAGUS SOUP} \index{CREAM OF ASPARAGUS SOUP}
\step{1 Tbsp oil \\
1 Tbsp buttermilk\\
1 \nicefrac{1}{2} cups chopped leek (white and tender parts only)\\
2 cloves garlic	\\
1 Tbsp flour\\
\nicefrac{1}{4} cup dry white wine	\\
4 cups chicken broth	\\
1 \nicefrac{1}{2} cups chopped potato	\\
2 lbs asparagus, trimmed and chopped\\
salt and pepper	\\
1 cup whipping cream\\
}{Heat oil and margarine in large pot. Add leek and garlic. Cook about 10 minutes, until leek is tender. Add flour. Heat and stir for about 1 minutes until smooth. Add wine. Heat until thickened. Add broth and potato. Bring to boil. Reduce heat to med. Simmer, uncovered for about 10 minutes, until potato is tender. Add asparagus (except tips) and seasonings. Cook for 5-7 minutes, until asparagus is tender. Process in blender until smooth. Return to pot. Add reserved asparagus tips and whipping cream. Heat and stir on med-high heat for about 5 minutes, until asparagus tips are tender crisp.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAM OF GREEN BEAN SOUP} \index{CREAM OF GREEN BEAN SOUP}
\step{\nicefrac{1}{2} cup butter	\\
6 cups green string beans, cut in short pieces\\
\nicefrac{1}{4} cup finely chopped onion\\
\nicefrac{1}{4} cup flour	\\
2 tsp salt\\
\nicefrac{1}{4} tsp pepper\\
3 \nicefrac{1}{2} cups milk	\\
3 cups water\\
1 cup chicken stock\\
12 oz. canned corned beef}{Saut\'e beans and onion in butter until onion is clear. Stir in flour, salt, and pepper and let thicken. Add milk, water, stock, and corned beef. Simmer until beans are cooked. Serve with a dollop of sour cream or grated cheddar cheese.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CREAMY PEANUT SOUP} \index{CREAMY PEANUT SOUP}
\step{3 Tbsp butter	\\
2 celery stalks\\
1 small onion	\\
\nicefrac{1}{2} cup shredded carrot\\
2 Tbsp flour	\\
2 cups chicken stock\\
1 cup smooth peanut butter\\
2 \nicefrac{1}{2} cups cream or milk\\
\nicefrac{1}{4} tsp salt}{Saut\'e celery, onion, and carrot in butter. Stir in flour and chicken stalk until vegetables are tender. Add peanut butter. Add milk and salt.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BEEF BARLEY SOUP} \index{BEEF BARLEY SOUP}
\step{6 cups water \\
6 beef bouillon cubes\\
796 ml canned tomatoes, mashed	\\
284 ml condensed tomato soup\\
2 cups shredded carrots	\\
2 cups shredded potato\\
1 \nicefrac{1}{2} cups chopped onion\\	
1 cup chopped celery\\
\nicefrac{1}{2} cup pearl or pot barley	\\
6 cups water\\
1 Tbsp parsley flakes	\\
1 tsp sugar\\
1 tsp salt	\\
\nicefrac{1}{4} tsp pepper\\
\nicefrac{1}{4} tsp thyme\\
3 cups cooked roast beef, chopped}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ZUPPA TOSCANA (GF*)} \index{ZUPPA TOSCANA (GF*)} \index{Gluten Free!soups} 
\step{1 lb of hot Italian sausage, 
\\ 3 medium to large potatoes 
\\ 1 small onion
\\ 3 strips of thick sliced bacon
\\ 4 cloves of garlic
\\ 3 cups of kale (sliced in ribbons) 
\\ 32 oz of chicken broth 
\\ 2.5 cups of water
\\ 1 \nicefrac{1}{4} cups of half \& half}{
Remove the casings from the sausage and brown in a skillet, then put aside in a stockpot. In skillet, cook bacon and onions and put in the stockpot after chopping bacon. Add sliced potatoes, chicken broth, minced garlic, and water and let boil for about 30 min, until the potatoes are tender. Add kale and half \& half and let simmer another 15 min until the kale is tender.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TOMATO BISQUE} \index{TOMATO BISQUE}  
\step{2 Tbsp of butter
\\ 1 large onion, quartered \& sliced
\\ 2 Tbsp dried dill weed
\\ \nicefrac{1}{2} tsp sugar
\\ 1 tsp salt or to taste
\\ pepper to taste
\\ 1 qt whole tomatoes (2-14 \nicefrac{1}{2} oz cans)
\\ \nicefrac{1}{4} cup flour
\\ 3 \nicefrac{1}{3} cup chicken broth
\\ 1-12 oz can evaporated milk (skim is okay if you want)}{
Add butter, onion, dill, salt, pepper \& sugar to pot.  Cook until onions are soft. Add tomatoes.  Bring to a boil, break down tomatoes with a wooden spoon into smaller pieces.  Cover and simmer for 15 min. Add broth, reserving about \nicefrac{1}{2} cup.  Add flour to the reserved liquid and slowly add flour mixture to bisque, stirring constantly.  Simmer 5 min.  Add evaporated milk, continue to stir bringing bisque up to serving temperature.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TOMATO SOUP JUST LIKE CAMPBELL'S} \index{TOMATO SOUP JUST LIKE CAMPBELL'S} 
\step{398 ml canned tomatoes \\
2 cups milk\\
1 Tbsp flour	\\
\nicefrac{1}{2} tsp salt\\
\nicefrac{1}{8} tsp pepper\\	
\nicefrac{1}{2} tsp sugar\\
\nicefrac{1}{4} cup milk	\\
\nicefrac{1}{4} tsp baking soda}{Heat tomatoes in small saucepan. Mash or put through blender before heating. Heat first amount of milk in another saucepan. Mix flour, salt, pepper, sugar and second amount of milk together in small dish until no lumps remain. Stir into simmering milk until it boils and thickens. Stir baking soda into hot tomatoes. Stir hot tomatoes slowly into hot milk.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MULLIGATAWNY SOUP (GF*)} \index{MULLIGATAWNY SOUP (GF*)} \index{Gluten Free!soups} 
\textit{(Rebekah Yates)\\ 
The original recipe calls for chicken (2 boneless, skinless chicken breasts cut into small pieces), which you add at the same time as the apple. We like it better with cauliflower, but it's good with chicken, too. This soup is also really good with naan, of course.} \\
\step{1 cup onion, chopped	
	\\ 2 carrots, chopped
	\\ 1 red bell pepper, chopped	
	\\ 2 Tbsp butter
	\\ 3 Tbsp flour	
	\\ 1 Tbsp curry powder
	\\ 8 cups chicken broth	
	\\ \nicefrac{1}{2}-1 large head of cauliflower, broken/cut into small pieces
	\\ 1 apple, chopped	
	\\ \nicefrac{1}{2} cup rice (uncooked) or 1 cup cooked rice
	\\ salt to taste	ground black pepper to taste
	\\ a few shakes of dried thyme	
	\\ half \& half to pour on top}{
Brown onions, pepper, and carrots in the butter. Add flour and curry powder, and cook until it looks like it's getting too dry. Add chicken broth a bit at a time to get to 5 min, mix well, and bring to a boil. Add the cauliflower and simmer about \nicefrac{1}{2} hour.  Add apple, salt, pepper, thyme, and rice if you're using uncooked rice. Simmer 15-20 min (until the uncooked rice is done), or 10-15 min if you're going to use pre-cooked rice (we always use pre-cooked since we eat brown rice and it takes an hour at least). If you're using pre-cooked rice, add it now and keep simmering until the rice is heated. Serve with a bit of half-and-half poured on top.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{TORTILLA SOUP (GF*)} \index{TORTILLA SOUP (GF*)} \index{Gluten Free!soups} 
\step{2 4-oz chicken breasts, cubed	
	\\ 2 cups whole kernel corn
	\\ 1 large onion, chopped	
	\\ 2 cloves garlic, pressed
	\\ 3 \nicefrac{1}{2} cups chicken broth	
	\\ 10 \nicefrac{3}{4} oz can tomato puree
	\\ 10 \nicefrac{3}{4} oz can diced tomatoes with green chillies
	\\ 1 tsp salt	
	\\ 2 tsp ground cumin
	\\ 1 tsp chilli powder	
	\\ \nicefrac{1}{8} tsp ground red pepper
	\\ \nicefrac{1}{8} tsp ground black pepper	
	\\ 1 bay leaf
	\\ taco chips for garnish
	\\ salsa (opt)}{}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FIRST PRIZE TEXAS CHILI (GF*)} \index{FIRST PRIZE TEXAS CHILI (GF*)} \index{Gluten Free!soups} 
\step{2 lbs coarse ground beef
\\ 1 Tbsp cooking oil
\\ 1 Tbsp granulated onion
\\ 1 8-oz can tomato sauce
\\ 4 cups beef broth
\\ 5 Tbsp chili powder*
\\ 1 tsp garlic powder
\\ 1 Tbsp ground cumin
\\ \nicefrac{1}{2} tsp black pepper
\\ 1 tsp paprika
\\ \nicefrac{1}{2} tsp cayenne pepper
\\ \nicefrac{1}{2} tsp salt
\\ 1 chicken bouillion cube
}{Lightly brown meat. Add ingredients Leave covered and simmer for at least 1 hour or until desired consistency.  This is a very spicy chili.  Leave off the cayenne pepper if you don't like your chili too spicy.\\
*I like to combine several types of chili powder, such as Mexican green chili, Mexican red chili, and American chili spice.}
		
\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ITALIAN CHILI} \index{ITALIAN CHILI} 
\textit{(Rebekah Yates)\\
Adapted from Pampered Chef Lazy Lasagna Chili} \\
\step{1 cup zucchini, chopped (opt.)	
	\\ 1 bell pepper, chopped
	\\ 1 large onion, chopped	
	\\ 1-2 links sweet Italian sausage
	\\ 3 garlic cloves, chopped or pressed	
	\\ 1 tsp oregano	
	\\ 1 tsp basil	
	\\ 1-2 tsp sugar
	\\ 1 jar spaghetti sauce	
	\\ 4 cups beef broth
	\\ 1 cup water	
	\\ 1 cup pasta (I usually use shells)}{
Remove casings from sausage and brown the sausage, onions, pepper, and garlic. Drain any excess fat. Add spaghetti sauce, broth, sugar, oregano, basil, and water, and bring to a boil. Stir in pasta. Reduce heat, and simmer uncovered for about 7 min. Add the zucchini and simmer for 3-5 min or until zucchini is desired tenderness (I sometimes also add fresh/frozen spinach sometime in here). Top with parmesan.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{WHITE CHICKEN CHILI (GF*)} \index{WHITE CHICKEN CHILI (GF*)} \index{Gluten Free!soups}
\textit{(Laura Haines)} \\
\step{1 lb boneless skinless chicken breast (3-4) diced in cubes
\\ 1 med onion diced	
\\ 2 cloves of garlic
\\ 1 Tbs oil	
\\ 1 large (40 oz) can Great Northern beans
\\ 1 can Chicken broth	
\\ 1 tsp salt
\\ 1 tsp cumin	
\\ 1 tsp oregano
\\ \nicefrac{1}{2} tsp pepper	
\\ \nicefrac{1}{4} tsp cayenne pepper
	\\ 1 cup sour cream	
	\\ \nicefrac{1}{2} cup whipping cream}{
Brown chicken in pan. Saut\'e onions and garlic in oil. Add all ingredients except sour cream and whipping cream to the crockpot. Simmer. Add sour cream and whipping cream before serving.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BLACK BEAN SOUP (GF*)}  \index{BLACK BEAN SOUP (GF*)} \index{Gluten Free!soups} 
\textit{(Rebekah Yates)\\
adapted from Betty Crocker} \\
\step{1 large onion, chopped	
\\ 3 cloves of garlic, minced
\\ 2 \nicefrac{2}{3} cups dried black beans (1 pound)	
\\ 3 cups beef broth
\\ 3 cups water	
	\\ \nicefrac{1}{4} cup dark rum or apple cider (juice works, like grapefruit or cranberry)
	\\ 1 \nicefrac{1}{2} tsps ground cumin	
	\\ 1 \nicefrac{1}{2} tsps dried oregano
	\\ 1 bell pepper, chopped	
	\\ 1 large tomato, chopped}{
Brown the onion and garlic together. Stir in remaining ingredients; heat to boiling. Boil 2 min; reduce heat. Cover and simmer about 2 hours or until beans are tender (it can take a lot longer than two hours, depending on your beans--one way to make it faster is to add the tomatoes after 1 \nicefrac{1}{2} hours or so instead of right away). Serve with lime, cheese, and sour cream. 
If you're making it in a crockpot, decrease the water to 2 cups and just throw everything in right away. Cook on high for 6-10 hours.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LENTIL SOUP (GF*)} \index{LENTIL SOUP (GF*)} \index{Gluten Free!soups}
\step{8 cups chicken stock	\\
2 cups lentils, red or brown\\
2 med onions, chopped	\\
2 med carrots, cut up\\
1 med potato, cut up	\\
\nicefrac{1}{4} tsp garlic powder or 1 clove minced\\
\nicefrac{1}{2} tsp salt	\\
\nicefrac{1}{4} tsp pepper}
{Combine all ingredients. Cover and simmer for about 45 minutes. (Variation:  can be made with ham stock.)}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUMPKIN SOUP (GF*)} \index{PUMPKIN SOUP (GF*)} \index{Gluten Free!soups}
\textit{(Company's Coming)} \\
\step{2 Tbsp butter	
	\\ \nicefrac{1}{2} cup chopped onion
	\\ 2 cups chicken broth
	\\ 1 good size potato
	\\ \nicefrac{1}{2} tsp salt
	\\ \nicefrac{1}{4} tsp pepper
	\\ \nicefrac{1}{8} tsp thyme
	\\ 14 oz. cooked, mashed pumpkin	
	\\ 2 cups milk}{
Saut\'e onions in butter. Do NOT brown. Add remaining ingredients except pumpkin and milk. Bring to boil. Simmer until potato is tender. Run through blender. Stir in pumpkin and milk.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CURRIED PUMPKIN SOUP} \index{CURRIED PUMPKIN SOUP}
\step{2 Tb butter	
	\\ 1.5 cups half-and-half cream
	\\ 3 Tbsp flour	
	\\ 2 Tbsp soy sauce
	\\ 2 Tbsp curry powder	
	\\ 1 Tbsp sugar
	\\ 4 cups vegetable broth	
	\\ salt and pepper to taste
	\\ 1 (29 oz) can of pumpkin}{
Melt butter in a large pot over medium heat. Stir in flour and curry powder until smooth. Cook, stirring, until mixture begins to bubble. Gradually whisk in broth, and cook until thickened. Stir in pumpkin and half-and-half. Season with soy sauce, sugar, salt, and pepper. Bring just to a boil, then remove from heat.}

\end{minipage}