\section{Bars and Squares}

\begin{minipage}{\linewidth}\rtitle{CINNAMON COFFEE BARS} \index{CINNAMON COFFEE BARS}
\step{\nicefrac{1}{4} cup soft margarine	
\\ 1 cup brown sugar, packed
\\ 1 egg
\\ \nicefrac{1}{2} cup hot coffee
\\ 1 \nicefrac{1}{2} cups sifted flour	
\\ \nicefrac{1}{4} tsp soda
\\ 1 tsp baking powder	
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{1}{2} tsp cinnamon
\\ \nicefrac{1}{2} cup seedless raisins	
\\ \nicefrac{1}{4} cup chopped nuts
\stepspace ICING:
\\ 1 cup icing sugar	
\\ \nicefrac{1}{2} tsp vanilla or other flavouring	
\\ 1 \nicefrac{1}{2} Tbsp cream or 1 Tbsp coffee}{Cream margarine, brown sugar, and egg. Stir in coffee. Sift together and stir in flour, baking soda, baking powder, salt, and cinnamon. Blend in raisins and nuts. Spread in greased $13 x 9$" pan. Bake at 350${}^\circ$F for 18--20 minutes. Cut into bars. Frost while warm with a thin coating of icing.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GRANOLA BARS (GF)} \index{GRANOLA BARS (GF)} \index{Gluten Free!granola bars}
\step{2 cups GF rolled oats
\\ \nicefrac{3}{4} cup rice bran
\\ 1 cup of nuts, crushed
\\ \nicefrac{3}{4} cup seeds (sunflower, pumpkin, flax, sesame, etc)
\\ \nicefrac{2}{3} cup brown sugar
\\ \nicefrac{1}{2} cup honey
\\ \nicefrac{1}{4} cup butter
\\ 2 tsp vanilla
\\ \nicefrac{1}{2} tsp cinnamon
\\ \nicefrac{1}{2} tsp salt
\\ 1 cup chopped dried fruit}{Preheat oven to 400${}^\circ$F. Line a large rimmed baking sheet with foil. 
Mix together all dry ingredients on the baking sheet. Toast in oven for 10--12 minutes, stirring every few minutes. As soon as the ingredients are toasted, remove the pan from the oven. While the dry ingredients are toasting, line a $9 \times 13$" rimmed pan with waxed paper and spray it lightly with cooking oil. Next, cook brown sugar, honey, butter, cinnamon and salt over med-high heat. Bring mixture to a strong boil for 2 minutes, stirring constantly. Remove from heat and stir in vanilla. Combine toasted ingredients and dried fruit in large bowl. Pour the hot mixture into the bowl and stir aggressively until it is well combined.  Scrape the mixture into the baking sheet, pressing down to evenly spread out the mixture.  Let the bars cool for 2--3 hours until they are hardened. Once hard, remove them from the baking pan and turn out onto a cutting board. Remove the wax paper. Ironing with a heated skillet helps to release the wax paper if it is stubborn. Cut the granola into 26 bars.}

%\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{FLAPJACK COPYCAT} \index{FLAPJACK COPYCAT}
%\name{A soft granola bar}\\
%\step{1 stick of unsalted butter
%\\ \nicefrac{1}{4} cup of honey or golden syrup
%\\ \nicefrac{1}{2} cup brown sugar
%\\ \nicefrac{1}{2} tsp vanilla
%\\ \nicefrac{1}{2} Tbsp cinnamon
%\\ \nicefrac{1}{4} tsp allspice
%\\ \nicefrac{1}{2} tsp salt
%\\ 2\nicefrac{1}{2} cups quick cooking oats
%Dried fruit, coconut, nuts, chia seeds, mini chocolate chips (opt)}{Add the butter, honey, and brown sugar to a sauce pan and stir over medium-low heat until the mixture begins to bubble. Stir slowly for 2--3 minutes and remove from heat. Add vanilla, cinnamon, allspice, and salt. Whisk to combine. In a large bowl, add the oats and any additional items you might want in your bars. Add the caramel mixture to the oats and stir. Lightly spray an $8\times8$" pan with non-stick spray, or line with plastic wrap or parchment paper. Press into pan. Allow the bars to cool completely before slicing.
%Rolled oats can be used instead of quick-cooking oats. Just give them a pulse or two in the food processor or blender first. Oats can be toasted in a preheated 350${}^\circ$F oven for 1-2 minutes. For crispier bars: Press the mixture into an $8\times8$" pan and bake in a preheated 350${}^\circ$F oven for about 10 minutes. I've actually gotten sidetracked and left them in the oven for up to 15 minutes and they were fine. Allow to cool completely before slicing into bars.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{HONEY SPICE FIG BARS} \index{HONEY SPICE FIG BARS}
\name{(Canadian Living)}\\
\step{1 egg	
\\ 1 cup liquid honey
\\ \nicefrac{1}{2} cup unsweetened applesauce	
\\ 1 tsp each grated lemon and orange rind
\\ 1 \nicefrac{3}{4} cups flour	
\\ 1 \nicefrac{1}{2} tsp cinnamon
\\ 1 tsp baking soda	
\\ \nicefrac{1}{2} tsp each ground ginger and allspice
\\ 1 \nicefrac{1}{2} cups finely chopped dried figs	
\\ \nicefrac{1}{2} cup slivered almonds
\stepspace  GLAZE:
\\ \nicefrac{1}{2} cup icing sugar
\\4 tsp lemon juice}{
Whisk egg until frothy; whisk in honey, applesauce and lemon and orange rinds until smooth. In separate bowl, stir together flour, baking soda and spices. Stir into honey mixture. Stir in figs and almonds just until combined; spread in greased $9 \times 13$" cake pan. Bake at 350${}^\circ$F for 22--25 minutes or until cake tester inserted in center comes out clean. Let cool for 15 minutes. Brush glaze over top. Let cool completely. Makes 36 bars.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE AND PECAN SQUARES} \index{CHOCOLATE AND PECAN SQUARES}
\name{(Pearl Klippenstein)}\\
\step{1 \nicefrac{1}{3} cup flour	
\\ 3 Tbsp sugar
\\ \nicefrac{1}{2} cup margarine
\\ 2 cups pecans	
\\ 1 cup chocolate chips
\\ 2 eggs	
\\ \nicefrac{1}{2} cup sugar
\\ \nicefrac{1}{2} cup corn syrup	
\\ 2 Tbsp margarine, melted}{Blend flour, sugar, and margarine together to form crumbs and press into a glass 9" pan. Bake for 15 minutes at 350${}^\circ$F. Let cool. Sprinkle pecans and chocolate chips on base. Mix together eggs, sugar, corn syrup, and margarine, and pour over nuts and chocolate chips. Bake 30 minutes at 350${}^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MATRIMONIAL CAKE (DATE SQUARES)} \index{MATRIMONIAL CAKE (DATE SQUARES)}
\step{1 \nicefrac{3}{4} cups all purpose flour	
\\ 1 tsp baking soda
\\ 1 tsp salt	
\\ 1 cup brown sugar
\\ 2 cups rolled oats	
\\ 1 cup butter
\stepspace FILLING:
\\ \nicefrac{1}{2} lb. dates	
\\ 1 cup water
\\ \nicefrac{1}{2} cup brown sugar	
\\ 1 tsp instant coffee
\\ 1 tsp vanilla
\\ few drops of lemon extract}{Mix all dry ingredients. Work in the butter to resemble coarse crumbs. Pat half this mixture into a $7 \times 12$ pan. spread with date filling and top with remaining crumbs, pat lightly and bake at 375${}^\circ$F until light brown.\par
FILLING: Boil dates, water, sugar, and coffee until thick and smooth. Add vanilla and a few drops of lemon extract.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{GUMDROP SQUARES} \index{GUMDROP SQUARES}
\name{(Loraine Hiebert)}\\
\step{1 cup tiny gumdrops, sliced	
\\ \nicefrac{1}{4} cup flour
\\ 4 eggs	
\\ 1 Tbsp cold water
\\ 2 cups light brown sugar
\\ 1 \nicefrac{3}{4} cup flour	
\\ \nicefrac{1}{4} tsp salt
\\ 1 tsp cinnamon
\\ \nicefrac{1}{2} cup chopped pecan meats
\\ powdered sugar}{Mix gumdrops with flour and set aside. Beat eggs and cold water until light. Beat sugar into eggs gradually. Sift together flour, salt, and cinnamon and add to eggs and sugar. Stir in the gumdrops and pecans. Spread in $10 \times 4$" pan. Bake 30 minutes. at 325${}^\circ$F. Cut in 2" squares. Roll in powdered sugar. Makes 36.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{MARS BARS SQUARES} \index{MARS BARS SQUARES}
\step{4 regular size Mars Bars \\
\nicefrac{1}{2} cup butter \\
3 cups Rice Krispies \\
1 cup chocolate chips \\
Chopped nuts (opt)}{
Melt butter and Mars Bars. Stir in Rice Krispies and nuts. Press into greased $8 \times 8$" pan. Melt chocolate chips and spread over squares.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RHUBARB DREAM BARS} \index{RHUBARB DREAM BARS}
\name{(Yvonne Hiebert)}\\
\step{CRUST:
\\ 2 cups flour
\\ \nicefrac{3}{4} cup icing sugar
\\ 1 cup butter
\stepspace  FILLING:
\\ 4 eggs
\\ 2 cups sugar
\\ \nicefrac{1}{2} cup flour
\\ \nicefrac{1}{2} tsp salt
\\ 4 cups rhubarb, sliced thin}{Press crust into a $10 \times 15$" cookie sheet. Bake 15 minutes at 350${}^\circ$F. Beat filling ingredients together. Fold in rhubarb. Spread over crust. Bake 40--45 minutes.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{ALMOND APRICOT SQUARES} \index{ALMOND APRICOT SQUARES}
\name{(Canadian Living)}\\
\step{\nicefrac{3}{4} cup packed dried apricots	
\\ \nicefrac{1}{4} cup butter
\\ 1 cup flour	
\\ \nicefrac{3}{4} cup sugar
\\ 2 Tbsp plain yoghurt	
\\ 2 eggs
\\ pinch salt	
\\ \nicefrac{1}{2} cup slivered almonds}{Combine apricots with enough water to cover. Cover and bring to boil or microwave at high for 1 minutes. Remove from heat. Let stand for 1 minutes. Drain and let cool. Chop finely and set aside. Cut butter into flour until in fine crumbs. Stir in \nicefrac{1}{4} cup sugar and yoghurt until combined. Press into greased $8 \times 8$" square cake pan. Bake at 350${}^\circ$F for about 20 minutes. Meanwhile, beat together eggs, remaining sugar and salt just until combined. Stir in apricots. Pour over base, sprinkle with almonds. Bake at 350${}^\circ$F for about 30 minutes or until set and golden brown. Let cool before cutting into squares.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DANISH APPLE BAR} \index{DANISH APPLE BAR}
\name{(Esther Braun)}\\
\step{2 \nicefrac{1}{2} cups flour
\\ 1 tsp salt
\\ 1 cup shortening	
\\ 1 egg yolk
\\ milk}{Sift together flour and salt. Add shortening. Mix with fork until crumbly. Beat egg yolk lightly and add milk to make \nicefrac{2}{3} cup liquid. Add to flour mixture. Do not work dough too much. Take half the dough and roll out. Put in 15 \nicefrac{1}{2} x 10 \nicefrac{1}{2} inch cookie sheet. Pull dough up to sides of pan. Sprinkle one cup corn flakes (crushed) on dough. Then add apples.
Sprinkle one cup sugar and cinnamon on apples. Roll out remaining half of dough and cover apples. Seal. Do not make slits in dough for steam to escape. Beat one egg white stiff. Brush over top of crust. Bake at 375${}^\circ$F for 1 hour. Cool slightly, then frost lightly with following icing: 1 cup powdered sugar, 1 Tbsp butter and 1 tsp flavouring.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON BARS} \index{LEMON BARS}
\name{(LaDonna Mann)}\\
\step{1 cup flour	
\\ \nicefrac{1}{2} cup butter
\\ \nicefrac{1}{4} cup powdered sugar
\\ 2 eggs (beat until light and fluffy)	
\\ \nicefrac{3}{4} cup sugar
\\ \nicefrac{1}{2} tsp baking powder	
\\ \nicefrac{1}{4} tsp salt
\\ 2 -- 3 Tbsp lemon juice	
\\ 2 Tbsp flour}{Combine flour, butter and powdered sugar. Press into a $9 \times 9$" pan. Bake at 350${}^\circ$ for 20 minutes. Combine eggs, sugar, baking powder, salt, lemon juice, and flour. Pour over hot crust and Bake 25 minutes until crust is light brown.}


\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LEMON DESSERT SQUARES (GF)} \index{LEMON DESSERT SQUARES (GF)} \index{Gluten Free!desserts}
\step{CRUST:\\
\hyperlink{rhubarbmeringuelink}{See Rhubarb Meringue crust}\\
\stepspace FILLING:  
\\ 1 8 oz package cream cheese	
\\1 cup icing sugar
\\ 2 pkgs lemon pie filling
\stepspace TOPPING:  
\\ \nicefrac{1}{2} cups whipping cream	
\\ \nicefrac{1}{4} cup sugar
\\ 1 tsp vanilla
\\ \nicefrac{3}{4} cup toasted almonds}{Make crust as for Rhubarb Meringue crust.  Bake 15 minutes.  Cool before putting filling on top. Whip cream cheese with icing sugar until smooth.  Spread onto cooled base.\par
FILLING: Prepared lemon pie filling according to pkg instructions.  I use slightly less water than called for.\par
TOPPING: Whip cream, sugar and vanilla until stiff.  Spread over lemon filling. Sprinkle toasted almonds over the top. Chill in fridge for a few hours before serving.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{NANAIMO BAR} \index{NANAIMO BAR}
\step{\nicefrac{1}{2} cup butter	
\\ 5 Tbsp sugar
	\\ 5 Tbsp cocoa	
	\\ 2 cups graham wafer crumbs (26 wafers)
	\\ 1 cup coconut	
	\\ 1 egg
	\\ \nicefrac{1}{2} cup chopped walnuts	
	\\ \nicefrac{1}{2} tsp vanilla
	\stepspace ICING:
\\ 4 Tbsp butter	
\\ 2 Tbsp milk
	\\ 2 Tbsp vanilla custard powder	
	\\ 2 cups icing sugar
	\\ 2 squares melted semi-sweet chocolate
	\\ 1 Tbsp butter}{
Place softened butter, sugar, cocoa, vanilla and egg in a bowl set in a pan of boiling water. Stir mixture until butter has melted and is the consistency of custard. Mix wafer crumbs, coconut and nuts together. Add to the cocoa mixture. Pack into ungreased 9 inch square pan and spread with the icing.\par
ICING: Cream butter. Combine milk with custard powder and add to butter. Mix in icing sugar. Spread over chocolate base and allow to harden. Mix melted chocolate squares with 1 Tbsp butter and spread evenly. Refrigerate.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{SQUAMISH BARS} \index{SQUAMISH BARS}
\step{1 cup peanut butter	
\\ \nicefrac{1}{2} cup packed brown sugar
	\\ \nicefrac{1}{2} cup corn syrup	
	\\ 1 cup rice crisp cereal
	\\ 1 cup corn flakes
	\stepspace  FILLING: \\
	2 cups icing sugar	\\
	\nicefrac{1}{4} cup butter, softened \\
	2 Tbsp cream	\\
	1\nicefrac{1}{2} tsp vanilla 
	\stepspace TOPPING: \\
	3 oz (90 g) bittersweet or semisweet chocolate \\
	1 Tbsp butter}{
Heat peanut butter, sugar and syrup in large saucepan, over low heat, until blended. Remove from heat. Add cereals. Press into greased 9" square cake pan. Let cool. Spread filling over base and chill for at least 30 minutes. Melt chocolate and butter over double boiler. Spread over filling. Chill for 20 minutes. Cut into bars. Yield:  36 bars.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PLAUTSE} \index{PLAUTSE}
\name{(Mrs. Harry Fast)\\
This is one of those desserts that shows up at every funeral.} \\
	\step{3 cups flour		
	\\ \nicefrac{3}{4} cup lard
	\\ 3 tsp baking powder	
	\\ 1 beaten egg
	\\ 1 tsp salt
	\stepspace TOPPING:
\\ 3 Tbsp butter	
	\\ 1 \nicefrac{1}{4} cups flour
	\\ \nicefrac{1}{2} tsp baking powder	
	\\ 1 cup sugar	}{
To beaten egg, add enough milk to equal 1 cup. Place dough into cookie sheet. Cover with fruit. If fruit is sour, sprinkle with sugar. \par
TOPPING: Cream ingredients. Drizzle plautse with icing sugar.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CRISP PEANUT SLICES} \index{CRISP PEANUT SLICES}
\name{Less sweet than the Squamish bars. Just as good and easier to make!}\\
\step{3 cups rice crisp cereal
\\ \nicefrac{1}{2} cup peanuts, coarsely chopped
\\ \nicefrac{1}{2} cup packed brown sugar	
\\ \nicefrac{1}{2} cup corn syrup
\\ \nicefrac{1}{4} cup butter	
\\ \nicefrac{2}{3} cup peanut butter
\\ 1 tsp vanilla	
\\ 1 cup semisweet chocolate chips}{Bring sugar, syrup and butter to boil, stirring until smooth. Boil for 1 minute without stirring. Remove from heat. Vigorously beat in \nicefrac{1}{2} cup peanut butter and vanilla. Sir into cereal mixture. Press into greased 8" square pan. Let cool to room temp. Melt chocolate chips with remaining peanut butter; spread over cereal mixture. Refrigerate for 1 hour or until chocolate is set. Cut into bars.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CARAMEL SLICE} \index{CARAMEL SLICE}
\name{(Heather Wiebe)}\\
\step{\nicefrac{1}{2} cup margarine \\
1 \nicefrac{1}{2} cup brown sugar \\
2 egg, beaten \\
1 cup chopped walnuts \\
1 \nicefrac{1}{2} cup flour \\
2 tsp baking powder \\
\nicefrac{1}{2} tsp salt \\
1 cup coconut
\stepspace ICING: \\
\nicefrac{1}{2} cup margarine \\
1 cup brown sugar \\
\nicefrac{1}{4} cup milk \\
2 cups icing sugar}{
Melt butter. Remove from heat. Add sugar and eggs. Stir in rest of ingredients. Scrape into greased $8 \times 8$" pan. Bake at 350${}^{\circ}$F for 20 minutes. Frost when cool. \par
ICING: Combine butter, sugar and milk in saucepan. Bring to a boil and simmer 2 minutes. Set in cold water to cool. Stir in icing sugar. Smooth over bars.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE CARAMEL BARS} \index{CHOCOLATE CARAMEL BARS}
\name{(Heather Wiebe)}\\
\step{1 cup flour \\
\nicefrac{1}{2} cup brown sugar, packed \\
\nicefrac{1}{2} cup butter \\
2 cups pecans, coarsely chopped \\
1 cup coconut \\
300 ml sweetened condensed milk \\
227 g Hershey Caramels (approx. 26) \\
2 Tbsp milk or light cream \\
1 cup semi-sweet chocolate chips}{
Combine flour and brown sugar. Cut in butter until mixture is crumbly. Press firmly into greased $9 \times 13$" pan. Bake at 350${}^{\circ}$F for 12--15 minutes or until light golden. Sprinkle pecans and coconut over crust. Pour sweetened condensed milk evenly on top. Bake 25--30 minutes or until filling is set. Cool in pan for 10 minutes. Heat caramels and cream over low heat, stirring often until smoothly melted. Drizzle over filling. Sprinkle with chocolate chips. Cool completely. Cut into bars.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE MINT SQUARES} \index{CHOCOLATE MINT SQUARES}
\step{1 cup flour	
\\ 1 cup sugar
\\ \nicefrac{1}{2} cup butter softened	
\\ 4 eggs
\\ 1 \nicefrac{1}{2} cups chocolate syrup	
\\ 2 cups powdered sugar
\\ \nicefrac{1}{2} cup butter, softened	
\\ 2 Tbsp cr\`eme de Menthe
\\ 6 Tbsp butter	
\\ 1 cup chocolate chips, semi-sweet}{Grease $9 \times 13$ pan. Mix flour, sugar, butter, eggs and syrup. Beat until smooth. Bake 25-30 minutes. Cool. Spread with mint center: sugar, butter, cr?\`eme de menthe (can substitute 1 Tbsp water, \nicefrac{3}{4} tsp mint extract and 3 drops green food colouring for cr\`eme de menthe) Cover. Refrigerate at least 1 hour. Spread with glaze: heat over low 6 Tbsp butter and 1 cup choc chips. Cool slightly.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{BROWNIES} \index{BROWNIES}
\name{(Lori Cowman)}\\
\step{1 cup melted butter	
\\ \nicefrac{2}{3} cup cocoa powder
	\\ 2 cups sugar	
	\\ 4 eggs
	\\ 1 tsp vanilla	
	\\ 1\nicefrac{3}{4} cups flour}{
Beat together butter and sugar. Add cocoa powder. Add eggs one at a time, beating well after each egg. Add vanilla and flour. Bake in buttered $9\times13$" pan for 25-30 minutes at 350$^\circ$F.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{DELUXE CHOCOLATE MARSHMALLOW BARS} \index{DELUXE CHOCOLATE MARSHMALLOW BARS}
\step{\nicefrac{1}{2} cup margarine
\\ \nicefrac{3}{4} cup sugar
\\ 2 eggs
\\ 1 tsp vanilla
\\ 3 Tbsp cocoa
\\ \nicefrac{1}{4} tsp baking powder
\\ \nicefrac{1}{4} tsp salt
\\ \nicefrac{3}{4} cup flour
\\ 6 oz chocolate chips
\\ 1 cup peanut butter
\\ 1 \nicefrac{1}{2} cups Rice Krispies
\\ \nicefrac{1}{2} bag marshmallows}{Cream butter and sugar. Beat in eggs and vanilla. Add cocoa, baking powder, flour and salt. Spread in a $9 \times 13$" pan. Bake 15--20 minutes at 350${}^\circ$F. sprinkle marshmallow evenly over top. Bake 3 minutes. cool. Melt chocolate chips and peanut butter. Add Rice Krispies. Spread on top of cooked bars. Quick option: Bake a fudge brownie mix ($9\times13$") instead of baking the first 8 ingredients.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{LUNCH LADY BROWNIES (GF)} \index{LUNCH LADY BROWNIES (GF)} \index{Gluten Free!brownies}
\name{(Faithfully Gluten Free)}\\
\step{1 cup unsalted butter, melted \\
\nicefrac{1}{2} cup cocoa powder \\
2 cups sugar \\
\nicefrac{2}{3} cup brown rice flour \\
\nicefrac{2}{3} cup sorghum flour \\
\nicefrac{2}{3} cup tapioca starch \\
1 tsp xanthan gum \\
4 large eggs \\
1 Tbsp vanilla extract
\stepspace ICING: \\
\nicefrac{1}{4} cup cocoa powder \\
\nicefrac{1}{4} cup unsalted butter, softened \\
\nicefrac{1}{4} cup milk \\
\nicefrac{1}{4} tsp salt \\
3 cups icing sugar}{
Combine butter and cocoa powder. In a separate bowl whisk together dry ingredients. Stir sugar/flour mixture into butter mixture. Add eggs and vanilla. Mix just until combined. Scrape batter into greased $9 \times 13$" pan. Bake at 350${}^{\circ}$F for 20--25 minutes. Remove from oven and allow to cool for 10 minutes before frosting. \par
ICING: Beat all ingredients together. Spread evenly on still warm cake. Let cool before cutting.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PUFFED WHEAT CANDY SQUARES} \index{PUFFED WHEAT CANDY SQUARES}
\step{\nicefrac{1}{3} cup butter	
\\ 2 Tbsp cocoa
	\\ \nicefrac{1}{2} cup syrup	
	\\ 1 tsp vanilla
	\\ 1 cup brown sugar	
	\\ 8 cups puffed wheat}{
Melt butter in saucepan. Add syrup, sugar, cocoa and vanilla. Bring to boil and pour over puffed wheat. Press into $9\times 13$" pan.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{PEANUT BUTTER MARSHMALLOW SQUARES} \index{PEANUT BUTTER MARSHMALLOW SQUARES}
\step{\nicefrac{1}{4} cup margarine, melted	
\\ 1 cup peanut butter
	\\ 1 pkg chocolate chips (1 \nicefrac{1}{4} cups)	
	\\ 1 pkg butterscotch chips (1 \nicefrac{1}{4} cups)
	\\ 1 pkg marshmallows (miniature)}{
Melt margarine, peanut butter, and chips in microwave until chocolate chips are barely melted. Add marshmallow and press into $9\times 13$" pan.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{RICE KRISPIE MARSHMALLOW SQUARES} \index{RICE KRISPIE MARSHMALLOW SQUARES}
\step{\nicefrac{1}{4} cup butter	
\\ 7 cups Rice Krispies
\\ 40 marshmallows	
\\ \nicefrac{1}{2} tsp vanilla}{Melt butter and marshmallow in double boiler. Add vanilla. Beat thoroughly to blend. Put Rice Krispies in large buttered bowl and pour marshmallow mixture over, stirring briskly. Press into shallow pan.}

\end{minipage}\par\begin{minipage}{\linewidth}\rtitle{CHOCOLATE MARSHMALLOW ROLL} \index{CHOCOLATE MARSHMALLOW ROLL}
\step{4 squares chocolate	
\\ 1 tsp vanilla
\\ 2 Tbsp butter	
\\ 2 \nicefrac{1}{2} cups miniature marshmallows
\\ 1 cup icing sugar	
\\ 1 cup cherries
\\ 1 cup walnuts	
\\ 1 egg, well beaten}{Melt chocolate and butter together. Stir in sugar and egg. Pour over other ingredients. Sprinkle coconut on waxed paper and roll mixture in it. Refrigerate.}
\end{minipage}